```{r}
# Load necessary libraries
library(tidyverse)
library(ggpubr)
library(here)

# set function directory paths
fxn_path <- here("src")

# Source functions
invisible(map(
  list.files(fxn_path, pattern = "*.R", full.names = TRUE),
  ~ source(.x, echo = FALSE)
))

# load all the flagged data, pre verification
flagged_data <- read_rds(here("data","virridy_verification","all_data_flagged_complete.RDS"))
```

```{r}
# Make list of parameter specifications for joining
unique_parameters <- names(flagged_data) %>% 
  str_extract(pattern = "(?<=-).*") %>% 
  unique(.)

parameter_specifications <- tibble(
  parameter = unique_parameters,
  accuracy = list(
    NA,
    NA,
    0.1,
    NA,
    5,
    0.1,
    c(0.5, 1, 2), # these are percentages
    0.1,
    2 # Percentage
  ),
  range = list(
    NA,
    NA,
    c(0,20),
    NA,
    c(-1400,1400),
    c(0,14),
    list(c(0,100000), c(100000,200000), c(200000,350000)), # related ranges for percentages
    c(-5,50), # in C
    list(c(0,1000), c(1000,4000))
  ),
  precision = list(
    NA,
    NA,
    0.01,
    NA,
    0.1,
    0.01,
    0.1,
    0.01,
    c(0.01,0.1)
  )
)
```

## Note on percent change vs percent difference:
Percent change: 100*(new_value - old_value)/old_value
  Used when tracking changes over time
  Shows the direction of change
  Uses the old value as a reference
  Asymmetric
  
Percent difference: 100*(abs(new_value - old_value)/mean(new_value,old_value))
  Used when you want to compare the relative difference between two independent values
  Does not show the direction of change
  uses the mean of both values as a reference
  Symmetric
```{r}
flagged_data_altered <- map(flagged_data, function(df) {
  
  altered_df <- df %>% 
    # select for the most relevant columns
    select(DT_join, DT_round, site, parameter, mean, flag) %>% 
    mutate(
      # calculate difference
      difference = mean - lag(mean),
      # calculate percent change
      percent_change = if_else(
        mean != 0 & lag(mean) != 0, # prevent divide by 0 errors
        ((mean-lag(mean))/lag(mean))*100,
        NA_integer_),
      # calculate percent difference
      percent_difference = if_else(
        mean != 0 & lag(mean) != 0, # prevent divide by 0 errors
        (abs(mean-lag(mean))/((mean+lag(mean))/2))*100,
        NA_integer_),
      # center and scale the data for easy comparisons across sites
      percent_change_standardized = (percent_change - mean(percent_change, na.rm = T))/sd(percent_change, na.rm = T),
      percent_difference_standardized = (percent_difference - mean(percent_difference, na.rm = T))/sd(percent_difference, na.rm = T)
    ) %>% 
    left_join(parameter_specifications, by = "parameter")
    
  return(altered_df)
})
```

```{r}
flags <- paste0(c("site visit", "sv window"), collapse = "|")

site_visit_data <- map(flagged_data_altered, function(df) {
  altered_df <- df %>% 
    filter((lag(grepl(flags, flag)) | lead(grepl(flags, flag))) &
             !grepl(flags, flag))
})
```

# Histograms
extremely skewed data is hard to visualize
```{r}
# sensitivity for Turbidity

# sensitivity for Chl-a

# sensitivity for FDOM

# extremely skewed data
```
