---
title: "Comparing data between Timberline and Prospect sites"
author: "ROSSyndicate"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE, evaluate = FALSE)
```

# Goal
 
 The Timberline and Prospect sites bracket Spring Creek as it flows into the Cache la Poudre River. From a visual perspective, the datasets are nearly the same other than biofilm build up at Prospect which causes turbidity to drift in the late summer. 
 This analysis will compare the two datasets and determine if there is a statistical difference between the two sites. 
 
 
```{r setup}
source("src/package_loader.R")
lapply(c("data.table", "arrow", "tidyverse", "rvest", "readxl", "lubridate", "zoo", "padr","plotly", "feather", "RcppRoll"), package_loader)


library(forecast)
library(lmtest)
library(fUnitRoots)
library(TSA)
library(dplyr)

```


```{r load_datasets}
prospect <- read_csv_arrow(file = "data/api/Prospect_2023-08-07.csv")%>%
  filter(!grepl("vulink", name, ignore.case = TRUE))%>%
  pivot_wider(id_cols = c("site", "id", "name", "timestamp"),names_from = parameter, values_from = value)%>%
  select(-c(Baro, 'Battery Level'))

timberline <- read_csv_arrow(file = "data/api/Timberline_2023-08-07.csv")%>%
  filter(!grepl("vulink", name, ignore.case = TRUE))%>%
  pivot_wider(id_cols = c("site", "id", "name", "timestamp"),names_from = parameter, values_from = value)

archery <- read_csv_arrow(file = "data/api/Archery_2023-08-07.csv")%>%
  filter(!grepl("vulink", name, ignore.case = TRUE))%>%
  pivot_wider(id_cols = c("site", "id", "name", "timestamp"),names_from = parameter, values_from = value)

lincoln <- read_csv_arrow(file = "data/api/lincoln_2023-08-07.csv")%>%
  filter(!grepl("vulink", name, ignore.case = TRUE))%>%
  pivot_wider(id_cols = c("site", "id", "name", "timestamp"),names_from = parameter, values_from = value)%>%
  select(-c(Baro, 'Battery Level'))
  #select(-c(Baro, 'Battery Level'))
pros_timb <- rbind(prospect, timberline)

```

```{r stats}

# Assuming ts1 and ts2 are your time series data for parameter 1
make_comparison <- function(parameter, site1, site2){
  
  site1_name <- site1$name[1]
  site2_name <- site2$name[1]
  
  ts1 <- site1%>%
    select(timestamp, param_site1 = parameter)
  ts2 <- site2%>%
    select(timestamp, param_site2 = parameter)
  ts_comb <- ts1%>%
    left_join(ts2, by = "timestamp")%>%
    na.omit()
  
  model <- lm(param_site1 ~ param_site2, data = ts_comb)
  
  # Perform Breusch-Pagan test for homoscedasticity
bptest(model)


# Get residuals from the model
residuals <- residuals(model)

# Create a data frame
data <- data.frame(TS2 = ts_comb$param_site2, Residuals = residuals)
  
param_range <- range(min(ts_comb$param_site1, ts_comb$param_site2),max(ts_comb$param_site1, ts_comb$param_site2))

ggplot(ts_comb, aes(x = param_site1, y = param_site2)) +
  geom_point() +
   geom_smooth(method = "lm", se = FALSE, color = "blue") + 
   geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red") +
  labs(
    title = parameter,
    x = site1_name,
    y = site2_name
  )+
  coord_fixed(ratio = 1)+
  xlim(param_range)+
  ylim(param_range)+
  theme_bw()
}
```

Making comparisons 
```{r making_comps}
timb_linc <- make_comparison("Temperature", site1 = timberline, site2 = lincoln)
timb_pros <- make_comparison("Temperature", site1 = timberline, site2 = prospect)
timb_arch <- make_comparison("Temperature", site1 = timberline, site2 = archery)

timb_comp <- ggpubr::ggarrange(timb_linc, timb_pros, timb_arch, nrow = 1)
ggsave("images/timberline_temp_comparison.png",plot = timb_comp, dpi = 300)
```

