---
title: "Tidying Sensor Data"
author: "Katie Willi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

library(lubridate)

library(rvest)

library(dygraphs)

library(labelled)

library(zoo)

library(anomalize)
```

Functions that you need!

```{r}
try(plyr::ldply(list.files(path="src/",
                           pattern="*.R",
                           full.names=TRUE),
                source))
```

Listed accuracy and range for sensors:

Temperature: ±0.1 Celsius, -5 to 50 C

Barometric Pressure: ±1.0 mbars, 300 to 1,100 mbars

pH: ±0.1 pH, 0 to 14 pH

ORP: ±5 mV

Conductivity: ±0.5% of reading plus 1 μS/ cm from 0 to 100,000 μS/cm; ±1.0% of reading from 100,000 to 200,000 μS/cm; ±2.0% of reading from 200,000 to 350,000 μS/cm

TDS/Salinity: range of 0 to 350 ppt/0 to 350 PSU

RDO: ±0.1 mg/L or ±2% of reading (whichever is greater)

Turbidity: ±2% of reading or ±0.5 NTU (whichever is greater)

TSS: range of 1 to 1,500 mg/L

Pressure: ±0.1% FS from -5 to 50°C

Chlorophyll-a: range of 0-100 RFU or 1-1,000 μg/L

#### Pulling in previous years' data

```{r}
pre_2022 <- read_csv('data/pretty/all_sensor_data_pre2022.csv') %>%
  mutate(site = case_when(sensor == "Rist" ~ "rist",
                          sensor == "Legacy" ~ "legacy",
                          sensor == "Timberline" ~ "timberline",
                          sensor == "Prospect" ~ "prospect",
                          sensor == "ELC" ~ "elc",
                          sensor == "Archery" ~ "archery"
  )) %>%
  rename(pH1=pH,
         comment_pre = comments) %>%
  select(-c(sensor,year, date, data))
```

#### Pulling up field notes

This is the first year that there are consistent field notes. 

```{r}
field_notes <- readxl::read_excel('data/sensor_field_notes.xlsx') %>%
  mutate(DT = (paste0(date, " ", start_time_mst))) %>%
  mutate(DT = ymd_hm(DT)) %>%
  arrange(DT) %>%
  mutate(DT = round_date(DT, "15 minutes"))
```

#### Downloading calibration reports. 

These are a bit tricky to automate nicely because the calibration table structure is different depending on what sensors are on the sonde, and what ports they're in...

```{r}
cal_files <- list.files("data/calibration_reports", pattern=".html")

cal_table <- vector("list", length = length(cal_files)) 

for(i in 1:length(cal_table)){
  
  cal <- rvest::read_html(paste0("data/calibration_reports/", cal_files[i])) %>%
    rvest::html_nodes('div') %>%
    rvest::html_text() %>%
    as_tibble()
  
  rdo <- cal %>% filter(grepl("RDO", value)) %>% pull() %>% str_replace_all(., " ", "")
  
  ph_orp <- cal %>% filter(grepl("pH/ORP", value)) %>% pull() %>% str_replace_all(., " ", "")
  
  conductivity <- cal %>% filter(grepl("Conductivity",value)) %>% pull() %>% str_replace_all(., " ", "")
  
  turbidity <- cal %>% filter(grepl("Turbidity",value)) %>% pull() %>% str_replace_all(., " ", "")
  
  time_mst <- paste0(str_sub(cal_files[i], -13, -12),":", str_sub(cal_files[i], -11, -10))
  
  date <- paste0(str_sub(cal_files[i], -22, -19),"-", str_sub(cal_files[i], -18, -17),"-", str_sub(cal_files[i], -16, -15))
  
  cal_table[[i]] <- tibble(site = sub("\\_.*", "", cal_files[i]),
                           
                           DT = ymd_hm(paste0(date, " ", time_mst)),
                           
                           #Dissolved Oxygen
                           rdo_slope = str_match(rdo, "Slope\\s*(.*?)\\s*Offset")[,2],
                           rdo_offset = str_match(rdo, "Offset\\s*(.*?)\\s*mg/L")[,2],
                           rdo_100 = str_match(rdo, "PreMeasurement\\s*(.*?)\\s*%SatPost")[,2],
                           rdo_conc = str_match(rdo, "Concentration\\s*(.*?)\\s*mg/LPreMeasurement")[,2],
                           rdo_temp = str_match(rdo, "Temperature\\s*(.*?)\\s*°C")[,2],
                           rdo_pressure = str_match(rdo, "Pressure\\s*(.*?)\\s*mbar")[,2],
                           
                           #pH
                           ph_slope_pre = str_match(ph_orp, "Offset1Slope\\s*(.*?)\\s*mV/pH")[,2],
                           ph_offset_pre = str_match(ph_orp, "mV/pHOffset\\s*(.*?)\\s*mVSlopeandOffset2")[,2],
                           ph_slope_post = str_match(ph_orp, "Offset2Slope\\s*(.*?)\\s*mV/pH")[,2],
                           ph_offset_post = str_match(ph_orp, paste0(ph_slope_post,"mV/pHOffset\\s*(.*?)\\s*mVORPORP"))[,2],
                           ph_7_nice = str_sub(str_match(ph_orp, "PostMeasurementpH7\\s*(.*?)\\s*mVCal")[,2], 10, nchar(str_match(ph_orp, "PostMeasurementpH7\\s*(.*?)\\s*mVCal")[,2])),
                           ph_7_other = str_sub(str_match(ph_orp, "PostMeasurementpH6\\s*(.*?)\\s*mVCal")[,2], 10, nchar(str_match(ph_orp, "PostMeasurementpH6\\s*(.*?)\\s*mVCal")[,2])),
                           ph_7 = ifelse(is.na(ph_7_nice), ph_7_other, ph_7_nice),
                           
                           #ORP
                           orp_offset = ifelse(is.na(str_match(ph_orp, "Zobell'sOffset\\s*(.*?)\\s*mVTemperature")[,2]),
                                               str_match(ph_orp, "ZoBell'sOffset\\s*(.*?)\\s*mVTemperature")[,2],
                                               str_match(ph_orp, "Zobell'sOffset\\s*(.*?)\\s*mVTemperature")[,2]),
                           
                           #Conductivity
                           tds_conversion_ppm = str_sub(str_match(conductivity, "TDSConversionFactor\\s*(.*?)\\s*CellConstant")[,2], 6, nchar(str_match(conductivity, "TDSConversionFactor\\s*(.*?)\\s*CellConstant")[,2])),
                           cond_cell_constant = str_match(conductivity, "CellConstant\\s*(.*?)\\s*ReferenceTemperature")[,2],
                           cond_pre = str_match(conductivity,paste0(str_match(conductivity,
                                                                              "PreMeasurementActual\\s*(.*?)\\s*SpecificConductivity")[,2],"SpecificConductivity\\s*(.*?)\\s*µS/cmPost"))[,2],
                           cond_post = str_match(conductivity,paste0(str_match(conductivity,
                                                                               "PostMeasurementActual\\s*(.*?)\\s*SpecificConductivity")[,2],"SpecificConductivity\\s*(.*?)\\s*µS/cm"))[,2],
                           
                           #Turbidity
                           ntu_slope = str_match(turbidity, "Slope\\s*(.*?)\\s*Offset")[,2],
                           ntu_offset = str_match(turbidity, "Offset\\s*(.*?)\\s*NTU")[,2],
                           ntu_10 = str_match(turbidity, "CalibrationPoint1PreMeasurement\\s*(.*?)\\s*NTUPost")[,2],
                           ntu_100 = str_match(turbidity, "CalibrationPoint2PreMeasurement\\s*(.*?)\\s*NTUPost")[,2],
                           
                           #Factory Defaults
                           factory_defaults = paste0(ifelse(is.na(ntu_slope), "Turbidity ", ""),
                                                     ifelse(is.na(rdo_slope), "RDO ", ""),
                                                     ifelse(is.na(ph_slope_post), "pH ", ""),
                                                     ifelse(is.na(orp_offset), "ORP ", ""),
                                                     ifelse(is.na(cond_post), "Conductivity ", ""))) %>%
    select(-c(ph_7_nice, ph_7_other))
}

cal_table <- bind_rows(cal_table) %>%
  distinct(.keep_all = TRUE) %>%
  group_by(site) %>%
  mutate(DT = round_date(DT, "15 minutes")) %>%
  padr::pad(by='DT', group = 'site')

rm(cal, cal_files, conductivity, date, i, ph_orp, rdo, time_mst, turbidity)
```


#### Downloading sonde data

#### Downloading relevant outside datasets

```{r}
# usgs_lincoln <- dataRetrieval::readNWISuv("06752260", parameterCd = "00065", startDate = "2019-09-01", endDate = "2022-12-01") %>%
#   mutate(DT=ymd_hms(dateTime))%>%
#   rename(Depth_ft = X_00065_00000) %>%
#   select(DT, 
#          Depth_ft) %>%
#   mutate(site = "usgs_lincoln")
```


# Rist

```{r}
# Full Dataset:
rawless_rist <- going_rawless(site_name = "rist", trolled = NA) %>%
  mutate(DT = ymd_hms(DT)) %>%
  # Dataset got swapped to Rist's sensor, so need to remove data that 
  # is actually Rist. Sensor also capped from 5/6/2022 - 5/9/2022 (flow too low)
  filter(ymd_hms(DT) <= ymd_hms("2022-05-30 09:00:00")) %>%
  filter(!(ymd_hms(DT) >= ymd_hms('2022-05-06 12:00:00') & ymd_hms(DT) <= ymd_hms('2022-05-09 14:30:00'))) %>%
  padr::pad(by = 'DT') %>%
  # Link up calibration data:
  full_join(na.locf(na.locf(filter(cal_table, site == "rist")), fromLast = TRUE), 
            by = c('site','DT'))
```


## Temperature

Specs for temperature: ±0.1 Celsius, -5 to 50 C

```{r}
rist_temp <- first_pass(what = rawless_rist, parama = "Water_Temp_C", min = -5, max = 50) %>%
  mutate(site="rist") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/rist_temp.feather')

# What's it look like?
# dygraph(xts::xts(select(rist_temp, c(DT, p1, sd3)), order.by = ymd_hms(rist_temp$DT)),
#         main="Water Temperature Timeseries (UTC)") %>% 
#   dyRangeSelector()

```


## Depth

```{r}
rist_depth <- dplyr::select(rawless_rist, c(DT, Depth_ft)) %>%
  first_pass(., parama ="Depth_ft", max=7, min=0) %>%
  mutate(site = 'rist') %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/rist_depth.feather')

# dygraph(xts::xts(select(rist_depth, p1, DT, sd3), order.by = ymd_hms(rist_depth$DT)), 
#         main="Depth Timeseries (UTC)") %>% 
#   dyRangeSelector()
```


## Conductivity

Conductivity: ±0.5% of reading plus 1 μS/ cm from 0 to 100,000 μS/cm; ±1.0% of reading from 100,000 to 200,000 μS/cm; ±2.0% of reading from 200,000 to 350,000 μS/cm

```{r}
rist_conductivity <-  first_pass(what = rawless_rist, parama = "Specific_Conductivity_µS_cm", min = 40, max = 10000) %>%
  mutate(site = "rist") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/rist_conductivity.feather')

# dygraph(xts::xts(select(rist_conductivity, p1, sd3, DT), order.by = ymd_hms(rist_conductivity$DT)),
#         main="SpC Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## DO

RDO: ±0.1 mg/L or ±2% of reading (whichever is greater)

```{r}
rist_do <- first_pass(what = rawless_rist, parama = "DO_ppm", min = 0, max = 25) %>%
  mutate(site = "rist") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/rist_do.feather')

# dygraph(xts::xts(select(rist_do, p1, DT, sd3), order.by = ymd_hms(rist_do$DT)), 
#         main="DO Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## pH

```{r}
rist_ph <- first_pass(what = rawless_rist, parama = "pH1", min = 0, max = 14) %>%
  mutate(site = "rist") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/rist_ph.feather')

# dygraph(xts::xts(select(rist_ph, p1, DT, sd3), order.by = ymd_hms(rist_ph$DT)), 
#         main="pH Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


# Legacy

So far in 2022, all data has been sent to HydroVu outside of genomic sampling on 2022-09-19. This location encountered several issues this field season: sensor pulled 2022-05-24 due to fears that its infrastructure would wash away. Sensor was re-deployed 2022-06-01, but was then pulled out due to tech issues 2022-07-08 and turbidity problems. Sometime between then and 2022-07-12, turbidity sensor totally broke. 2022-07-16, the turbidity sensor was replaced with the one that was previously being used at Archery. Between 2022-07-18 and 2022-07-21, the back-up sensor stopped working. After this we we swapped the sonde with sensor from Rist 2022-08-03. On 2022-08-04, the sensor was pulled because flows were too low (sensor was likely not suspended in the water 8/3 - 8/4). Redeployed on 2022-08-25, though issues with turbidity and ORP occurred from then until

```{r}
# No VuLink connection during final genomic survey (water was too low for full deployment)
raw_troll_legacy <- map_dfr(grep(list.files("data/sensor_data/2022/legacy/manual/", full.names = T), pattern = "trolled", invert = F, value = T), troll_reader)
names(raw_troll_legacy) <- make.names(names(raw_troll_legacy), unique = T)

rawless_troll_legacy <- raw_troll_legacy %>% 
  select(DT = contains('Date.Time'),
         Water_Temp_C = as.numeric(contains('Temperature...C')),
         pH = contains('pH'),
         ORP_mV = contains('ORP'),
         Specific_Conductivity_µS_cm = contains('Specific.Conductivity..µS.cm.'),
         DO_ppm = contains('RDO.concentration'),
         Turbidity_NTU = contains('Turbidity'),
         Depth_ft = contains('Depth..ft')) %>%
  mutate(DT = ymd_hms(DT)) %>%
  mutate(DT = DT - lubridate::hours(1)) %>% # reported in MDT >:(
  mutate(DT = as.character(round_date(ymd_hms(DT), "15 minutes"))) %>%
  mutate(DT = ymd_hms(DT)) %>%
  mutate_at(vars(2:ncol(.)), as.numeric)

# Full Dataset:
rawless_legacy <- going_rawless(site_name = "legacy", trolled = rawless_troll_legacy) %>%
  # Remove data ranges where sensor was pulled out of field (THAT I KNOW OF, IE 2022 ONLY)
  dplyr::filter(!(ymd_hms(DT) >= ymd_hms('2021-12-04 19:30:00') & ymd_hms(DT) < ymd_hms('2022-04-06 17:30:00')),
                !(ymd_hms(DT) >= ymd_hms('2022-05-24 09:30:00') & ymd_hms(DT) < ymd_hms('2022-06-01 13:30:00')),
                !(ymd_hms(DT) > ymd_hms('2022-07-08 14:00:00') & ymd_hms(DT) <= ymd_hms('2022-07-12 10:00:00')),
                !(ymd_hms(DT) >= ymd_hms('2022-08-04 09:50:00') & ymd_hms(DT) <= ymd_hms('2022-08-25 16:15:00')),
                !(ymd_hms(DT) > ymd_hms('2022-09-07 06:57:00') & ymd_hms(DT) <= ymd_hms('2022-09-18 07:00:00'))) %>%
  mutate(DT = ymd_hms(DT)) %>%
  padr::pad(by = 'DT') %>%
  # Link up calibration data:
  full_join(na.locf(na.locf(filter(cal_table, site == "legacy")), fromLast = TRUE), 
            by = c('site','DT'))
rm(raw_troll_legacy,rawless_troll_legacy)
```


## Temperature

Specs for temperature: ±0.1 Celsius, -5 to 50 C

```{r}
legacy_temp <- first_pass(what = rawless_legacy, parama = "Water_Temp_C", min = -5, max = 50) %>%
  mutate(site="legacy") %>%
  feather::write_feather('data/sensor_data/p1_backup/legacy_temp.feather')

# What's it look like?
# dygraph(xts::xts(select(legacy_temp, c(DT, p1, sd3)), order.by = ymd_hms(legacy_temp$DT)),
#         main="Water Temperature Timeseries (UTC)") %>% 
#   dyRangeSelector()
```


## Depth

We had a couple issues with "level" calibration. Here, I am "back-calibrating" for them to match previous and/or post level when they were correct. Assumes (though subjectively verified in field) that river depth did not change during the field visit. I want to spruce this code up - it is definitely the not-so-savvy fix for now. When time permits I plan to explore using level calibrations from the cal report for more refinement!

```{r}
legacy_depth <- dplyr::select(rawless_legacy, c(DT, Depth_ft)) %>%
  filter(year(DT)>2021) %>%
  mutate(Depth_ft_p1 = ifelse(DT >= ymd_hms('2022-04-06 06:00:00') & DT < ymd_hms('2022-04-12 09:30:00'), 
                              Depth_ft + 
                                abs(
                                  filter(dplyr::select(rawless_legacy, c(DT, Depth_ft)), DT == ymd_hms('2022-04-12 09:15:00'))$Depth_ft - 
                                    filter(dplyr::select(rawless_legacy, c(DT, Depth_ft)), DT == ymd_hms('2022-04-12 09:30:00'))$Depth_ft
                                ), 
                              Depth_ft))
legacy_depth <- legacy_depth %>%
  mutate(Depth_ft_p2 = ifelse(DT >= ymd_hms('2022-07-22 11:30:00') & DT <= ymd_hms('2022-07-25 14:15:00'), 
                              Depth_ft_p1 + 
                                abs(
                                  filter(legacy_depth, DT == ymd_hms('2022-07-22 11:15:00'))$Depth_ft_p1 -
                                    filter(legacy_depth, DT == ymd_hms('2022-07-22 11:30:00'))$Depth_ft_p1
                                ), 
                              Depth_ft_p1)) %>%
  first_pass(., parama ="Depth_ft_p2", max=7, min=0) %>%
  mutate(site = 'legacy') %>%
  feather::write_feather('data/sensor_data/p1_backup/legacy_depth.feather')

# dygraph(xts::xts(select(legacy_depth, p1, DT, sd3), order.by = ymd_hms(legacy_depth$DT)), 
#         main="Depth Timeseries (UTC)") %>% 
#   dyRangeSelector()
```


## Conductivity

Conductivity: ±0.5% of reading plus 1 μS/ cm from 0 to 100,000 μS/cm; ±1.0% of reading from 100,000 to 200,000 μS/cm; ±2.0% of reading from 200,000 to 350,000 μS/cm

```{r}
legacy_conductivity <-  first_pass(what = rawless_legacy, parama = "Specific_Conductivity_µS_cm", min = 40, max = 10000) %>%
  mutate(site = "legacy") %>%
  feather::write_feather('data/sensor_data/p1_backup/legacy_conductivity.feather')

# dygraph(xts::xts(select(legacy_conductivity, p1, sd3, DT), order.by = ymd_hms(legacy_conductivity$DT)),
#         main="SpC Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## DO

RDO: ±0.1 mg/L or ±2% of reading (whichever is greater)

```{r}
legacy_do <- first_pass(what = rawless_legacy, parama = "DO_ppm", min = 0, max = 25) %>%
  mutate(site = "legacy") %>%
  feather::write_feather('data/sensor_data/p1_backup/legacy_do.feather')

# dygraph(xts::xts(select(legacy_do, p1, DT, sd3), order.by = ymd_hms(legacy_do$DT)), 
#         main="DO Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## pH

```{r}
legacy_ph <- first_pass(what = rawless_legacy, parama = "pH1", min = 0, max = 14) %>%
  mutate(site = "legacy") %>%
  feather::write_feather('data/sensor_data/p1_backup/legacy_ph.feather')

# dygraph(xts::xts(select(legacy_ph, p1, DT, sd3), order.by = ymd_hms(legacy_ph$DT)), 
#         main="pH Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```

# Lincoln

```{r}
# Full Dataset:
raw <- readxl::read_excel('data/sensor_data/2022/lincoln/lincoln.xlsx')

names(raw) <- make.names(names(raw), unique = T)

rawless_lincoln <- raw %>%
  select(DT = contains('Date.Time'),
         Water_Temp_C = as.numeric(contains('Temperature')),
         pH = contains('pH'),
         ORP_mV = contains('ORP'),
         Specific_Conductivity_µS_cm = contains('Specific.Conductivity..µS.cm.'),
         DO_ppm = contains('RDO.Conc'),
         Turbidity_NTU = contains('Turbidity'),
         Depth_ft = contains('Depth')) %>%
  mutate(DT = ymd_hms(DT)) %>%
  mutate(DT = DT - lubridate::hours(1)) %>%
  mutate_at(vars(2:ncol(.)), as.numeric) %>%
  mutate(site = 'lincoln') %>%
  arrange(ymd_hms(DT)) %>%
  mutate(DT = as.character(round_date(ymd_hms(DT), "15 minutes"))) %>%
  mutate(DT = ymd_hms(DT)) %>%
  # Link up field notes:
  full_join(filter(field_notes, site == 'lincoln'), by = c('DT','site')) %>%
  mutate(date = as_date((DT)),
         hour = hour(DT),
         year = year(DT),
         month = month(DT)) %>%
  arrange(ymd_hms(DT)) %>%
  mutate(DT = ymd_hms(DT)) %>%
  padr::pad(by = 'DT') 
```

## Temperature

Specs for temperature: ±0.1 Celsius, -5 to 50 C

```{r}
lincoln_temp <- first_pass(what = rawless_lincoln, parama = "Water_Temp_C", min = 0, max = 50) %>%
  mutate(site="lincoln") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/lincoln_temp.feather')

# What's it look like?
# dygraph(xts::xts(select(lincoln_temp, c(DT, p1, sd3)), order.by = ymd_hms(lincoln_temp$DT)),
#         main="Water Temperature Timeseries (UTC)") %>% 
#   dyRangeSelector()

```


## Depth

```{r}
lincoln_depth <- dplyr::select(rawless_lincoln, c(DT, Depth_ft)) %>%
  first_pass(., parama ="Depth_ft", max=7, min=0) %>%
  mutate(site = 'lincoln') %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/lincoln_depth.feather')

# dygraph(xts::xts(select(lincoln_depth, p1, DT, sd3), order.by = ymd_hms(lincoln_depth$DT)), 
#         main="Depth Timeseries (UTC)") %>% 
#   dyRangeSelector()
```


## Conductivity

Conductivity: ±0.5% of reading plus 1 μS/ cm from 0 to 100,000 μS/cm; ±1.0% of reading from 100,000 to 200,000 μS/cm; ±2.0% of reading from 200,000 to 350,000 μS/cm

```{r}
lincoln_conductivity <-  first_pass(what = rawless_lincoln, parama = "Specific_Conductivity_µS_cm", min = 40, max = 10000) %>%
  mutate(site = "lincoln") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/lincoln_conductivity.feather')

# dygraph(xts::xts(select(lincoln_conductivity, p1, sd3, DT), order.by = ymd_hms(lincoln_conductivity$DT)),
#         main="SpC Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## DO

RDO: ±0.1 mg/L or ±2% of reading (whichever is greater)

```{r}
lincoln_do <- first_pass(what = rawless_lincoln, parama = "DO_ppm", min = 0, max = 25) %>%
  mutate(site = "lincoln") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/lincoln_do.feather')

# dygraph(xts::xts(select(lincoln_do, p1, DT, sd3), order.by = ymd_hms(lincoln_do$DT)), 
#         main="DO Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## pH

```{r}
lincoln_ph <- first_pass(what = rawless_lincoln, parama = "pH1", min = 0, max = 14) %>%
  mutate(site = "lincoln") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/lincoln_ph.feather')

# dygraph(xts::xts(select(lincoln_ph, p1, sd3, DT), order.by = ymd_hms(lincoln_ph$DT)), 
#         main="pH Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


# Timberline

```{r}
rawless_timberline <- going_rawless(site_name="timberline",trolled=NA) %>%
  # remove data ranges where sensor was pulled out of field.
  dplyr::filter(!(ymd_hms(DT) > ymd_hms('2021-01-01 08:15:00') & ymd_hms(DT) <= ymd_hms('2022-04-06 08:15:00'))) %>%
  mutate(DT = ymd_hms(DT)) %>%
  padr::pad(by = 'DT') %>%
  # Link up calibration data:
  full_join(na.locf(na.locf(filter(cal_table, site == "timberline")), fromLast = TRUE),
            by = c('site','DT'))
```


## Depth

We had a couple issues with "level" calibration. Here, I am "back-calibrating" for them to match previous and/or post level when they were correct. Assumes (though subjectively verified in field) that river depth did not change during field visit. Moreover, we had to change the depth of the sonde several times due to root growth in the bank, as well as massive sediment dumps at this station. 

```{r}
timberline_depth <- dplyr::select(rawless_timberline, c(DT, Depth_ft, site)) %>%
  # arrange(ymd_hms(DT)) %>%
  # group_by(site,DT) %>%
  # summarize(Depth_ft = mean((Depth_ft))) %>%
  # ungroup() %>%
  # distinct(DT,.keep_all=T) %>%
  mutate(Depth_ft_p1 = ifelse(DT >= ymd_hms('2022-04-06 08:00:00') & DT < ymd_hms('2022-04-07 17:15:00'), 
                              Depth_ft + abs(
                                filter(dplyr::select(rawless_timberline, c(DT, Depth_ft)), DT == ymd_hms('2022-04-07 16:15:00'))$Depth_ft - 
                                  filter(dplyr::select(rawless_timberline, c(DT, Depth_ft)), DT == ymd_hms('2022-04-07 17:15:00'))$Depth_ft
                              ), 
                              Depth_ft))

timberline_depth <- timberline_depth %>%
  mutate(Depth_ft_p1 = ifelse(DT > '2022-09-14 13:15:00', 
                              Depth_ft_p1 +
                                abs(
                                  filter(dplyr::select(timberline_depth, c(DT, Depth_ft_p1)), DT == ymd_hms('2022-09-14 13:00:00'))$Depth_ft_p1 -
                                    filter(dplyr::select(timberline_depth, c(DT, Depth_ft_p1)), DT == ymd_hms('2022-09-14 13:30:00'))$Depth_ft_p1
                                ), 
                              Depth_ft_p1)) %>%
  first_pass(., parama ="Depth_ft_p1", max=7, min=0) %>%
  mutate(site = 'timberline') %>%
  feather::write_feather('data/sensor_data/p1_backup/timberline_depth.feather')

# dygraph(xts::xts(select(timberline_depth, p1, DT, sd3), order.by = ymd_hms(timberline_depth$DT)), 
#         main="Depth Timeseries (UTC)") %>% 
#   dyRangeSelector()
```


## Temperature

Specs for temperature: ±0.1 Celsius, -5 to 50 C

```{r}
timberline_temp <- first_pass(what = rawless_timberline, parama = "Water_Temp_C", min = 0, max = 50) %>%
  mutate(site="timberline") %>%
  feather::write_feather('data/sensor_data/p1_backup/timberline_temp.feather')

# dygraph(xts::xts(select(timberline_temp, c(DT, p1, sd3)), order.by = ymd_hms(timberline_temp$DT)),
#         main="Water Temperature Timeseries (UTC)") %>% 
#   dyRangeSelector()
```


## Conductivity

Conductivity: ±0.5% of reading plus 1 μS/ cm from 0 to 100,000 μS/cm; ±1.0% of reading from 100,000 to 200,000 μS/cm; ±2.0% of reading from 200,000 to 350,000 μS/cm

```{r}
timberline_conductivity <-  first_pass(what = rawless_timberline, parama = "Specific_Conductivity_µS_cm", min = 40, max = 10000) %>%
  mutate(site = "timberline") %>%
  feather::write_feather('data/sensor_data/p1_backup/timberline_conductivity.feather')

# dygraph(xts::xts(select(timberline_conductivity, p1, sd3, DT), order.by = ymd_hms(timberline_conductivity$DT)),
#         main="SpC Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## DO

RDO: ±0.1 mg/L or ±2% of reading (whichever is greater)

```{r}
timberline_do <- first_pass(what = rawless_timberline, parama = "DO_ppm", min = 0, max = 25) %>%
  mutate(site = "timberline") %>%
  feather::write_feather('data/sensor_data/p1_backup/timberline_do.feather')

# dygraph(xts::xts(select(timberline_do, sd3, p1, DT), order.by = ymd_hms(timberline_do$DT)), 
#         main="DO Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## pH

```{r}
timberline_ph <- first_pass(what = rawless_timberline, parama = "pH1", min = 0, max = 14) %>%
  mutate(site = "timberline") %>%
  feather::write_feather('data/sensor_data/p1_backup/timberline_ph.feather')

# dygraph(xts::xts(select(timberline_ph, p1, sd3, DT), order.by = ymd_hms(timberline_ph$DT)),
#         main="pH Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


# Prospect

Was not deployed in 2021 due to damage to the PVC.

```{r}
# Full Dataset:
rawless_prospect <- going_rawless(site_name = "prospect", trolled = NA) %>%
  mutate(DT = ymd_hms(DT)) %>%
  padr::pad(by = 'DT') %>%
  filter(!is.na(DT)) %>%
  # Link up calibration data:
  full_join(na.locf(na.locf(filter(cal_table, site == "prospect")), fromLast = TRUE), 
            by = c('site','DT'))
```


## Temperature

Specs for temperature: ±0.1 Celsius, -5 to 50 C

```{r}
prospect_temp <- first_pass(what = rawless_prospect, parama = "Water_Temp_C", min = 0, max = 50) %>%
  mutate(site="prospect")  %>%
  feather::write_feather('data/sensor_data/p1_backup/prospect_temp.feather')

# What's it look like?
# dygraph(xts::xts(select(prospect_temp, c(DT, sd3, p1)), order.by = ymd_hms(prospect_temp$DT)),
#         main="Water Temperature Timeseries (UTC)") %>% 
#   dyRangeSelector()
```


## Depth

```{r}
prospect_depth <- dplyr::select(rawless_prospect, c(DT, Depth_ft)) %>%
  first_pass(., parama ="Depth_ft", max=7, min=0) %>%
  mutate(site = 'prospect') %>%
  feather::write_feather('data/sensor_data/p1_backup/prospect_depth.feather')

# dygraph(xts::xts(select(prospect_depth, p1, sd3, DT), order.by = ymd_hms(prospect_depth$DT)), 
#         main="Depth Timeseries (UTC)") %>% 
#   dyRangeSelector()
```


## Conductivity

Conductivity: ±0.5% of reading plus 1 μS/ cm from 0 to 100,000 μS/cm; ±1.0% of reading from 100,000 to 200,000 μS/cm; ±2.0% of reading from 200,000 to 350,000 μS/cm

```{r}
prospect_conductivity <-  first_pass(what = rawless_prospect, parama = "Specific_Conductivity_µS_cm", min = 40, max = 10000) %>%
  mutate(site = "prospect") %>%
  feather::write_feather('data/sensor_data/p1_backup/prospect_conductivity.feather')

# dygraph(xts::xts(select(prospect_conductivity, p1, sd3, DT), order.by = ymd_hms(prospect_conductivity$DT)),
#         main="SpC Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## DO

RDO: ±0.1 mg/L or ±2% of reading (whichever is greater)

```{r}
prospect_do <- first_pass(what = rawless_prospect, parama = "DO_ppm", min = 0, max = 25) %>%
  mutate(site = "prospect") %>%
  feather::write_feather('data/sensor_data/p1_backup/prospect_do.feather')

# dygraph(xts::xts(select(prospect_do, p1, DT, sd3), order.by = ymd_hms(prospect_do$DT)), 
#         main="DO Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## pH

```{r}
prospect_ph <- first_pass(what = rawless_prospect, parama = "pH1", min = 0, max = 14) %>%
  mutate(site = "prospect") %>%
  feather::write_feather('data/sensor_data/p1_backup/prospect_ph.feather')

# dygraph(xts::xts(select(prospect_ph, p1, DT, sd3), order.by = ymd_hms(prospect_ph$DT)), 
#         main="pH Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


# ELC

Was not deployed in 2021 due to damage to the PVC.

```{r}
# No VuLink connection during final genomic survey (water was too low for full deployment)
raw_troll_elc <- map_dfr(grep(list.files("data/sensor_data/2022/elc/manual/", full.names = T), pattern = "trolled", invert = F, value = T), troll_reader)
names(raw_troll_elc) <- make.names(names(raw_troll_elc), unique = T)

rawless_troll_elc <- raw_troll_elc %>% 
  select(DT = contains('Date.Time'),
         Water_Temp_C = as.numeric(contains('Temperature...C')),
         pH = contains('pH'),
         ORP_mV = contains('ORP'),
         Specific_Conductivity_µS_cm = contains('Specific.Conductivity..µS.cm.'),
         DO_ppm = contains('RDO.concentration'),
         Turbidity_NTU = contains('Turbidity'),
         Depth_ft = contains('Depth..ft')) %>%
  mutate(DT = ymd_hms(DT)) %>%
  mutate(DT = DT - lubridate::hours(1)) %>% # reported in MDT >:(
  mutate(DT = as.character(round_date(ymd_hms(DT), "15 minutes"))) %>%
  mutate(DT = ymd_hms(DT)) %>%
  mutate_at(vars(2:ncol(.)), as.numeric) 


# Full Dataset:
rawless_elc <- going_rawless(site_name = "elc", trolled = NA) %>%
  mutate(DT = ymd_hms(DT)) %>%
  # Dataset got swapped to Rist's sensor, so need to remove data that 
  # is actually Rist
  filter(!(year(DT)>=2022 & DT < ymd_hms("2022-05-30 09:00:00"))) %>%
  bind_rows(rawless_troll_elc) %>%
  padr::pad(by = 'DT') %>%
  # Link up calibration data:
  full_join(na.locf(na.locf(filter(cal_table, site == "elc")), fromLast = TRUE), 
            by = c('site','DT'))
rm(rawless_troll_elc,raw_troll_elc)
```


## Temperature

Specs for temperature: ±0.1 Celsius, -5 to 50 C

```{r}
elc_temp <- first_pass(what = rawless_elc, parama = "Water_Temp_C", min = 0, max = 50) %>%
  mutate(site="elc") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/elc_temp.feather')

# What's it look like?
# dygraph(xts::xts(select(elc_temp, c(DT, p1, sd3)), order.by = ymd_hms(elc_temp$DT)),
#         main="Water Temperature Timeseries (UTC)") %>% 
#   dyRangeSelector()

```


## Depth

```{r}
elc_depth <- dplyr::select(rawless_elc, c(DT, Depth_ft)) %>%
  first_pass(., parama ="Depth_ft", max=7, min=0) %>%
  mutate(site = 'elc') %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/elc_depth.feather')

# dygraph(xts::xts(select(elc_depth, p1, DT, sd3), order.by = ymd_hms(elc_depth$DT)), 
#         main="Depth Timeseries (UTC)") %>% 
#   dyRangeSelector()
```


## Conductivity

Conductivity: ±0.5% of reading plus 1 μS/ cm from 0 to 100,000 μS/cm; ±1.0% of reading from 100,000 to 200,000 μS/cm; ±2.0% of reading from 200,000 to 350,000 μS/cm

```{r}
elc_conductivity <-  first_pass(what = rawless_elc, parama = "Specific_Conductivity_µS_cm", min = 40, max = 10000) %>%
  mutate(site = "elc") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/elc_conductivity.feather')

# dygraph(xts::xts(select(elc_conductivity, p1, sd3, DT), order.by = ymd_hms(elc_conductivity$DT)),
#         main="SpC Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## DO

RDO: ±0.1 mg/L or ±2% of reading (whichever is greater)

```{r}
elc_do <- first_pass(what = rawless_elc, parama = "DO_ppm", min = 0, max = 25) %>%
  mutate(site = "elc") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/elc_do.feather')

# dygraph(xts::xts(select(elc_do, p1, DT, sd3), order.by = ymd_hms(elc_do$DT)), 
#         main="DO Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## pH

```{r}
elc_ph <- first_pass(what = rawless_elc, parama = "pH1", min = 0, max = 14) %>%
  mutate(site = "elc") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/elc_ph.feather')

# dygraph(xts::xts(select(elc_ph, p1, sd3, DT), order.by = ymd_hms(elc_ph$DT)), 
#         main="pH Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


# Archery

Was not deployed in 2021 due to damage to the PVC.

```{r}
# Full Dataset:
rawless_archery <- going_rawless(site_name = "archery", trolled = NA) %>%
  mutate(DT = ymd_hms(DT)) %>%
  padr::pad(by = 'DT') %>%
  mutate(Chl_a= ifelse(is.na(Chla), Chla_RFU, NA),
         Chl_a = ifelse(is.na(Chl_a), Chla_µg_L/10, NA)) %>%
  # Link up calibration data:
  full_join(na.locf(na.locf(filter(cal_table, site == "archery")), fromLast = TRUE), 
            by = c('site','DT'))
```


## Temperature

Specs for temperature: ±0.1 Celsius, -5 to 50 C

```{r}
archery_temp <- first_pass(what = rawless_archery, parama = "Water_Temp_C", min = 0, max = 50) %>%
  mutate(site="archery") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/archery_temp.feather')

# What's it look like?
# dygraph(xts::xts(select(archery_temp, c(DT, p1, sd3)), order.by = ymd_hms(archery_temp$DT)),
#         main="Water Temperature Timeseries (UTC)") %>% 
#   dyRangeSelector()

```


## Depth

```{r}
archery_depth <- dplyr::select(rawless_archery, c(DT, Depth_ft)) %>%
  first_pass(., parama ="Depth_ft", max=7, min=0) %>%
  mutate(site = 'archery') %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/archery_depth.feather')

# dygraph(xts::xts(select(archery_depth, p1, DT, sd3), order.by = ymd_hms(archery_depth$DT)), 
#         main="Depth Timeseries (UTC)") %>% 
#   dyRangeSelector()
```


## Conductivity

Conductivity: ±0.5% of reading plus 1 μS/ cm from 0 to 100,000 μS/cm; ±1.0% of reading from 100,000 to 200,000 μS/cm; ±2.0% of reading from 200,000 to 350,000 μS/cm

```{r}
archery_conductivity <-  first_pass(what = rawless_archery, parama = "Specific_Conductivity_µS_cm", min = 40, max = 10000) %>%
  mutate(site = "archery") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/archery_conductivity.feather')

# dygraph(xts::xts(select(archery_conductivity, p1, sd3, DT), order.by = ymd_hms(archery_conductivity$DT)),
#         main="SpC Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## DO

RDO: ±0.1 mg/L or ±2% of reading (whichever is greater)

```{r}
archery_do <- first_pass(what = rawless_archery, parama = "DO_ppm", min = 0, max = 25) %>%
  mutate(site = "archery") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/archery_do.feather')

# dygraph(xts::xts(select(archery_do, p1, DT, sd3), order.by = ymd_hms(archery_do$DT)), 
#         main="DO Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


## pH

```{r}
archery_ph <- first_pass(what = rawless_archery, parama = "pH1", min = 0, max = 14) %>%
  mutate(site = "archery") %>%
  filter(!is.na(DT)) %>%
  feather::write_feather('data/sensor_data/p1_backup/archery_ph.feather')

# dygraph(xts::xts(select(archery_ph, p1, sd3, DT), order.by = ymd_hms(archery_ph$DT)), 
#         main="pH Timeseries (UTC)") %>% 
#   dyRangeSelector() 
```


```{r}
depth <- plyr::ldply(list.files(path='data/sensor_data/p1_backup', pattern = '*depth.feather', full.names = TRUE), feather::read_feather) %>%
  select(DT,Depth_ft=p1,site)
temperature <- plyr::ldply(list.files(path='data/sensor_data/p1_backup', pattern = '*temp.feather', full.names = TRUE), feather::read_feather) %>%
  select(DT,Temperature_C=p1,site)
conductivity <- plyr::ldply(list.files(path='data/sensor_data/p1_backup', pattern = '*conductivity.feather', full.names = TRUE), feather::read_feather) %>%
  select(DT,Specific_Conductivity_µS_cm=p1,site)
do <- plyr::ldply(list.files(path='data/sensor_data/p1_backup', pattern = '*do.feather', full.names = TRUE), feather::read_feather) %>%
  select(DT,DO_ppm=p1,site)
ph <- plyr::ldply(list.files(path='data/sensor_data/p1_backup', pattern = '*ph.feather', full.names = TRUE), feather::read_feather) %>%
  select(DT,pH=p1,site)

all_data <- list(depth,temperature,conductivity,do,ph) %>%
  reduce(full_join, by=c('site','DT')) %>%
  mutate(tracer = case_when(site=="rist" ~ "1",
                            site=="legacy" ~ "2",
                            site=="lincoln" ~ "3",
                            site=="timberline" ~ "4",
                            site=="prospect" ~ "5",
                            site=="elc" ~ "6",
                            site=="archery" ~ "7"))

daily <- all_data %>%
  mutate(daily=as_date(ymd_hms(DT))) %>%
  group_by(site,tracer,daily) %>%
  summarize_all(., mean, na.rm=T) 

hourly <- all_data %>%
  mutate(hourly = ymd_hms(as.character(round_date(ymd_hms(DT), "1 hour")))) %>%
  group_by(site,tracer,hourly) %>%
  summarize_all(., mean, na.rm=T)

cols <- c("#7C221D", "#D1520A", "#DF810B", "#D9B35B", "#4F6010", "#374105", "#20331a")

cols <- c("#ff0a54", "#ff0072",  "#ff177f", "#ff2e8c", "#ff4598", "#ff5ca5", "#ff74b2", "#ff8bbf", "#ffa2cb", "#ffb9d8", "#ffd0e5")

cols <- rev(c("#7C221D", "#E7331A", "#F16A16", "#FFC82F", "#0D98BA", "#0074A5", "#2E5895"))


october_pulse <- hourly %>% filter(as_date(hourly) > ymd('2022-10-18') & as_date(hourly) < ymd('2022-10-26')) %>%
  ungroup() %>%
  select(DT,site,tracer,DO_ppm,Specific_Conductivity_µS_cm,Depth_ft) %>%
  pivot_longer(cols=-c(DT,tracer,site), names_to="Parameter")

ggplot(october_pulse) +
  geom_path(aes(x = DT, y = value, color = tracer), size = 0.75) +
  scale_color_manual(values = cols, labels = c("Lincoln","Timberline","Prospect","ELC", "Archery")) +
  facet_wrap(~Parameter, scales = "free_y", ncol = 1) +
  theme_bw() +
  theme(legend.position="bottom", legend.title = element_blank())


bw_event <- hourly %>% filter(as_date(hourly) > ymd('2022-08-15') & as_date(hourly) < ymd('2022-08-23')) %>%
  ungroup() %>%
  select(DT,site,tracer,DO_ppm,Specific_Conductivity_µS_cm,Depth_ft) %>%
  pivot_longer(cols=-c(DT,tracer,site), names_to="Parameter")

ggplot(bw_event)+
  geom_path(aes(x = DT, y = value, color = tracer)) +
  scale_color_manual(values = cols, labels = c("Archery", "ELC", "Lincoln", "Prospect", "Timberline")) +
  facet_wrap(~Parameter, scales = "free_y", ncol = 1) +
  theme_bw() +
  theme(legend.position="bottom", legend.title = element_blank())


runoff <- hourly %>% filter(as_date(hourly) > ymd('2022-06-01') & as_date(hourly) < ymd('2022-06-15')) %>%
  ungroup() %>%
  select(DT,site,tracer,DO_ppm,Specific_Conductivity_µS_cm,Depth_ft) %>%
  pivot_longer(cols=-c(DT,tracer,site), names_to="Parameter")

ggplot(runoff) +
  geom_path(aes(x = DT, y = value, color = tracer)) +
  scale_color_manual(values = cols, labels = c("Archery", "ELC", "Lincoln", "Prospect", "Timberline")) +
  facet_wrap(~Parameter, scales = "free_y", ncol = 1) +
  theme_bw() +
  theme(legend.position="bottom", legend.title = element_blank())
```

