---
title: "poudre_pre2022"
author: "Katie Willi"
date: "2/22/2022"
output: html_document
---

```{r}
library(janitor) # 
library(rvest)
library(tidyverse)
library(dygraphs)
library(lubridate)
library(padr)
library(ggpubr)
library(dygraphs)
```

 Listed accuracy and range for sensors:

 Temperature: ±0.1 Celsius, -5 to 50 C

 Barometric Pressure: ±1.0 mbars, 300 to 1,100 mbars

 pH: ±0.1 pH, 0 to 14 pH

 ORP: ±5 mV

 Conductivity: ±0.5% of reading plus 1 μS/ cm from 0 to 100,000 μS/cm; ±1.0% of reading from 100,000 to 200,000 μS/cm; ±2.0% of reading from 200,000 to 350,000 μS/cm

 TDS/Salinity: range of 0 to 350 ppt/0 to 350 PSU

 RDO: ±0.1 mg/L or ±2% of reading (whichever is greater)

 Turbidity: ±2% of reading or ±0.5 NTU (whichever is greater)

 TSS: range of 1 to 1,500 mg/L

 Pressure: ±0.1% FS from -5 to 50°C

 Chlorophyll-a: range of 0-100 RFU or 1-1,000 μg/L


HTML readers, one for HydroVu htmls, one for direct downloads from the AquaTROLL 600, and one for downloading from the Vulink in the field:
```{r}
# from HydroVu:
html_reader <- function(file) {
    
    raw_data <- rvest::read_html(file) %>%
      rvest::html_node('table') %>%
      rvest::html_table() %>%
      slice(-1:-8) %>%
      janitor::row_to_names(row_number = 1) 
}

# from AquaTROLL 600:
direct_download_reader <- function(file) {
  
  raw_data <- rvest::read_html(file) %>%
    rvest::html_node('table') %>%
    rvest::html_table() %>%
    slice(-1:-25) %>%
    janitor::row_to_names(row_number = 1) 
}

# from VuLink in the field:
vulink_on_reader <- function(file) {
  
  raw_data <- rvest::read_html(file) %>%
    rvest::html_node('table') %>%
    rvest::html_table() %>%
    slice(-1:-31) %>%
    janitor::row_to_names(row_number = 1) 
}

```

## Rist
```{r}
raw <- map_dfr(grep(list.files("data/new_upload/rist/", full.names = T), pattern = "M", invert = T, value = T), html_reader)
names(raw) <- make.names(names(raw), unique = T)

vusitu <- raw %>%
  select(DT = Date.Time,
         Water_Temp_C = Temperature..C.,
         pH = pH..pH.,
         ORP_mV = ORP..mV.,
         Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm.,
         Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm.,
         Salinity_PSU = Salinity..psu.,
         TDS_ppt = Total.Dissolved.Solids..ppt.,
         DO_ppm = DO..ppm.,
         Perc_O2_Sat = X..Saturation.O2....sat.,
         Turbidity_NTU = Turbidity..FNU.,
         TSS_mg_L = Total.Suspended.Solids..mg.L.,
         #Chla_RFU = Chl.a.Fluorescence..RFU.,
         #Chla_µg_L = Chl.a.Concentration..µg.L.,
         Pressure_PSI = Pressure..psi.,
         Depth_ft = Depth..ft.,
         Elevation_m = Level..Elevation..m.,
         Depth_to_Water_ft = Level..Depth.to.Water..ft.) %>%
  mutate(DT = as_datetime(DT, tz = "UTC")) %>%
  mutate(DT = with_tz(DT, tzone = "MST"))

# mdt <- map_dfr(grep(list.files("data/new_upload/rist/", full.names = T), pattern = "MDT_DIRECT", value = T), direct_download_reader)
# mst <- map_dfr(grep(list.files("data/new_upload/rist/", full.names = T), pattern = "MST_DIRECT", value = T), direct_download_reader)
# 
# names(mdt) <- make.names(gsub("[[:digit:]]", "", names(mdt)), unique = T)
# names(mst) <- make.names(gsub("[[:digit:]]", "", names(mst)), unique = T)
#
# mdt <- mdt %>%
#   select(DT = Date.Time,
#          Water_Temp_C = Temperature...C....,
#          pH = pH..pH....,
#          ORP_mV = ORP..mV....,
#          Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
#          Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
#          Salinity_PSU = Salinity..PSU....,
#          TDS_ppt = Total.Dissolved.Solids..ppt....,
#          DO_ppm = RDO.Concentration..mg.L....,
#          Perc_O2_Sat = RDO.Saturation...Sat....,
#          Turbidity_NTU = Turbidity..NTU....,
#          TSS_mg_L = Total.Suspended.Solids..mg.L....,
#          Pressure_PSI = Pressure..psi....,
#          Depth_ft = Depth..ft....) %>%
#   mutate(DT = as_datetime(DT, tz = "MST")) %>%
#   mutate(DT = DT - hours(1))
#   
#   mst <- mst %>%
#     select(DT = Date.Time,
#            Water_Temp_C = Temperature...C....,
#            pH = pH..pH....,
#            ORP_mV = ORP..mV....,
#            Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
#            Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
#            Salinity_PSU = Salinity..PSU....,
#            TDS_ppt = Total.Dissolved.Solids..ppt....,
#            DO_ppm = RDO.Concentration..mg.L....,
#            Perc_O2_Sat = RDO.Saturation...Sat....,
#            Turbidity_NTU = Turbidity..NTU....,
#            #TSS_mg_L = Total.Suspended.Solids..mg.L....,
#            Pressure_PSI = Pressure..psi....,
#            Depth_ft = Depth..ft....) %>%
#     mutate(DT = as_datetime(DT, tz = "MST")) %>%
#     mutate(DT = with_tz(DT, tzone = "MST"))
  
rist <- vusitu %>% #  bind_rows(vusitu,mdt,mst) %>%
  mutate(data = "Yes") %>%
  mutate(DT = round_date(DT, "15 minutes")) %>%
  mutate(year = lubridate::year(DT)) %>%
  padr::pad(.,group = "year") %>%
  mutate(date = as_date(substr(DT, 1, 10))) %>%
  distinct(.keep_all=TRUE) %>%
  mutate(sensor = "Rist",
         comments = NA)
```

## Legacy
```{r}
raw <- map_dfr(grep(list.files("data/new_upload/legacy/", full.names = T), pattern = "M", invert = T, value = T), html_reader)
names(raw) <- make.names(names(raw), unique = T)

vusitu <- raw %>%
  select(DT = Date.Time,
         Water_Temp_C = Temperature..C.,
         pH = pH..pH.,
         ORP_mV = ORP..mV.,
         Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm.,
         Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm.,
         Salinity_PSU = Salinity..psu.,
         TDS_ppt = Total.Dissolved.Solids..ppt.,
         DO_ppm = DO..ppm.,
         Perc_O2_Sat = X..Saturation.O2....sat.,
         Turbidity_NTU = Turbidity..FNU.,
         TSS_mg_L = Total.Suspended.Solids..mg.L.,
         #Chla_RFU = Chl.a.Fluorescence..RFU.,
         #Chla_µg_L = Chl.a.Concentration..µg.L.,
         Pressure_PSI = Pressure..psi.,
         Depth_ft = Depth..ft.,
         #Elevation_m = Level..Elevation..m.,
         Depth_to_Water_ft = Level..Depth.to.Water..ft.) %>%
  mutate(DT = as_datetime(DT, tz = "UTC")) %>%
  mutate(DT = with_tz(DT, tzone = "MST"))

mdt <- map_dfr(grep(list.files("data/new_upload/legacy/", full.names = T), pattern = "MDT_DIRECT", value = T), direct_download_reader)
mdt_manual <-  map_dfr(grep(list.files("data/new_upload/legacy/", full.names = T), pattern = "MDT_MANUAL", value = T), vulink_on_reader) %>% select(-2:-4)
mst <- map_dfr(grep(list.files("data/new_upload/legacy/", full.names = T), pattern = "MST_DIRECT", value = T), direct_download_reader)
# mst_manual <-  map_dfr(grep(list.files("data/new_upload/legacy/", full.names = T), pattern = "MST_MANUAL", value = T), vulink_on_reader) %>%
#   select(-2:-4)


names(mdt) <- make.names(gsub("[[:digit:]]", "", names(mdt)), unique = T)
names(mdt_manual) <- make.names(gsub("[[:digit:]]", "", names(mdt_manual)), unique = T)
names(mst) <- make.names(gsub("[[:digit:]]", "", names(mst)), unique = T)
#names(mst_manual) <- make.names(gsub("[[:digit:]]", "", names(mst_manual)), unique = T)

mdt_manual <- mdt_manual %>% #bind_rows(mdt,mdt_manual) %>%
  select(DT = Date.Time,
         Water_Temp_C = Temperature...C....,
         pH = pH..pH....,
         ORP_mV = ORP..mV....,
         Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
         Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
         Salinity_PSU = Salinity..PSU....,
         TDS_ppt = Total.Dissolved.Solids..ppt....,
         DO_ppm = RDO.Concentration..mg.L....,
         Perc_O2_Sat = RDO.Saturation...Sat....,
         Turbidity_NTU = Turbidity..NTU....,
         TSS_mg_L = Total.Suspended.Solids..mg.L....,
         Pressure_PSI = Pressure..psi....,
         Depth_ft = Depth..ft....) %>%
  mutate(DT = as_datetime(DT, tz = "MST")) %>%
  mutate(DT = DT - hours(1)) %>%
  filter(DT < "2021-07-25 00:00:00" | DT >"2021-08-25 23:00:00")
  
mdt_direct <- mdt %>% #bind_rows(mdt,mdt_manual) %>%
  select(DT = Date.Time,
         Water_Temp_C = Temperature...C....,
         pH = pH..pH....,
         ORP_mV = ORP..mV....,
         Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
         Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
         Salinity_PSU = Salinity..PSU....,
         TDS_ppt = Total.Dissolved.Solids..ppt....,
         DO_ppm = RDO.Concentration..mg.L....,
         Perc_O2_Sat = RDO.Saturation...Sat....,
         Turbidity_NTU = Turbidity..NTU....,
         TSS_mg_L = Total.Suspended.Solids..mg.L....,
         Pressure_PSI = Pressure..psi....,
         Depth_ft = Depth..ft....) %>%
  mutate(DT = as_datetime(DT, tz = "MST")) %>%
  mutate(DT = DT - hours(1)) %>%
  filter(DT >= "2021-07-25 00:00:00" & DT <="2021-08-25 23:00:00") 

mdt <- bind_rows(mdt_manual,mdt_direct)


  mst <- mst %>% # bind_rows(mst,mst_manual) %>%
    select(DT = Date.Time,
           Water_Temp_C = Temperature...C....,
           pH = pH..pH....,
           ORP_mV = ORP..mV....,
           Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
           Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
           Salinity_PSU = Salinity..PSU....,
           TDS_ppt = Total.Dissolved.Solids..ppt....,
           DO_ppm = RDO.Concentration..mg.L....,
           Perc_O2_Sat = RDO.Saturation...Sat....,
           Turbidity_NTU = Turbidity..NTU....,
           #TSS_mg_L = Total.Suspended.Solids..mg.L....,
           Pressure_PSI = Pressure..psi....,
           Depth_ft = Depth..ft....) %>%
    mutate(DT = as_datetime(DT, tz = "MST")) %>%
    mutate(DT = with_tz(DT, tzone = "MST"))
  
legacy <- bind_rows(vusitu,mdt,mst) %>%
  filter(!is.na(Water_Temp_C)) %>%
  mutate(data = "Yes") %>%
  mutate(DT = round_date(DT, "15 minutes")) %>%
  mutate(year = lubridate::year(DT)) %>%
  padr::pad(.,group = "year") %>%
  mutate(date = as_date(substr(DT, 1, 10))) %>%
  distinct(.keep_all=TRUE) %>%
  mutate(sensor = "Legacy",
  comments = NA)
```

## Timberline
```{r}
raw <- map_dfr(grep(list.files("data/new_upload/timberline/", full.names = T), pattern = "M", invert = T, value = T), html_reader)
names(raw) <- make.names(names(raw), unique = T)

vusitu <- raw %>%
  select(DT = Date.Time,
         Water_Temp_C = Temperature..C.,
         pH = pH..pH.,
         ORP_mV = ORP..mV.,
         Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm.,
         Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm.,
         Salinity_PSU = Salinity..psu.,
         TDS_ppt = Total.Dissolved.Solids..ppt.,
         DO_ppm = DO..ppm.,
         Perc_O2_Sat = X..Saturation.O2....sat.,
         Turbidity_NTU = Turbidity..FNU.,
         TSS_mg_L = Total.Suspended.Solids..mg.L.,
         #Chla_RFU = Chl.a.Fluorescence..RFU.,
         #Chla_µg_L = Chl.a.Concentration..µg.L.,
         Pressure_PSI = Pressure..psi.,
         Depth_ft = Depth..ft.,
         Elevation_m = Level..Elevation..m.,
         Depth_to_Water_ft = Level..Depth.to.Water..ft.) %>%
  mutate(DT = as_datetime(DT, tz = "UTC")) %>%
  mutate(DT = with_tz(DT, tzone = "MST"))

# mdt <- map_dfr(grep(list.files("data/new_upload/timberline/", full.names = T), pattern = "MDT_DIRECT", value = T), direct_download_reader)
# mdt_manual <-  map_dfr(grep(list.files("data/new_upload/timberline/", full.names = T), pattern = "MDT_MANUAL", value = T), vulink_on_reader) %>% select(-2:-4)
# mst <- map_dfr(grep(list.files("data/new_upload/timberline/", full.names = T), pattern = "MST_DIRECT", value = T), direct_download_reader)
# mst_manual <-  map_dfr(grep(list.files("data/new_upload/timberline/", full.names = T), pattern = "MST_MANUAL", value = T), vulink_on_reader) %>%
#   select(-2:-4)
# 
# 
# names(mdt) <- make.names(gsub("[[:digit:]]", "", names(mdt)), unique = T)
# names(mdt_manual) <- make.names(gsub("[[:digit:]]", "", names(mdt_manual)), unique = T)
# names(mst) <- make.names(gsub("[[:digit:]]", "", names(mst)), unique = T)
# names(mst_manual) <- make.names(gsub("[[:digit:]]", "", names(mst_manual)), unique = T)
# 
# mdt <- bind_rows(mdt,mdt_manual) %>%
#   select(DT = Date.Time,
#          Water_Temp_C = Temperature...C....,
#          pH = pH..pH....,
#          ORP_mV = ORP..mV....,
#          Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
#          Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
#          Salinity_PSU = Salinity..PSU....,
#          TDS_ppt = Total.Dissolved.Solids..ppt....,
#          DO_ppm = RDO.Concentration..mg.L....,
#          Perc_O2_Sat = RDO.Saturation...Sat....,
#          Turbidity_NTU = Turbidity..NTU....,
#          TSS_mg_L = Total.Suspended.Solids..mg.L....,
#          Pressure_PSI = Pressure..psi....,
#          Depth_ft = Depth..ft....) %>%
#   mutate(DT = as_datetime(DT, tz = "MST")) %>%
#   mutate(DT = DT - hours(1))
#   
#   mst <- bind_rows(mst,mst_manual) %>%
#     select(DT = Date.Time,
#            Water_Temp_C = Temperature...C....,
#            pH = pH..pH....,
#            ORP_mV = ORP..mV....,
#            Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
#            Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
#            Salinity_PSU = Salinity..PSU....,
#            TDS_ppt = Total.Dissolved.Solids..ppt....,
#            DO_ppm = RDO.Concentration..mg.L....,
#            Perc_O2_Sat = RDO.Saturation...Sat....,
#            Turbidity_NTU = Turbidity..NTU....,
#            #TSS_mg_L = Total.Suspended.Solids..mg.L....,
#            Pressure_PSI = Pressure..psi....,
#            Depth_ft = Depth..ft....) %>%
#     mutate(DT = as_datetime(DT, tz = "MST")) %>%
#     mutate(DT = with_tz(DT, tzone = "MST"))
  
timberline <- vusitu %>% # bind_rows(vusitu,mdt,mst) %>%
  mutate(data = "Yes") %>%
  mutate(DT = round_date(DT, "15 minutes")) %>%
  mutate(year = lubridate::year(DT)) %>%
  padr::pad(.,group = "year") %>%
  mutate(date = as_date(substr(DT, 1, 10))) %>%
  distinct(.keep_all=TRUE) %>%
  mutate(sensor = "Timberline",
         comments = NA)
```

## Prospect
```{r}
raw <- map_dfr(grep(list.files("data/new_upload/prospect/", full.names = T), pattern = "M", invert = T, value = T), html_reader)
names(raw) <- make.names(names(raw), unique = T)

vusitu <- raw %>%
  select(DT = Date.Time,
         Water_Temp_C = Temperature..C.,
         pH = pH..pH.,
         ORP_mV = ORP..mV.,
         Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm.,
         Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm.,
         Salinity_PSU = Salinity..psu.,
         TDS_ppt = Total.Dissolved.Solids..ppt.,
         DO_ppm = DO..ppm.,
         Perc_O2_Sat = X..Saturation.O2....sat.,
         Turbidity_NTU = Turbidity..FNU.,
         TSS_mg_L = Total.Suspended.Solids..mg.L.,
         #Chla_RFU = Chl.a.Fluorescence..RFU.,
         #Chla_µg_L = Chl.a.Concentration..µg.L.,
         Pressure_PSI = Pressure..psi.,
         Depth_ft = Depth..ft.,
         Elevation_m = Level..Elevation..m.,
         Depth_to_Water_ft = Level..Depth.to.Water..ft.) %>%
  mutate(DT = as_datetime(DT, tz = "UTC")) %>%
  mutate(DT = with_tz(DT, tzone = "MST"))

# mdt <- map_dfr(grep(list.files("data/new_upload/prospect/", full.names = T), pattern = "MDT_DIRECT", value = T), direct_download_reader)
# mdt_manual <-  map_dfr(grep(list.files("data/new_upload/prospect/", full.names = T), pattern = "MDT_MANUAL", value = T), vulink_on_reader) %>% select(-2:-4)
# mst <- map_dfr(grep(list.files("data/new_upload/prospect/", full.names = T), pattern = "MST_DIRECT", value = T), direct_download_reader)
# mst_manual <-  map_dfr(grep(list.files("data/new_upload/prospect/", full.names = T), pattern = "MST_MANUAL", value = T), vulink_on_reader) %>%
#   select(-2:-4)
# 
# 
# names(mdt) <- make.names(gsub("[[:digit:]]", "", names(mdt)), unique = T)
# names(mdt_manual) <- make.names(gsub("[[:digit:]]", "", names(mdt_manual)), unique = T)
# names(mst) <- make.names(gsub("[[:digit:]]", "", names(mst)), unique = T)
# names(mst_manual) <- make.names(gsub("[[:digit:]]", "", names(mst_manual)), unique = T)
# 
# mdt <- bind_rows(mdt,mdt_manual) %>%
#   select(DT = Date.Time,
#          Water_Temp_C = Temperature...C....,
#          pH = pH..pH....,
#          ORP_mV = ORP..mV....,
#          Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
#          Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
#          Salinity_PSU = Salinity..PSU....,
#          TDS_ppt = Total.Dissolved.Solids..ppt....,
#          DO_ppm = RDO.Concentration..mg.L....,
#          Perc_O2_Sat = RDO.Saturation...Sat....,
#          Turbidity_NTU = Turbidity..NTU....,
#          TSS_mg_L = Total.Suspended.Solids..mg.L....,
#          Pressure_PSI = Pressure..psi....,
#          Depth_ft = Depth..ft....) %>%
#   mutate(DT = as_datetime(DT, tz = "MST")) %>%
#   mutate(DT = DT - hours(1))
#   
#   mst <- bind_rows(mst,mst_manual) %>%
#     select(DT = Date.Time,
#            Water_Temp_C = Temperature...C....,
#            pH = pH..pH....,
#            ORP_mV = ORP..mV....,
#            Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
#            Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
#            Salinity_PSU = Salinity..PSU....,
#            TDS_ppt = Total.Dissolved.Solids..ppt....,
#            DO_ppm = RDO.Concentration..mg.L....,
#            Perc_O2_Sat = RDO.Saturation...Sat....,
#            Turbidity_NTU = Turbidity..NTU....,
#            #TSS_mg_L = Total.Suspended.Solids..mg.L....,
#            Pressure_PSI = Pressure..psi....,
#            Depth_ft = Depth..ft....) %>%
#     mutate(DT = as_datetime(DT, tz = "MST")) %>%
#     mutate(DT = with_tz(DT, tzone = "MST"))
  
prospect <- vusitu %>% # bind_rows(vusitu,mdt,mst) %>%
  mutate(data = "Yes") %>%
  mutate(DT = round_date(DT, "15 minutes")) %>%
  mutate(year = lubridate::year(DT)) %>%
  padr::pad(.,group = "year") %>%
  mutate(date = as_date(substr(DT, 1, 10))) %>%
  distinct(.keep_all=TRUE) %>%
  mutate(sensor = "Prospect",
    comments = NA)
```
## ELC
```{r}
raw <- map_dfr(grep(list.files("data/new_upload/elc/", full.names = T), pattern = "M", invert = T, value = T), html_reader)
names(raw) <- make.names(names(raw), unique = T)

vusitu <- raw %>%
  select(DT = Date.Time,
         Water_Temp_C = Temperature..C.,
         pH = pH..pH.,
         ORP_mV = ORP..mV.,
         Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm.,
         Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm.,
         Salinity_PSU = Salinity..psu.,
         TDS_ppt = Total.Dissolved.Solids..ppt.,
         DO_ppm = DO..ppm.,
         Perc_O2_Sat = X..Saturation.O2....sat.,
         Turbidity_NTU = Turbidity..FNU.,
         TSS_mg_L = Total.Suspended.Solids..mg.L.,
         #Chla_RFU = Chl.a.Fluorescence..RFU.,
         #Chla_µg_L = Chl.a.Concentration..µg.L.,
         Pressure_PSI = Pressure..psi.,
         Depth_ft = Depth..ft.,
         Elevation_m = Level..Elevation..m.,
         Depth_to_Water_ft = Level..Depth.to.Water..ft.) %>%
  mutate(DT = as_datetime(DT, tz = "UTC")) %>%
  mutate(DT = with_tz(DT, tzone = "MST"))

mdt <- map_dfr(grep(list.files("data/new_upload/elc/", full.names = T), pattern = "MDT_DIRECT", value = T), direct_download_reader)
# mdt_manual <-  map_dfr(grep(list.files("data/new_upload/elc/", full.names = T), pattern = "MDT_MANUAL", value = T), vulink_on_reader) %>% select(-2:-4)
# mst <- map_dfr(grep(list.files("data/new_upload/elc/", full.names = T), pattern = "MST_DIRECT", value = T), direct_download_reader)
# mst_manual <-  map_dfr(grep(list.files("data/new_upload/elc/", full.names = T), pattern = "MST_MANUAL", value = T), vulink_on_reader) %>%
#   select(-2:-4)
# 
# 
 names(mdt) <- make.names(gsub("[[:digit:]]", "", names(mdt)), unique = T)
# names(mdt_manual) <- make.names(gsub("[[:digit:]]", "", names(mdt_manual)), unique = T)
# names(mst) <- make.names(gsub("[[:digit:]]", "", names(mst)), unique = T)
# names(mst_manual) <- make.names(gsub("[[:digit:]]", "", names(mst_manual)), unique = T)

 mdt <- mdt %>% # bind_rows(mdt,mdt_manual) %>%
   select(DT = Date.Time,
          Water_Temp_C = Temperature...C....,
          pH = pH..pH....,
        ORP_mV = ORP..mV....,
          Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
          Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
          Salinity_PSU = Salinity..PSU....,
          TDS_ppt = Total.Dissolved.Solids..ppt....,
          DO_ppm = RDO.Concentration..mg.L....,
          Perc_O2_Sat = RDO.Saturation...Sat....,
          Turbidity_NTU = Turbidity..NTU....,
          TSS_mg_L = Total.Suspended.Solids..mg.L....,
          Pressure_PSI = Pressure..psi....,
          Depth_ft = Depth..ft....) %>%
   mutate(DT = as_datetime(DT, tz = "MST")) %>%
   mutate(DT = DT - hours(1))
   
#   mst <- bind_rows(mst,mst_manual) %>%
#     select(DT = Date.Time,
#            Water_Temp_C = Temperature...C....,
#            pH = pH..pH....,
#            ORP_mV = ORP..mV....,
#            Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
#            Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
#            Salinity_PSU = Salinity..PSU....,
#            TDS_ppt = Total.Dissolved.Solids..ppt....,
#            DO_ppm = RDO.Concentration..mg.L....,
#            Perc_O2_Sat = RDO.Saturation...Sat....,
#            Turbidity_NTU = Turbidity..NTU....,
#            #TSS_mg_L = Total.Suspended.Solids..mg.L....,
#            Pressure_PSI = Pressure..psi....,
#            Depth_ft = Depth..ft....) %>%
#     mutate(DT = as_datetime(DT, tz = "MST")) %>%
#     mutate(DT = with_tz(DT, tzone = "MST"))
  
elc <- bind_rows(vusitu,mdt) %>%
  mutate(data = "Yes") %>%
  mutate(DT = round_date(DT, "15 minutes")) %>%
  mutate(year = lubridate::year(DT)) %>%
  padr::pad(.,group = "year") %>%
  mutate(date = as_date(substr(DT, 1, 10))) %>%
  distinct(.keep_all=TRUE) %>%
  mutate(sensor = "ELC",
    comments = NA)
```

## Archery
```{r}
raw <- map_dfr(grep(list.files("data/new_upload/archery/", full.names = T), pattern = "M", invert = T, value = T), html_reader)
names(raw) <- make.names(names(raw), unique = T)

vusitu <- raw %>%
  select(DT = Date.Time,
         Water_Temp_C = Temperature..C.,
         pH = pH..pH.,
         ORP_mV = ORP..mV.,
         Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm.,
         Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm.,
         Salinity_PSU = Salinity..psu.,
         TDS_ppt = Total.Dissolved.Solids..ppt.,
         DO_ppm = DO..ppm.,
         Perc_O2_Sat = X..Saturation.O2....sat.,
         Turbidity_NTU = Turbidity..FNU.,
         TSS_mg_L = Total.Suspended.Solids..mg.L.,
         Chla_RFU = Chl.a.Fluorescence..RFU.,
         Chla_µg_L = Chl.a.Concentration..µg.L.,
         Pressure_PSI = Pressure..psi.,
         Depth_ft = Depth..ft.,
         Elevation_m = Level..Elevation..m.,
         Depth_to_Water_ft = Level..Depth.to.Water..ft.) %>%
  mutate(DT = as_datetime(DT, tz = "UTC")) %>%
  mutate(DT = with_tz(DT, tzone = "MST"))

#mdt <- map_dfr(grep(list.files("data/new_upload/archery/", full.names = T), pattern = "MDT_DIRECT", value = T), direct_download_reader)
# mdt_manual <-  map_dfr(grep(list.files("data/new_upload/archery/", full.names = T), pattern = "MDT_MANUAL", value = T), vulink_on_reader) %>% select(-2:-4)
# mst <- map_dfr(grep(list.files("data/new_upload/archery/", full.names = T), pattern = "MST_DIRECT", value = T), direct_download_reader)
# mst_manual <-  map_dfr(grep(list.files("data/new_upload/archery/", full.names = T), pattern = "MST_MANUAL", value = T), vulink_on_reader) %>%
#   select(-2:-4)
# 
# 
# names(mdt) <- make.names(gsub("[[:digit:]]", "", names(mdt)), unique = T)
# names(mdt_manual) <- make.names(gsub("[[:digit:]]", "", names(mdt_manual)), unique = T)
# names(mst) <- make.names(gsub("[[:digit:]]", "", names(mst)), unique = T)
# names(mst_manual) <- make.names(gsub("[[:digit:]]", "", names(mst_manual)), unique = T)
# 
# mdt <- mdt %>% # bind_rows(mdt,mdt_manual) %>%
#   select(DT = Date.Time,
#          Water_Temp_C = Temperature...C....,
#          pH = pH..pH....,
#        ORP_mV = ORP..mV....,
#          Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
#          Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
#          Salinity_PSU = Salinity..PSU....,
#          TDS_ppt = Total.Dissolved.Solids..ppt....,
#          DO_ppm = RDO.Concentration..mg.L....,
#          Perc_O2_Sat = RDO.Saturation...Sat....,
#          Turbidity_NTU = Turbidity..NTU....,
#          TSS_mg_L = Total.Suspended.Solids..mg.L....,
#          Pressure_PSI = Pressure..psi....,
#          Depth_ft = Depth..ft....) %>%
#   mutate(DT = as_datetime(DT, tz = "MST")) %>%
#   mutate(DT = DT - hours(1))
#   
#   mst <- bind_rows(mst,mst_manual) %>%
#     select(DT = Date.Time,
#            Water_Temp_C = Temperature...C....,
#            pH = pH..pH....,
#            ORP_mV = ORP..mV....,
#            Actual_Conductivity_µS_cm = Actual.Conductivity..µS.cm....,
#            Specific_Conductivity_µS_cm = Specific.Conductivity..µS.cm....,
#            Salinity_PSU = Salinity..PSU....,
#            TDS_ppt = Total.Dissolved.Solids..ppt....,
#            DO_ppm = RDO.Concentration..mg.L....,
#            Perc_O2_Sat = RDO.Saturation...Sat....,
#            Turbidity_NTU = Turbidity..NTU....,
#            #TSS_mg_L = Total.Suspended.Solids..mg.L....,
#            Pressure_PSI = Pressure..psi....,
#            Depth_ft = Depth..ft....) %>%
#     mutate(DT = as_datetime(DT, tz = "MST")) %>%
#     mutate(DT = with_tz(DT, tzone = "MST"))
  
archery <- vusitu %>% # bind_rows(vusitu,mdt) %>%
  mutate(data = "Yes") %>%
  mutate(DT = round_date(DT, "15 minutes")) %>%
  mutate(year = lubridate::year(DT)) %>%
  padr::pad(.,group = "year") %>%
  mutate(date = as_date(substr(DT, 1, 10))) %>%
  distinct(.keep_all=TRUE) %>%
  mutate(sensor = "Archery",
         comments = case_when(DT == "2019-09-30 03:45:00" ~ "sensor deployed",
                              DT == "2020-01-06 21:45:00" ~ "rental sensor battery dead",
                              DT == "2020-01-10 08:45:00" ~ "rental sensor battery replaced",
                              DT == "2020-04-04 18:00:00" ~ "rental sensor battery dead",
                              DT == "2020-04-17 11:15:00" ~ "rental sensor battery replaced",
                              DT == "2020-04-24 23:00:00" ~ "rental sensor stopped working?",
                              DT == "2020-04-25 15:45:00" ~ "rental sensor swapped with new sensor",
                              DT == "2021-08-17 09:00:00" ~ "sensor cleaned",
                              DT == "2021-08-17 09:15:00" ~ "sensor re-deployed",
                              DT == "2021-09-19 05:15:00" ~ "sensor stopped working - overheating?",
                              DT == "2021-09-25 09:30:00" ~ "sensor removed from field",
                              DT == "2021-10-04 09:00:00" ~ "sensor re-deployed",
                              DT == "2021-10-05 07:45:00" ~ "sensor checked, then re-deployed",
                              DT == "2021-12-04 09:00:00" ~ "sensor pulled for season"))
```


Bind all datasets together:
```{r}
# sunrise_sunset <- read_csv('data/outside_data/sunrise_sunset.csv') %>%
#   mutate(date=mdy(date),
#     sunrise=as_datetime(sunrise),
#          sunset=as_datetime(sunset)) %>%
#   mutate(sunrise_mst=sunrise-hours(1)) %>%
#   mutate(sunup = ifelse(Timezone == "MDT", sunrise_mst, sunrise)) %>%
#   mutate(sunup=as_datetime(sunup)) %>%
#   mutate(sunset_mst=sunset-hours(1)) %>%
#   mutate(sundown = ifelse(Timezone == "MDT", sunset_mst, sunset)) %>%
#   mutate(sundown=as_datetime(sundown)) %>%
#   select(date,sunup,sundown)

raw <- bind_rows(rist,legacy,timberline,prospect,elc,archery) %>% write_csv('data/all_sensor_data_pre2022.csv')
```

