---
title: "Organizing raw data"
author: "ROSSyndicate"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 90
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE)
```

Load necessary packages:

```{r}
source("src/package_loader.R")
lapply(c("data.table", "tidyverse", "rvest", "readxl", "lubridate", "zoo", "padr","plotly", "feather", "RcppRoll"), package_loader)
```

# Import and collate data

Load and munge field calibration files:

```{r}
cal_files <- list.files("data/calibration_reports", pattern=".html")

cal_tabler <- function(cal_files){
  
  cal <- read_html(file.path("data/calibration_reports/", cal_files)) %>%
    html_nodes("div") %>%
    html_text() %>%
    as_tibble()
  
  rdo <- cal %>% filter(grepl("RDO", value)) %>% pull() %>% str_replace_all(., " ", "") %>% tolower()
  
  ph_orp <- cal %>% filter(grepl("pH/ORP", value)) %>% pull() %>% str_replace_all(., " ", "") %>% tolower()
  
  conductivity <- cal %>% filter(grepl("Conductivity",value)) %>% pull() %>% str_replace_all(., " ", "") %>% tolower()
  
  turbidity <- cal %>% filter(grepl("Turbidity",value)) %>% pull() %>% str_replace_all(., " ", "") %>% tolower()
  
  # Always the fifth sensor when depth is available:
  try(depth <- cal %>% .[5,] %>% pull() %>% str_replace_all(., " ", "") %>% tolower())
  
  time_mst <- paste0(str_sub(cal_files, -13, -12),":", str_sub(cal_files, -11, -10))
  
  date <- paste0(str_sub(cal_files, -22, -19),"-", str_sub(cal_files, -18, -17),"-", str_sub(cal_files, -16, -15))
  
  cal_table <- tibble(site = sub("\\_.*", "", cal_files),
                      
                      DT = ymd_hm(paste(date, time_mst, tz = "MST")),
                      
                      # Depth
                      depth_cal_date = "None",
                      depth_offset = "None",
                      depth_ref_depth = "None",
                      depth_ref_offset = "None",
                      depth_pre_psi = "None",
                      depth_post_psi = "None",
                      
                      # Dissolved Oxygen
                      rdo_slope = str_match(rdo, "slope\\s*(.*?)\\s*offset")[,2],
                      rdo_offset = str_match(rdo, "offset\\s*(.*?)\\s*mg/l")[,2],
                      rdo_100 = str_match(rdo, "premeasurement\\s*(.*?)\\s*%satpost")[,2],
                      rdo_conc = str_match(rdo, "concentration\\s*(.*?)\\s*mg/lpremeasurement")[,2],
                      rdo_temp = str_match(rdo, "temperature\\s*(.*?)\\s*°c")[,2],
                      rdo_pressure = str_match(rdo, "pressure\\s*(.*?)\\s*mbar")[,2],
                      
                      # pH
                      ph_slope_pre = str_match(ph_orp, "offset1slope\\s*(.*?)\\s*mv/ph")[,2],
                      ph_offset_pre = str_match(ph_orp, "mv/phoffset\\s*(.*?)\\s*mvslopeandoffset2")[,2],
                      ph_slope_post = str_match(ph_orp, "offset2slope\\s*(.*?)\\s*mv/ph")[,2],
                      ph_offset_post = str_match(ph_orp, paste0(ph_slope_post,"mv/phoffset\\s*(.*?)\\s*mvorporp"))[,2],
                      # Sometimes, the post value can actually be in the high 6 pH... therefore the post measurement regex matching text is conditional
                      ph_7_nice = str_sub(str_match(ph_orp, "postmeasurementph7\\s*(.*?)\\s*mvcal")[,2], 10, nchar(str_match(ph_orp, "postmeasurementph7\\s*(.*?)\\s*mvcal")[,2])),
                      ph_7_other = str_sub(str_match(ph_orp, "postmeasurementph6\\s*(.*?)\\s*mvcal")[,2], 10, nchar(str_match(ph_orp, "postmeasurementph6\\s*(.*?)\\s*mvcal")[,2])),
                      ph_7 = ifelse(is.na(ph_7_nice), ph_7_other, ph_7_nice),
                      
                      # ORP
                      #Newly encountered thing: sometimes the calibration report calls the ORP standard Zobell's, sometimes it's just called "ORP Standard":
                      orp_offset = ifelse(is.na(str_match(ph_orp, "zobell'soffset\\s*(.*?)\\s*mvtemperature")[,2]),
                                          str_match(ph_orp, "orpstandardoffset\\s*(.*?)\\s*mvtemperature")[,2],
                                          str_match(ph_orp, "zobell'soffset\\s*(.*?)\\s*mvtemperature")[,2]),
                      
                      # Conductivity
                      tds_conversion_ppm = str_sub(str_match(conductivity, "tdsconversionfactor\\s*(.*?)\\s*cellconstant")[,2], 6, nchar(str_match(conductivity, "tdsconversionfactor\\s*(.*?)\\s*cellconstant")[,2])),
                      cond_cell_constant = str_match(conductivity, "cellconstant\\s*(.*?)\\s*referencetemperature")[,2],
                      cond_pre = str_match(conductivity,paste0(str_match(conductivity,
                                                                         "premeasurementactual\\s*(.*?)\\s*specificconductivity")[,2],"specificconductivity\\s*(.*?)\\s*µs/cmpost"))[,2],
                      cond_post = str_match(conductivity,paste0(str_match(conductivity,
                                                                          "postmeasurementactual\\s*(.*?)\\s*specificconductivity")[,2],"specificconductivity\\s*(.*?)\\s*µs/cm"))[,2],
                      
                      # Turbidity
                      ntu_slope = "None",
                      ntu_offset = "None",
                      ntu_10 = "None",
                      ntu_100 = "None") %>%
    
    select(-c(ph_7_nice, ph_7_other))
  
  # Not all sondes have depth. So, we "try" to get the values.
  try(cal_table <- cal_table %>%
        mutate(
          # Depth
          depth_cal_date = str_match(depth, "lastcalibrated\\s*(.*?)\\s*calibrationdetails")[,2],
          depth_offset = str_match(depth, "zerooffset\\s*(.*?)\\s*psireferencedepth")[,2],
          depth_ref_depth = str_match(depth, "psireferencedepth\\s*(.*?)\\s*ftreferenceoffset")[,2],
          depth_ref_offset = str_match(depth, "ftreferenceoffset\\s*(.*?)\\s*psipremeasurement")[,2],
          depth_pre_psi = str_match(depth, "psipremeasurement\\s*(.*?)\\s*psipostmeasurement")[,2],
          depth_post_psi = str_match(depth, "psipostmeasurement\\s*(.*?)\\s*psi")[,2]))
  
  
  
  # Not all sondes have turbidity. So, we "try" to get the values.
  try(cal_table <- cal_table %>%
        mutate(     
          # Turbidity
          ntu_slope = str_match(turbidity, "slope\\s*(.*?)\\s*offset")[,2],
          ntu_offset = str_match(turbidity, "offset\\s*(.*?)\\s*ntu")[,2],
          ntu_10 = str_match(turbidity, "calibrationpoint1premeasurement\\s*(.*?)\\s*ntupost")[,2],
          ntu_100 = str_match(turbidity, "calibrationpoint2premeasurement\\s*(.*?)\\s*ntupost")[,2]))
  
  cal_table <- cal_table %>%
    mutate(
      #Factory Defaults
      factory_defaults = paste0(ifelse(is.na(ntu_slope), "Turbidity ", ""),
                                ifelse(is.na(rdo_slope), "RDO ", ""),
                                ifelse(is.na(ph_slope_post), "pH ", ""),
                                ifelse(is.na(orp_offset), "ORP ", ""),
                                ifelse(is.na(cond_post), "Conductivity ", ""),
                                ifelse(is.na(depth_cal_date), "Depth ", "")))
  
  cal_table
  
}

cal_table <- map_dfr(cal_files, cal_tabler) %>%
  distinct(.keep_all = TRUE) %>%
  group_by(site) %>%
  mutate(DT = round_date(DT, "15 minutes"))
# this creates a lot of errors, is it okay to ignore them all? Just make a note that these will create a lot of errors.

rm(cal_files, cal_tabler, package_loader)
```

Load field notes and define the start time as the 15 minute preceding the field time

```{r}
field_notes <- read_excel("data/sensor_field_notes.xlsx") %>%
  mutate(start_DT = ymd_hm(paste(date, start_time_mst, tzone = "MST"))) %>%
  mutate(#start_DT = with_tz(start_DT, tzone = "MST"),
         DT_round = floor_date(start_DT, "15 minutes"),
         DT_join = as.character(DT_round),
         site = tolower(site),
         season = year(DT_round)) %>%
  arrange(DT_round) %>%
  # binary version of deployed/pulled options. may need to play around with this some
  # more
  mutate(where = case_when(!is.na(sensor_pulled) & !is.na(sensor_deployed) ~ 0,
                           !is.na(sensor_pulled) & is.na(sensor_deployed) ~ 1,
                           is.na(sensor_pulled) & !is.na(sensor_deployed) ~ 0,
                           is.na(sensor_pulled) & is.na(sensor_deployed) ~ 0)) 
```

Munge field notes

```{r}
# field_notes_clean <- field_notes %>% 
#   mutate(sonde_impact = case_when(grepl('sonde', visit_comments, ignore.case = T) ~ 'y',
#                                   grepl('calib', visit_comments, ignore.case = T) ~ 'y',
#                                   sensor_pulled == 'x' ~ 'y',
#                                   sensor_deployed == 'x' ~ 'y',
#                                   grepl('yes', sensors_cleaned, ignore.case = T) ~ 'y'
#   ),
#   end_DT = case_when(sensor_pulled == 'x' ~ ymd_hm(paste0(season, '-12-31 23:59'), tz = 'MST'),
#                      sensor_deployed == 'x' ~ start_DT,
#                      TRUE ~ start_DT + minutes(15)),
#   start_DT = case_when(sensor_deployed == 'x' ~ ymd_hm(paste0(season, '-01-01 00:00'), tz = 'MST'),
#                        TRUE ~ start_DT)) %>% 
#   filter(sonde_impact == 'y', !is.na(start_DT))
```

Merge the data sets from all API pulls:

```{r}
all_data <- list.files(path = "data/api/", full.names = TRUE, pattern = "*.csv") %>%
  map_dfr(~data.table::fread(.) %>% select(-id)) %>%
  # remove overlapping API-pull data
  distinct() %>%
  # remove VuLink data
  filter(!grepl("vulink", name, ignore.case = TRUE)) %>%
  # Convert DT to MST:
  mutate(DT = as_datetime(timestamp, tz = "UTC")) %>%
  mutate(DT = with_tz(DT, tzone = "MST"),
         DT_round = round_date(DT, "15 minutes"),
         DT_join = as.character(DT_round),
         site = tolower(site)) %>%
  # Lastly, we swapped Boxelder's sonde out for Rist's late in 2022:
  mutate(site = ifelse(site == "rist" & DT > "2022-09-20" & DT < "2023-01-01", "boxelder", site))
```

### Export collated raw file

```{r}
#write_feather(all_data, paste0('data/SOME_FOLDER_FOR_POSTERITY/collated_raw_sonde_v', Sys.Date(), '.feather'))
```

# Level 1 QA-QC

### Recoding data where sonde was out of water

Filter instances in which a sonde was pulled out of field mid-season (basically a backup filter in case a sonde was pulled out of water but the log didn't get stopped)

```{r}
#this function is not working... not going to debug right now, but this is meant to do the lifting of this code block, but in an automated way... 
# 
# recode_for_maintenance = function(start, end, site) {
#   # start_DT = ymd_hm(start, tz = 'MST')
#   # end_DT = ymd_hm(end, tz = 'MST')
#   all_data %>%
#     setDT(.) %>%
#     mutate(value = if_else(ymd_hms(DT) >= ymd_hms(start) &
#                              ymd_hms(DT) <= ymd_hms(end) &
#                              site == site,
#                            NA_real_,
#                            value),
#            flag = if_else(ymd_hms(DT) >= ymd_hms(start) &
#                             ymd_hms(DT) <= ymd_hms(end) &
#                             site == site,
#                           'recoded for sensor maintenance',
#                           NA_character_))
# }

# preserving this for now.
# all_data <- all_data %>% 
#   setDT(.) %>%
#   # Rist
#   filter(!(ymd_hms(DT_round) >= ymd_hms("2021-09-11 09:00:00") & ymd_hms(DT_round) <= ymd_hms("2022-04-22 14:00:00") & site == "rist"),
#          !(ymd_hms(DT_round) <= ymd_hms("2022-05-30 09:00:00") & site == "rist"),
#          !(ymd_hms(DT_round) >= ymd_hms('2022-05-06 12:00:00') & ymd_hms(DT_round) <= ymd_hms('2022-05-09 14:30:00') & site == "rist"),
#          # Legacy
#          !(ymd_hms(DT_round) >= ymd_hms('2021-12-04 19:30:00') & ymd_hms(DT_round) < ymd_hms('2022-04-06 17:30:00') & site == "legacy"),
#          !(ymd_hms(DT_round) >= ymd_hms('2022-05-24 09:30:00') & ymd_hms(DT_round) < ymd_hms('2022-06-01 13:30:00') & site == "legacy"),
#          !(ymd_hms(DT_round) > ymd_hms('2022-07-08 14:00:00') & ymd_hms(DT_round) <= ymd_hms('2022-07-12 10:00:00') & site == "legacy"),
#          !(ymd_hms(DT_round) >= ymd_hms('2022-08-04 09:50:00') & ymd_hms(DT_round) <= ymd_hms('2022-08-25 16:15:00') & site == "legacy"),
#          !(ymd_hms(DT_round) > ymd_hms('2022-09-07 06:57:00') & ymd_hms(DT_round) <= ymd_hms('2022-09-18 07:00:00') & site == "legacy"),
#          # Timberline
#          !(ymd_hms(DT_round) > ymd_hms('2022-01-01 08:15:00') & ymd_hms(DT_round) <= ymd_hms('2022-04-06 08:15:00') & site == "timberline"),
#          # Archery
#          !(ymd_hms(DT_round) > ymd_hms('2022-10-04 15:00:00') & ymd_hms(DT_round) <= ymd_hms('2022-10-07 16:00:00') & site == "archery"))
```

### Temperature at Archery

I think we will want to develop pipelines specific for each site and parameter for
processing speed (targets?). Here I am starting a pipeline for Archery's temperature:

#### Format data

```{r}
# This chunk is giving me issues...
# What I want to happen is to keep the flag comment as a site visit from all_data
temperature_archery <- all_data %>%
  filter(parameter == "Temperature" & site == "archery") %>%
  select(-name) %>%
  distinct() %>%
  group_by(DT_round) %>%
  # I WOULD LIKE TO PRESERVE THE RAW VALS THAT WENT INTO MAKING THIS AVERAGE
  # IN A NESTED DATAFRAME VIA NEST(). IT WON'T WORK >:(
  summarize(p1 = as.numeric(mean(value, na.rm = T)), 
            diff = abs(min(value, na.rm = T) - max(value, na.rm = T)),
            n_obs = n()) %>% 
  ungroup() %>%
  arrange(DT_round) %>%
  # pad the dataset so that all 15-min timestamps are present
  pad(by = "DT_round", interval = "15 min") %>%
  mutate(DT_join = as.character(DT_round)) %>%
  full_join(filter(dplyr::select(field_notes, where, visit_comments, sensor_malfunction, DT_join, site), site == "archery"), 
            by = c('DT_join')) # adding from DT_join here adds things that are not necessarily from temperature data

temperature_archery <- cbind(select(temperature_archery, -where), data.table::setnafill(x = temperature_archery[,6], type = "locf")) %>%
  # add flag for no data times
  mutate(flag = if_else(is.na(p1) | where == 1, 'no data', NA_character_)) %>%
  dplyr::filter(is.na(flag)) %>% # what does this do?
  pad(by = "DT_round", interval = "15 min") %>%
  # ... so that we can get the proper leading/lagging values across our entire timeseries:
  mutate(front1 = lead(p1, n = 1),
         back1 = lag(p1, n = 1),
         rollavg = roll_mean(p1, n = 7, align = 'center', na.rm = F, fill = NA_real_),
         rollsd = roll_sd(p1, n = 7, align = 'center', na.rm = F, fill = NA_real_)) %>% 
  mutate(slope_ahead = abs(front1 - p1)/15,
         slope_behind = abs(p1 - back1)/15,
         # add some summary info for future us
         month = month(DT_round),
         year = year(DT_round),
         y_m = paste(year, '-', month))

ggplot(temperature_archery, aes(x = DT_round, y = p1)) + 
  geom_point() +
  labs('Raw Temperature at Archery') +
  theme_bw()
```

```{r}
# Determine each site and parameter in all_data 
sites <- unique(all_data$site)
params <- unique(all_data$parameter)
# Constructing a df to iterate over each site-parameter combination
combinations <- crossing(sites, params)

# Function to summarize site-parameter combinations
summarize_site_param <- function(site_arg, parameter_arg, api_data) {
  
  print(paste0('Trying site ', site_arg, " with parameter ", parameter_arg, "."))
  
  # filtering the data and generating results
  summary <- tryCatch({ 
    api_data %>%
    filter(site == site_arg & parameter == parameter_arg) %>% 
    select(-name) %>%
    distinct() %>%
    group_by(DT_round, site, parameter) %>%
    # to do: preserve values used with nest()
    summarize(mean = as.numeric(mean(value, na.rm = T)),
              diff = abs(min(value, na.rm = T) - max(value, na.rm = T)),
              n_obs = n()) %>%
    ungroup() %>%
    arrange(DT_round) %>%
    # pad the dataset so that all 15-min timestamps are present
    pad(by = "DT_round", interval = "15 min") %>%
    mutate(DT_join = as.character(DT_round),
           site = site_arg,
           parameter = parameter_arg) %>% 
    full_join(filter(dplyr::select(field_notes, where, visit_comments, sensor_malfunction, DT_join, site)),
                 by = c('DT_join', 'site'))
    },
    error = function(err) {
      # error message
      cat("An error occurred with site ", site_arg, " parameter ", parameter_arg, ".\n")
      cat("Error message:", conditionMessage(err), "\n")
      flush.console() # Immediately print the error messages
      NULL  # Return NULL in case of an error
    })
  
  # Determine if the sonde was deployed or not.
  try({
    summary <- cbind(select(summary, -where), data.table::setnafill(x = summary[,8], type = "locf")) 
  })
    
    return(summary)
}

# Make a list of the summarized data
all_data_summary_list <- map2(combinations$sites, 
                         combinations$params, 
                         summarize_site_param,
                         api_data = all_data)

# Remove null values from list
all_data_summary_list <- all_data_summary_list %>% 
  keep(~ !is.null(.))

# Bind rows for each df in list
all_data_summary_df <- bind_rows(all_data_summary_list)
```


#### Set thresholds

```{r}
# value range
temp_max = 30
temp_min = 0

# slope threshold
slope_thresh = 1/15
```

#### Add the flags

```{r}
# Add flag column to all_data_summary_df and begin flagging data
all_data_summary_df <- all_data_summary_df %>%
  mutate(flag = if_else(is.na(mean) | where == 1, 'no data', NA_character_)) %>% 
  mutate(flag = if_else((!is.na(visit_comments)),
                if_else(is.na(flag), "Site visit", 
                                paste(flag, "Site visit", sep = "; ")),
                        flag))
```

Data out of range:

```{r}
# flag for values out of acceptable range
temperature_archery <- temperature_archery %>%
  mutate(flag = if_else(p1 >= temp_max | p1 <= temp_min, "Out of bounds", flag),
         p1 = if_else(p1 >= temp_max | p1 <= temp_min, NA_real_, p1))

temperature_archery <- temperature_archery %>%
  mutate(flag = if_else(p1 >= temp_max | p1 <= temp_min,
    # true
    ifelse(is.na(flag), "Out of bounds",
           paste(flag, "Out of bounds", sep = "; ")),
    # false
    flag),
         p1 = if_else(p1 >= temp_max | p1 <= temp_min, NA_real_, p1))

# Here is where I would need to add the paste so that it doesn't replace what is already in the flag column completely
```

Site visits: 

```{r site visits}
# flag the start time of a site visit
temperature_archery <- temperature_archery %>%
  mutate(flag = if_else((!is.na(visit_comments)),
                if_else(is.na(flag), "Site visit",
                                paste(flag, "Site visit", sep = "; ")),
                        flag))
```

For wonky data next to each other (defined by roll sd) - here we make some seasonal summaries to help with this:

```{r}
temperature_summary <- temperature_archery %>% 
  group_by(y_m) %>% 
  summarise(ym_sd = sd(p1, na.rm = T))

# flag data points that are outside the range of 3 sds from the mean of previous + future 3 data points:
temperature_archery <- temperature_archery %>%
  left_join(temperature_summary) %>% 
  # Do we want to play around with using the monthly sd instead of the rolling sd?
    mutate(flag = if_else((p1 <= rollavg - (3 * ym_sd) | p1 >= rollavg + (3 * ym_sd)), 
                if_else(is.na(flag), "Outside SD range",
                                paste(flag, "Outside sd range", sep = "; ")),
                        flag))
```

For data that repeats:

```{r}
# flag data that repeat across time:
temperature_archery <- temperature_archery %>% 
  mutate(flag = if_else((p1 == front1 | p1 == back1), 
                if_else(is.na(flag), "Repeated value",
                                paste(flag, "Repeated value", sep = "; ")),
                        flag))
```

For instances where change in a 15m period is > 1degC

```{r}
# flag data where change in a 15m period is > 1degC
temperature_archery <- temperature_archery %>% 
  mutate(flag = if_else(slope_ahead >= slope_thresh | slope_behind >= slope_thresh, 
                        if_else(is.na(flag),
                                "Slope exceedance",
                                paste(flag, "Slope exceedance", sep = "; ")),
                        flag)) 
```

#### Visualize the flags

```{r}
# Current vis:
ggplot() +
  geom_point(data = filter(temperature_archery, is.na(flag)), 
             aes(x=DT_round, y = p1)) +
  geom_point(data = filter(temperature_archery, !is.na(flag)), 
             aes(x=DT_round, y = p1, color = flag)) +
  theme_bw() +
  theme(legend.position = 'bottom') 
```
