---
title: "drift_correction_2024"
output: html_document
author: "Juan De La Torre"
---

The objective of this notebook is to manually correct the drift in the turbidity
and FDOM sensors for 2024. 

# Environment set up

```{r}
knitr::opts_chunk$set(
  eval = FALSE,
  echo = TRUE
)
```

```{r}
#Installing and loading all packages
invisible(
  lapply(c(
    "tidyverse", # Data manipulation
    "lubridate", # Date-Time Manipulation
    "readxl", # Reading excel files
    "here", # Easy, cross platform file referencing
    "ggplot2", # Plotting libraries
    "patchwork",
    "ggpubr",
    "plotly",
    "devtools", # For downloading GitHub packages
    "remotes",
    "arrow", # Reading parquet files
    "groupdata2",
    "ross.wq.tools" # In house functions
  ),
  function(x) {
    if (x %in% installed.packages()) {
      suppressMessages({
        library(x, character.only = TRUE)
      })
    } else {
      suppressMessages({
        install.packages(x)
        library(x, character.only = TRUE)
      })
    }
  })
)
```

## Functions from ross.wq.tools

Local copies of `ross.wq.tools` functions used in this workflow. The version of
`cal_exp_one_point_drift` below extends the package version with an `exp_coef`
parameter so that a fitted `k` can be supplied for exponential corrections.

```{r}
#' @title Add a column to a data frame if it does not exist
#' @param df Data frame to modify
#' @param column_name Name of the column to add
#' @param default_value Fill value for the new column (default NA)

add_column_if_not_exists <- function(df, column_name, default_value = NA) {
  if (!column_name %in% colnames(df)) {
    df <- df %>% dplyr::mutate(!!sym(column_name) := default_value)
  }
  return(df)
}
```

```{r}
#' @title Temporal Weight Factor Calculation
#' @description Adds a weight column ranging from 0 (first timestamp) to 1
#'   (last timestamp) based on elapsed time. Used to scale drift corrections
#'   proportionally across a calibration window.
#' @param df Data frame containing the datetime column
#' @param dt_col Name of the POSIXct datetime column
#' @param wt_col Name to give the computed weight column (default "wt")

cal_wt <- function(df, dt_col, wt_col = "wt"){

  if(!dt_col %in% colnames(df)){
    stop(paste0("The specified dt_col '", dt_col, "' is not present in the dataframe."))
  }

  first_dt <- min(df[[dt_col]])
  last_dt  <- max(df[[dt_col]])
  tot_time <- as.numeric(difftime(last_dt, first_dt, units = "mins"))

  df <- df %>%
    dplyr::mutate(!!wt_col := as.numeric(difftime(.data[[dt_col]], first_dt, units = "mins")) / tot_time)

  return(df)
}
```

```{r}
#' @title Exponential One Point Drift Calibration (local — adds exp_coef param)
#'
#' @param df Tibble containing sensor data bounded by two calibrations
#' @param lm_trans_col Column name containing linearly transformed data
#' @param pre_col Column name for pre-cleaning measurement
#' @param post_col Column name for post-cleaning measurement
#' @param wt_col Column name containing temporal weight parameters
#' @param drift_type Shape of the weight curve applied to the correction:
#'   - "linear": weight increases linearly from 0 to 1 (default)
#'   - "exponential": weight follows (exp(k*wt)-1)/(exp(k)-1); convex, correction
#'     accelerates toward the end. NOTE: not used by the current workflow —
#'     "exponential" decisions in the decision sheet route to
#'     exponential_correction_fxn, which applies "log" (not this branch).
#'   - "log": weight follows log(1 + wt*(exp(k)-1))/k; concave, correction
#'     accumulates faster early and decelerates toward the end
#'   - "uniform": constant weight of 1 applied to every observation (full correction
#'     applied uniformly across the window)
#'   - "fitted_linear": OLS line is fit to the observed values in the window; the
#'     slope b is used in a hyperbolic multiplicative correction anchored at post_val:
#'     corrected(t) = observed(t) * post_val / (post_val + b * wt(t)).
#'     Head (wt=0) is always untouched; tail ratio is data-informed via b.
#'     Always positive. Falls back to linear if fewer than 3 non-NA observations.
#'     exp_coef is not used for this drift_type.
#' @param correction_type "additive" (default) or "multiplicative"
#' @param exp_coef Rate parameter k for "exponential" and "log" drift types
#'   (default 1, equivalent to linear). Supply a fitted k from exp_k().

cal_exp_one_point_drift <- function(df, lm_trans_col, pre_col, post_col, wt_col,
                                    drift_type = "linear", correction_type = "additive",
                                    exp_coef = 1){

  transformed_col <- paste0(str_split_1(lm_trans_col, "_")[1], "_drift_trans")

  pre_drift_back_calibration  <- df[[pre_col]][[nrow(df)]]
  post_drift_back_calibration <- df[[post_col]][[nrow(df)]]

  if (is.na(pre_drift_back_calibration) || is.na(post_drift_back_calibration)) {
    df <- df %>%
      dplyr::mutate(!!transformed_col := NA_integer_)
    return(df)
  }

  if (drift_type == "fitted_linear") {
    fit_data <- df %>% dplyr::filter(!is.na(.data[[lm_trans_col]]))
    if (nrow(fit_data) >= 3) {
      fit     <- lm(as.formula(paste0("`", lm_trans_col, "` ~ `", wt_col, "`")), data = fit_data)
      b_slope <- coef(fit)[[wt_col]]
      # Hyperbolic multiplicative correction anchored at post_val.
      # corrected(t) = observed(t) * post_val / (post_val + b * wt(t))
      # At wt=0: ratio = 1 (head untouched).
      # At wt=1: ratio = post_val / (post_val + b), data-informed tail.
      # Always positive. Shape determined by OLS slope b.
      df <- df %>%
        dplyr::mutate(!!transformed_col := .data[[lm_trans_col]] *
                        (post_drift_back_calibration /
                           (post_drift_back_calibration + b_slope * .data[[wt_col]])))
      return(df)
    }
    # fall back to linear if too few observations
  }

  if (drift_type == "exponential") {
    df <- df %>%
      dplyr::mutate(wt_exp = (exp(exp_coef * .data[[wt_col]]) - 1) / (exp(exp_coef) - 1))
    wt_col_to_use <- "wt_exp"
  } else if (drift_type == "log") {
    df <- df %>%
      dplyr::mutate(wt_log = log(1 + .data[[wt_col]] * (exp(exp_coef) - 1)) / exp_coef)
    wt_col_to_use <- "wt_log"
  } else if (drift_type == "uniform") {
    df <- df %>%
      dplyr::mutate(wt_uniform = 1)
    wt_col_to_use <- "wt_uniform"
  } else {
    wt_col_to_use <- wt_col
  }

  if (correction_type == "multiplicative") {
    drift_ratio <- post_drift_back_calibration / pre_drift_back_calibration
    df <- df %>%
      dplyr::mutate(!!transformed_col := .data[[lm_trans_col]] * (1 - .data[[wt_col_to_use]] + .data[[wt_col_to_use]] * drift_ratio))
  } else {
    standard_delta <- post_drift_back_calibration - pre_drift_back_calibration
    df <- df %>%
      dplyr::mutate(!!transformed_col := .data[[lm_trans_col]] + (.data[[wt_col_to_use]] * standard_delta))
  }

  return(df)
}
```

```{r}
#' @title Low-pass filter for turbidity noise reduction
#' @description Applies a 5-point binomial kernel three times in succession to
#'   smooth optical noise. For non-Turbidity parameters, copies correction_col
#'   directly into smoothed_mean without filtering.
#' @param df Data frame containing the sensor data; must have a "parameter" column
#' @param correction_col Column to smooth (default "mean_drift_trans")

low_pass_filter <- function(df, correction_col = "mean_drift_trans") {

  if (unique(df$parameter) == "Turbidity") {

    binomial_kernel <- function(int_vec) {
      kernel <- c(1, 4, 6, 4, 1)
      x <- sum(int_vec * kernel) / 16
      return(x)
    }

    df <- df %>%
      add_column_if_not_exists(column_name = "smoothed_mean") %>%
      mutate(
        smoothed_mean = if_else(is.na(smoothed_mean),
                                data.table::frollapply(!!sym(correction_col), N = 5, FUN = binomial_kernel,
                                                       fill = NA, align = "center"),
                                smoothed_mean),
        smoothed_mean = if_else(is.na(smoothed_mean),
                                data.table::frollapply(smoothed_mean, N = 5, FUN = binomial_kernel,
                                                       fill = NA, align = "center"),
                                smoothed_mean),
        smoothed_mean = if_else(is.na(smoothed_mean),
                                data.table::frollapply(smoothed_mean, N = 5, FUN = binomial_kernel,
                                                       fill = NA, align = "center"),
                                smoothed_mean)
      )

    return(df)
  } else {
    df <- df %>% mutate(smoothed_mean = .data[[correction_col]])
    return(df)
  }
}
```

```{r}
#' @title Interpolate missing data within a maximum gap
#' @description Fills NA values in the value column using linear or spline
#'   interpolation, up to max_gap consecutive missing observations. Warns if
#'   timestamps are not equally spaced (expects padr::pad() to have been called).
#' @param df Data frame containing sensor data
#' @param site_col Name of the site column (default "site")
#' @param parameter_col Name of the parameter column (default "parameter")
#' @param dt_col Name of the POSIXct datetime column (default "DT_round")
#' @param value_col Column containing values to interpolate (default "smoothed_mean")
#' @param max_gap Maximum number of consecutive NA observations to fill (default 4)
#' @param new_value_col Name for the output column of interpolated values (default "mean_filled")
#' @param method "linear" (default) or "spline"

apply_interpolation_missing_data <- function(df, site_col = "site", parameter_col = "parameter",
                                             dt_col = "DT_round", value_col = "smoothed_mean",
                                             max_gap = 4, new_value_col = "mean_filled",
                                             method = "linear") {

  dt_vals <- df[[dt_col]]
  if (!lubridate::is.POSIXt(dt_vals)) {
    stop("Error: The datetime column must be POSIXct/POSIXt.")
  }

  pad_check <- df %>%
    dplyr::group_by(dplyr::across(all_of(c(site_col, parameter_col)))) %>%
    dplyr::group_walk(~ {
      dt_vals      <- sort(unique(.x[[dt_col]]))
      dt_diffs     <- diff(dt_vals)
      unique_diffs <- unique(dt_diffs)
      if (length(unique_diffs) > 1) {
        warning(
          paste0("Error: Datetime column is not equally spaced for site = ",
                 unique(.y[[site_col]]), ", parameter = ", unique(.y[[parameter_col]]),
                 ". Please pad with padr::pad() first.")
        )
      }
    })

  `%nin%` = Negate(`%in%`)

  if(method %nin% c("spline", "linear")){
    stop("method must be either 'spline' or 'linear'")
  }

  if(method == "linear") {
    return(
      df %>%
        arrange(!!sym(site_col), !!sym(parameter_col), !!sym(dt_col)) %>%
        group_by(!!sym(site_col), !!sym(parameter_col)) %>%
        mutate(
          !!sym(new_value_col) := zoo::na.approx(
            x      = as.numeric(!!sym(dt_col)),
            object = !!sym(value_col),
            maxgap = max_gap,
            na.rm  = FALSE
          )
        ) %>%
        ungroup()
    )
  }

  if(method == "spline"){
    return(
      df %>%
        arrange(!!sym(site_col), !!sym(parameter_col), !!sym(dt_col)) %>%
        group_by(!!sym(site_col), !!sym(parameter_col)) %>%
        mutate(
          !!sym(new_value_col) := zoo::na.spline(
            x      = as.numeric(!!sym(dt_col)),
            object = !!sym(value_col),
            maxgap = max_gap,
            na.rm  = FALSE
          )
        ) %>%
        ungroup()
    )
  }
}
```

# Plotting functions

```{r}
# Template to find downstream and upstream data
site_order <- list(
  clp = c("joei", "cbri", "chd", "pfal", "pbr", "pman", "pbd", "bellvue",
          "salyer", "udall", "riverbend", "cottonwood", "elc", "archery", "riverbluffs"),
  springcreek = c("riverbend", "springcreek", "cottonwood"),
  boxcreek = c("elc", "boxcreek", "archery"),
  sfm = c("sfm"),
  mtn_campus = c("mtn_campus")
)
```

```{r}
#' @title Plot final corrected data with correction type highlighted
#' @description Plots the corrected time series coloured by how each segment
#'   was treated: raw (no correction), linear, exponential (log), uniform,
#'   fitted_linear, or unflagged. Upstream/downstream neighbours are shown in
#'   grey for network context.
#' @param df Corrected data frame for a single site-parameter; must have
#'   DT_round, mean_analysis, smoothed_mean, correction_type, and pre_post_source
#' @param data_list Named list of all site-parameter data frames (used to look up
#'   upstream/downstream neighbours)
#' @param site_order_template Named list defining stream network order (e.g. site_order)

plot_final_corrections <- function(df, data_list, site_order_template) {

  site_name      <- unique(na.omit(df$site))
  parameter_name <- unique(na.omit(df$parameter))
  plot_title     <- paste(site_name, parameter_name, "- Final Corrections")

  # Upstream / downstream neighbours
  matching_networks <- keep(site_order_template, ~ site_name %in% .x)

  above_df <- NULL
  below_df <- NULL

  if (length(matching_networks) > 0) {
    if (site_name %in% names(matching_networks)) {
      sites_order <- matching_networks[[site_name]]
    } else {
      sites_order <- matching_networks[[1]]
    }

    site_index <- which(sites_order == site_name)

    if (site_index > 1) {
      above_key <- paste0(sites_order[site_index - 1], "-", parameter_name)
      if (above_key %in% names(data_list)) above_df <- data_list[[above_key]]
    }

    if (site_index < length(sites_order)) {
      below_key <- paste0(sites_order[site_index + 1], "-", parameter_name)
      if (below_key %in% names(data_list)) below_df <- data_list[[below_key]]
    }
  }

  # correction_type is stamped by the orchestrator — use it directly
  plot_df <- df

  # Build plot — neighbours first so they sit behind the main traces
  p <- plot_ly()

  if (!is.null(above_df)) {
    p <- p %>%
      add_trace(data = above_df,
                x = ~DT_round, y = ~mean_analysis,
                type = "scatter", mode = "markers",
                marker = list(color = "rgba(150, 150, 150, 0.25)", symbol = "triangle-up", size = 7),
                name = paste0(unique(above_df$site), " (above)"),
                legendgroup = "above")
  }

  if (!is.null(below_df)) {
    p <- p %>%
      add_trace(data = below_df,
                x = ~DT_round, y = ~mean_analysis,
                type = "scatter", mode = "markers",
                marker = list(color = "rgba(150, 150, 150, 0.25)", symbol = "triangle-down", size = 7),
                name = paste0(unique(below_df$site), " (below)"),
                legendgroup = "below")
  }

  # Raw mean_analysis in red with light alpha — visible behind everything as the
  # "corrected from" reference for all points
  p <- p %>%
    add_trace(data = plot_df,
              x = ~DT_round, y = ~mean_analysis,
              type = "scatter", mode = "markers",
              marker = list(color = "rgba(255, 0, 0, 0.15)", size = 4),
              name = "raw")

  # Final smoothed/interpolated values for uncorrected rows in black
  raw_df <- plot_df %>% filter(correction_type == "raw")

  p <- p %>%
    add_trace(data = raw_df,
              x = ~DT_round, y = ~smoothed_mean,
              type = "scatter", mode = "markers",
              marker = list(color = "black", size = 4),
              name = "no correction")

  # Corrected values overlaid in colour — one trace per type for legend entries,
  # with per-point hover showing the range strategy (A, B, C, etc.)
  type_colors <- c(
    "unflagged"      = "seagreen",
    "linear"         = "steelblue",
    "exponential"    = "mediumpurple",
    "uniform"        = "darkorange",
    "fitted_linear"  = "firebrick"
  )

  corrected_df <- plot_df %>%
    filter(correction_type != "raw") %>%
    mutate(hover_text = paste0(
      "Type: ", correction_type,
      if_else(is.na(pre_post_source), "", paste0("<br>Range strategy: ", pre_post_source))
    ))

  for (ct in intersect(names(type_colors), unique(corrected_df$correction_type))) {
    ct_df <- corrected_df %>% filter(correction_type == ct)
    p <- p %>%
      add_trace(data = ct_df,
                x = ~DT_round, y = ~smoothed_mean,
                type = "scatter", mode = "markers",
                marker = list(color = type_colors[[ct]], size = 4),
                name = ct,
                text = ~hover_text,
                hovertemplate = "%{x}<br>%{y:.2f}<br>%{text}<extra></extra>")
  }

  p %>%
    layout(title = plot_title,
           xaxis = list(title = "Date"),
           yaxis = list(title = parameter_name))
}
```

# Correction functions

```{r}
#' @title Boundary averages
#' @description Computes the pre-cleaning (drifted) and post-cleaning (clean)
#'   boundary values that bracket each drift correction window. Three independent
#'   sources are tried and the one with greater correction potential is returned.
#'
#'   **Option A — time-window average from mean_analysis:**
#'   `from_val` is the mean of all non-NA `mean_analysis` readings in the hour
#'   leading up to (and including) `end_dt`; it represents the drifted sensor
#'   state just before the field crew cleaned the sensor.
#'   `to_val` is the mean of the first four non-NA `mean_analysis` readings
#'   strictly after `end_dt`; it represents the clean sensor state after the
#'   visit.
#'
#'   **Option B — field note pre/post measurements from mWater:**
#'   `from_val` is the most recent `turb_pre_clean` (or `fdom_pre_clean`) value
#'   at or before `end_dt` — the field crew's recorded reading of the fouled
#'   sensor before cleaning.
#'   `to_val` is the most recent `turb_post_clean` (or `fdom_post_clean`) value
#'   at or before `end_dt` — the field crew's recorded reading after cleaning.
#'
#'   These columns are filled forward by the data prep step so the most recent
#'   field note is always available on the visit row.
#'
#'   **Option C — upstream/downstream network neighbours:**
#'   Used when the post-cleaning gap exceeds `gap_threshold_mins` (i.e. Option A's
#'   `to_val` cannot be reliably computed because clean data is unavailable soon
#'   after the visit). Requires `data_list` and `site_order_template`.
#'   `from_val` is the mean of the last four non-NA `mean_analysis` readings at
#'   the target site up to `end_dt`. `to_val` is the mean of the neighbouring
#'   site(s) at those same timestamps. For Turbidity, Option C is rejected if the
#'   upstream and downstream neighbours disagree by more than 10 NTU, since
#'   conditions are too different to use as a shared anchor.
#'
#'   **Selection logic:**
#'   A pair is considered valid only when both endpoints are finite (guards
#'   against NA, NaN, and Inf). Valid pairs are then checked for two additional
#'   criteria before being used:
#'
#'   1. *Direction constraint* — biofouling pushes sensors in a known direction,
#'      so a pair must correct in the physically expected direction or it is
#'      rejected outright, no matter how large its difference is:
#'      - **FDOM**: biofouling coats the optical window and causes the sensor to
#'        read *lower* than actual (downward drift). The correction must therefore
#'        go *upward*, meaning `to_val >= from_val`.
#'      - **Turbidity**: biofouling scatters additional light and causes the
#'        sensor to read *higher* than actual (upward drift). The correction must
#'        therefore go *downward*, meaning `from_val >= to_val`.
#'   2. *Magnitude constraint* — a difference >= 1000 NTU/RFU almost certainly
#'      reflects a data error; such pairs are rejected.
#'
#'   When the post-cleaning gap exceeds `gap_threshold_mins` and Option C passes
#'   all checks, Option C is returned immediately (source = "C").
#'   Otherwise, the valid option with the largest `|from - to|` is returned,
#'   with priority order A > C > B on ties.
#'   If no option passes all checks, the function falls back: if Option A has
#'   both finite endpoints it is returned as-is (source = "A_fallback"); otherwise
#'   the best finite endpoint from each source is mixed (source = "mixed_fallback").
#' @param sensor_df_arg Data frame for a single site-parameter containing
#'   DT_round, mean_analysis, and optionally turb/fdom pre/post clean columns
#' @param end_dt POSIXct timestamp of the field visit (end of the drift window)
#' @param data_list Named list of all site-parameter data frames; required for
#'   Option C (default NULL disables Option C)
#' @param site_order_template Named list defining stream network order; required
#'   for Option C (default NULL disables Option C)
#' @param gap_threshold_mins Minutes after end_dt with no clean data before
#'   Option C is preferred over A (default 120)

cal_range_values <- function(sensor_df_arg, end_dt,
                             data_list = NULL, site_order_template = NULL,
                             gap_threshold_mins = 120) {

  # --- Option A: mean_analysis based ---
  from_val_a <- sensor_df_arg %>%
    filter(
      !is.na(mean_analysis),
      between(DT_round, end_dt - hours(1), end_dt)
    ) %>%
    pull(mean_analysis) %>%
    mean()

  to_val_a <- sensor_df_arg %>%
    filter(
      !is.na(mean_analysis),
      DT_round > end_dt
    ) %>%
    slice_head(n = 4) %>%
    pull(mean_analysis) %>%
    mean()

  # --- Option B: field note pre/post columns ---
  param    <- unique(sensor_df_arg$parameter)[[1]]
  is_turb  <- stringr::str_detect(param, stringr::regex("turb", ignore_case = TRUE))
  pre_col  <- if (is_turb) "turb_pre_clean"  else "fdom_pre_clean"
  post_col <- if (is_turb) "turb_post_clean" else "fdom_post_clean"

  from_val_b <- NA_real_
  to_val_b   <- NA_real_

  if (pre_col %in% colnames(sensor_df_arg)) {
    from_val_b <- sensor_df_arg %>%
      filter(DT_round <= end_dt, !is.na(.data[[pre_col]])) %>%
      slice_tail(n = 1) %>%
      pull(pre_col) %>%
      { if (length(.) == 0) NA_real_ else .[[1]] }
  }

  if (post_col %in% colnames(sensor_df_arg)) {
    to_val_b <- sensor_df_arg %>%
      filter(DT_round <= end_dt, !is.na(.data[[post_col]])) %>%
      slice_tail(n = 1) %>%
      pull(post_col) %>%
      { if (length(.) == 0) NA_real_ else .[[1]] }
  }

  # --- Option C: upstream/downstream network neighbors at same timestamps ---
  from_val_c <- NA_real_
  to_val_c   <- NA_real_

  if (!is.null(data_list) && !is.null(site_order_template)) {
    site_name_lookup  <- stringr::str_remove(unique(sensor_df_arg$site)[[1]], "_virridy$")
    matching_networks <- purrr::keep(site_order_template, ~ site_name_lookup %in% .x)

    if (length(matching_networks) > 0) {
      sites_order <- matching_networks[[1]]
      site_index  <- which(sites_order == site_name_lookup)

      last4_dts <- sensor_df_arg %>%
        filter(!is.na(mean_analysis), DT_round <= end_dt) %>%
        slice_tail(n = 4) %>%
        pull(DT_round)

      if (length(last4_dts) > 0) {
        from_val_c <- sensor_df_arg %>%
          filter(DT_round %in% last4_dts) %>%
          pull(mean_analysis) %>%
          mean(na.rm = TRUE)

        above_mean <- NA_real_
        below_mean <- NA_real_

        if (site_index > 1) {
          above_key <- paste0(sites_order[site_index - 1], "-", param)
          if (above_key %in% names(data_list)) {
            vals <- data_list[[above_key]] %>%
              filter(DT_round %in% last4_dts) %>%
              pull(mean_analysis)
            if (any(!is.na(vals))) above_mean <- mean(vals, na.rm = TRUE)
          }
        }

        if (site_index < length(sites_order)) {
          below_key <- paste0(sites_order[site_index + 1], "-", param)
          if (below_key %in% names(data_list)) {
            vals <- data_list[[below_key]] %>%
              filter(DT_round %in% last4_dts) %>%
              pull(mean_analysis)
            if (any(!is.na(vals))) below_mean <- mean(vals, na.rm = TRUE)
          }
        }

        neighbor_means <- c(above_mean, below_mean)
        neighbor_means <- neighbor_means[is.finite(neighbor_means)]

        # For Turbidity: reject Option C if upstream and downstream means disagree
        # by more than 10 NTU — conditions are too different to use as a shared anchor
        turb_neighbor_disagree <- is_turb &&
          is.finite(above_mean) && is.finite(below_mean) &&
          abs(above_mean - below_mean) > 10

        if (!turb_neighbor_disagree && length(neighbor_means) > 0) {
          to_val_c <- mean(neighbor_means)
        }
      }
    }
  }

  # --- Post-cleaning gap: time from end_dt to first non-NA reading after ---
  first_post_dt <- sensor_df_arg %>%
    filter(!is.na(mean_analysis), DT_round > end_dt) %>%
    slice_head(n = 1) %>%
    pull(DT_round)

  gap_mins <- if (length(first_post_dt) == 1)
    as.numeric(difftime(first_post_dt, end_dt, units = "mins"))
  else
    Inf

  large_gap <- gap_mins > gap_threshold_mins

  # --- Select the best option ---
  a_valid <- is.finite(from_val_a) && is.finite(to_val_a)
  b_valid <- is.finite(from_val_b) && is.finite(to_val_b)
  c_valid <- is.finite(from_val_c) && is.finite(to_val_c)

  direction_ok <- function(from, to) {
    diff <- abs(from - to)
    direction <- if (!is_turb) to >= from else from >= to
    diff < 1000 && direction
  }

  a_ok <- a_valid && direction_ok(from_val_a, to_val_a)
  b_ok <- b_valid && direction_ok(from_val_b, to_val_b)
  c_ok <- c_valid && direction_ok(from_val_c, to_val_c)

  # When the post-cleaning gap is large and Option C is valid, prefer C outright
  if (large_gap && c_ok) {
    return(list(from = from_val_c, to = to_val_c, source = "C"))
  }

  # Otherwise pick the valid option with the largest correction magnitude (A > C > B on ties)
  candidates <- list(
    a = list(from = from_val_a, to = to_val_a, ok = a_ok),
    c = list(from = from_val_c, to = to_val_c, ok = c_ok),
    b = list(from = from_val_b, to = to_val_b, ok = b_ok)
  )

  passing <- Filter(function(x) x$ok, candidates)

  if (length(passing) > 0) {
    best_idx <- which.max(sapply(passing, function(x) abs(x$from - x$to)))
    best     <- passing[[best_idx]]
    return(list(from = best$from, to = best$to, source = toupper(names(passing)[best_idx])))
  }

  # Fall back: mix best finite endpoints from A
  if (a_valid) return(list(from = from_val_a, to = to_val_a, source = "A_fallback"))

  from_val <- if (is.finite(from_val_a)) from_val_a else from_val_b
  to_val   <- if (is.finite(to_val_a))   to_val_a   else to_val_b
  return(list(from = from_val, to = to_val, source = "mixed_fallback"))
}
```

```{r}
#' @title Fit exponential rate parameter k for drift correction
#' @description Normalizes the observed sensor values in the drift window to a
#'   0-1 fraction of the total drift, then fits the exponential weight formula
#'   to find the k that best describes how drift accumulated over time. Falls
#'   back to k = 1 (linear-equivalent) when pre_val == post_val (no drift to
#'   fit), when fewer than 3 non-NA observations are available, or when nls
#'   fitting fails.
#' @param df Prepped drift data frame with columns: wt, pre_val, post_val, and
#'   the column named by correction_col
#' @param correction_col Column name of observed sensor values to fit against
#'   (default "mean_analysis")

exp_k <- function(df, correction_col = "mean_analysis") {

  pre_val  <- df[["pre_val"]][[1]]
  post_val <- df[["post_val"]][[nrow(df)]]

  if (is.na(pre_val) || is.na(post_val) || pre_val == post_val) return(1)

  fit_data <- df %>%
    filter(!is.na(.data[[correction_col]])) %>%
    mutate(observed_frac = (.data[[correction_col]] - post_val) / (pre_val - post_val)) %>%
    filter(is.finite(observed_frac)) %>%
    select(wt, observed_frac)

  if (nrow(fit_data) < 3) return(1)

  k <- tryCatch({
    fit <- nls(
      observed_frac ~ (exp(k * wt) - 1) / (exp(k) - 1),
      data    = fit_data,
      start   = list(k = 1),
      control = nls.control(maxiter = 100, warnOnly = TRUE)
    )
    coef(fit)[["k"]]
  }, error = function(e) {
    message("exp_k: nls fit failed, defaulting to k = 1. Error: ", conditionMessage(e))
    1
  })

  return(k)
}
```


```{r}
#' @title Unflagging function
#' @description Removes "drift" from user_flag and sets drift = FALSE for all
#'   rows falling within the time windows defined in decision_df_arg. Does not
#'   alter mean_analysis or any corrected value columns.
#' @param decision_df_arg Data frame of unflag decisions filtered to a single
#'   site-parameter; must have start_dt and end_dt columns
#' @param sensor_df_arg Data frame for a single site-parameter; must have
#'   DT_round, user_flag, and drift columns

unflag_fxn <- function(decision_df_arg, sensor_df_arg) {

  if (nrow(decision_df_arg) == 0) return(sensor_df_arg)

  in_unflag_window <- map2(
    .x = pull(decision_df_arg, start_dt),
    .y = pull(decision_df_arg, end_dt),
    function(start, end) between(sensor_df_arg$DT_round, start, end)
  ) %>%
    reduce(`|`)

  remove_drift_token <- function(flag_str) {
    if (is.na(flag_str)) return(NA_character_)
    tokens <- str_split(flag_str, ";")[[1]] %>%
      str_replace_all("\\n", " ") %>%
      str_trim()
    cleaned <- tokens[tokens != "drift" & tokens != ""]
    if (length(cleaned) == 0) return(NA_character_)
    paste(cleaned, collapse = ";")
  }

  corrected_df <- sensor_df_arg %>%
    mutate(
      user_flag = if_else(
        in_unflag_window,
        map_chr(user_flag, remove_drift_token),
        user_flag
      ),
      drift = if_else(in_unflag_window, FALSE, drift)
    )

  return(corrected_df)
}
```

```{r}
#' @title General single-point drift correction function
#' @description Applies a single-point drift correction across each calibration
#'   window defined in decision_df_arg. The weight curve shape (linear, uniform,
#'   fitted_linear) is read from the arg_drift_type column of decision_df_arg and
#'   passed through to cal_exp_one_point_drift. Used directly for linear, uniform,
#'   and fitted_linear correction types; exponential corrections use
#'   exponential_correction_fxn instead (which also fits k via exp_k()).
#' @param decision_df_arg Data frame of correction decisions for a single
#'   site-parameter; must have start_dt, end_dt, arg_drift_type, and
#'   arg_correction_type columns
#' @param sensor_df_arg Data frame for a single site-parameter containing
#'   DT_round, mean_analysis, and field note pre/post columns
#' @param correction_col Column to apply the correction to (default "mean_analysis")
#' @param data_list Named list of all site-parameter data frames passed to
#'   cal_range_values for Option C (default NULL)
#' @param site_order_template Network order list passed to cal_range_values for
#'   Option C (default NULL)
#' @param gap_threshold_mins Passed to cal_range_values (default 120)

linear_correction_fxn <- function(decision_df_arg, sensor_df_arg, correction_col = "mean_analysis",
                                  data_list = NULL, site_order_template = NULL,
                                  gap_threshold_mins = 120){

  start_dt_values <- pull(decision_df_arg, start_dt)
  end_dt_values   <- pull(decision_df_arg, end_dt)

  data_to_correct <- map2(
    .x = start_dt_values,
    .y = end_dt_values,
    function(start, end) {
      sensor_df_arg %>%
        filter(between(DT_round, start, end))
    }
  )

  correction_values <- map(
    .x = end_dt_values,
    function(end_dt){
      cal_range_values(sensor_df_arg = sensor_df_arg, end_dt = end_dt,
                       data_list = data_list, site_order_template = site_order_template,
                       gap_threshold_mins = gap_threshold_mins)
    }
  )

  drift_type_values      <- pull(decision_df_arg, arg_drift_type)
  correction_type_values <- pull(decision_df_arg, arg_correction_type)

  corrected_data <- pmap(
    .l = list(data_to_correct, drift_type_values, correction_type_values, correction_values),
    function(df, drift, correction, corr_values) {

      prepped_df <- df %>%
        cal_wt(dt_col = "DT_round") %>%
        mutate(
          pre_val        = corr_values$from,
          post_val       = corr_values$to,
          pre_post_source = corr_values$source
        )

      corrected_df <- cal_exp_one_point_drift(
        df             = prepped_df,
        lm_trans_col   = correction_col,
        pre_col        = "pre_val",
        post_col       = "post_val",
        wt_col         = "wt",
        drift_type     = drift,
        correction_type = correction
      )

      return(corrected_df)
    }
  ) %>%
    bind_rows() %>%
    select(DT_round, wt, pre_val, post_val, pre_post_source, mean_drift_trans)

  final_data <- sensor_df_arg %>%
    left_join(corrected_data, by = "DT_round") %>%
    mutate(mean_drift_trans = ifelse(is.na(mean_drift_trans), !!sym(correction_col), mean_drift_trans))

  return(final_data)
}
```

```{r}
#' @title Exponential drift correction function
#' @description Same structure as linear_correction_fxn but fits k per
#'   calibration window via exp_k(), then applies the log weight — the concave
#'   transpose of the exponential curve with the same k:
#'   wt_log = log(1 + wt * (exp(k) - 1)) / k.
#'   This gives a correction that accumulates faster early and decelerates toward
#'   the end, matching how biofouling drift typically behaves.
#' @param decision_df_arg Data frame of exponential correction decisions for a
#'   single site-parameter; must have start_dt, end_dt, and arg_correction_type
#' @param sensor_df_arg Data frame for a single site-parameter containing
#'   DT_round, mean_analysis, and field note pre/post columns
#' @param correction_col Column to apply the correction to (default "mean_analysis")
#' @param data_list Named list of all site-parameter data frames passed to
#'   cal_range_values for Option C (default NULL)
#' @param site_order_template Network order list passed to cal_range_values for
#'   Option C (default NULL)
#' @param gap_threshold_mins Passed to cal_range_values (default 120)

exponential_correction_fxn <- function(decision_df_arg, sensor_df_arg, correction_col = "mean_analysis",
                                       data_list = NULL, site_order_template = NULL,
                                       gap_threshold_mins = 120) {

  start_dt_values <- pull(decision_df_arg, start_dt)
  end_dt_values   <- pull(decision_df_arg, end_dt)

  data_to_correct <- map2(
    .x = start_dt_values,
    .y = end_dt_values,
    function(start, end) {
      sensor_df_arg %>%
        filter(between(DT_round, start, end))
    }
  )

  correction_values <- map(
    .x = end_dt_values,
    function(end_dt) {
      cal_range_values(sensor_df_arg = sensor_df_arg, end_dt = end_dt,
                       data_list = data_list, site_order_template = site_order_template,
                       gap_threshold_mins = gap_threshold_mins)
    }
  )

  correction_type_values <- pull(decision_df_arg, arg_correction_type)

  corrected_data <- pmap(
    .l = list(data_to_correct, correction_type_values, correction_values),
    function(df, correction, corr_values) {

      prepped_df <- df %>%
        cal_wt(dt_col = "DT_round") %>%
        mutate(
          pre_val         = corr_values$from,
          post_val        = corr_values$to,
          pre_post_source = corr_values$source
        )

      k <- exp_k(prepped_df, correction_col = correction_col)

      corrected_df <- cal_exp_one_point_drift(
        df              = prepped_df,
        lm_trans_col    = correction_col,
        pre_col         = "pre_val",
        post_col        = "post_val",
        wt_col          = "wt",
        drift_type      = "log",
        correction_type = correction,
        exp_coef        = k
      )

      return(corrected_df)
    }
  ) %>%
    bind_rows() %>%
    select(DT_round, wt, pre_val, post_val, pre_post_source, mean_drift_trans)

  final_data <- sensor_df_arg %>%
    left_join(corrected_data, by = "DT_round") %>%
    mutate(mean_drift_trans = ifelse(is.na(mean_drift_trans), !!sym(correction_col), mean_drift_trans))

  return(final_data)
}
```


# Load and prepare data

```{r}
sensor_f <- list.files(here("data", "raw", "sensor", "manual_data_verification",
                            "2024_cycle", "in_progress", "verified_directory"),
                       pattern = "Turbidity|FDOM",
                       ignore.case = TRUE,
                       full.names = TRUE) 

raw_data <- map(sensor_f, arrow::read_parquet) %>%
  set_names(str_remove(basename(sensor_f), "_FINAL_.*\\.parquet$"))

rm(sensor_f)
```

The Virridy sites were back-calibrated out of order via `prep_virridy_2024_for_cal_app.R`. The corrected values are recovered here from the finalized calibration RDS so that `mean_analysis` — and therefore all drift correction outputs — are computed from the back-calibrated base.

```{r}
virridy_cal_corrections <- read_rds(here("data", "raw", "sensor", "manual_data_verification",
                                          "complete_dataset", "calibrated_sensor_field_data_finalized.rds"))[["2024"]] %>%
  keep(~ grepl("virridy", unique(.$site))) %>%
  map_dfr(~ select(., DT_round, site, parameter, mean_cleaned_cal)) %>%
  rename(mean_virridy_post_cal = mean_cleaned_cal)
```

```{r}
field_notes <- grab_mWater_sensor_notes(load_mWater())

prepped_data <- raw_data %>%
  map(function(df) {
    df %>%
      add_field_notes(field_notes) %>%
      left_join(virridy_cal_corrections, by = c("DT_round", "site", "parameter")) %>%
      mutate(
        mean = if_else(!is.na(mean_virridy_post_cal), mean_virridy_post_cal, mean),
        drift = ifelse(stringr::str_detect(user_flag, "drift"), TRUE, FALSE),
        drift = ifelse(is.na(drift), FALSE, drift),
        mean_analysis = ifelse(verification_status %in% c("FLAGGED", "PASS"), mean, NA)
      ) %>%
      select(-mean_virridy_post_cal) %>%
      fill(c("turb_pre_clean", "turb_post_clean", "fdom_pre_clean", "fdom_post_clean"),
           .direction = "down")
  })

rm(raw_data)
gc()
```

# The whole workflow orchestrated


```{r}
decision_df <- read_excel(here("data", "derived", "auto_qaqc_files",
                               "drift_corrections", "2024_drift_corrections.xlsx")) %>%
  fix_site_names()

# For each site-parameter, apply all corrections in order then stitch together.
# Exponential decisions use the log correction (the functional inverse of the
# exponential weight), which better matches how biofouling drift accumulates.

corrected_data <- prepped_data %>%
  imap(function(df, key) {

    # Convert sensor timestamps from MST to UTC so all data is stored in UTC
    df <- df %>% mutate(DT_round = with_tz(DT_round, "UTC"))

    site_val      <- unique(df$site)
    parameter_val <- unique(df$parameter)

    # Filter decisions for this site-parameter
    site_decisions <- decision_df %>%
      filter(site == site_val, parameter == parameter_val)

    # 1. Unflag: update drift flags and user_flag (does not change mean_analysis)
    df_working <- unflag_fxn(
      decision_df_arg = site_decisions %>% filter(decision == "unflag"),
      sensor_df_arg   = df
    )

    # Helper: boolean vector marking rows inside any window in a decision subset
    in_windows <- function(dec_df) {
      if (nrow(dec_df) == 0) return(rep(FALSE, nrow(df_working)))
      map2(
        pull(dec_df, start_dt),
        pull(dec_df, end_dt),
        function(s, e) between(df_working$DT_round, s, e)
      ) %>% reduce(`|`)
    }

    # 2. Identify which rows belong to each correction window type
    unflag_decision_df <- site_decisions %>% filter(decision == "unflag")
    linear_decision_df         <- site_decisions %>% filter(arg_drift_type == "linear")
    exp_decision_df            <- site_decisions %>% filter(arg_drift_type == "exponential")
    uniform_decision_df        <- site_decisions %>% filter(arg_drift_type == "uniform")
    fitted_linear_decision_df  <- site_decisions %>% filter(arg_drift_type == "fitted_linear")

    in_unflag        <- in_windows(unflag_decision_df)
    in_linear        <- in_windows(linear_decision_df)
    in_exp           <- in_windows(exp_decision_df)
    in_uniform       <- in_windows(uniform_decision_df)
    in_fitted_linear <- in_windows(fitted_linear_decision_df)

    # 3. Compute corrections and join results back onto df_working by DT_round.
    #    distinct() guards against row expansion from overlapping decision windows.
    if (any(in_linear)) {
      linear_join <- linear_correction_fxn(
        decision_df_arg     = linear_decision_df,
        sensor_df_arg       = df_working,
        data_list           = prepped_data,
        site_order_template = site_order
      ) %>%
        distinct(DT_round, .keep_all = TRUE) %>%
        select(DT_round, linear_trans = mean_drift_trans, linear_source = pre_post_source)
      df_working <- df_working %>% left_join(linear_join, by = "DT_round")
    } else {
      df_working <- df_working %>% mutate(linear_trans = NA_real_, linear_source = NA_character_)
    }

    if (any(in_exp)) {
      exp_join <- exponential_correction_fxn(
        decision_df_arg     = exp_decision_df,
        sensor_df_arg       = df_working %>% select(-any_of(c("linear_trans", "linear_source"))),
        data_list           = prepped_data,
        site_order_template = site_order
      ) %>%
        distinct(DT_round, .keep_all = TRUE) %>%
        select(DT_round, exp_trans = mean_drift_trans, exp_source = pre_post_source)
      df_working <- df_working %>% left_join(exp_join, by = "DT_round")
    } else {
      df_working <- df_working %>% mutate(exp_trans = NA_real_, exp_source = NA_character_)
    }

    if (any(in_uniform)) {
      uniform_join <- linear_correction_fxn(
        decision_df_arg     = uniform_decision_df,
        sensor_df_arg       = df_working %>% select(-any_of(c("linear_trans", "linear_source", "exp_trans", "exp_source"))),
        data_list           = prepped_data,
        site_order_template = site_order
      ) %>%
        distinct(DT_round, .keep_all = TRUE) %>%
        select(DT_round, uniform_trans = mean_drift_trans, uniform_source = pre_post_source)
      df_working <- df_working %>% left_join(uniform_join, by = "DT_round")
    } else {
      df_working <- df_working %>% mutate(uniform_trans = NA_real_, uniform_source = NA_character_)
    }

    if (any(in_fitted_linear)) {
      fitted_linear_join <- linear_correction_fxn(
        decision_df_arg     = fitted_linear_decision_df,
        sensor_df_arg       = df_working %>% select(-any_of(c("linear_trans", "linear_source", "exp_trans", "exp_source", "uniform_trans", "uniform_source"))),
        data_list           = prepped_data,
        site_order_template = site_order
      ) %>%
        distinct(DT_round, .keep_all = TRUE) %>%
        select(DT_round, fitted_linear_trans = mean_drift_trans, fitted_linear_source = pre_post_source)
      df_working <- df_working %>% left_join(fitted_linear_join, by = "DT_round")
    } else {
      df_working <- df_working %>% mutate(fitted_linear_trans = NA_real_, fitted_linear_source = NA_character_)
    }

    # 4. Stitch: assign corrected values and stamp correction_type for plotting
    df_corrected <- df_working %>%
      mutate(
        mean_drift_trans = case_when(
          in_linear        ~ linear_trans,
          in_exp           ~ exp_trans,
          in_uniform       ~ uniform_trans,
          in_fitted_linear ~ fitted_linear_trans,
          TRUE             ~ mean_analysis
        ),
        correction_type = case_when(
          in_linear        ~ "linear",
          in_exp           ~ "exponential",
          in_uniform       ~ "uniform",
          in_fitted_linear ~ "fitted_linear",
          in_unflag        ~ "unflagged",
          TRUE             ~ "raw"
        ),
        pre_post_source = case_when(
          in_linear        ~ linear_source,
          in_exp           ~ exp_source,
          in_uniform       ~ uniform_source,
          in_fitted_linear ~ fitted_linear_source,
          TRUE             ~ NA_character_
        )
      ) %>%
      select(-linear_trans, -exp_trans, -uniform_trans, -fitted_linear_trans,
             -linear_source, -exp_source, -uniform_source, -fitted_linear_source)

    # 5. Post-process: smooth (Turbidity only) then interpolate short gaps
    df_corrected %>%
      apply_interpolation_missing_data(value_col = "mean_drift_trans", new_value_col = "mean_filled")%>%
       low_pass_filter(correction_col = "mean_filled")
  })
```

After all of this work, the final column to consider is: `smoothed_mean`

# Plotting the final corrections

Explore the final results here.

```{r}
plot_final_corrections(
  df                  = corrected_data$`udall-FDOM Fluorescence`,
  data_list           = prepped_data,
  site_order_template = site_order
)
```

# Save the outputs

```{r}
# Save each site-parameter data frame as a parquet file.
# File names match the list keys with spaces replaced by underscores.

save_dir <- here("data", "raw", "sensor", "manual_data_verification",
                 "2024_cycle", "post_verification")

iwalk(corrected_data, function(df, key) {
  filename  <- paste0(str_replace_all(key, " ", "_"), ".parquet")
  arrow::write_parquet(df, file.path(save_dir, filename))
})
```
