---
title: "Processing 2024 Data Pull from HydroVu with Auto Back-Calibration and QA/QC Flagging"
author: "Sam Struthers, Juan De La Torre - CSU ROSSyndicate"
date: "`r Sys.Date()`"
output: html_document
---

# Script Purpose & Scope

This script documents the processing of sensor data for the 2024 monitoring 
season. Data was pulled from HydroVu, run through automated QA/QC flagging, and 
manually verified before being exported for back-calibration decisions. Drift 
corrections were applied after the fact — the drift correction workflow was 
developed after the 2024 season concluded and was subsequently applied to the 
2024 data retroactively. The final processed dataset is prepared here for upload 
to HydroShare.

The order of operations for 2024 is:

1. Pull sensor data from HydroVu and parse any downloaded log files
2. Run automated QA/QC flagging
3. Manual verification of auto-flagged data (Shiny verification tool)
4. Export data for back-calibration decisions and apply back-calibration
5. Apply drift corrections (`drift_correction_2024.Rmd`)
6. Prepare final datasets for HydroShare upload

## Setup Libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# loading packages
package_loader <- function(x) {
  if (x %in% installed.packages()) {
    suppressMessages({
      library(x, character.only = TRUE)
    })
  } else {
    suppressMessages({
      install.packages(x)
      library(x, character.only = TRUE)
    })
  }
}

invisible(
  lapply(c("arrow",
           "sf",
           "tmap",
           "data.table",
           "httr2",
           "tidyverse",
           "lubridate",
           "zoo",
           "padr",
           "stats",
           "RcppRoll",
           "yaml",
           "here",
           "ross.wq.tools",
           "furrr",
           "plotly"
  ),
  package_loader)
)

# Set up parallel processing
num_workers <- min(availableCores() - 1, 4) # Use at most 4 workers
plan(multisession, workers = num_workers)
set_furr_options <- furrr_options(
  globals = TRUE,
  packages = c("arrow", "data.table", "httr2", "tidyverse","dplyr", 
               "lubridate", "zoo", "padr", "stats", "RcppRoll", "yaml", 
               "here", "ross.wq.tools")
)

# suppress scientific notation to ensure consistent formatting
options(scipen = 999)

```

## Setting up the site/time range/parameters for the data pull

```{r}
#Adjust dates for specific pull
mst_start <- ymd_hms("2024-03-01 00:00:00", tz = "America/Denver")
mst_end <- ymd_hms("2024-11-30 23:59:59", tz = "America/Denver")

sites <- c(
  #Upper sites
  "joei", "cbri", "chd","pfal", "pbr", "sfm",  "pman", "pbd",
  #Lower sites
  "bellvue","salyer", "udall", "riverbend","cottonwood", "elc","archery","riverbluffs",
  #lower tribs
  "boxcreek", "springcreek")

#Setting parameters of interest
parameters <- c("Specific Conductivity", "Temperature", "DO", "pH", "ORP", "Depth", #Standard vars
                "Chl-a Fluorescence", "Turbidity", "FDOM Fluorescence") #optical vars
```

## Establishing directory paths.

These are the folders where raw, and flagged data will be saved. Update 
base_folder to the current year and log directory as needed

```{r}
base_folder <- here("data","raw", "sensor","manual_data_verification","2024_cycle")
# Make sure base folder exists and create if not
if (!dir.exists(base_folder)) {
  dir.create(base_folder)
}

#folder with downloaded logs
log_directory <- here("data","raw", "sensor", "log_download", "2024")  #Change as needed

#Sub folders for raw and flagged data
staging_directory <- here(base_folder, "hydro_vu_pull", "raw_data")
flagged_temp_dir <- here(base_folder, "hydro_vu_pull", "flagged_data_temp")
flagged_directory <- here(base_folder, "hydro_vu_pull", "flagged_data")

#check to make sure these all exist and create if needed
if (!dir.exists(staging_directory)) {
  dir.create(staging_directory, recursive = TRUE)
}
if (!dir.exists(flagged_temp_dir)) {
  dir.create(flagged_temp_dir, recursive = TRUE)
}
if (!dir.exists(flagged_directory)) {
  dir.create(flagged_directory, recursive = TRUE)
}

```

Specific for 2024: the original data was prepared by `process_2024.R`, which used
different folder names (`raw/` and `flagged/`) and saved flagged data as CSVs rather
than parquets. The chunk below migrates those files into the folder structure and
format established above, then removes the old folders once the transfer is complete.

```{r}
raw_old_dir      <- here(base_folder, "hydro_vu_pull", "raw")
flagged_old_dir  <- here(base_folder, "hydro_vu_pull", "flagged")

# --- Migrate raw parquets (rename to 2025-style: {site}{YYYYMMDD}-T{HHMMSS}Z) ---
if (dir.exists(raw_old_dir)) {
  raw_files <- list.files(raw_old_dir, pattern = "\\.parquet$", full.names = TRUE)
  walk(raw_files, function(f) {
    m <- str_match(basename(f), "^(.*?)(\\d{4}-\\d{2}-\\d{2})_(\\d{4})\\.parquet$")
    site_clean <- str_remove(m[, 2], "_$")
    date_clean  <- str_remove_all(m[, 3], "-")
    time_clean  <- paste0(m[, 4], "00")
    new_name <- paste0(site_clean, date_clean, "-T", time_clean, "Z.parquet")
    file.copy(f, file.path(staging_directory, new_name), overwrite = FALSE)
  })
  unlink(raw_old_dir, recursive = TRUE)
  message("Raw parquets migrated to raw_data/ and raw/ removed.")
} else {
  message("raw/ folder not found — transfer already completed.")
}

# --- Migrate flagged CSVs to parquets ---
if (dir.exists(flagged_old_dir)) {
  flagged_files <- list.files(flagged_old_dir, pattern = "\\.csv$", full.names = TRUE)
  walk(flagged_files, function(f) {
    out_name <- paste0(tools::file_path_sans_ext(basename(f)), ".parquet")
    df <- read_csv(f, show_col_types = FALSE)
    write_parquet(df, file.path(flagged_directory, out_name))
  })
  unlink(flagged_old_dir, recursive = TRUE)
  message("Flagged CSVs converted to parquets in flagged_data/ and flagged/ removed.")
} else {
  message("flagged/ folder not found — transfer already completed.")
}
```

The `extra_data/` folder contains `SFM_2024-12-10_1430.csv`, the raw HydroVu pull
for the SFM site pulled separately on 2024-12-10. It covers 2023-10-24 through
2024-11-13 but the pre-season stretch (before April 2024) was excluded from
flagging. SFM is fully represented in `flagged_data/` (April 25 – November 13,
2024, all 9 parameters, no gaps) so this file is retained here as an artifact 
of the earlier data processing for 2024.

## Read in thresholds and credentials

Sensor thresholds are from In-Situ Inc spec sheets and seasonal_thresholds are 
created using `ross.wq.tools::make_threshold_table()` using cleaned data from 
previous years.

mWater and HydroVu creds are created from their respective websites, 
contact Sam Struthers, Juan De La Torre or Katie Willi for help obtaining these.

```{r}
# Read in the threshold data first
sensor_thresholds <- read_yaml(here("data","derived","auto_qaqc_files", 
                                    "thresholds",  "sensor_spec_thresholds.yml"))

season_thresholds <- read_csv(here("data","derived","auto_qaqc_files", 
                                   "thresholds", "updated_seasonal_thresholds_2025_sjs.csv"), # We use 2025 thresholds because those are the most up to date thresholds
                              show_col_types = FALSE) %>%
  fix_site_names()

# Read in credentials
mWater_creds <- read_yaml(here("creds", "mWaterCreds.yml"))

hv_creds <- read_yaml(here("creds", "HydroVuCreds.yml"))
hv_token <- hv_auth(client_id = as.character(hv_creds["client"]),
                    client_secret = as.character(hv_creds["secret"]))

```

# Data Pulls

**Note:** This script was reconstructed after the fact to document the 2024 
processing workflow. The code below reflects the steps that were taken to 
generate the 2024 data, but this specific script was not the one used to produce 
it. Running these sections should reproduce equivalent results.

All data pulls were completed during the 2024 monitoring season and the raw data
is already saved in the staging directory. These sections are kept here for 
documentation purposes and should remain commented out unless re-running from 
scratch is necessary.

## Pulling in field notes from mWater
```{r}
# Pull in all notes
mWater_data <- load_mWater(creds = mWater_creds)

# Only extract sensor visits
all_field_notes <- grab_mWater_sensor_notes(mWater_api_data = mWater_data)%>%
  # grab_mWater_sensor_notes converts this to MST, converting back to UTC for DS use
  mutate(DT_round = with_tz(DT_round, tzone = "UTC"), 
         last_site_visit = with_tz(last_site_visit, tzone = "UTC"),
         DT_join = as.character(DT_round))

# Only extract sensor malfunctions
sensor_malfunction_notes <- grab_mWater_malfunction_notes(mWater_api_data = mWater_data)%>%
  # grab_mWater_malfunction_notes converts this to MST, converting back to UTC for DS use
  mutate(start_DT = with_tz(start_DT, tzone = "UTC"),
         end_DT = with_tz(end_DT, tzone = "UTC"))
```

## Pulling in the sensor data from hydrovu

## HydroVu Pull

This section will take quite a while to load (~ 2-4 min per month of data per site). 
Once data has been pulled and checked, comment this section out to avoid re-running it.

```{r}
# # Get all the site info from HydroVu
# hv_sites <- hv_locations_all(hv_token)
# #trim down to just the sites/types of devices we want
# hv_sites <- hv_sites %>%
#   #Remove Vulinks
#   filter(!grepl("vulink", name, ignore.case = TRUE))%>%
#   #Remove Virridy sites/sondes
#   filter(!grepl("virridy", name, ignore.case = TRUE))#%>%
#    #remove any older sites (containing 2023 in the name)
#   filter(!grepl("2023", name, ignore.case = TRUE))
#
#
# walk(sites,
#      function(site) {
#        message("Requesting HV data for: ", site)
#        api_puller(
#          site = site,
#          start_dt = with_tz(mst_start, tzone = "UTC"),
#          end_dt = with_tz(mst_end, tzone = "UTC"),
#          api_token = hv_token,
#          hv_sites_arg = hv_sites,
#          dump_dir = staging_directory
#        )
#      }
# )
#
# # beep to let you know when it's done
# beepr::beep(1)
```

## Pulling in any downloaded log data

No log files were merged here (unlike 2025) since all data either uploaded to 
HydroVu via Vulink, we would upload AquaTroll logs or could upload Vulink Logs 
with AT 500/700 data.

# Raw Data Processing

This is where we will read in all the pulled data from HydroVu and our parsed 
logs to then be tidied and checked.

## Load in and tidy the raw files

**Note:** The raw data has already been munged and the results are saved in
`flagged_data/`. Only re-run this section if starting from scratch. The
`tidy_data` object produced here is used by the Data Flagging section below,
which is also already complete.

A custom munge was used instead of `munge_api_data()` to preserve the Virridy
sites in the 2024 data. The raw parquet files are read directly, Vulinks are
filtered out, and Virridy sondes are kept with `_virridy` appended to their site
names before passing through `fix_site_names()` and `tidy_api_data()`. See
`data_organization/Process_2024.R` for the original script where this approach
was first used.

Each list has DT_round (in UTC), site, parameter, units, mean, n_obs, spread,
DT_join and flag columns and is summarized to a 15 minute interval.

```{r}
# Custom munge to preserve Virridy sites (munge_api_data() filters them out).
# See Process_2024.R for the original implementation.
hv_data <- list.files(staging_directory, full.names = TRUE) %>%
  future_map_dfr(function(file_path) {
    read_parquet(file_path, as_data_frame = TRUE)
  }, .progress = TRUE) %>%
  data.table() %>%
  select(-id) %>%
  mutate(units = as.character(units)) %>%
  filter(!grepl("vulink", name, ignore.case = TRUE)) %>%
  mutate(
    DT = timestamp,
    DT_round = round_date(DT, "15 minutes"),
    DT_join = as.character(DT_round),
    site = tolower(site),
    site = ifelse(grepl("virridy", name, ignore.case = TRUE), str_replace(site, " virridy", "_virridy"), site)
  ) %>%
  select(-name) %>%
  fix_site_names() %>%
  distinct(.keep_all = TRUE) %>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  keep(~nrow(.) > 0)

tidy_data <- hv_data %>%
  future_map(~tidy_api_data(api_data = .), .progress = TRUE, .options = set_furr_options) %>%
  keep(~!is.null(.)) %>%
  # Only keep parameters we are interested in
  keep(~unique(.$parameter) %in% parameters)

```

## Double check that pulls were successful

We are giving it a quick look over to make sure there aren't any large data gaps
(>1 day) in the data pulled, that all site names are being applied correctly and
that we don't have duplicate data. We are also adding in our field notes to the
plots to make sure the data we have lines up with the periods we expect the
sondes to be deployed and recording data.

Reads directly from `raw_data/` so this check can be run without re-running the
full munge above.

```{r}
raw_check <- list.files(staging_directory, pattern = "\\.parquet$", full.names = TRUE) %>%
  map_dfr(~read_parquet(.x)) %>%
  mutate(
    site = tolower(site),
    site = ifelse(grepl("virridy", name, ignore.case = TRUE),
                  str_replace(site, " virridy", "_virridy"), site),
    DT_round = round_date(timestamp, "15 minutes"),
    DT_hourly = floor_date(DT_round, "1 hour")
  ) %>%
  fix_site_names() %>%
  filter(parameter %in% parameters)

data_check_plots <- raw_check %>%
  group_by(site, parameter, DT_hourly) %>%
  summarize(hourly_med = median(value, na.rm = TRUE), .groups = "drop") %>%
  split(f = list(.$site)) %>%
  map(function(df) {
    field_notes <- all_field_notes %>%
      filter(site == unique(df$site) & year(DT_round) == "2024") %>%
      select(DT_round, sonde_employed) %>%
      mutate(sonde_changed = case_when(sonde_employed == 0 ~ "Deployed",
                                       sonde_employed == 1 ~ "Pulled",
                                       TRUE ~ "Active"))
    ggplot(df, aes(x = DT_hourly, y = hourly_med)) +
      geom_point() +
      geom_vline(data = field_notes, aes(xintercept = DT_round, color = sonde_changed)) +
      facet_wrap(~parameter, scales = "free_y") +
      labs(title = unique(df$site),
           x = "Date",
           y = "Hourly Median Value",
           color = "Sonde Status")
  })

walk(.x = data_check_plots, .f = print)
```

If there are discrepancies in the data, double check the raw files in `raw_data/`
to make sure everything looks correct. Occasionally there are issues with the
HydroVu download missing data and that can be rerun for an individual site. If
there continue to be large gaps in data (>3 days) during deployment periods,
check field notes or contact Sam Struthers for troubleshooting.

# Data Flagging

**Note:** Flagging was completed during the 2024 monitoring season using the
original `process_2024.R` script. The results are already saved in `flagged_data/`.
These sections are kept for documentation purposes.

## Combine with field notes
Here we read in our field notes and then join them to the tidied data using
`add_field_notes()`. We then generate summary statistics (slope, lag, etc) using
`generate_summary_statistics()`.
```{r}
# Add the field note data to all of the data
all_field_notes <- all_field_notes %>%
  fix_site_names()

combined_data <- tidy_data %>%
  future_map(~add_field_notes(df = ., notes = all_field_notes), .progress = TRUE)

# Add summary statistics
summarized_data <- combined_data %>%
  map(~generate_summary_statistics(.))
```

## Single Sensor Flags

This is the first round of flagging that is done on a per-site-parameter basis.
Here we are applying functions to flag field visits, missing data, DO noise,
repeating values, depth shifts, optical sensor drift, spec range violations and
seasonal range violations. This can take ~5-15 min depending on data volume.

```{r}
# Chunk the data for furrr
summarized_data_chunks <- split(1:length(summarized_data),
                                ceiling(seq_along(1:length(summarized_data))/10))
# Flag data...
# Single parameter flags
single_sensor_flags <- list()
for (chunk_idx in seq_along(summarized_data_chunks)) {
  message("\n=== Processing chunk ", chunk_idx, " of ", length(summarized_data_chunks), " ===")

  # Get the indices for this chunk
  indices <- summarized_data_chunks[[chunk_idx]]
  chunk_data <- summarized_data[indices]

  # Process the chunk in parallel
  chunk_results <- chunk_data %>%
    future_map(
      function(data) {
        flagged_data <- data %>%
          data.table(.) %>%
          # flag field visits
          add_field_flag(df = .) %>%
          # flag missing data
          add_na_flag(df = .) %>%
          # flag DO noise
          find_do_noise(df = .) %>%
          # flag repeating values
          add_repeat_flag(df = .) %>%
          # find times when sonde was moved up/down in housing
          add_depth_shift_flag(df = ., level_shift_table =  all_field_notes, post2024 = TRUE) %>%
          # find instances of sensor drift (FDOM, Chl-a, Turbidity only)
          add_drift_flag(df = .)

        if (unique(data$parameter) %in% names(sensor_thresholds)) {
          # flag instances outside the spec range
          flagged_data <- flagged_data %>%
            data.table(.) %>%
            add_spec_flag(df = ., spec_table = sensor_thresholds)
        }

        if (unique(data$parameter) %in% unique(season_thresholds$parameter)) {
          # flag instances outside the spec range
          flagged_data <- flagged_data %>%
            data.table(.) %>%
            add_seasonal_flag(df = ., threshold_table = season_thresholds)
        }

        flagged_data <- flagged_data %>%
          data.table(.)

        return(flagged_data)
      },
      .progress = TRUE, .options = set_furr_options
    )

  # Add chunk to list
  single_sensor_flags <- c(single_sensor_flags, chunk_results)

  if (chunk_idx < length(summarized_data_chunks)) {
    message("Taking a short break before next chunk...")
    gc()
    Sys.sleep(0.1)
  }
}

# beep to let you know when it's done
beepr::beep(1)

```

## Intrasensor flags

Now we will apply flags that require multiple parameters from the same sensor to
be present. This includes frozen water flagging (temp < 0C), unsubmerged
flagging (depth < 0 or SC < 10) and sonde burial flagging (long-term DO noise).
We also do an intersensor check to remove slope violation flags that occur
concurrently with temp or depth violations to reduce overflagging. This can take
~5-15 min depending on data volume.

```{r}
intrasensor_flags <- single_sensor_flags %>%
  rbindlist(fill = TRUE) %>%
  split(by = "site")

# Chunk the data for furrr
intrasensor_data_chunks <- split(1:length(intrasensor_flags),
                                 ceiling(seq_along(1:length(intrasensor_flags))/3))

intrasensor_flags_list <- list()
for (chunk_idx in seq_along(intrasensor_data_chunks)) {
  message("\n=== Processing chunk ", chunk_idx, " of ", length(intrasensor_data_chunks), " ===")

  # Get the indices for this chunk
  indices <- intrasensor_data_chunks[[chunk_idx]]
  chunk_data <- intrasensor_flags[indices]
  # Process the chunk in parallel
  chunk_results <- chunk_data %>%
    future_map(
      function(data) {
        # A chunk is a site df
        flagged_data <- data %>%
          data.table() %>%
          # flag times when water was below freezing
          add_frozen_flag(.) %>%
          # overflagging correction. remove slope violation flag if it occurs concurrently
          # with temp or depth
          intersensor_check(.) %>%
          # add sonde burial. If DO is noise is long-term, likely burial:
          add_burial_flag(.) %>%
          # flag times when sonde was unsubmerged
          add_unsubmerged_flag(.)

        return(flagged_data)
      }, .progress = TRUE, .options = set_furr_options
    ) %>%
    rbindlist(fill = TRUE) %>%
    # lil' cleanup of flag column contents
    dplyr::mutate(flag = ifelse(flag == "", NA, flag)) %>%
    distinct(site, parameter, DT_round, mean, .keep_all = TRUE) %>%
    # transform back to site-parameter dfs
    split(f = list(.$site, .$parameter), sep = "-") %>%
    purrr::discard(~ nrow(.) == 0) %>%
    # Add in KNOWN instances of sensor malfunction
    map(~add_malfunction_flag(df = ., malfunction_records = sensor_malfunction_notes))

  # Add chunk to list
  intrasensor_flags_list <- c(intrasensor_flags_list, chunk_results)

  if (chunk_idx < length(intrasensor_data_chunks)) {
    message("Taking a short break before next chunk...")
    gc()
    Sys.sleep(0.1)
  }
}

# beep to let you know when it's done
beepr::beep(1)
```

### Let's temporarily save this data so we can remove everything else from memory

```{r}
iwalk(intrasensor_flags_list, ~write_parquet(.x, here(flagged_temp_dir, paste0(.y, ".parquet"))))

#remove everything other than intrasensor flags from memory
rm(list=setdiff(ls(), c("base_folder", "intrasensor_flags_list", "flagged_directory")))
#clean up memory
gc()
```

## Applying network check

The network check function `ross.wq.tools::network_check()` compares data across
sites to identify when data is being overflagged and remove flags as needed.
This step requires knowledge of the site order, which is read in from a YAML
file and should be updated as sites change.

```{r}
#Read in site order for year/pull
site_order_2024 <- load_site_order( here("data","derived","auto_qaqc_files",
                                         "site_order", "site_order_2024.yml"))

#Applying Network check (non parrallel so only map used)
final_flags <- intrasensor_flags_list %>%
  map(~network_check(df = ., intrasensor_flags_arg = intrasensor_flags_list, site_order_arg = site_order_2024)) %>%
  rbindlist(fill = TRUE) %>%
  tidy_flag_column() %>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  map(~add_suspect_flag(.)) %>%
  rbindlist(fill = TRUE)

v_final_flags <- final_flags%>%
  mutate(auto_flag = ifelse(is.na(auto_flag), NA,
                            ifelse(auto_flag == "suspect data" & is.na(lag(auto_flag, 1)) & is.na(lead(auto_flag, 1)), NA, auto_flag))) %>%
  select(c("DT_round", "DT_join", "site", "parameter", "mean", "units", "n_obs", "spread", "auto_flag", "mal_flag", "sonde_moved","sonde_employed", "season", "last_site_visit")) %>%
  mutate(auto_flag = ifelse(is.na(auto_flag), NA, ifelse(auto_flag == "", NA, auto_flag))) %>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  keep(~nrow(.) > 0)

# beep to let you know when it's done
beepr::beep(1)
```

## Check final output

Here we are making sure that all sites data were flagged and giving a quick look
at the flagged data to make sure everything looks correct. With newer
sites/parameters, we expect there to be over-flagging as the seasonal
ranges/slopes are going to be very small.

```{r}
v_final_flags%>%
  bind_rows()%>%
  split(f = list(.$site))%>%
  map(., function(df) {
    ggplot(df, aes(x = DT_round, y = mean, color = auto_flag)) +
      geom_point() +
      facet_wrap(~parameter, scales = "free_y")+
      labs(title = unique(df$site),
           x = "Date",
           y = "Mean Value")
  }) %>%
  walk(plot)
```

# Save Final Flagged Dataset

We will save it into two places:
- Individually flagged site-parameter parquet files for posterity and comparison with manual verification to determine effectiveness of auto-flagging
- A combined raw data parquet file for use in the manual verification shiny app. Once starting manual verification for the year, this will be used the as "uploaded" data to generate all the necessary files for the app.

```{r}
# Save the data individually.
iwalk(v_final_flags, ~write_parquet(.x, here(flagged_directory,  paste0(.y, ".parquet"))))

#saving our data into the "raw_data" folder of the manual verification folder for use in the shiny app
write_parquet(v_final_flags%>%bind_rows(), here(base_folder,"in_progress","raw_data", "raw_data_2024.parquet"))
```

# Pass data through Shiny Tool

This tool is located in the folder `shiny_ver_tool`. Here we are manually
verifying the data, making any necessary corrections and then saving the output
in the "verified_directory" folder for this year. The key columns added are:
- final_status: "PASS" if the user has verified the data as good, "FLAGGED" if
the user has flagged the data for suspect but still useable data, "OMIT if the
user has concluded that the data should not be used in analysis due to sensor error.
- user_flag: more specific flag added by the user to indicate why they
flagged/omitted the data (e.g. "suspect data", "sonde burial", "frozen water",
"unsubmerged", "depth shift", "drift", "field visit", "other malfunction" etc).
This is for posterity and to help inform auto-flagging performance.
- mean_analysis: this is the values where the "OMIT" final status was not applied.

# Apply Back-calibration as needed

This uses the Shiny App (https://github.com/juandlt-csu/manual_calibration_verification) 
developed by Juan. We are essentially deciding when a sensor needs to be 
back-calibrated based on field notes and applying the back-calibration to the 
raw data before flagging. The majority of calibrations are fine as is but we 
want to "skip" over the bad ones.

## Read in calibration data

```{r}
#This creates calibration_data list object needed for the back-calibration functions
# load_calibration_data(
#   cal_data_file_path = here::here("data", "collated", "sensor", "cal_reports", "munged_calibration_data.RDS"),
#     update = FALSE, # set to TRUE when running for the first time
#   field_cal_dir = here::here("data", "raw", "sensor", "calibration_reports")
# )

```

## Organize sensor data to match formatting for `cal_join_sensor_calibration_data()`

Data should be in a nested list structure: `sensor_data$years$site-parameter`

```{r}
# sensor_data <- tidy_data %>%
#   bind_rows()%>%
#   split(f = year(.$DT_round)) %>%
#   map(~ {
#     split_data <- split(.x, f = list(.x$site, .x$parameter), sep = "-")
#     discard(split_data, ~is.null(.) || nrow(.) == 0)
#   })
```

## Join to calibration data and apply back-calibration

This workflow follows the workflow outlined in the `ross.wq.tools` vignette on 
back calibration. First, we join the calibration and sensor data so that each 
time instance has the slope and intercept info needed for back-calibration.
Next, we prepare the calibration windows to split the data into calibration windows.
Lastly we loop through each calibration window to apply the back-calibration 
using `cal_back_calibrate()`.

```{r}

sensor_calibration_data <- cal_join_sensor_calibration_data(
  sensor_data_list = sensor_data,
  calibration_data_list = calibration_data
)

prepped_snsr_cal_data <- cal_prepare_calibration_windows(
  sensor_calibration_data_list = sensor_calibration_data
)

calibrated_data <- prepped_snsr_cal_data%>%
  map(function(year){
    year%>%
      map(function(site_param){
        site_param %>%
          map_dfr(function(chunk){
            cal_back_calibrate(chunk)
          })
      })
  })

beepr::beep(1)

```

## Save to back calibrated folder

This will become the "original" file in the shiny app for manual verification

```{r}

write_rds(calibrated_data, here("data", "raw", "sensor", "manual_data_verification", 
                                "2024_cycle", "hydro_vu_pull", "back_calibration", 
                                "calibrated_sensor_data_2024.rds"))

```

Take ^ file and run through the shiny app to verify back-calibration and make any manual adjustments as needed.

## Virridy sites: separate back-calibration

Virridy sites (archery_virridy, cottonwood_virridy, riverbend_virridy) required a
separate back-calibration workflow. The original 2024 pipeline used `munge_api_data()`
which filtered out Virridy sites, and a filter in an earlier version of
`ross.wq.tools` also excluded them from `cal_extract_markup_data()`. As a result
they were not included in the standard back-calibration pipeline above.

Instead, after Shiny manual verification was complete, Virridy sites were
back-calibrated using `scratch/data_tidying/prep_virridy_2024_for_cal_app.R`.
That script reads the post-verification Virridy parquets from `verified_directory`,
runs the standard `cal_back_calibrate()` pipeline on the four calibratable
parameters (Chl-a Fluorescence, FDOM Fluorescence, Specific Conductivity,
Turbidity), and injects the results directly into the app tracking RDS at
`data/raw/sensor/manual_data_verification/complete_dataset/calibrated_sensor_field_data_tracking.rds`.

**Do not re-run `prep_virridy_2024_for_cal_app.R`.** The write step (Section 9
of that script) is already commented out. Re-running it would duplicate the
Virridy entries in the tracking RDS and cause downstream issues.

## Read in user corrected back-calibrated data

```{r}
calibrated_data_final <- read_rds(
  here("data", "raw", "sensor", "manual_data_verification",
       "complete_dataset", "calibrated_sensor_field_data_finalized.rds")
)[["2024"]] # Only extract the 2024 data
```

## Quick look at the back-calibrated data

All of this should already have been double checked by the user but we just want 
to make sure everything looks good before proceeding to flagging. This plot will 
show the raw vs back-calibrated data ("final") with vertical lines indicating 
when the calibration events occurred.

```{r}
plots <- map(names(calibrated_data_final),
             function(site_param) {
               plot_data <- calibrated_data_final[[site_param]]

               vline_df <- plot_data %>%
                 group_by(sensor_date) %>%
                 slice_min(DT_round, n = 1) %>%
                 arrange(DT_round)%>%
                 ungroup()%>%
                 select(DT_round, file_date)%>%
                 mutate(file_date_mst = with_tz(file_date, tzone = "MST"),
                        file_date_mst_utc = force_tz(file_date_mst, tzone = "UTC"))

               param <- unique(plot_data$parameter)
               site <- unique(plot_data$site)

               ggplotly(ggplot(plot_data, aes(DT_round))+
                          geom_line(aes(y = mean_cleaned, color = "raw"))+
                          geom_line(aes(y = mean_cleaned_cal, color = "final"))+
                          geom_vline(xintercept = vline_df$file_date_mst_utc, linetype = "dashed")+
                          scale_color_manual(name = "Data Type", values = c("raw" = "blue", "final" = "green4"))+
                          labs(title = paste0(site, " - ", param),
                               x = "Date",
                               y = param))
             })%>%
  set_names(names(calibrated_data_final))

#Typically easiest to go parameter-wise through the plots
plots[grepl("pH", names(plots))]

```

## Remove columns as needed

Here we are removing columns that are not needed downstream to reduce memory
usage. We are also merging back in the units, n_obs, spread and auto_flag columns
from `flagged_data/`. Temperature and Depth are not passed into the
back-calibration process so we will grab those from `flagged_data/` as well.
We will also add the column "back_cal_performed" to indicate whether a
back-calibration was actually applied to the data or not.

```{r}
# Read all flagged parquets into a named list keyed by site-parameter.
# This is the source for units, n_obs, spread, and auto_flag since tidy_data
# is not available for 2024 (data was flagged in the original Process_2024.R pipeline).
flagged_data_list <- list.files(flagged_directory, pattern = "\\.parquet$", full.names = TRUE) %>%
  map(read_parquet) %>%
  set_names(
    list.files(flagged_directory, pattern = "\\.parquet$") %>%
      tools::file_path_sans_ext()
  )

cal_corrected_data <- calibrated_data_final %>%
  map(function(df) {

    site      <- unique(df$site)
    parameter <- unique(df$parameter)
    site_param <- paste0(site, "-", parameter)

    add_data <- flagged_data_list[[site_param]] %>%
      mutate(DT_join = as.character(DT_join)) %>%
      select(DT_join, units, n_obs, spread, auto_flag)

    if ("updated_slope_from" %in% names(df)) {
      df <- df %>%
        mutate(back_cal_performed = if_else(slope == updated_slope_to & slope == updated_slope_from, F, T))
    } else {
      df <- df %>%
        mutate(back_cal_performed = F)
    }

    df %>%
      select(
        DT_round,
        site,
        parameter,
        mean_pre_cal = mean_cleaned,
        mean = mean_cleaned_cal,
        back_cal_performed
      ) %>%
      mutate(DT_join = as.character(DT_round)) %>%
      left_join(add_data, by = "DT_join")
  })

# Grab Depth and Temperature (not back-calibrated) from flagged_data/
non_cal_corrected_data <- flagged_data_list %>%
  keep(~unique(.$parameter) %in% c("Depth", "Temperature")) %>%
  map(function(df) {
    df %>%
      mutate(back_cal_performed = FALSE,
             mean_pre_cal = mean) %>%
      select(
        DT_round,
        site,
        parameter,
        mean_pre_cal,
        mean,
        back_cal_performed,
        DT_join,
        units,
        n_obs,
        spread,
        auto_flag
      )
  })

# Bind all data together
tidy_cal_data <- c(cal_corrected_data, non_cal_corrected_data)

```

# Pass data through Drift Correction Tool

This tool is located in the script `data_organization/drift_correction_2024.Rmd`. 
Here we are applying the drift corrections identified in the manual verification 
tool to the data and then saving the output in the "post_verification" folder.

## Read in pre-calibration raw values

The 2024 data was processed before the `mean_pre_cal` column was added to the 
pipeline. Raw pre-calibration values are recovered here from `raw_data.parquet` 
and joined to the verified data downstream.

```{r}
raw_values <- read_parquet(here(base_folder, "in_progress", "raw_data", "raw_data.parquet")) %>%
  select(DT_round, site, parameter, mean_pre_cal = value)
```

## Read in Virridy back-calibrated corrections

The Virridy sites were back-calibrated out of order via 
`prep_virridy_2024_for_cal_app.R`. The back-calibrated values were saved to the 
finalized calibration RDS but never written back to `verified_directory/`. We 
recover them here to correct `value_post_cal_corr` for Virridy downstream. 
Depth and Temperature are not present (no calibration applied to those parameters).

```{r}
virridy_cal_corrections <- read_rds(here("data", "raw", "sensor", "manual_data_verification",
                                          "complete_dataset", "calibrated_sensor_field_data_finalized.rds"))[["2024"]] %>%
  keep(~ grepl("virridy", unique(.$site))) %>%
  map_dfr(~ select(., DT_round, site, parameter, mean_cleaned_cal)) %>%
  rename(mean_virridy_post_cal = mean_cleaned_cal)
```

# Prep for HydroShare Upload

We will be creating two datasets here:
- A "raw" dataset that includes all the original data with flags and all 
"versions" of the data: no manual corrections applied, calibration correction, 
post verification, and post drift correction. This is for posterity and to have 
a record of what the original data looked like before and after manual 
verification/corrections.
- A "cleaned" dataset that includes only the final value (post drift correction 
if it exists, post verification if not) and a column indicating what modifications 
were made to the data (manual exclusion, calibration correction, drift correction,
etc). This is the dataset that will be uploaded to HydroShare and used for analysis.

```{r}
drift_corrected_files <- list.files(path = 'data/raw/sensor/manual_data_verification/2024_cycle/post_verification/', pattern = "*.parquet", full.names = TRUE)

drift_corrected_data <- map_dfr(drift_corrected_files, read_parquet) %>%
  left_join(raw_values, by = c("DT_round", "site", "parameter")) %>%
  select(
    DT_round, DT_join, site, parameter, units, value_raw = mean_pre_cal,
    value_post_cal_corr = mean, value_post_ver = mean_analysis,
    value_post_drift_corr = mean_drift_trans,
    auto_qc_flag = auto_flag, mal_flag,
    user_qc_flag = user_flag, qc_status = final_status) %>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  keep(~ nrow(.x) > 0) #remove any empty datasets

non_drift_corrected_files <- list.files(path = 'data/raw/sensor/manual_data_verification/2024_cycle/in_progress/verified_directory/', pattern = "*.parquet", full.names = TRUE)

non_drift_corrected_data <- map_dfr(non_drift_corrected_files, read_parquet) %>%
  left_join(raw_values, by = c("DT_round", "site", "parameter")) %>%
  left_join(virridy_cal_corrections, by = c("DT_round", "site", "parameter")) %>%
  mutate(mean = if_else(!is.na(mean_virridy_post_cal), mean_virridy_post_cal, mean),
         mean_analysis = ifelse(verification_status %in% c("FLAGGED", "PASS"), mean, NA)) %>%
  select(DT_round, DT_join, site, parameter, units,
         value_raw = mean_pre_cal,
         value_post_cal_corr = mean,
         value_post_ver = mean_analysis,
         auto_qc_flag = auto_flag,
         mal_flag,
         user_qc_flag = user_flag,
         qc_status = final_status) %>%
  split(f = list(.$site, .$parameter), sep = "-")

#only keep non drift corrected site parameters if they are not in the drift corrected data (i.e. if they haven't been drift corrected yet)
all_datasets <- c(non_drift_corrected_data[!names(non_drift_corrected_data) %in% names(drift_corrected_data)], drift_corrected_data)%>%
  keep(~ nrow(.x) > 0) #remove any empty datasets


#units lookup table

units_table <- all_datasets%>%
  bind_rows()%>%
  select(parameter, units)%>%
  distinct()%>%
  filter(!is.na(parameter) & !is.na(units))

raw_dataset <- all_datasets%>%
  bind_rows()%>%
  #exclude springcreek and boxcreek since they were not verified in 2024
  filter(!(site %in% c("springcreek", "boxcreek")))%>%
  # if value_post_drift corr is NA, then fill with value_post_ver (this means that the data was verified but not drift corrected, so the post verification value is the most "final" version of the data we have for those instances) This is for parameters other than FDOM and Turbidity
  mutate(value_post_drift_corr = if_else(is.na(value_post_drift_corr), value_post_ver, value_post_drift_corr),
         #round all values to 3 decimal places for consistency with HydroShare upload
         value_raw = round(value_raw, 3),
         value_post_cal_corr = round(value_post_cal_corr, 3),
         value_post_ver = round(value_post_ver, 3),
         value_post_drift_corr = round(value_post_drift_corr, 3),
         #Create modifications column to indicate what modifications were made to the data for easier filtering and analysis downstream
         modifications = case_when( is.na(value_post_ver) & !is.na(value_raw) ~ "manual data exclusion",
                                    value_raw == value_post_cal_corr & value_post_ver != value_post_drift_corr ~ "drift correction",
                                    value_raw != value_post_cal_corr & value_post_ver == value_post_drift_corr ~ "calibration correction",
                                    value_raw != value_post_cal_corr & value_post_ver != value_post_drift_corr ~ "calibration correction;drift correction",
                                    TRUE ~ NA),
         #convert to UTC
         DateTime_UTC = with_tz(DT_round, tzone = "UTC"))%>%
  select(-units)%>%
  left_join(units_table, by = "parameter")%>%
  select(DateTime_MST = with_tz(DT_round, "MST"),
         DateTime_UTC,
         site, parameter, units,
         #Actual data
         value_raw,
         value_post_cal_corr,
         value_post_ver,
         value_post_drift_corr,
         #QC Info
         auto_qc_flag, mal_flag, user_qc_flag, qc_status, modifications)

final_dataset <- raw_dataset %>%
  select(DateTime_UTC, site, parameter, units, value_raw, value_final = value_post_drift_corr,user_qc_flag, modifications)

```

### Plot to Double Check

```{r}
plots <- map(unique(final_dataset$site), function(site_name) {
  ggplot(final_dataset %>% filter(site == site_name), aes(x = DateTime_UTC, y = value_final, color = modifications)) +
    geom_point(aes(y = value_raw), color = "gray", alpha = 0.5) + # add raw data points for comparison
    geom_point() +
    facet_wrap(~parameter, scales = "free_y") +
    labs(title = site_name,
         x = "Date",
         y = "Value",
         color = "QC Status")
})
walk(plots, print)
```

### Save Data

```{r}
year <- "2024"

#check if the folder exists, if not create it
if (!dir.exists(here( "data/collated/sensor/hydroshare_pub", year))) {
  dir.create(here( "data/collated/sensor/hydroshare_pub", year), recursive = TRUE)
}

cleaned_file_name <- here( "data/collated/sensor/hydroshare_pub", year, paste0("CSU_ROSS_", year,"_cleaned.csv"))

raw_file_name <- here( "data/collated/sensor/hydroshare_pub", year, paste0("CSU_ROSS_", year,"_raw.csv"))

write_csv(final_dataset, cleaned_file_name)

write_csv(raw_dataset, raw_file_name)
```

## Field Notes

```{r}
sensor_field_notes <- grab_mWater_sensor_notes(load_mWater())%>%
  filter(year(DT_round) == year & !(site %in% c("springcreek", "boxcreek")))%>%
  rename(DateTime_UTC = DT_round) %>%
  select(-photos_downloaded,-DT_join, -cal_report_collected, -sensor_swapped_notes, -end_dt, -last_site_visit, -date,-sensor_deployed, -sensor_pulled)%>%
  #Clean up crew to just initials and remove any extra text
  mutate(crew = crew %>%
    str_replace_all("Other \\(please specify\\)", "Other") %>%
    str_replace_all("([A-Z])[a-z]+", "\\1") %>%
    str_replace_all("(?<=[A-Z])\\s+(?=[A-Z])", "")
  )

field_notes_file <- here("data/collated/sensor/hydroshare_pub", year, paste0("CSU_ROSS_sensor_field_notes_", year, ".csv"))

write_csv(sensor_field_notes, field_notes_file)
```

## Location Metadata

Here we will load and double check the location metadata file created by Sam Struthers and verified by Katie Willi

```{r}
location_meta <- read_csv("data/collated/sensor/hydroshare_pub/CSU_ROSS_sonde_location_metadata.csv",
                           show_col_types = FALSE)%>%
  mutate(data_start_date = as.POSIXct(data_start_date, tz = "UTC", format = "%m/%d/%y"),
         data_end_date =  if_else( is.na(data_end_date),
                                   ymd("2024-11-30"),
                                   as.POSIXct(data_end_date, tz = "UTC", format = "%m/%d/%y")))%>%

  mutate(min_year = year(data_start_date),
         max_year = year(data_end_date),
         year_range = paste0(min_year, "-", max_year))
#update as needed
#write_csv(location_meta, here("data/collated/sensor/hydroshare_pub/CSU_ROSS_sonde_location_metadata.csv"))

tmap_mode("view")
tm_basemap("OpenStreetMap") +
  tm_shape(location_meta %>% st_as_sf(coords = c("longitude", "latitude"), crs = 4326)) +
  #color is SiteID and shape is year_range
  tm_symbols(col = "SiteID", shape = "year_range", size = 0.5, border.col = "black")

```
