---
title: "process_2022_drd"
author: "Danny Duncan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the workflow for organizing 2022 Poudre Sonde Network data. This data was collected before our current protocol was produced, and therefore requires a slightly different workflow for performing our auto-QAQC pipeline.

Generally, this year had some pretty low-quality data, as the majority of sensors' life cycles ended all at once.

## 1) Set-up

### 1.1) Package Load
```{r}
# load required packages
package_loader <- function(x) {
  if (x %in% installed.packages()) {
    suppressMessages({
      library(x, character.only = TRUE)
    })
  } else {
    suppressMessages({
      install.packages(x)
      library(x, character.only = TRUE)
    })
  }
}
non_cran_packages <- c("rossyndicate/ross.wq.tools")
invisible(
  lapply(non_cran_packages, function(x) {
    pack_name <- unlist(strsplit(x, "/"))[2] #get package name (no GH username)
    
    if (pack_name %in% installed.packages()) {
      suppressMessages({
        library(pack_name, character.only = TRUE)
      })
    } else {
      suppressMessages({
        devtools::install_github(x)
        library(pack_name, character.only = TRUE)
      })
    }
  })
)
# load all required packages
invisible(
  lapply(c("arrow", "data.table", "httr2", "tidyverse", "lubridate", "zoo", "ggpubr",
           "plotly", "padr", "stats", "RcppRoll", "yaml", "here", "furrr", "ross.wq.tools"),
         package_loader)
)

```

### 1.2) Parallel Compute Configuration
```{r}
# Configure parallel processing
max_workers <- 4  # Maximum number of parallel workers
num_workers <- min(availableCores() - 1, max_workers)
plan(multisession, workers = num_workers)
furrr_ops <- furrr_options(globals = TRUE,
                           packages = c("arrow", "data.table", "httr2", "tidyverse", "lubridate", "zoo",
                                        "padr", "stats", "RcppRoll", "yaml", "here", "ross.wq.tools")
                           )
```

### 1.3) Directory Configuration
```{r}
base_dir <- here("data","raw", "sensor","manual_data_verification","2022_cycle")
# Make sure base dir exists; create if not
if (!dir.exists(base_dir)) {
  dir.create(base_dir)
}

# Folder with downloaded logs
log_dir <- here("data","raw", "sensor", "log_download", "2022")

#Sub folders for raw and flagged data
staging_dir <- here(base_dir,"hydro_vu_pull" ,"raw_data")
flagged_temp_dir <- here(base_dir,"hydro_vu_pull" ,"flagged_data_temp")
flagged_dir <- here(base_dir,"hydro_vu_pull" ,"flagged_data")

all_path = here(base_dir,"in_progress","all_data_directory")
pre_verification_path = here(base_dir, "in_progress","pre_verification_directory")
intermediary_path = here(base_dir, "in_progress","intermediary_directory")
verified_path = here(base_dir, "in_progress","verified_directory")
raw_data_path = here(base_dir, "in_progress","raw_data")
meta_folder_path = here(base_dir, "in_progress","meta")

#check to make sure these all exist and create if needed
if (!dir.exists(staging_dir)) {
  dir.create(staging_dir, recursive = TRUE)
  }
if (!dir.exists(flagged_temp_dir)) {
  dir.create(flagged_temp_dir, recursive = TRUE)
  }
if (!dir.exists(flagged_dir)) {
  dir.create(flagged_dir, recursive = TRUE)
  }
if (!dir.exists(all_path)) {
  dir.create(all_path)
  }
if (!dir.exists(pre_verification_path)) {
  dir.create(pre_verification_path)
  }
if (!dir.exists(intermediary_path)) {
  dir.create(intermediary_path)
  }
if (!dir.exists(verified_path)) {
  dir.create(verified_path)
  }
if (!dir.exists(raw_data_path)) {
  dir.create(raw_data_path)
}
# The meta folder and associated files are necessary to run future ShinyApps
if (!dir.exists(meta_folder_path)) {
  dir.create(meta_folder_path)
  # Save copies of meta files to 2022_cycle
  # Site order file
  file.copy(from = here("data", "derived", "auto_qaqc_files", "site_order", "site_order_pre2023.yml"), 
            to = meta_folder_path)
  # Seasonal threshold file
  file.copy(from = here("data","derived","auto_qaqc_files", "thresholds","seasonal_thresholds20260304-T175010Z.csv"), 
            to = here(meta_folder_path,"seasonal_thresholds.csv"))
  # Available flags file
  file.copy(from = here("data","raw","sensor", "manual_data_verification","2025_cycle", "in_progress", "meta",   "available_flags.csv"), to = meta_folder_path)
  # Parameter auto selections file
  file.copy(from = here("data","raw","sensor", "manual_data_verification","2025_cycle", "in_progress", "meta",   "parameter_autoselections.csv"), to = meta_folder_path)
  }
```

## 2) Credentials, Thresholds, Field Notes

### 2.1) Credentials
```{r}
# Configure your credentials files
mwater_creds_file <- here("creds","creds","mWaterCreds.yml")
mWater_creds <- read_yaml(mwater_creds_file)

# pull field data from mWater API
mWater_data <- load_mWater(creds = mWater_creds)

# grab sensor malfunction records - so auto-QAQC works.
sensor_malfunction_notes <- grab_mWater_malfunction_notes(mWater_api_data = mWater_data) %>%
  mutate(start_DT = with_tz(start_DT, tzone = "UTC"),
         end_DT = with_tz(end_DT, tzone = "UTC"))

```

### 2.2) Thresholds
```{r}
# Read in the threshold data first
sensor_thresholds <- read_yaml(here("data","derived","auto_qaqc_files", "thresholds", "sensor_spec_thresholds.yml"))
season_thresholds <- read_csv(here("data","derived","auto_qaqc_files", "thresholds", "seasonal_thresholds20260304-T175010Z.csv"), show_col_types = FALSE) %>%
  fix_site_names()
```

### 2.3) Field Notes
```{r}
all_field_notes <- readxl::read_excel(here("data","raw","field_notes","sensor_field_notes.xlsx")) %>% 
  mutate(DT = (paste0(date, " ", start_time_mst))) %>%
  mutate(DT = ymd_hm(DT) + hours(7)) %>%
  arrange(DT) %>%
  mutate(DT_round = round_date(DT, "15 minutes")) %>%
  mutate(DT_round = with_tz(DT_round, tzone = "UTC"),
         last_site_visit = with_tz(DT_round, tzone = "UTC"),
         DT_join = as.character(DT_round),
         sonde_moved = NA,
         sonde_employed = case_when(is.na(sensor_deployed) & is.na(sensor_pulled) ~ NA,
                                    sensor_deployed == "x" ~ 0, 
                                    sensor_pulled == "x" ~ 1), 
         site = ifelse(site == "rist", "bellvue", site)) %>%
  ross.wq.tools::fix_site_names()%>%
  #add extra cols
  mutate(rdo_pre_clean = NA, 
         rdo_post_clean = NA,
         rdo_post_cal = NA,
         cond_pre_clean = NA,
         cond_post_clean = NA,
         cond_post_cal = NA,
         ph_pre_clean = NA,
         ph_post_clean = NA,
         ph_post_cal = NA,
         orp_pre_clean = NA,
         orp_post_clean = NA,
         orp_post_cal = NA,
         turb_pre_clean = NA,
         turb_post_clean = NA,
         turb_post_cal = NA,
         fdom_pre_clean = NA,
         fdom_post_clean = NA,
         fdom_post_cal = NA,
         chla_pre_clean = NA,
         chla_post_clean = NA,
         chla_post_cal = NA)%>%
  select(-sensors_cleaned, -wiper_working, -cal_report_collected)

```

## 3) Raw Data Ingest & Standardization

### 3.1) Ingest Data

#### 3.1.1) Rist

- Start: 2022-04-22
- End: 2022-05-20
- Notes: 
  - Sensor “capped” during low flow period. Damaged during peak flows and not re-installed during 2022.

```{r}
# Original timezone is UTC, but we'll convert to MST for linking with field notes and then convert back to UTC for auto-QAQC
rist_final <- list.files(here::here(log_dir, "rist"), full.names = TRUE, recursive = TRUE) %>%
  purrr::map_dfr(~ xml2::read_html(.x) %>% ross.wq.tools::parse_insitu_html_log()) %>% 
  mutate(DT_mst = with_tz(DT, tzone = "MST"),
         DT_mst_round = with_tz(DT_round, tzone = "MST")) %>%
  rename(DT_utc = DT, 
         DT_utc_round = DT_round) %>% 
  # Sensor pulled 2022-05-30 after sensor housing destroyed
  dplyr::filter(DT_mst_round <= ymd_hms("2022-05-30 09:00:00")) %>%
  # Sensor also capped from 5/6/2022 - 5/9/2022 (flow too low)
  dplyr::filter(!(DT_mst_round >= ymd_hms('2022-05-06 12:00:00') & DT_mst_round <= ymd_hms('2022-05-09 14:30:00'))) %>%
  dplyr::group_by(parameter) %>%
  dplyr::arrange(DT_utc) %>%
  dplyr::mutate(site = "rist",
                id = "rist",
                name = "rist") %>%
  dplyr::select(site, id, name, timestamp = DT_utc, parameter, value, units = unit) %>%
  dplyr::ungroup() %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(timestamp)) %>%
  dplyr::arrange(timestamp)

ggplot(data = rist_final) + geom_point(aes(x = timestamp, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.2) Legacy

- Start: 2022-04-07
- End: 2022-09-19
- Notes:
    - 2022-05-24: Pulled due to questionable housing integrity
    - 2022-06-01: Redeployed
    - 2022-07-08: Pulled (turbidity & conductivity problems)
    - Between 2022-07-08 & 2022-07-12: turbidity sensor completely breaks; replaced with sensor previously used at archery
    - Between 2022-07-18 & 2022-07-21: back-up sensor stopped working
    - 2022-08-03: Sonde swapped w/ rist
    - 2022-08-03/2022-08-04: Sensor suspended out of water
    - 2022-08-04: Sonde pulled due to low flows
    - 2022-08-25: Redeployed; continued turbidity & ORP issues until end of season
    
```{r}
# # Legacy genomic survey; MDT tz
genomic_survey <- grep(list.files(here::here(log_dir, "legacy", "manual"), full.names = T), pattern = "trolled", invert = FALSE, value = TRUE) %>%
  xml2::read_html() %>% ross.wq.tools::parse_insitu_html_log() %>% 
  # Convert to UTC
  mutate(DT_utc = lubridate::ymd_hms(DT) + lubridate::hours(6),
         DT_utc_round = lubridate::ymd_hms(DT_round) + lubridate::hours(6),
         # Convert original MDT time to MST
         DT = lubridate::ymd_hms(DT) - lubridate::hours(1),
         DT_round = lubridate::ymd_hms(DT_round) - lubridate::hours(1)) %>% 
  # Rename DT columns to reflect MST timezone (since that's what they actually are now)
  rename(DT_mst = DT,
         DT_mst_round = DT_round) %>%
  mutate(DT_mst = force_tz(DT_mst, tzone = "MST"),
         DT_mst_round = force_tz(DT_mst_round, tzone = "MST"))

# Legacy; UTC tz
legacy_final <- grep(list.files(here::here(log_dir, "legacy"), full.names = TRUE), pattern = "manual", invert = TRUE, value = TRUE) %>%
  purrr::map_dfr(~xml2::read_html(.x) %>% ross.wq.tools::parse_insitu_html_log()) %>% 
  mutate(DT_mst = with_tz(DT, tzone = "MST"),
         DT_mst_round = with_tz(DT_round, tzone = "MST")) %>%
  rename(DT_utc = DT, 
         DT_utc_round = DT_round) %>%
  # Remove data ranges where sensor was pulled out of field (THAT I KNOW OF, IE 2022 ONLY)
  # These are in MST time, so filter based on DT_mst_round
  dplyr::filter(!((DT_mst_round) >= ('2021-12-04 19:30:00') & (DT_mst_round) < ('2022-04-06 17:30:00')),
                !((DT_mst_round) >= ('2022-05-24 09:30:00') & (DT_mst_round) < ('2022-06-01 13:30:00')),
                !((DT_mst_round) > ('2022-07-08 14:00:00') & (DT_mst_round) <= ('2022-07-12 10:00:00')),
                !((DT_mst_round) >= ('2022-08-04 09:50:00') & (DT_mst_round) <= ('2022-08-25 16:15:00')),
                !((DT_mst_round) > ('2022-09-07 06:57:00') & (DT_mst_round) <= ('2022-09-18 07:00:00'))) %>%
  dplyr::bind_rows(genomic_survey) %>%
  dplyr::mutate(site = "legacy",
                id = "legacy",
                name = "legacy") %>%
  dplyr::select(site, id, name, timestamp = DT_utc, parameter, value, units = unit) %>%  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(timestamp)) %>%
  dplyr::arrange(timestamp)

ggplot(data = legacy_final) + geom_point(aes(x = timestamp, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.3) Lincoln (Udall)

- Start: 2022-03-24
- End: 2022-07-22
- Notes:
    - Site ran by in-situ
    - Excel of data sent mid season and not again until end of season, so data is pretty spotty.

```{r}
# OG in MDT.
raw <- readxl::read_excel(here::here(log_dir, "lincoln", "lincoln.xlsx"))

names(raw) <- make.names(names(raw), unique = T)

lincoln_final <- raw %>%
  dplyr::select(DT_instrument = tidyr::contains('Date.Time'),
                Water_Temp_C = as.numeric(contains('Temperature')),
                pH = tidyr::contains('pH'),
                ORP_mV = tidyr::contains('ORP'),
                Specific_Conductivity_µS_cm = tidyr::contains('Specific.Conductivity..µS.cm.'),
                DO_ppm = tidyr::contains('RDO.Conc'),
                Turbidity_NTU = tidyr::contains('Turbidity'),
                Depth_ft = tidyr::contains('Depth')) %>%
  dplyr::mutate_at(vars(2:ncol(.)), as.numeric) %>%
  tidyr::pivot_longer(-DT_instrument, names_to = "var", values_to = "value") %>%
  dplyr::mutate(value = as.numeric(value),
                parameter = dplyr::case_when(var == "Water_Temp_C" ~ "Temperature",
                                             var == "pH1" ~ "pH",
                                             var == "ORP_mV" ~ "ORP",
                                             var == "Specific_Conductivity_µS_cm" ~ "Specific Conductivity",
                                             var == "DO_ppm" ~ "DO",
                                             var == "Depth_ft" ~ "Depth",
                                             var ==  "Turbidity_NTU" ~ "Turbidity"),
                # Original units
                original_unit = dplyr::case_when(var == "Water_Temp_C" ~ "C",
                                                 var == "pH1" ~ "pH",
                                                 var == "ORP_mV" ~ "mV",
                                                 var == "Depth_ft" ~ "ft",
                                                 var == "Specific_Conductivity_µS_cm" ~ "µS/cm",
                                                 var == "DO_ppm" ~ "ppm",
                                                 var == "Turbidity_NTU" ~ "NTU"),
                # Target units
                units = dplyr::case_when(var == "Water_Temp_C" ~ "C",
                                         var == "pH1" ~ "pH",
                                         var == "ORP_mV" ~ "V",
                                         var == "Depth_ft" ~ "m",
                                         var == "Specific_Conductivity_µS_cm" ~ "µS/cm",
                                         var == "DO_ppm" ~ "mg/L",
                                         var == "Turbidity_NTU" ~ "NTU"),
                # Convert values to new units
                value = dplyr::case_when(var == "DO_ppm" ~ value, # ppm is equivalent to mg/L for dissolved oxygen 
                                         var == "Depth_ft" ~ value * 0.3048, # feet to meters
                                         var == "ORP_mV" ~ value / 1000, # millivolts to volts
                                         TRUE ~ value),
                # Fix site/id/name from lincoln to udall
                site = "lincoln",
                id = "lincoln",
                name = "lincoln") %>% 
  # MDT to UTC
  rename(DT_mdt_instrument = DT_instrument) %>%
  dplyr::mutate(DT_utc_instrument = lubridate::ymd_hms(DT_mdt_instrument) + lubridate::hours(6)) %>%
  dplyr::select(site, id, name, timestamp = DT_utc_instrument, parameter, value, units) %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(parameter)) %>%
  dplyr::filter(!is.na(timestamp)) %>%
  dplyr::arrange(timestamp) %>%
  pivot_wider(id_cols = c(site, id, name, timestamp),
              names_from = parameter, values_from = value)%>%
  filter(!(is.na(pH) & Temperature <= 0)) %>%
  pivot_longer( cols = any_of(c("Temperature", "Depth", "Specific Conductivity", "DO", "pH", "Turbidity", "ORP")),
                names_to = "parameter",values_to = "value")

ggplot(data = lincoln_final) + geom_point(aes(x = timestamp, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.4) Timberline

- Start: 2022-04-06
- End: 2022-11-15
- Notes:

```{r}
# Timberline; UTC tz
timberline_final <- grep(list.files(here::here(log_dir, "timberline"), full.names = TRUE), pattern = "manual", invert = TRUE, value = TRUE) %>%
  purrr::map_dfr(~xml2::read_html(.x) %>% ross.wq.tools::parse_insitu_html_log()) %>% 
  mutate(DT_mst = with_tz(DT, tzone = "MST"),
         DT_mst_round = with_tz(DT_round, tzone = "MST")) %>%
  rename(DT_utc = DT, 
         DT_utc_round = DT_round) %>%
  dplyr::filter(!(DT_mst_round > ymd_hms('2022-01-01 08:15:00') & DT_mst_round <= ymd_hms('2022-04-06 08:15:00'))) %>% 
  dplyr::mutate(site = "timberline",
                id = "timberline",
                name = "timberline") %>%
  dplyr::select(site, id, name, timestamp = DT_utc, parameter, value, units = unit) %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(timestamp)) %>%
  dplyr::arrange(timestamp)

ggplot(data = timberline_final) + geom_point(aes(x = timestamp, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.5) Prospect

- Start: 2022-04-30
- End: 2022-11-15
- Notes:

```{r}
# Prospect; UTC tz
prospect_final <- grep(list.files(here::here(log_dir, "prospect"), full.names = TRUE), pattern = "manual", invert = TRUE, value = TRUE) %>%
  purrr::map_dfr(~xml2::read_html(.x) %>% ross.wq.tools::parse_insitu_html_log()) %>% 
  mutate(DT_mst = with_tz(DT, tzone = "MST"),
         DT_mst_round = with_tz(DT_round, tzone = "MST")) %>%
  rename(DT_utc = DT, 
         DT_utc_round = DT_round) %>% 
  dplyr::mutate(site = "prospect",
                id = "prospect",
                name = "prospect") %>%
  dplyr::select(site, id, name, timestamp = DT_utc, parameter, value, units = unit) %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(timestamp)) %>%
  dplyr::arrange(timestamp)

ggplot(data = prospect_final) + geom_point(aes(x = timestamp, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.6) ELC

- Start: 2022-04-23
- End: 2022-11-15
- Notes:
    - 2022-05-26: Pulled (unsuitable site)
    - 2022-06—23: Manual measurements for genomic survey
    - 2022-07-27: Re-deployed near boxelder WWTP outfall; continued issues with turbidity and ORP until end of season

```{r}
# ELC manual data; MDT tz
elc_spring <- grep(list.files(here::here(log_dir, "elc", "manual"), full.names = TRUE), pattern = "trolled", invert = FALSE, value = TRUE) %>%
  purrr::map_dfr(~xml2::read_html(.x) %>% ross.wq.tools::parse_insitu_html_log()) %>% 
  # Convert to UTC
  mutate(DT_utc = lubridate::ymd_hms(DT) + lubridate::hours(6),
         DT_utc_round = lubridate::ymd_hms(DT_round) + lubridate::hours(6),
         # Convert original MDT time to MST
         DT = lubridate::ymd_hms(DT) - lubridate::hours(1),
         DT_round = lubridate::ymd_hms(DT_round) - lubridate::hours(1)) %>% 
  # Rename DT columns to reflect MST timezone (since that's what they actually are now)
  rename(DT_mst = DT,
         DT_mst_round = DT_round) %>%
  mutate(DT_mst = force_tz(DT_mst, tzone = "MST"),
         DT_mst_round = force_tz(DT_mst_round, tzone = "MST")) %>% 
  dplyr::filter(lubridate::month(DT_utc) < 7) %>% 
  select(!c(DT_mst, DT_mst_round, DT_utc_round, DT_join))

# ELC boxelder data; UTC tz
elc_at_boxelder <- grep(list.files(here::here(log_dir, "elc"), full.names = TRUE), pattern = "Boxelder", invert = FALSE, value = TRUE) %>%
  purrr::map_dfr(~xml2::read_html(.x) %>% ross.wq.tools::parse_insitu_html_log()) %>% 
  mutate(DT_mst = with_tz(DT, tzone = "MST"),
         DT_mst_round = with_tz(DT_round, tzone = "MST")) %>%
  rename(DT_utc = DT, 
         DT_utc_round = DT_round) %>%
  dplyr::filter(!is.na(value)) %>% 
  select(!c(DT_mst, DT_mst_round, DT_utc_round, DT_join))

# OG UTC
elc_replacement <- grep(list.files(here::here(log_dir, "elc"), full.names = TRUE), pattern = "Rist", invert = FALSE, value = TRUE) %>%
  purrr::map_dfr(~xml2::read_html(.x) %>% ross.wq.tools::parse_insitu_html_log()) %>% 
  mutate(DT_mst = with_tz(DT, tzone = "MST"),
         DT_mst_round = with_tz(DT_round, tzone = "MST")) %>%
  rename(DT_utc = DT, 
         DT_utc_round = DT_round) %>% 
  dplyr::filter(lubridate::month(DT_utc) >= 9) %>%
  dplyr::filter(!is.na(value)) %>% 
  select(!c(DT_mst, DT_mst_round, DT_utc_round, DT_join))

elc_final <- elc_spring %>%
  dplyr::bind_rows(elc_at_boxelder) %>%
  dplyr::bind_rows(elc_replacement) %>%
  dplyr::mutate(site = "elc",
                id = "elc",
                name = "elc") %>%
  dplyr::select(site, id, name, timestamp = DT_utc, parameter, value, units = unit) %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(timestamp)) %>%
  dplyr::arrange(timestamp)
```

#### 3.1.7) Archery

- Start: 2022-04-06
- End: 2022-11-15
- Notes:
    - Swapped w/ back-up sensor (Fossil Creek) due to early season issues with Chl-a, temp, cond.
    - Between 2022-07-01 & 2022-07-06: Burried
    - 2022-07-14: Unclogged
    - 2022-10-04 & 2022-10-07: Sensor capped

```{r}
#OG data in UTC.
# parse_insitu_html() doesn't pick up the Chl-a, for some reason... so, need to grab outside that function here...
archery_chla <- grep(list.files(here::here("data", "raw", "sensor", "log_download", "2022", "archery"), full.names = TRUE), pattern = "TROLL", invert = FALSE, value = TRUE) %>%
  map_dfr(~rvest::read_html(.) %>%
            rvest::html_node('table') %>%
            rvest::html_table() %>%
            dplyr::slice(-1:-8) %>%
            janitor::row_to_names(row_number = 1) %>%
            select(DT_utc = `Date Time`, value = `Chl-a Fluorescence (RFU)`) %>%
            mutate(DT_utc = ymd_hms(DT_utc),
                   DT_utc_round = round_date(DT_utc, "15 minutes"),
                   DT_mst = with_tz(DT_utc, tzone = "MST"),
                   DT_mst_round = with_tz(DT_utc_round, tzone = "MST"),
                   unit = "RFU",
                   parameter = "Chl-a Fluorescence",
                   value = as.numeric(value)) %>%
            filter(!is.na(value)))

# OG data in UTC
archery_final <- grep(list.files(here::here("data", "raw", "sensor", "log_download", "2022", "archery"), full.names = TRUE), pattern = "TROLL", invert = FALSE, value = TRUE) %>%
  purrr::map_dfr(~xml2::read_html(.x) %>% ross.wq.tools::parse_insitu_html_log()) %>%   
  mutate(DT_mst = with_tz(DT, tzone = "MST"),
         DT_mst_round = with_tz(DT_round, tzone = "MST")) %>%
  rename(DT_utc = DT, 
         DT_utc_round = DT_round) %>%
  dplyr::bind_rows(archery_chla) %>%
  dplyr::filter(!(DT_mst_round > ymd_hms('2022-10-04 15:00:00') & DT_mst_round <= ymd_hms('2022-10-07 16:00:00'))) %>% 
  dplyr::mutate(site = "archery",
                id = "archery",
                name = "archery") %>%
  dplyr::select(site, id, name, timestamp = DT_utc, parameter, value, units = unit) %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(timestamp)) %>%
  dplyr::arrange(timestamp)

ggplot(data = archery_final) + geom_point(aes(x = timestamp, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

### 3.2) Standardize Data

#### 3.2.1) Combine Site Data
 
```{r}
all_sites <- bind_rows(rist_final, legacy_final, lincoln_final, timberline_final, 
                       prospect_final, elc_final, archery_final)
```

#### 3.2.2) Depth Mis-calibration Correction

```{r}
# Legacy depth corrections
legacy_depth_corrected <- all_sites %>%
    filter(parameter == "Depth",
           site == "legacy") %>%  
  # UTC to MST conversion to link with field notes
  mutate(timestamp = with_tz(timestamp, tzone = "MST")) %>%
  # First correction: 2022-04-06 to 2022-04-12
  mutate(value_p1 = ifelse(timestamp >= ymd_hms('2022-04-06 06:00:00', tz = 'MST') & timestamp < ymd_hms('2022-04-12 9:20:00', tz = 'MST'), 
                           value + abs(filter(., timestamp == ymd_hms('2022-04-12 09:15:00', tz = "MST"))$value 
                                       - filter(., timestamp == ymd_hms('2022-04-12 16:30:00', tz = "MST"))$value), 
                           value)
         ) %>%
  # Second correction: 2022-07-22 to 2022-07-25
  #timestamp > ymd_hms('2022-07-22 16:45:00') & timestamp < ymd_hms('2022-07-25 21:29:00')
  mutate(value_p2 = ifelse(timestamp > ymd_hms('2022-07-22 09:45:00', tz = 'MST') & timestamp < ymd_hms('2022-07-25 14:29:00', tz = 'MST'), 
                           value_p1 + abs(filter(., timestamp == ymd_hms('2022-07-25 14:15:00', tz = "MST"))$value_p1 
                                          - filter(., timestamp == ymd_hms('2022-07-25 14:29:00', tz = "MST"))$value_p1), 
                           value_p1)
         ) %>%
  mutate(value = value_p2) %>%
  select(-value_p1, 
         -value_p2) %>%
  # Convert timestamp back to UTC
  mutate(timestamp = with_tz(timestamp, tzone = "UTC"))

```

```{r}
# Timberline depth corrections
# weird mis-calibration
timberline_depth_corrected <- all_sites %>%
  filter(parameter == "Depth",
         site == "timberline") %>%
  # UTC to MST conversion to link with field notes
  mutate(timestamp = with_tz(timestamp, tzone = "MST")) %>%
  # First correction: 2022-04-06 to 2022-04-07
  mutate(value_p1 = ifelse(timestamp >= ymd_hms('2022-04-06 07:00:00', tz = 'MST') & timestamp < ymd_hms('2022-04-07 16:56:00', tz = 'MST'), 
                           value + abs(filter(., timestamp == ymd_hms('2022-04-07 16:15:00', tz = 'MST'))$value 
                                       - filter(., timestamp == ymd_hms('2022-04-07 17:15:00', tz = 'MST'))$value), 
                           value)
         ) %>% 
  # purposefully shifted sonde up in housing:
  # Second correction: after 2022-09-14
  mutate(value_p2 = ifelse(timestamp >= ymd_hms('2022-09-14 13:15:00', tz = 'MST'), 
                           value_p1 + abs(filter(., timestamp == ymd_hms('2022-09-14 13:00:00', tz = "MST"))$value_p1 
                                          - filter(., timestamp == ymd_hms('2022-09-14 13:15:00', tz = "MST"))$value_p1),
                           value_p1)
         ) %>%
  mutate(value = value_p2) %>%
  select(-value_p1,
         -value_p2) %>%
  # Convert timestamp back to UTC
  mutate(timestamp = with_tz(timestamp, tzone = "UTC"))

```

```{r}
# combine corrected depths with original data
all_sites_corrected <- all_sites %>%
  filter(!(parameter == "Depth" & site == "legacy")) %>%
  filter(!(parameter == "Depth" & site == "timberline")) %>%
  bind_rows(legacy_depth_corrected, timberline_depth_corrected) %>%
  fix_site_names() %>%
  arrange(site, timestamp, parameter)
```

```{r}
# Red indicates the complete corrected depth time series
# Black indicates the original depth mis-calibrations
plotly::ggplotly(ggplot() +
  geom_line(data = all_sites %>% filter(parameter == "Depth" & site %in% c("legacy")), aes(x = timestamp, y = value), color = "black")+
  geom_line(data = all_sites_corrected %>% filter(parameter == "Depth" & site %in% c("salyer")), aes(x = timestamp, y = value),linetype = "solid", color = "red"))

plotly::ggplotly(ggplot() +
  geom_line(data = all_sites %>% filter(parameter == "Depth" & site %in% c("timberline")), aes(x = timestamp, y = value), color = "black")+
  geom_line(data = all_sites_corrected %>% filter(parameter == "Depth" & site %in% c("riverbend")), aes(x = timestamp, y = value),linetype = "solid", color = "red"))
```

## 4) Save Raw Data

### 4.1) Split by Site & Year
```{r}
raw_data_site_year <- all_sites_corrected %>%
  distinct(.keep_all = TRUE) %>%
  mutate(year = year(timestamp)) %>%
  split(f = list(.$site, .$year), sep = "_", drop = TRUE)
```

### 4.2) Save as Parquet
```{r}
# Save files
iwalk(raw_data_site_year, ~ {
  latest_ts <- format(max(.x$timestamp, na.rm = TRUE), "%Y-%m-%d_%H%M")
  site_name <- str_split(.y, "_")[[1]][1]  # Extract just the site name (first part)
  data_dir <- here(staging_dir)
  if (!dir.exists(data_dir)) {
    dir.create(data_dir, recursive = TRUE)
  }  
  filename <- here(staging_dir, paste0(tolower(site_name), "_", latest_ts, ".parquet"))
  .x %>% select(-year) %>% write_parquet(filename)
  cat("Saved:", filename, "\n")
})
```

## 5) Tidy, Join, & Summarize

### 5.1) Tidy Raw Data
```{r}
# tidy raw data (default 15-minute intervals)
tidy_data <-  raw_data_site_year %>%
  bind_rows() %>%
  mutate(DT_round = round_date(timestamp, "15 minutes")) %>%
  mutate(DT_join = as.character(paste(DT_round))) %>%
  ross.wq.tools::fix_site_names(., site_col = "site") %>%
  select(DT_round, DT_join, site, parameter, value, units) %>%
  mutate(site = ifelse(site == "rist", "bellvue", site)) %>%
  distinct(.keep_all = TRUE) %>%
  modify_if(., is.numeric, ~ ifelse(is.nan(.x) | is.infinite(.x), NA, .x)) %>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  keep(~nrow(.) > 0) %>%
  future_map(~tidy_api_data(api_data = .), .progress = TRUE) %>%
  keep(~!is.null(.))
```

### 5.2) Join with Field Notes
```{r}
combined_data <- tidy_data %>%
  future_map(~add_field_notes(df = ., notes = all_field_notes), .progress = TRUE)
```

### 5.3) Summary Statistics
```{r}
# generate summary statistics
summarized_data <- combined_data %>%
  map(~generate_summary_statistics(.)) %>%
  # extra step to get rid of NaN and Inf values
  map(~ {modify_if(.x, is.numeric, ~ ifelse(is.nan(.x) | is.infinite(.x), NA, .x))})
```

### 5.4) Visualize Summary Statistics
```{r}
summary_plotz <- map(names(summarized_data), ~ {
  ggplot(data = summarized_data[[.x]]) +
    geom_point(aes(x = DT_round, y = mean), na.rm = TRUE) +
    labs(
      title = .x,
      x = "Date/Time",
      y = "Mean Value"
    ) +
    theme_minimal()
})

walk(summary_plotz, print)
```

### 5.5) Back-Calibration

#### 5.5.1) Load Calibration Data
```{r read-cal-data}
# This creates calibration_data list object needed for the back-calibration functions
# 2022 cal_data is present
load_calibration_data(
  cal_data_file_path = here::here("data", "collated", "sensor", "cal_reports", "munged_calibration_data.RDS"),
  update = FALSE, # set to TRUE when running for the first time
  field_cal_dir = here::here("data", "raw", "sensor", "calibration_reports")
)
```

When initially running this script, only five sites were passed to the back-calibration app. Upon further inspection, it was discovered that the site names in the calibration data did not match the site names in the sensor data. Although the 'fix_site_names()' function works for sensor_data, it does not work for calibration data. The following code fixes this issue by renaming the sites in the calibration data to match the sensor data (updated site names).
```{r fix-cal-site-names}

calibration_data[["2022"]] <- calibration_data[["2022"]] %>% 
  bind_rows() %>% 
  mutate(site = if_else(site == "rist", "bellvue", site),
         site = if_else(site == "legacy", "salyer", site),
         site = if_else(site == "lincoln", "udall", site),
         site = if_else(site == "timberline", "riverbend", site),
         site = if_else(site == "prospect", "cottonwood", site),
         site = if_else(site == "boxelder", "elc", site)
         ) %>% 
  split(f = list(.$site, .$sensor), sep = "-")

```

#### 5.5.2) Join Sensor & Cal Data

Organize sensor data to match calibration data
```{r organize-sensor-data}
# Results in a nested list structure: `sensor_data$2022$site-parameter`
sensor_data <- tidy_data %>%
  bind_rows() %>%
  split(f = year(.$DT_round)) %>%
  map(~ {
    split_data <- split(.x, f = list(.x$site, .x$parameter), sep = "-")
    discard(split_data, ~is.null(.) || nrow(.) == 0)
  })
```

Join sensor & calibration data
```{r join-cal-data}
sensor_calibration_data <- cal_join_sensor_calibration_data(
  sensor_data_list = sensor_data,
  calibration_data_list = calibration_data
)
# No calibration data for lincoln/udall
# This results in the lack of udall files in post back-calibration file.
```

Prep data for back-calibration
```{r prep-data}
prepped_snsr_cal_data <- cal_prepare_calibration_windows(
  sensor_calibration_data_list = sensor_calibration_data
) 
```

#### 5.5.3) Back-Calibrate Sensor Data
```{r apply-back-cal}
calibrated_data <- prepped_snsr_cal_data%>%
  map(function(year){
    year%>%
      map(function(site_param){
        site_param %>% 
          map_dfr(function(chunk){
            cal_back_calibrate(chunk)
          })
      })
  })
```

#### 5.5.4) Save Back-Calibrated Data

Write back-calibrated data as an .rds file in the 2022 dir
```{r}
write_rds(calibrated_data, here(base_dir,"hydro_vu_pull","back_calibration", "calibrated_sensor_data_2022.rds"))
```

FUTURE WORK: Copy the app into the PSN repo so that the app can be run directly from this document 
(See section 7.1 for example)
From here, we will review the back-calibrated data in Juan's ShinyApp

```{r}
# To load this ShinyApp directly from the script, fork Juan's ShinyApp from GitHub, save it to your local directory, and then link the local directory path below
back_cal_path <- "~/github/manual_cal_ver"

```

### 5.6) Manual Calibration Verification

#### 5.6.1) Load Finalized Back-Calibrated Data

Load our finalized calibrated data. This is the file generated from finalization of the back-calibration ShinyApp
```{r}
calibrated_data_final <- read_rds(here("data", "raw", "sensor", "manual_data_verification", "2022_cycle","hydro_vu_pull","back_calibration", "calibrated_sensor_field_data_finalized.rds"))[["2022"]]
```

#### 5.6.2) Plot Calibrated Data
```{r}
plots <- map(names(calibrated_data_final), 
             function(site_param) {
               plot_data <- calibrated_data_final[[site_param]]
               
               vline_df <- plot_data %>% 
                 group_by(sensor_date) %>% 
                 slice_min(DT_round, n = 1) %>%
                 arrange(DT_round)%>%
                 ungroup()%>%
                 select(DT_round, file_date)%>%
                 mutate(file_date_mst = with_tz(file_date, tzone = "MST"), 
                        file_date_mst_utc = force_tz(file_date_mst, tzone = "UTC"))
               
               param <- unique(plot_data$parameter)
               site <- unique(plot_data$site)
               
               ggplotly(ggplot(plot_data, aes(DT_round))+
                          geom_line(aes(y = mean, color = "raw"))+
                          geom_line(aes(y = mean_cal, color = "final"))+
                          geom_vline(xintercept = vline_df$file_date_mst_utc, linetype = "dashed")+
                          scale_color_manual(name = "Data Type", values = c("raw" = "blue", "final" = "green4"))+
                          labs(title = paste0(site, " - ", param),
                               x = "Date",
                               y = param))
             })%>%
  set_names(names(calibrated_data_final))

#Typically easiest to go parameter-wise through the plots 
plots[grepl("pH", names(plots))]
```

#### 5.6.3) Tidy Back-Calibrated Data

Here we are removing columns that are not needed downstream to reduce memory usage.
We are also merging back in the units, n_obs, spread and flag columns from the original tidy data.
Temperature and Depth are not passed into the back-calibration process so we will grab those from the original tidy data as well.
We will also add the column "back_cal_performed" to indicate whether a back-calibration was actually applied to the data or not.

```{r}
cal_corrected_data <- calibrated_data_final%>%
  map(., function(df){
    
    site <- unique(df$site)
    parameter <- unique(df$parameter)
    
    site_param = paste0(site, "-", parameter)
    
    add_data <- tidy_data[[site_param]]%>%
      select( DT_join, units, n_obs, spread, flag)
    
    if("updated_slope_from" %in% names(df)){
      df <- df%>%
        mutate(back_cal_performed = if_else(slope == updated_slope_to & slope == updated_slope_from, F, T))
    } else {
      df <- df%>%
        mutate(back_cal_performed = F)
    }
    
    df%>%
      select(
        DT_round,
        site,
        parameter,
        mean_pre_cal = mean,
        mean = mean_cal,
        back_cal_performed
      )%>%
      mutate(DT_join = as.character(DT_round))%>%
      left_join(add_data, by = c("DT_join"))
  })

# Since Udall (lincoln) data was not included in the post back-calibration data, we will need to grab that data from the tidy_data object and merge it here as well.
# We will also need to grab the Depth and Temperature data (not back calibrated) and merge it here.
non_cal_udall_data <- tidy_data %>%
  keep(~unique(.$site) %in% c("udall")) %>% 
    map(., function(df){
    df%>%
      mutate(back_cal_performed = FALSE,
             mean_pre_cal = mean)%>%
      select(,
             DT_round,
             site,
             parameter,
             mean_pre_cal,
             mean,
             back_cal_performed,
             DT_join,
             units,
             n_obs,
             spread,
             flag
      )
  })

non_cal_corrected_data <- tidy_data%>%
  keep(~unique(.$parameter) %in% c("Depth", "Temperature"))%>%
  map(., function(df){
    df%>%
      mutate(back_cal_performed = FALSE,
             mean_pre_cal = mean)%>%
      select(,
             DT_round,
             site,
             parameter,
             mean_pre_cal,
             mean,
             back_cal_performed,
             DT_join,
             units,
             n_obs,
             spread,
             flag
      )
  })

# Bind all data together
tidy_cal_data <- c(cal_corrected_data, non_cal_udall_data, non_cal_corrected_data)
```

Now, we'll combine the field notes for a final dataset that can undergo data-flagging
```{r}
# Add the field note data to our tidy data
combined_data <- tidy_cal_data %>%
  future_map(~add_field_notes(df = ., notes = all_field_notes), .progress = TRUE)

# Add summary statistics
summarized_data <- combined_data %>%
  map(~generate_summary_statistics(.))
```

## 6) Data Flagging

### 6.1) Single-Sensor Flagging

The first stage of data flagging is within each sensor itself, operating on a per-site-parameter basis.
These next functions apply flags to the data based on the following criteria:
- Field visit notes
- Missing data
- Repeating values
- Depth shifts
- Optical sensor drift
- Specification range violations
- Seasonal range violations

```{r}
# Chunk the data for furrr
summarized_data_chunks <- split(1:length(summarized_data),
                                ceiling(seq_along(1:length(summarized_data))/10))
# Flag data...
# Single parameter flags
single_sensor_flags <- list()
for (chunk_idx in seq_along(summarized_data_chunks)) {
  message("\n=== Processing chunk ", chunk_idx, " of ", length(summarized_data_chunks), " ===")
  
  # Get the indices for this chunk
  indices <- summarized_data_chunks[[chunk_idx]]
  chunk_data <- summarized_data[indices]
  
  # Process the chunk in parallel
  chunk_results <- chunk_data %>%
    future_map(
      function(data) {
        flagged_data <- data %>%
          data.table(.) %>%
          # flag field visits
          add_field_flag(df = .) %>%
          # flag missing data
          add_na_flag(df = .) %>%
          # flag DO noise
          find_do_noise(df = .) %>%
          # flag repeating values
          add_repeat_flag(df = .) %>%
          # find times when sonde was moved up/down in housing
          add_depth_shift_flag(df = ., level_shift_table =  all_field_notes) %>%
          # find instances of sensor drift (FDOM, Chl-a, Turbidity only)
          add_drift_flag(df = .)
        
        if (unique(data$parameter) %in% names(sensor_thresholds)) {
          # flag instances outside the spec range
          flagged_data <- flagged_data %>%
            data.table(.) %>%
            add_spec_flag(df = ., spec_table = sensor_thresholds)
        }
        
        if (unique(data$parameter) %in% unique(season_thresholds$parameter)) {
          # flag instances outside the spec range
          flagged_data <- flagged_data %>%
            data.table(.) %>%
            add_seasonal_flag(df = ., threshold_table = season_thresholds)
        }
        
        flagged_data <- flagged_data %>%
          data.table(.)
        
        return(flagged_data)
      },
      .progress = TRUE, .options = furrr_ops
    )
  
  # Add chunk to list
  single_sensor_flags <- c(single_sensor_flags, chunk_results)
  
  if (chunk_idx < length(summarized_data_chunks)) {
    message("Taking a short break before next chunk...")
    gc()
    Sys.sleep(0.1)
  }
}

# beep to let you know when it's done
beepr::beep(1)
```

### 6.2) Intra-Sensor Flagging

The second stage of flagging requires multiple data parameters from the same sensor to be present.
The intra-sensor function will flag data based on the following criteria:
- Frozen water (temperature < 0°C)
- Unsubmerged sonde (depth < 0 ft, specific conductivity < 10 µS/cm)
- Buried sonde (long-term DO noise)

To prevent overflagging, an inter-sensor check removes slope violation flags that occur concurrently with temp or depth violations.

```{r}
intrasensor_flags <- single_sensor_flags %>%
  rbindlist(fill = TRUE) %>%
  split(by = "site")

# Chunk the data for furrr
intrasensor_data_chunks <- split(1:length(intrasensor_flags),
                                 ceiling(seq_along(1:length(intrasensor_flags))/3))

intrasensor_flags_list <- list()
for (chunk_idx in seq_along(intrasensor_data_chunks)) {
  message("\n=== Processing chunk ", chunk_idx, " of ", length(intrasensor_data_chunks), " ===")
  
  # Get the indices for this chunk
  indices <- intrasensor_data_chunks[[chunk_idx]]
  chunk_data <- intrasensor_flags[indices]
  # Process the chunk in parallel
  chunk_results <- chunk_data %>%
    future_map(
      function(data) {
        # A chunk is a site df
        flagged_data <- data %>%
          data.table() %>%
          # flag times when water was below freezing
          add_frozen_flag(.) %>%
          # overflagging correction. remove slope violation flag if it occurs concurrently
          # with temp or depth
          intersensor_check(.) %>%
          # add sonde burial. If DO is noise is long-term, likely burial:
          add_burial_flag(.) %>%
          # flag times when sonde was unsubmerged
          add_unsubmerged_flag(.)
        
        return(flagged_data)
      }, .progress = TRUE, .options = furrr_ops
    ) %>%
    rbindlist(fill = TRUE) %>%
    # lil' cleanup of flag column contents
    dplyr::mutate(flag = ifelse(flag == "", NA, flag)) %>%
    distinct(site, parameter, DT_round, mean, .keep_all = TRUE) %>%
    # transform back to site-parameter dfs
    split(f = list(.$site, .$parameter), sep = "-") %>%
    purrr::discard(~ nrow(.) == 0) %>%
    # Add in KNOWN instances of sensor malfunction
    map(~add_malfunction_flag(df = ., malfunction_records = sensor_malfunction_notes))
  
  # Add chunk to list
  intrasensor_flags_list <- c(intrasensor_flags_list, chunk_results)
  
  if (chunk_idx < length(intrasensor_data_chunks)) {
    message("Taking a short break before next chunk...")
    gc()
    Sys.sleep(0.1)
  }
}

# beep to let you know when it's done
beepr::beep(1)
```

Save the single-sensor/intra-sensor flagged data as a checkpoint.
```{r}
# Save newest flagged datasets to temp dir
iwalk(intrasensor_flags_list, ~write_parquet(.x, here(flagged_temp_dir, paste0(.y, ".parquet"))))

# Load the flagged datasets back in from temp dir (if needed)
intrasensor_flags_list <- list.files(here(flagged_temp_dir), pattern = "*.parquet", full.names = TRUE) %>%
  map(~read_parquet(.x)) %>% 
  set_names(list.files(here(flagged_temp_dir), pattern = "*.parquet", full.names = FALSE) %>%
              str_remove(".parquet"))
```

### 6.3) Network Flagging

The function `ross.wq.tools::network_check()` compares data across sensor sites within the sonde network to identify over-flagging occurrences and remove flags when needed.

This step requires knowledge of the site order, which is read in from a YAML file and should be updated as sites change.
```{r}
# Read in site order from YAML file (pre-2023)
site_order_22 <- load_site_order(here("data","derived","auto_qaqc_files", "site_order", "site_order_pre2023.yml"))

# Network flagging
network_flags <- intrasensor_flags_list %>%
  map(~network_check(df = ., intrasensor_flags_arg = intrasensor_flags_list, site_order_arg = site_order_22)) %>%
  rbindlist(fill = TRUE) %>%
  tidy_flag_column() %>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  map(~add_suspect_flag(.)) %>%
  rbindlist(fill = TRUE)

# Final flagging
final_flags <- network_flags %>%
  mutate(auto_flag = ifelse(is.na(auto_flag), 
                            NA,
                            ifelse(auto_flag == "suspect data" & is.na(lag(auto_flag, 1)) & is.na(lead(auto_flag, 1)), 
                                   NA, 
                                   auto_flag)
                            )
         ) %>%
  select(c("DT_round", "DT_join", "site", "parameter", 
           "mean_pre_cal", "mean", "units", "n_obs", "spread", 
           "auto_flag", "mal_flag", "sonde_moved","sonde_employed", 
           "season", "last_site_visit", "depth_change", "back_cal_performed")
         ) %>%
  mutate(auto_flag = ifelse(is.na(auto_flag), 
                            NA, 
                            ifelse(auto_flag == "", 
                                   NA, 
                                   auto_flag))) %>%
  mutate(year = year(DT_round)) %>%
  split(f = list(.$site, .$parameter), sep = "_") %>%
  keep(~nrow(.) > 0)

# beep to let you know when it's done
beepr::beep(1)
```

```{r}
final_plot_data <- final_flags %>% 
  bind_rows() %>%
  split(f = list(.$site)) %>%
  keep(~nrow(.) > 0)
  
final_plotz <- map(names(final_plot_data), ~ {
  ggplot(data = final_plot_data[[.x]]) +
    geom_point(aes(x = DT_round, y = mean, color = auto_flag), na.rm = TRUE) +
    facet_wrap(~parameter, scales = "free_y") +
    #remove legend for auto_flag
    theme(legend.key = element_blank(),
          legend.title = element_blank(),
          legend.position = "none") +
    labs(
      title = .x,
      x = "Date/Time",
      y = "Mean Value"
    )
})

walk(final_plotz, print)
```

### 6.4) Save Final Flagged Dataset

With all flagging steps complete, we'll save the results in two separate directories:
- Individually flagged site-parameter parquet files for posterity and comparison with manual verification.
- A single combined parquet file for use in the manual verification process.

```{r}
# Save individual datasets
iwalk(final_flags, ~write_parquet(.x, here(flagged_dir, paste0(.y, ".parquet"))))

# Saving our data into the "raw_data" folder of the manual verification folder for use in the shiny app
write_parquet(final_flags %>% bind_rows(), here(base_dir,"in_progress","raw_data","raw_data_2022.parquet"))

# Load the flagged datasets back in from temp dir (if needed)
# final_flags_par <- read_parquet(here(base_dir,"in_progress","raw_data","raw_data_2022.parquet"))
```

## 7) Shiny Tools & Data Preparation

### 7.1) Shiny Verification Tool

For manual verification of the data, a ShinyApp has been created that allows users to visualize the data, review the flags, make any necessary corrections, and save the output. The application, and all associated files, are located within "~/shiny_ver_tool".

Key columns added by the tool include:
- final_status:
  - "PASS":  user has verified the data as good
  - "FLAGGED": user has flagged the data for suspect but still usable data
  - "OMIT": user has concluded that the data should not be used in analysis due to sensor error. 
- user_flag:
  - Specific flag added by user to indicate why data was flagged/omitted. (e.g. "suspect data", "sonde burial",
  "frozen water", "unsubmerged", "depth shift", "drift", "field visit", "other malfunction" etc). 
  This is for posterity and to help inform auto-flagging performance. 
- mean_analysis: 
  - Values where the "OMIT" final status was not applied.
  
Once complete, the output is saved in the "verified_directory" for the specified year.

```{r shiny-dependencies}
# Load required packages for ShinyApp
invisible(lapply(c("shiny","bslib","DT","tidyverse","lubridate","here","ggpubr","gridExtra","plotly",
                   "keys","patchwork","digest","fs","shinyFiles","shinyWidgets","glue","anytime","arrow"),
                 package_loader)
          )
```

Run this codechunk to launch the ShinyApp. The app will open in a new window or tab in your default web browser.
```{r, echo=FALSE}
shiny::shinyAppDir(
  appDir = here("shiny_ver_tool"),
  options = list(width = "100%", height = "100%")
)
```

### 7.2) Drift Correction Tool

Optical sensor drift is a common issue with in-situ sonde deployments, namely turbidity, fDOM and Chl-A. 

An initial RMarkdown has been created to correct the drift of these parameters for 2025. This document is located at:  "~/data_organization/drift_correction_2025.Rmd".

Although not tailored for 2022, future work will implement Juan's code for drift correction of 2022 data.

### 7.3) Data Preparation for Shiny Tools

We will be creating two datasets here: 
- A "raw" dataset that includes all the original data with flags and all "versions" of the data: no manual corrections applied, calibration correction, post verification, and post drift correction.
This is for posterity and to have a record of what the original data looked like before and after manual verification/corrections.
- A "cleaned" dataset that includes only the final value (post drift correction if it exists, post verification if not) and a column indicating what modifications were made to the data (manual exclusion, calibration correction, drift correction, etc).

This is the dataset that will be uploaded to HydroShare and used for analysis.

```{r}
drift_corrected_files <- list.files(path = 'data/raw/sensor/manual_data_verification/2022_cycle/post_verification/', pattern = "*.parquet", full.names = TRUE)

drift_corrected_data <- map_dfr(drift_corrected_files, read_parquet)%>%
  select(DT_round, DT_join, site, parameter,units, value_raw = mean_pre_cal, value_post_cal_corr = mean, value_post_ver = mean_analysis, value_post_drift_corr = mean_drift_trans,   auto_qc_flag = auto_flag, mal_flag, user_qc_flag = user_flag, qc_status = final_status)%>%
  split(f = list(.$site, .$parameter), sep = "-")%>%
  keep(~ nrow(.x) > 0) #remove any empty datasets

non_drift_corrected_files <- list.files(path = 'data/raw/sensor/manual_data_verification/2025_cycle/in_progress/verified_directory/', pattern = "*.parquet", full.names = TRUE)

non_drift_corrected_data <- map_dfr(non_drift_corrected_files, read_parquet)%>%
  mutate( mean_analysis = ifelse(verification_status %in% c("FLAGGED", "PASS"), mean, NA))%>%
  select(DT_round, DT_join, site, parameter,units,
         value_raw = mean_pre_cal, 
         value_post_cal_corr = mean, 
         value_post_ver = mean_analysis,
         auto_qc_flag = auto_flag, 
         mal_flag, 
         user_qc_flag = user_flag,
         qc_status = final_status)%>%
  split(f = list(.$site, .$parameter), sep = "-")

#only keep non drift corrected site parameters if they are not in the drift corrected data (i.e. if they haven't been drift corrected yet)
all_datasets <- c(non_drift_corrected_data[!names(non_drift_corrected_data) %in% names(drift_corrected_data)], drift_corrected_data)%>%
  keep(~ nrow(.x) > 0) #remove any empty datasets


#units lookup table

units_table <- all_datasets%>%
  bind_rows()%>%
  select(parameter, units)%>%
  distinct()%>%
  filter(!is.na(parameter) & !is.na(units))

raw_dataset <- all_datasets%>%
  bind_rows()%>%
  #exclude springcreek and boxcreek since they were not verified in 2025
  filter(!(site %in% c("springcreek", "boxcreek")))%>%
  # if value_post_drift corr is NA, then fill with value_post_ver (this means that the data was verified but not drift corrected, so the post verification value is the most "final" version of the data we have for those instances) This is for parameters other than FDOM and Turbidity
  mutate(value_post_drift_corr = if_else(is.na(value_post_drift_corr), value_post_ver, value_post_drift_corr),
         #round all values to 3 decimal places for consistency with HydroShare upload
         value_raw = round(value_raw, 3),
         value_post_cal_corr = round(value_post_cal_corr, 3),
         value_post_ver = round(value_post_ver, 3),
         value_post_drift_corr = round(value_post_drift_corr, 3),
         #Create modifications column to indicate what modifications were made to the data for easier filtering and analysis downstream
         modifications = case_when( is.na(value_post_ver) & !is.na(value_raw) ~ "manual data exclusion",
                                    value_raw == value_post_cal_corr & value_post_ver != value_post_drift_corr ~ "drift correction",
                                    value_raw != value_post_cal_corr & value_post_ver == value_post_drift_corr ~ "calibration correction",
                                    value_raw != value_post_cal_corr & value_post_ver != value_post_drift_corr ~ "calibration correction;drift correction",
                                    TRUE ~ NA), 
         #convert to UTC
         DateTime_UTC = with_tz(DT_round, tzone = "UTC"))%>%
  select(-units)%>%
  left_join(units_table, by = "parameter")%>%
  select(DateTime_MST = DT_round,
         DateTime_UTC,
         site, parameter, units, 
         #Actual data
         value_raw, 
         value_post_cal_corr,
         value_post_ver,
         value_post_drift_corr, 
         #QC Info
         auto_qc_flag, mal_flag, user_qc_flag, qc_status, modifications)
    
final_dataset <- raw_dataset %>%
  select(DateTime_UTC, site, parameter, units, value_raw, value_final = value_post_drift_corr,user_qc_flag, modifications)

```
