---
title: "Processing 2026 Data Pull from HydroVu with Auto Back-Calibration and QA/QC Flagging"
author: "Sam Struthers - CSU ROSSyndicate"
date: "`r Sys.Date()`"
output: html_document
---

# Script Purpose & Scope

This script is designed to pull in sensor data from HydroVu for the 2026 monitoring season, apply auto back-calibrations, export data for manual checks of back calibration issues, and run through the automated QA/QC flagging process. The final flagged dataset will be saved for manual review and verification.



## Setup Libraries 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# loading packages
package_loader <- function(x) {
  if (x %in% installed.packages()) {
    suppressMessages({
      library(x, character.only = TRUE)
    })
  } else {
    suppressMessages({
      install.packages(x)
      library(x, character.only = TRUE)
    })
  }
}

invisible(
  lapply(c("arrow",
           "sf",
           "tmap",
           "data.table",
           "httr2",
           "tidyverse",
           "lubridate",
           "zoo",
           "padr",
           "stats",
           "RcppRoll",
           "yaml",
           "here",
           "ross.wq.tools",
           "furrr",
           "plotly"
  ),
  package_loader)
)

# Set up parallel processing
num_workers <- min(availableCores() - 1, 4) # Use at most 4 workers
plan(multisession, workers = num_workers)
set_furr_options <- furrr_options(
  globals = TRUE,
  packages = c("arrow", "data.table", "httr2", "tidyverse","dplyr", "lubridate", "zoo",
               "padr", "stats", "RcppRoll", "yaml", "here", "ross.wq.tools")
)

# suppress scientific notation to ensure consistent formatting
options(scipen = 999)

```

## Setting up the site/time range/parameters for the data pull

We deploy our sensors in March and pull them by the end of November. 
Always triple check the sites listed below to remove sites no longer deployed and add sites deployed this year. 
Double check the parameters of interest for spelling and inclusion of all needed parameters.

```{r}
#Adjust dates for specific pull
mst_start <- ymd_hms("2026-03-01 00:00:00", tz = "America/Denver")
mst_end <- ymd_hms("2026-11-30 23:59:59", tz = "America/Denver")
# Compute UTC time once
mst_start_utc <- with_tz(mst_start, tzone = "UTC")
pull_end      <- with_tz(mst_end,   tzone = "UTC")

sites <- c(
  #Upper sites
  "chd","pfal", "pbr", "sfm",  "pman", "pbd",
  #Lower sites
  "bellvue","salyer", "udall", "riverbend","cottonwood", "elc","archery","riverbluffs")

#Setting parameters of interest
parameters <- c("Specific Conductivity", "Temperature", "DO", "pH", "ORP", "Depth", #Standard vars
                "Chl-a Fluorescence", "Turbidity", "FDOM Fluorescence") #optical vars
```

## Establishing directory paths.

These are the folders where raw, and flagged data will be saved. Update base_folder to the current year and log directory as needed

```{r}
base_folder <- here("data","raw", "sensor","manual_data_verification","2026_cycle")
# Make sure base folder exists and create if not
if (!dir.exists(base_folder)) {
  dir.create(base_folder)
}

#folder with downloaded logs
log_directory <- here("data","raw", "sensor",  "log_download", "2026")  #Change as needed

#Sub folders for raw and flagged data
staging_directory <- here(base_folder,"hydro_vu_pull" ,"raw_data")
flagged_temp_dir <- here(base_folder,"hydro_vu_pull" ,"flagged_data_temp")
flagged_directory <- here(base_folder,"hydro_vu_pull" ,"flagged_data")

#check to make sure these all exist and create if needed
if (!dir.exists(staging_directory)) {
  dir.create(staging_directory, recursive = TRUE)
}
if (!dir.exists(flagged_temp_dir)) {
  dir.create(flagged_temp_dir, recursive = TRUE)
}
if (!dir.exists(flagged_directory)) {
  dir.create(flagged_directory, recursive = TRUE)
}

```

### Clear folders
If you are re-running this script, you may want to clear out the flagged and flagged_temp folders to avoid duplicate data.
This is useful as we re-run the workflow throughout the field season for reporting and QA/QC purposes. When working on final verification, comment out these lines. 

```{r}
list.files(flagged_temp_dir, full.names = TRUE) %>%
  walk(file.remove)
list.files(flagged_directory, full.names = TRUE) %>%
  walk(file.remove)
```


## Read in thresholds and credentials

Sensor thresholds are from In-Situ Inc spec sheets and seasonal_thresholds are created using `ross.wq.tools::make_threshold_table()` using cleaned data from previous years. 
mWater and HydroVu creds are created from their respective websites, contact Sam Struthers, Juan De La Torre or Katie Willi for help obtaining these.

```{r}
# Read in the threshold data first
sensor_thresholds <- read_yaml(here("data","derived","auto_qaqc_files", "thresholds",  "sensor_spec_thresholds.yml"))
season_thresholds <- read_parquet(here("data","derived","auto_qaqc_files", "thresholds", "seasonal_thresholds20260304-T175010Z.parquet"), show_col_types = FALSE) %>%
  fix_site_names()

# Read in credentials
mWater_creds <- read_yaml(here("creds", "mWaterCreds.yml"))

hv_creds <- read_yaml(here("creds", "HydroVuCreds.yml"))
hv_token <- hv_auth(client_id = as.character(hv_creds["client"]),
                    client_secret = as.character(hv_creds["secret"]))

```

# Data Pulls

Once these sections have been run and data have been checked using plots below, these sections should be commented out as they will take a long time to re-run. 

## Pulling in field notes from mWater
```{r}
# Pull in all notes
mWater_data <- load_mWater(creds = mWater_creds)
# Only extract sensor visits
all_field_notes <- grab_mWater_sensor_notes(mWater_api_data = mWater_data)%>%
  mutate(DT_round = with_tz(DT_round, tzone = "UTC"), # grab_mWater_sensor_notes converts this to MST, converting back to UTC for DS use
         last_site_visit = with_tz(last_site_visit, tzone = "UTC"),
         DT_join = as.character(DT_round))
# Only extract sensor malfunctions
sensor_malfunction_notes <- grab_mWater_malfunction_notes(mWater_api_data = mWater_data)%>%
  mutate(start_DT = with_tz(start_DT, tzone = "UTC"),# grab_mWater_malfunction_notes converts this to MST, converting back to UTC for DS use
         end_DT = with_tz(end_DT, tzone = "UTC"))
```

## Pulling in the sensor data from hydrovu

## HydroVu Pull

This section will take quite a while to load (~ 2-4 min per month of data per site). Once data has been pulled and checked, comment this section out to avoid re-running it.

```{r}
# # Get all the site info from HydroVu
hv_sites <- hv_locations_all(hv_token)
#trim down to just the sites/types of devices we want
hv_sites <- hv_sites %>%
  #Remove Vulinks
  filter(!grepl("vulink", name, ignore.case = TRUE)) %>%
  #Remove Virridy sites/sondes
  filter(!grepl("virridy", name, ignore.case = TRUE)) %>%
  #remove any older sites (containing 2023 or 2024 in the name)
  filter(!grepl("2023|2024", name, ignore.case = TRUE))

# Helper: non-log staged files for one site
list_site_files <- function(site) {
  list.files(staging_directory, full.names = TRUE) %>%
    keep(~ startsWith(basename(.x), site) & !grepl("log", basename(.x)))
}

# Latest timestamp already staged, per site (UTC)
staged_files <- list.files(staging_directory, full.names = TRUE) %>%
  keep(~ !grepl("log", basename(.x)))

if (length(staged_files) > 0) {
  message("Staging directory is not empty. Only new data will be pulled.")
  max_dts <- staged_files %>%
    map_dfr(read_parquet, col_select = c(site, timestamp)) %>%
    group_by(site) %>%
    summarise(max_dt = max(timestamp, na.rm = TRUE), .groups = "drop") %>%
    mutate(max_dt = with_tz(max_dt, tzone = "UTC"))
  #check that all the sites are in max_dts and if not, add them with NA for max_dt
  missing_sites <- setdiff(sites, max_dts$site)
  if (length(missing_sites) > 0) {
    message("The following sites are missing from the staging directory and will pulled from the start DT: ", paste(missing_sites, collapse = ", "))
    max_dts <- bind_rows(max_dts, tibble(site = missing_sites, max_dt = as.POSIXct(NA, tz = "UTC")))
  }
  
} else {
  message("Staging directory is empty. All data will be pulled from HydroVu.")
  max_dts <- tibble(site = character(), max_dt = as.POSIXct(character(), tz = "UTC"))
}

walk(sites, function(site) {

  # Zero-length if the site has nothing staged; max() then falls back to mst_start
  last_staged_dt <- max_dts %>% filter(site == !!site) %>% pull(max_dt)
  pull_start <- max(c(last_staged_dt, mst_start_utc), na.rm = TRUE)

  if (pull_start >= pull_end) {
    message("Skipping ", site, ": staged data already runs through ", pull_start)
    return(invisible(NULL))
  }

  message("Requesting HV data for: ", site,
          " (", pull_start, " to ", pull_end, " UTC)")

  api_puller(
    site = site,
    start_dt = pull_start,
    end_dt = pull_end,
    api_token = hv_token,
    hv_sites_arg = hv_sites,
    dump_dir = staging_directory
  )

  # Merge this site's files into one (api_puller's new file + any existing ones)
  site_files <- list_site_files(site)
  if (length(site_files) == 0) {
    message("No staged data found for ", site, " after pull.")
    return(invisible(NULL))
  }

  all_site_data <- site_files %>%
    map_dfr(read_parquet) %>%
    distinct()   # also removes the overlapping row at pull_start

  max_dt_format <- format(max(all_site_data$timestamp, na.rm = TRUE),
                          "%Y%m%d-T%H%M%SZ", tz = "UTC")
  new_file <- file.path(staging_directory, paste0(site, max_dt_format, ".parquet"))

  # Write first, then remove only the old files (never the one just written)
  write_parquet(all_site_data, new_file)
  file.remove(site_files[basename(site_files) != basename(new_file)])
})

# beep to let you know when it's done
beepr::beep(1)
```

## Pulling in any downloaded log data

Some logs (Vulink Log if sonde is AT600/800) cannot be backed up to HydroVu. If you have any of these files, we will read them in here so that we are not missing any potential data. Once this has been run and data checked, comment this section out to avoid re-running it.

```{r}
log_files <- list.files(log_directory, pattern = "\\vulink.html$", full.names = TRUE)%>%
  #only keep files with our sites in them
  keep(~any(str_detect(tolower(.x), sites)))

log_files_simp <- log_files%>%
  str_replace(log_directory, "")%>%
  str_replace("/", "")%>%
  str_replace_all("\\.html", "")%>%
  str_squish()
# 
log_data <- map(log_files, ~rvest::read_html(.x)%>%
                            parse_insitu_html_log())

names(log_data) <- log_files_simp

cleaned_log_data <- log_data%>%
  rbindlist()%>%
  #fixing a few specific location names before passing to fix_site_names
  mutate( site = tolower(site),
          id = as.double(sensor_sn),
         timestamp = with_tz(DT, tzone = "UTC"),
         site = case_when(site == "archery range"~ "archery",
                         site == "boxelder creek" ~ "boxcreek",
                         site == "spring creek" ~ "springcreek",
                         TRUE ~ site),
         name = paste0("Vulink Log - ", site),
         #Correcting for parse log where temp is saved with degrees C rather than C
         units = case_when(parameter == "Temperature" ~ "C",
                           TRUE ~ unit)
         )%>%
  fix_site_names()%>%
  select(site, id, name, timestamp, parameter, value, units) %>%
  distinct(.keep_all = TRUE) %>%
  split(f = list(.$site), sep = "-") %>%
  keep(~nrow(.) > 0)

#write out the log data to the staging directory so it can be processed with the HV data
iwalk(cleaned_log_data, ~write_parquet(.x, here(staging_directory, paste0(.y, "_log_data.parquet"))))

# beep to let you know when it's done
beepr::beep(1)

```


# Raw Data Processing

This is where we will read in all the pulled data from HydroVu and our parsed logs to then be tidied and checked.

## Load in and tidy the raw files

Here we use `munge_api_data()` and `tidy_api_data()` functions from `ross.wq.tools` to read in and tidy the raw data files. Our output will include lists seperated by site-parameter combinations for easier processing downstream. Each list has DT_round (in UTC), site, parameter, units, mean, n_obs, spread, DT_join and flag columns and is summarized to a 15 minute interval
```{r}
#Since we no longer have any virridy sites in the network, we can just use a normal munge!
hv_data <- munge_api_data(api_dir = staging_directory,synapse_env = F)%>%
  # split into site-parameter combinations for parallel processing
  split(f = list(.$site, .$parameter), sep = "-") %>%
  keep(~nrow(.) > 0)

tidy_data <- hv_data %>%
  future_map(~tidy_api_data(api_data = .),.progress = TRUE, .options = set_furr_options) %>%  # the summarize interval default is 15 minutes
  keep(~!is.null(.))%>%
  # Only keep parameters we are interested in
  keep(~unique(.$parameter) %in% parameters)

```
## Double check that pulls were successful

Check that we have all the sites/parameters and date ranges we expect

```{r}
tidy_data%>%
  bind_rows()%>%
  mutate(parameter = case_when(
    parameter == "FDOM Fluorescence" ~ "FDOM",
    parameter == "Chl-a Fluorescence" ~ "Chl-a",
    parameter == "Specific Conductivity" ~ "SpCond",
    parameter == "Turbidity" ~ "Turb",
    parameter == "Temperature" ~ "Temp",
    TRUE ~ parameter
  ), 
  date = as.Date(DT_round))%>%
  summarise(date_range = paste(range(date, na.rm = T), collapse = " -- "),
            n_obs = n(),
            #get me a list of all the parameters in the data
            parameters = paste(unique(parameter), collapse = ", "), .by = "site")
```


We are giving it a quick look over to make sure there aren't any large data gaps (>1 day) in the data pulled, that all site names are being applied correctly and that we don't have duplicate data. We are also adding in our field notes to the plots to make sure the data we have lines up with the periods we expect the sondes to be deployed and recording data. 

```{r}

data_check <- tidy_data%>%
  bind_rows()%>%
  #Summarizing to an hour to speed up plotting
  mutate(DT_hourly = floor_date(DT_round, unit = "1 hour"))%>%
  group_by(site, parameter, DT_hourly)%>%
  summarize(hourly_med = median(mean,na.rm = T ))%>%
  split(f = list(.$site))

data_check_plots <- data_check%>%
  map(., function(df) {
    
    field_notes <- all_field_notes %>%filter(site == unique(df$site) & year(DT_round) == "2026")%>%
      select(DT_round,sonde_employed)%>%
      mutate(sonde_changed = case_when(sonde_employed == 0 ~ "Deployed",
                                       sonde_employed == 1 ~ "Pulled",
                                       TRUE ~ "Active"))
    malfunction_notes <- sensor_malfunction_notes %>%filter(site == unique(df$site) & year(start_DT) == "2026")%>%
      select(start_DT, end_DT, parameter)%>%
      mutate(parameter = ifelse(parameter == "FDOM",  "FDOM Fluorescence", parameter))
    
    ggplot(df) +
      geom_point(aes(x = DT_hourly, y = hourly_med)) +
      geom_vline(data = field_notes, aes(xintercept = DT_round, color = sonde_changed))+
      geom_rect(data = malfunction_notes, aes(xmin = start_DT, xmax = end_DT, ymin = -Inf, ymax = Inf), fill = "gray", alpha = 0.8)+
      facet_wrap(~parameter, scales = "free_y")+
      labs(title = unique(df$site),
           x = "Date",
           y = "Hourly Median Value", 
           color = "Sonde Status")
  })
#Plot
walk(.x = data_check_plots, .f = print)

```

If there are discrepancies in the data, double check the raw files downloaded from HydroVu and the log files to make sure everything looks correct. Ocassionally there are issues with the HydroVu download missing data and that can be rerun for an individual site. If there continue to be large gaps in data (>3 days) during deployment periods, check field notes or contact Sam Struthers for troubleshooting.

# Apply Back-calibration as needed

This uses the Shiny App (`calibration_correction_tool`) developed by Juan.
We are essentially deciding when a sensor needs to be back-calibrated based on field notes and applying the back-calibration to the raw data before flagging.
The majority of calibrations are fine as is but we want to "skip" over the bad ones.

## Read in calibration data

```{r}
#This creates calibration_data list object needed for the back-calibration functions
#NOTE: This will take a good while to run if update = T
# load_calibration_data(
#   cal_data_file_path = here::here("data", "collated", "sensor", "cal_reports", "munged_calibration_data.RDS"),
#     update = FALSE, # set to TRUE when running for the first time
#   field_cal_dir = here::here("data", "raw", "sensor", "calibration_reports")
# ) 


```

### Organize sensor data to match formatting for `cal_join_sensor_calibration_data()`

Data should be in a nested list structure: `sensor_data$years$site-parameter`

```{r}
# sensor_data <- tidy_data %>%
#   bind_rows()%>%
#   #filter out virridy data bc they were not calibrated for this year
#   filter(!grepl("virridy", site, ignore.case = T))%>%
#   split(f = year(.$DT_round)) %>%
#   map(~ {
#     split_data <- split(.x, f = list(.x$site, .x$parameter), sep = "-")
#     discard(split_data, ~is.null(.) || nrow(.) == 0)
#   })

```

### Join to calibration data and apply back-calibration

This workflow follows the workflow outlined in the `ross.wq.tools` vignette on back calibration.
First, we join the calibration and sensor data so that each time instance has the slope and intercept info needed for back-calibration.
Next, we prepare the calibration windows to split the data into calibration windows.
Lastly we loop through each calibration window to apply the back-calibration using `cal_back_calibrate()`.

```{r}
# 
# sensor_calibration_data <- cal_join_sensor_calibration_data(
#   sensor_data_list = sensor_data,
#   calibration_data_list = calibration_data
#  )
# 
# prepped_snsr_cal_data <- cal_prepare_calibration_windows(
#   sensor_calibration_data_list = sensor_calibration_data
#  )
# 
# calibrated_data <- prepped_snsr_cal_data%>%
#   map(function(year){
#     year%>%
#       map(function(site_param){
#         site_param %>%
#           map_dfr(function(chunk){
#             cal_back_calibrate(chunk)
#           })
#       })
#   })
# 
# beepr::beep(1)

```

## Save to back calibrated folder

This will become the "original" file in the shiny app for manual verification

```{r}
# 
#  back_cal_dir <- here("data", "raw", "sensor", "manual_data_verification", "2026_cycle","hydro_vu_pull","back_calibration")
# 
# if(!dir_exists(back_cal_dir)){
#   dir_create(back_cal_dir)
# }
# 
#  write_rds(calibrated_data, here(back_cal_dir, "calibrated_sensor_data_2026.rds"))
#  write_rds(new_tracking, here(back_cal_dir, "calibrated_sensor_field_data_tracking.rds"))
```

Take \^ file and run through the shiny app to verify back-calibration and make any manual adjustments as needed.

# Run back calibration shiny app

```{r}
# 
# # Load required packages for ShinyApp
#  invisible(lapply(c("shiny","bslib","DT","tidyverse","lubridate","here","ggpubr","gridExtra","plotly",
#                    "keys","patchwork","digest","fs","shinyFiles","shinyWidgets","glue","anytime","arrow"),
#                  package_loader)
#            )
```

Run this code chunk to launch the calibration correction tool.
The app will open in a new window or tab in your default web browser.

```{r, echo=FALSE}
# shiny::shinyAppDir(
#   appDir = here("calibration_correction_tool"),
#   options = list(width = "100%", height = "100%")
#  )
```

## Read in user corrected back-calibrated data

```{r}
 # calibrated_data_final <- read_rds(here("data", "raw", "sensor", "manual_data_verification", "2026_cycle","hydro_vu_pull","back_calibration", "calibrated_sensor_field_data_finalized.rds"))[["2026"]] # Only extract the 2026 data

```

## Quick look at the back-calibrated data

All of this should already have been double checked by the user but we just want to make sure everything looks good before proceeding to flagging.
This plot will show the raw vs back-calibrated data ("final") with vertical lines indicating when the calibration events occurred.

```{r}
# 
# plots <- map(names(calibrated_data_final),
#              function(site_param) {
#                plot_data <- calibrated_data_final[[site_param]]
# 
#                vline_df <- plot_data %>%
#                  group_by(sensor_date) %>%
#                  slice_min(DT_round, n = 1) %>%
#                  arrange(DT_round)%>%
#                  ungroup()%>%
#                  select(DT_round, file_date)%>%
#                  mutate(file_date_mst = with_tz(file_date, tzone = "MST"),
#                         file_date_mst_utc = force_tz(file_date_mst, tzone = "UTC"))
# 
#                param <- unique(plot_data$parameter)
#                site <- unique(plot_data$site)
# 
#                ggplotly(ggplot(plot_data, aes(DT_round))+
#                           geom_line(aes(y = mean, color = "raw"))+
#                           geom_line(aes(y = mean_cal, color = "final"))+
#                           geom_vline(xintercept = vline_df$file_date_mst_utc, linetype = "dashed")+
#                           scale_color_manual(name = "Data Type", values = c("raw" = "blue", "final" = "green4"))+
#                           labs(title = paste0(site, " - ", param),
#                                x = "Date",
#                                y = param))
#              })%>%
#    set_names(names(calibrated_data_final))
# 
# #Typically easiest to go parameter-wise through the plots
#  plots[grepl("pH", names(plots))]

```

## Remove columns as needed

Here we are removing columns that are not needed downstream to reduce memory usage.
We are also merging back in the units, n_obs, spread and flag columns from the original tidy data.
Temperature and Depth are not passed into the back-calibration process so we will grab those (and any other site-parameters that were not calibrated) from the original tidy data as well.
We will also add the column "back_cal_performed" to indicate whether a back-calibration was actually applied to the data or not.

```{r}
# # 
# cal_corrected_data <- calibrated_data_final%>%
#     map(., function(df){
# 
#     site <- unique(df$site)
#     parameter <- unique(df$parameter)
# 
#     site_param = paste0(site, "-", parameter)
# 
#     add_cols <- tidy_data[[site_param]]%>%
#       select( DT_join, units, n_obs, spread, flag)
#   
# 
#     if("updated_slope_from" %in% names(df)){
#       df <- df%>%
#         mutate(back_cal_performed = if_else(slope == updated_slope_to & slope == updated_slope_from, F, T))
#     } else {
#       df <- df%>%
#         mutate(back_cal_performed = F)
#     }
# 
#     df <- df%>%
#       select(
#         DT_round,
#         site,
#         parameter,
#         mean_pre_cal = mean,
#         mean = mean_cal,
#         back_cal_performed
#       )%>%
#       #DT_join is dropped in the calibration process so we need to add it back in to join with the tidy_data columns
#       #This is still in UTC so we can join with the tidy_data columns
#       mutate(DT_join = as.character(DT_round))%>%
#       left_join(add_data, by = c("DT_join"))
#     #Some data is missed if there is not sufficient calibration files to create windows across all data
#     #Here we can grab the data that was not back-calibrated and add it back in with the back_cal_performed column set to FALSE
#     non_caled_data <- tidy_data[[site_param]]%>%
#       filter(!(DT_join %in% df$DT_join))%>%
#        mutate(back_cal_performed = FALSE, 
#               mean_pre_cal = mean)
#    df%>%
#       bind_rows(non_caled_data)
#     })
# # 
# # # We will also need to grab the non-calibrated data (temperature and depth, virridy sites and other sites without calibration info) and add it back in with the back_cal_performed column set to FALSE
# 
# non_calibrated_names <- setdiff(names(tidy_data), names(calibrated_data_final))
# 
# non_cal_corrected_data <- tidy_data[non_calibrated_names]%>%
#   map(., function(df){
#     df%>%
#       mutate(back_cal_performed = FALSE,
#              mean_pre_cal = mean)%>%
#       select(,
#              DT_round,
#              site,
#              parameter,
#              mean_pre_cal,
#              mean,
#              back_cal_performed,
#              DT_join,
#              units,
#              n_obs,
#              spread,
#              flag
#       )
#   })
# 
# # 
# # # Bind all data together
#   tidy_cal_data <- c(cal_corrected_data, non_cal_corrected_data)

```

### Depth Corrections

If we have a site visit where depth was adjusted up or down, we want to try to correct that.
This code was originally done after the verification step but we should do it here to avoid having to re-run the verification step after depth corrections are applied.

This code will need to be modified to work with the new data structure.

#### Function

```{r}
# 
# adjust_depth_window <- function(data, 
#                                 site_oi,
#                                 win_start, 
#                                 win_end, 
#                                 dt_before, 
#                                 dt_start, 
#                                 site_col = "site",
#                                 tz = "MST") {
#   #Double check that the tz matches the data$DT_round tz
#   if (tz(data$DT_round) != tz) {
#     stop(paste("Timezone mismatch: data$DT_round is in", tz(data$DT_round), "but tz argument is", tz))
#   }
#   #Double check that this site exists in the data
#   if (!site_oi %in% unique(data[[site_col]])) {
#     stop(paste("Site", site_oi, "not found in data. Available sites:", paste(unique(data[[site_col]]), collapse = ", ")))
#   }  
#   
#   w_start   <- ymd_hm(win_start, tz = tz)
#   w_end     <- ymd_hm(win_end, tz = tz)
#   t_before  <- ymd_hm(dt_before, tz = tz)
#   t_start   <- ymd_hm(dt_start, tz = tz)
#   
#   # Ensure target column exists; initialize with 'mean' if it's the first run
#   if (!"adj_depth" %in% names(data)) {
#     data <- data %>% 
#       mutate(adj_depth = mean)%>%
#       mutate(depth_corrected = FALSE)
#   }
#   
#   # Extract values specifically for this site using current state of adj_depth
#   site_mask <- data[[site_col]] == site_oi
#   val_before <- data$adj_depth[site_mask & data$DT_round == t_before]
#   val_start  <- data$adj_depth[site_mask & data$DT_round == t_start]
#   
#   # Safety Check: check if timestamps exist
#   if (length(val_before) == 0 || length(val_start) == 0) {
#     warning(paste("Target timestamps missing for site:", site, "- Skipping."))
#     return(data)
#   }
#   
#   offset <- val_before[1] - val_start[1]
#   
#   # Update ONLY the matching rows, leaving all other sites/rows untouched
#   data %>%
#     mutate(
#       adj_depth = if_else(
#         .data[[site_col]] == site_oi & DT_round >= w_start & DT_round <= w_end & final_status != "OMIT",
#         adj_depth + offset,
#         adj_depth
#       ), 
#       depth_corrected = if_else(
#         .data[[site_col]] == site_oi & DT_round >= w_start & DT_round <= w_end,
#         TRUE,
#         depth_corrected
#       ), 
#       user_flag = if_else(
#         .data[[site_col]] == site_oi & DT_round >= w_start & DT_round <= w_end,
#         gsub("calibration error", "", user_flag),
#         user_flag
#       ), 
#       user_flag = if_else(user_flag == "", NA_character_, user_flag), 
#       #Update decision to "PASS"
#       final_status = if_else(
#         .data[[site_col]] == site_oi & DT_round >= w_start & DT_round <= w_end & final_status != "OMIT",
#         "PASS",
#         final_status
#       )
#     )
# }

```

#### Applying

```{r}
# 
# depth_files <- list.files(path = 'data/raw/sensor/manual_data_verification/2026_cycle/in_progress/verified_directory/', pattern = "*.parquet", full.names = TRUE)%>%
#   grep(pattern = "depth", x = ., ignore.case = TRUE,value = T)
# 
# depth_data <- map_dfr(depth_files, read_parquet)%>%
#   #Riverbend Depth Adjustment
#     adjust_depth_window(
#     site_oi      = "riverbend",
#     win_start = "2026-09-29 16:30",
#     win_end   = "2026-11-08 10:15",
#     dt_before = "2026-09-29 15:30",
#     dt_start  = "2026-09-29 16:30"
#   )%>%
#     adjust_depth_window(
#     site_oi      = "riverbend",
#     win_start = "2026-11-08 10:30",
#     win_end   = "2026-11-15 14:45",
#     dt_before = "2026-11-08 10:15",
#     dt_start  = "2026-11-08 10:30"
#   )%>%
#   #remove any instances where the final status is OMIT from the mean_analysis column so that they are not used in analysis
#   mutate(mean_analysis = ifelse(final_status  %in% c("FLAGGED", "PASS"), adj_depth, NA))
# 
# 
# 
# final_depth_data<- depth_data%>%
#   mutate(#double check that user flag is consistent with final status
#           user_flag = if_else(final_status == "PASS", NA, user_flag))%>%
#   select(DT_round, DT_join, site, parameter,units, 
#          value_raw = mean_pre_cal, #orginal raw data
#          value_post_cal_corr = adj_depth, # calibration corrected depth (code above)
#          value_post_ver = mean_analysis, # Omit data removed
#          value_post_drift_corr = mean_analysis,   # same as omit data removed
#          auto_qc_flag = auto_flag, mal_flag, 
#          user_qc_flag = user_flag, qc_status = final_status)
# 
# 
# ggplotly(ggplot(final_depth_data%>%filter(site %in% c( "riverbend")), aes(x = DT_round, y = value_raw))+
#   geom_point()+
#   geom_point(aes(y = value_post_ver, color = user_qc_flag),  alpha = 1)+
#   #geom_line(aes(y = value_post_cal_corr), color = "black", alpha = 0.5)+
# 
#   labs(title = "Depth Data with Adjustments",
#        x = "Date",
#        y = "Depth (m)",
#        color = "Depth Corrected")+
#   facet_wrap(~site, scales = "free_y"))

```


# Data Flagging

## Combine with field notes
Here we read in our field notes and then join them to the calibrated data using `add_field_notes()`. We then generate summary statistics (slope, lag, etc) using `generate_summary_statistics()`.
```{r}

# Add the field note data to all of the data
all_field_notes <- all_field_notes %>%
  fix_site_names()

combined_data <- tidy_data %>% #update to tidy_cal_data when ready to apply back-calibrated data
  future_map(~add_field_notes(df = ., notes = all_field_notes), .progress = TRUE)

# Add summary statistics
summarized_data <- combined_data %>%
  map(~generate_summary_statistics(.))

```

## Single Sensor Flags

This is the first round of flagging that is done on a per-site-parameter basis. Here we are applying functions to flag field visits, missing data, DO noise, repeating values, depth shifts, optical sensor drift, spec range violations and seasonal range violations. This can take ~5-15 min depending on data volume.

```{r}
# Chunk the data for furrr
summarized_data_chunks <- split(1:length(summarized_data),
                                ceiling(seq_along(1:length(summarized_data))/10))
# Flag data...
# Single parameter flags
single_sensor_flags <- list()
for (chunk_idx in seq_along(summarized_data_chunks)) {
  message("\n=== Processing chunk ", chunk_idx, " of ", length(summarized_data_chunks), " ===")
  
  # Get the indices for this chunk
  indices <- summarized_data_chunks[[chunk_idx]]
  chunk_data <- summarized_data[indices]
  
  # Process the chunk in parallel
  chunk_results <- chunk_data %>%
    future_map(
      function(data) {
        flagged_data <- data %>%
          data.table(.) %>%
          # flag field visits
          add_field_flag(df = .) %>%
          # flag missing data
          add_na_flag(df = .) %>%
          # flag DO noise
          find_do_noise(df = .) %>%
          # flag repeating values
          add_repeat_flag(df = .) %>%
          # find times when sonde was moved up/down in housing
          add_depth_shift_flag(df = ., level_shift_table =  all_field_notes, post2024 = TRUE) %>%
          # find instances of sensor drift (FDOM, Chl-a, Turbidity only)
          add_drift_flag(df = .)
        
        if (unique(data$parameter) %in% names(sensor_thresholds)) {
          # flag instances outside the spec range
          flagged_data <- flagged_data %>%
            data.table(.) %>%
            add_spec_flag(df = ., spec_table = sensor_thresholds)
        }
        
        if (unique(data$parameter) %in% unique(season_thresholds$parameter)) {
          # flag instances outside the spec range
          flagged_data <- flagged_data %>%
            data.table(.) %>%
            add_seasonal_flag(df = ., threshold_table = season_thresholds)
        }
        
        flagged_data <- flagged_data %>%
          data.table(.)
        
        return(flagged_data)
      },
      .progress = TRUE, .options = set_furr_options
    )
  
  # Add chunk to list
  single_sensor_flags <- c(single_sensor_flags, chunk_results)
  
  if (chunk_idx < length(summarized_data_chunks)) {
    message("Taking a short break before next chunk...")
    gc()
    Sys.sleep(0.1)
  }
}

# beep to let you know when it's done
beepr::beep(1)

```

## Intrasensor flags

Now we will apply flags that require multiple parameters from the same sensor to be present. This includes frozen water flagging (temp < 0C), unsubmerged flagging (depth < 0 or SC < 10) and sonde burial flagging (long-term DO noise). We also do an intersensor check to remove slope violation flags that occur concurrently with temp or depth violations to reduce overflagging. This can take ~5-15 min depending on data volume.

```{r}

intrasensor_flags <- single_sensor_flags %>%
  rbindlist(fill = TRUE) %>%
  split(by = "site")

# Chunk the data for furrr
intrasensor_data_chunks <- split(1:length(intrasensor_flags),
                                 ceiling(seq_along(1:length(intrasensor_flags))/3))

intrasensor_flags_list <- list()
for (chunk_idx in seq_along(intrasensor_data_chunks)) {
  message("\n=== Processing chunk ", chunk_idx, " of ", length(intrasensor_data_chunks), " ===")
  
  # Get the indices for this chunk
  indices <- intrasensor_data_chunks[[chunk_idx]]
  chunk_data <- intrasensor_flags[indices]
  # Process the chunk in parallel
  chunk_results <- chunk_data %>%
    future_map(
      function(data) {
        # A chunk is a site df
        flagged_data <- data %>%
          data.table() %>%
          # flag times when water was below freezing
          add_frozen_flag(.) %>%
          # overflagging correction. remove slope violation flag if it occurs concurrently
          # with temp or depth
          intersensor_check(.) %>%
          # add sonde burial. If DO is noise is long-term, likely burial:
          add_burial_flag(.) %>%
          # flag times when sonde was unsubmerged
          add_unsubmerged_flag(.)
        
        return(flagged_data)
      }, .progress = TRUE, .options = set_furr_options
    ) %>%
    rbindlist(fill = TRUE) %>%
    # lil' cleanup of flag column contents
    dplyr::mutate(flag = ifelse(flag == "", NA, flag)) %>%
    distinct(site, parameter, DT_round, mean, .keep_all = TRUE) %>%
    # transform back to site-parameter dfs
    split(f = list(.$site, .$parameter), sep = "-") %>%
    purrr::discard(~ nrow(.) == 0) %>%
    # Add in KNOWN instances of sensor malfunction
    map(~add_malfunction_flag(df = ., malfunction_records = sensor_malfunction_notes))
  
  # Add chunk to list
  intrasensor_flags_list <- c(intrasensor_flags_list, chunk_results)
  
  if (chunk_idx < length(intrasensor_data_chunks)) {
    message("Taking a short break before next chunk...")
    gc()
    Sys.sleep(0.1)
  }
}

# beep to let you know when it's done
beepr::beep(1)

```

### Let's temporarily save this data so we can remove everything else from memory

```{r}
iwalk(intrasensor_flags_list, ~write_parquet(.x, here(flagged_temp_dir, paste0(.y, ".parquet"))))

#remove everything other than intrasensor flags from memory
rm(list=setdiff(ls(), c("base_folder", "intrasensor_flags_list", "flagged_directory")))
#clean up memory
gc()

```

## Applying network check

The network check function `ross.wq.tools::network_check()` compares data across sites to identify when data is being overflagged and remove flags as needed. This step requires knowledge of the site order, which is read in from a YAML file and should be updated as sites change.

```{r}
#Read in site order for year/pull
site_order_2026 <- load_site_order( here("data","derived","auto_qaqc_files", "site_order", "PWQN_site_order_2026.yml"))

#Applying Network check (non parrallel so only map used)
final_flags <- intrasensor_flags_list %>%
  map(~network_check(df = ., intrasensor_flags_arg = intrasensor_flags_list, site_order_arg = site_order_2026)) %>%
  rbindlist(fill = TRUE) %>%
  tidy_flag_column() %>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  map(~add_suspect_flag(.)) %>%
  rbindlist(fill = TRUE)

v_final_flags <- final_flags%>%
  mutate(auto_flag = ifelse(is.na(auto_flag), NA,
                            ifelse(auto_flag == "suspect data" & is.na(lag(auto_flag, 1)) & is.na(lead(auto_flag, 1)), NA, auto_flag))) %>%
  select(c("DT_round", "DT_join", "site", "parameter",
           #"mean_pre_cal", 
           "mean", "units", "n_obs", "spread", "auto_flag", "mal_flag", "sonde_moved","sonde_employed", "season", "last_site_visit", "depth_change"))%>%
           #, "back_cal_performed")) %>%
  mutate(auto_flag = ifelse(is.na(auto_flag), NA, ifelse(auto_flag == "", NA, auto_flag))) %>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  keep(~nrow(.) > 0)

# beep to let you know when it's done
beepr::beep(1)

```

## Check final output

Here we are making sure that all sites data were flagged and giving a quick look at the flagged data to make sure everything looks correct. With newer sites/parameters, we expect there to be over-flagging as the seasonal ranges/slopes are going to be very small. 

```{r}
v_final_flags%>%
  bind_rows()%>%
  split(f = list(.$site))%>%
  map(., function(df) {
    ggplot(df, aes(x = DT_round, y = mean, color = auto_flag)) +
      geom_point() +
      facet_wrap(~parameter, scales = "free_y")+
      labs(title = unique(df$site),
           x = "Date",
           y = "Mean Value")
  }) %>%
  walk(plot)
```


# Save Final Flagged Dataset

We will save it into two places: 
- Individually flagged site-parameter parquet files for posterity and comparison with manual verification to determine effectiveness of auto-flagging
- A combined raw data parquet file for use in the manual verification shiny app. Once starting manual verification for the year, this will be used the as "uploaded" data to generate all the necessary files for the app. 

```{r}

# Save the data individually.
iwalk(v_final_flags, ~write_parquet(.x, here(flagged_directory,  paste0(.y, ".parquet"))))

#saving our data into the "raw_data" folder of the manual verification folder for use in the shiny app
#write_parquet(v_final_flags%>%bind_rows(), here(base_folder,"in_progress","raw_data", "raw_data_2026.parquet"))
```

# Shiny Tools & Data Preparation

## Shiny Verification Tool

For manual verification of the data, a ShinyApp has been created that allows users to visualize the data, review the flags, make any necessary corrections, and save the output. The application, and all associated files, are located within "~/manual_verification_tool".

Key columns added by the tool include:
- final_status:
  - "PASS":  user has verified the data as good
  - "FLAGGED": user has flagged the data for suspect but still usable data
  - "OMIT": user has concluded that the data should not be used in analysis due to sensor error. 
- user_flag:
  - Specific flag added by user to indicate why data was flagged/omitted. (e.g. "suspect data", "sonde burial",
  "frozen water", "unsubmerged", "depth shift", "drift", "field visit", "other malfunction" etc). 
  This is for posterity and to help inform auto-flagging performance. 
- mean_analysis: 
  - Values where the "OMIT" final status was not applied.
  
Once complete, the output is saved in the "verified_directory" for the specified year

```{r shiny-dependencies}
# Load required packages for ShinyApp
invisible(lapply(c("shiny","bslib","DT","tidyverse","lubridate","here","ggpubr","gridExtra","plotly",
                   "keys","patchwork","digest","fs","shinyFiles","shinyWidgets","glue","anytime","arrow"),
                 package_loader)
          )
```

Run this codechunk to launch the manual verification tool. The app will open in a new window or tab in your default web browser.
```{r, echo=FALSE}

shiny::shinyAppDir(
  appDir = here("manual_verification_tool"),
  options = list(width = "100%", height = "100%")
)
```

## Drift Correction Tool

Optical sensor drift is a common issue with in-situ sonde deployments, namely turbidity, fDOM and Chl-A. 

This tool is located in the script `drift_correction_tool`.
Here we are applying the drift corrections identified in the manual verification tool to the data and then saving the output in the "post_verification" folder.

The key columns added are:

- mean_drift_trans: new data column with drift corrected values

- correction_type: what kind of drift correction was applied (exponential, fitted linear, etc)

  - This can also be "non_resolved" if the drift could not be appropriately solved via the current methods.
    These data are then moved from final_status = "FLAGGED" to final_status = "OMIT"
    
- pre_post_source: A, B, C depending on where the correction values came from

  - Outlined in `data_organization/drift_correction_2024.rmd`
  
```{r, echo=FALSE}

shiny::shinyAppDir(
  appDir = here("drift_correction_tool"),
  options = list(width = "100%", height = "100%")
)
```

## Data Preparation for HydroShare Publication


## Organizing Data for pub

We will be creating two datasets here:

- A "raw" dataset that includes all the original data with flags and all "versions" of the data:

  - no manual corrections applied, calibration correction, post verification, and post drift correction.

  - This is for posterity and to have a record of what the original data looked like before and after manual verification/corrections.

- A "cleaned" dataset that includes only the final value (post drift correction if it exists, post verification if not) and a column indicating what modifications were made to the data (manual exclusion, calibration correction, drift correction, etc).

Both datasets will be uploaded to HydroShare

```{r}
drift_corrected_files <- list.files(path = 'data/raw/sensor/manual_data_verification/2026_cycle/post_verification/', pattern = "*.parquet", full.names = TRUE)

drift_corrected_data <- map_dfr(drift_corrected_files, read_parquet)%>%
  mutate(user_flag = if_else(final_status == "PASS", NA, user_flag))%>%
  select(DT_round, DT_join, site, parameter,units, 
         value_raw = mean_pre_cal, 
         value_post_cal_corr = mean, 
         value_post_ver = mean_analysis, 
         value_post_drift_corr = mean_drift_trans,   
         auto_qc_flag = auto_flag, mal_flag, 
         user_qc_flag = user_flag, qc_status = final_status, correction_type)%>%
  split(f = list(.$site, .$parameter), sep = "-")%>% 
  keep(~ nrow(.x) > 0) #remove any empty datasets

non_drift_corrected_files <- list.files(path = 'data/raw/sensor/manual_data_verification/2026_cycle/in_progress/verified_directory/', pattern = "*.parquet", full.names = TRUE)%>% grep(pattern = "Depth", x = ., ignore.case = TRUE,value = T,invert = T)

non_drift_corrected_data <- map_dfr(non_drift_corrected_files, read_parquet)%>%
  mutate( mean_analysis = ifelse(verification_status %in% c("FLAGGED", "PASS"), mean, NA), 
          #double check that user flag is consistent with final status
          user_flag = if_else(final_status == "PASS", NA, user_flag))%>%
  select(DT_round, DT_join, site, parameter,units,
         value_raw = mean_pre_cal, 
         value_post_cal_corr = mean, 
         value_post_ver = mean_analysis,
         auto_qc_flag = auto_flag, 
         mal_flag, 
         user_qc_flag = user_flag,
         qc_status = final_status)%>%
  #adding in the final depth data from above
  bind_rows(final_depth_data)%>% 
  split(f = list(.$site, .$parameter), sep = "-")

#only keep non drift corrected site parameters if they are not in the drift corrected data (i.e. if they haven't been drift corrected yet)
all_datasets <- c(non_drift_corrected_data[!names(non_drift_corrected_data) %in% names(drift_corrected_data)], drift_corrected_data)%>%
  keep(~ nrow(.x) > 0) #remove any empty datasets

#units lookup table
#--------------------------#
#DOUBLE CHECK IF NEW PARAMETERS ARE ADDED OR UNITS CHANGE
#--------------------------#
units_table <- tibble(
  parameter = c("Chl-a Fluorescence", "Depth", "DO", "ORP", "Specific Conductivity", "Temperature", "FDOM Fluorescence", "Turbidity"),
  units = c("RFU", "m", "mg/L", "V", "µS/cm", "C", "RFU", "NTU")
)

raw_dataset <- all_datasets%>%
  bind_rows()%>%
  mutate(DateTime_UTC = with_tz(DT_round, tzone = "UTC"),
  # if value_post_drift corr is NA, then fill with value_post_ver (this means that the data was verified but not drift corrected, so the post verification value is the most "final" version of the data we have for those instances) This is for parameters other than FDOM and Turbidity
  value_post_drift_corr = if_else(is.na(value_post_drift_corr), value_post_ver, value_post_drift_corr),
         #round all values to 3 decimal places for consistency with HydroShare upload
         value_raw = round(value_raw, 3),
         value_post_cal_corr = round(value_post_cal_corr, 3),
         value_post_ver = round(value_post_ver, 3),
         value_post_drift_corr = round(value_post_drift_corr, 3),
  # Descriptions to the modifications column
    modifications = case_when(
      correction_type == "non_resolved" ~ "non-resolved drift",
      is.na(value_post_ver) & !is.na(value_raw) ~ "manual data exclusion",
      value_raw == value_post_cal_corr & value_post_ver != value_post_drift_corr ~ "drift correction",
      value_raw != value_post_cal_corr & value_post_ver == value_post_drift_corr ~ "calibration correction",
      value_raw != value_post_cal_corr & value_post_ver != value_post_drift_corr ~ "calibration correction;drift correction",
      TRUE ~ NA_character_
     ), 
    value_post_drift_corr = if_else( !is.na(modifications) & modifications == "non-resolved drift" & parameter != "Chl-a Fluorescence", NA, value_post_drift_corr))%>%
  select(-units)%>%
  left_join(units_table, by = "parameter")%>%
  select(DateTime_UTC,
         site, parameter, units, 
         #Actual data
         value_raw, 
         value_post_cal_corr,
         value_post_ver,
         value_post_drift_corr, 
         #QC Info
         auto_qc_flag, mal_flag, user_qc_flag, qc_status, modifications)%>%
  #ensure turbidity is > 0 for value_post_drift_corr, value_post_ver, value_post_cal_corr, and value_raw. If not, set to 0.1
  mutate(value_post_drift_corr = if_else(parameter == "Turbidity" & value_post_drift_corr <= 0.1, 0.1, value_post_drift_corr),
         value_post_ver = if_else(parameter == "Turbidity" & value_post_ver <= 0.1, 0.1, value_post_ver),
         value_post_cal_corr = if_else(parameter == "Turbidity" & value_post_cal_corr <= 0.1, 0.1, value_post_cal_corr))
    
final_dataset <- raw_dataset %>%
  select(DateTime_UTC, site, parameter, units, value_raw, value_final = value_post_drift_corr,user_qc_flag, modifications)

```

# HydroShare Publication Prep

We will be creating two datasets here: 
- A "raw" dataset that includes all the original data with flags and all "versions" of the data: no manual corrections applied, calibration correction, post verification, and post drift correction. This is for posterity and to have a record of what the original data looked like before and after manual verification/corrections.
- A "cleaned" dataset that includes only the final value (post drift correction if it exists, post verification if not) and a column indicating what modifications were made to the data (manual exclusion, calibration correction, drift correction, etc). This is the dataset that will be uploaded to HydroShare and used for analysis.

## Review Final Dataset

### All parameters at a site

```{r}
all_data_plots <- map(unique(final_dataset$site), function(site_name) {
  
  final_dataset %>% 
           filter(site == site_name )%>%
           #remove turbidity values greater than 1000 NTU since they are likely erroneous and will skew the y-axis
           filter(!(parameter == "Turbidity" & value_raw > 1000))%>%
  ggplot(., 
         aes(x = DateTime_UTC, y = value_final, color = modifications)) +
    geom_point(aes(y = value_raw, color = modifications),size = 0.5, alpha = 0.1) + # add raw data points for comparison
    geom_point() +
    facet_wrap(~parameter, scales = "free_y") +
    labs(title = site_name,
         x = "Date",
         y = "Value",
         color = "QC Status")
})%>%
  set_names(unique(final_dataset$site))
#Best to run each site individually
#walk(plots, print)
clean_data_plots <- map(unique(final_dataset$site), function(site_name) {
  
  ggplot(final_dataset %>% 
           filter(site == site_name & !is.na(value_final))%>%
           #remove turbidity values greater than 1000 NTU since they are likely erroneous and will skew the y-axis
           filter(!(parameter == "Turbidity" & value_final > 1000)), 
         aes(x = DateTime_UTC, y = value_final, color = user_qc_flag)) +
    geom_point() +
    facet_wrap(~parameter, scales = "free_y") +
    labs(title = site_name,
         x = "Date",
         y = "Value",
         color = "QC Flag")
})%>%
  set_names(unique(final_dataset$site))
```

### One specific site-parameter

```{r}
additional_site <- final_dataset %>% filter(site == "riverbend" & parameter == "Turbidity")

#Check out a specific parameter for a specific site
ggplotly(ggplot(final_dataset %>% 
         filter(site == "cottonwood" & parameter == "Turbidity"), 
       aes(x = DateTime_UTC, y = value_final, color = modifications)) +
  #geom_point(aes(y = value_raw),size = 0.5, alpha = 0.1) + # add raw data points for comparison
  geom_point()+
    geom_line(data = additional_site, aes(x = DateTime_UTC, y = value_final), color = "black")+
  facet_wrap(~parameter, scales = "free_y"))

```


## Save Raw & Cleaned Dataset

For each year we will save a csv and parquet version of each file

```{r}
year <- "2026"

#check if the folder exists, if not create it
if (!dir.exists(here( "data/collated/sensor/hydroshare_pub", year))) {
  dir.create(here( "data/collated/sensor/hydroshare_pub", year), recursive = TRUE)
}

cleaned_file_name <- here( "data/collated/sensor/hydroshare_pub", year, paste0("CSU_ROSS_", year,"_cleaned.csv"))

raw_file_name <- here( "data/collated/sensor/hydroshare_pub", year, paste0("CSU_ROSS_", year,"_raw.csv"))

write_csv(final_dataset, cleaned_file_name)

write_csv(raw_dataset, raw_file_name)
# Repeat for parquet files
cleaned_file_name_parquet <- here( "data/collated/sensor/hydroshare_pub", year, paste0("CSU_ROSS_", year,"_cleaned.parquet"))

raw_file_name_parquet <- here( "data/collated/sensor/hydroshare_pub", year, paste0("CSU_ROSS_", year,"_raw.parquet"))

write_parquet(final_dataset, cleaned_file_name_parquet)

write_parquet(raw_dataset, raw_file_name_parquet)
```

## Save Field Notes Dataset

Here we will clean up the field notes data and save it to the hydroshare_pub folder for posterity. This will include cleaning up the crew column to just initials, cleaning up the cals_performed column to standardize the values, and removing any extra columns that are not needed for analysis.

```{r}
#mini function to clean up the cals_performed column in the field notes data. This will standardize the values to a consistent format and remove any variations of "none" or NA.
clean_cals <- function(text) {
  # 1. Clean NA and "none" variations directly inside the function
  if (is.na(text) || str_to_lower(str_trim(text)) %in% c("none", "")) {
    return("None")
  }
  
  cals <- character()
  
  # 2. Detect parameters via regex keyword search
  if (str_detect(text, regex("turb", ignore_case = TRUE)))     cals <- c(cals, "Turbidity")
  if (str_detect(text, regex("r?do", ignore_case = TRUE)))      cals <- c(cals, "DO")
  if (str_detect(text, regex("cond", ignore_case = TRUE)))     cals <- c(cals, "Conductivity")
  if (str_detect(text, regex("\\bph\\b", ignore_case = TRUE))) cals <- c(cals, "pH")
  if (str_detect(text, regex("orp", ignore_case = TRUE)))      cals <- c(cals, "ORP")
  if (str_detect(text, regex("level", ignore_case = TRUE)))    cals <- c(cals, "Level")
  
  # Return original string if no known keywords match (e.g., custom notes)
  if (length(cals) == 0) return(text) 
  
  # 3. Sort alphabetically and combine into a clean, unified string
  paste(sort(unique(cals)), collapse = ", ")
}

sensor_field_notes <- grab_mWater_sensor_notes(load_mWater())%>% 
  filter(year(DT_round) == year)%>%
  rename(DateTime_UTC = DT_round) %>%
  select(-photos_downloaded,-DT_join, -cal_report_collected, -sensor_swapped_notes, -end_dt, -last_site_visit, -date,-sensor_deployed, -sensor_pulled)%>%
  #Clean up crew to just initials and remove any extra text
  mutate(crew = crew %>%
    str_replace_all("Other \\(please specify\\)", "Other") %>%
    str_replace_all("([A-Z])[a-z]+", "\\1") %>%
    str_replace_all("(?<=[A-Z])\\s+(?=[A-Z])", "")%>%
    str_replace_all("sam struthers", "SS")%>%
    str_replace_all("sam", "S")%>%
    str_replace_all("and", ",")%>% 
    str_replace_all(" ", "")%>%
    str_replace_all("_", "")
  )%>%
  #replace any character columns that are "NA" or "na" with NA
  mutate(across(where(is.character), ~ na_if(., "NA")))%>%
  mutate(across(where(is.character), ~ na_if(., "na")))%>%
  mutate(cals_performed = map_chr(cals_performed, clean_cals))%>%
  mutate(ph_junction_replaced = ifelse(str_to_title(ph_junction_replaced) == "No"| is.na(ph_junction_replaced), "No", ph_junction_replaced),
         rdo_cap_replaced = ifelse(str_to_title(rdo_cap_replaced) == "No" | is.na(rdo_cap_replaced), "No", rdo_cap_replaced))%>%
   # across(c(ph_junction_replaced,rdo_cap_replaced )), ~ ifelse(str_to_title(.,) == "No", "No", .x))%>%
    select(any_of(c("site",  "crew","DateTime_UTC", "sonde_employed", "sensors_cleaned", "wiper_working",
                  "rdo_cap_condition", "rdo_cap_replaced", "ph_junction_replaced", "cals_performed",
                  "sonde_moved", "sensor malfunction", "visit_type", "start_DT", "visit_comments", 
                  "rdo_pre_clean",   "rdo_post_clean", "rdo_post_cal",
                  "cond_pre_clean", "cond_post_clean", "cond_post_cal",
                  "ph_pre_clean", "ph_post_clean", "ph_post_cal",
                  "orp_pre_clean", "orp_post_clean", "orp_post_cal",
                  "turb_pre_clean", "turb_post_clean", "turb_post_cal",
                  "fdom_pre_clean", "fdom_post_clean", "fdom_post_cal",
                  "chla_pre_clean", "chla_post_clean", "chla_post_cal")))%>%
  fix_site_names()

field_notes_file <- here("data/collated/sensor/hydroshare_pub", year, paste0("CSU_ROSS_sensor_field_notes_", year, ".csv"))

write_csv(sensor_field_notes, field_notes_file)

```

## Double Check Location Metadata

Here we will load and double check the location metadata file created by Sam Struthers and verified by Katie Willi

```{r}
 location_meta <- read_csv("data/collated/sensor/hydroshare_pub/CSU_ROSS_sonde_location_metadata.csv",
                           show_col_types = FALSE)%>%
  mutate(data_start_date = as.POSIXct(data_start_date, tz = "UTC", format = "%m/%d/%y"),
         data_end_date =  if_else( is.na(data_end_date) | data_end_date == "2025-11-17", 
                                   ymd("2026-11-17"),
                                   as.POSIXct(data_end_date, tz = "UTC", format = "%m/%d/%y")))%>%

  mutate(min_year = year(data_start_date),
         max_year = year(data_end_date), 
          year_range = paste0(min_year, "-", max_year)) 

#update as needed
#write_csv(location_meta, here("data/collated/sensor/hydroshare_pub/CSU_ROSS_sonde_location_metadata.csv"))
# 
# tmap_mode("view")
# tm_basemap("OpenStreetMap") +
#   tm_shape(location_meta %>% st_as_sf(coords = c("longitude", "latitude"), crs = 4326)) +
#   #color is SiteID and shape is year_range
#     tm_symbols(col = "SiteID", shape = "year_range", size = 0.5, border.col = "black")
# 


```


