---
title: "2024 Report and Figs"
author: "Sam Struthers- CSU ROSSyndicate"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
package_load <- function(package_names){
  for(i in 1:length(package_names)){
    if(!package_names[i] %in% installed.packages()){
      install.packages(package_names[i])
    }
    library(package_names[i],character.only = TRUE)
  }
}

#vector of packages
pack_req <- c( 
  # data wrangling packages
  "tidyverse","lubridate","padr","janitor","padr", "broom","arrow",
  #spatial packages
  "sf","terra","nhdplusTools", "tigris","raster", "leaflet","tmap",
  # plotting
  "ggpubr","ggthemes","scales","corrplot","gghighlight", "geomtextpath", "ggbeeswarm","plotly", "ggpmisc","flextable", "patchwork",
  # web scrapping
  "rjson", "rvest", "dataRetrieval", "httr", "jsonlite", "yaml",
  #extra
  "devtools", "trend")
package_load(pack_req)

library(cdssr)

`%nin%` = Negate(`%in%`)

save_2024_fig_plot <- function(plot, filename){

  ggsave(paste0("data/sharing/figures/2024/",filename, ".png"), plot, width = 12, height = 8, units = "in", dpi = 500)
}


options(dplyr.summarise.inform = FALSE)
rm(pack_req, package_load)
```


```{r}


site_names <- tibble(site = c("pbd", "tamasag", "legacy", "lincoln", "timberline", "prospect" ,"boxelder",  "archery", "riverbluffs"), 
                        site_name = c("Canyon Mouth", "Tamasag", "Legacy", "Lincoln", "Timberline", "Prospect" ,"Boxelder",  "Archery", "River Bluffs"), 
                     natural_name = c("Canyon Mouth", "Bellvue", "Salyer", "Udall", "Riverbend", "Cottonwood", "ELC", "Archery", "River Bluffs"))

labels <- tibble(param = c("Turbidity", "Specific Conductivity", "Depth", "Chl-a Fluorescence", "FDOM Fluorescence", "Temperature", "DO", 'pH', "Flow"),
                 label = c("Turbidity (NTU)", "Specific Conductivity (uS/cm)", "Depth (m)", "Chl-a Fluorescence (RFU)", "FDOM Fluorescence (RFU)", "Temperature (C)", "DO (mg/L)", 'pH', "Flow (cfs)"))

sensor_data <- read_feather(file = "data/api/sjs_test/psn_2024_3.feather")%>%
  left_join(site_names, by = c("site"))%>%
  left_join(labels, by = c( "parameter" = "param")) 


sensor_data_auto_clean <- filter(sensor_data, auto_cleaned_flag_binary == 0)

sensor_data_simple_clean <- sensor_data%>%
  filter(!grepl("site visit|sv window", flag))%>%
  filter(!grepl("sonde unsubmerged", flag))%>%
  filter(!grepl("sonde not employed", flag))%>%
  filter(!grepl("sensor malfunction", flag))  %>%
filter(!(parameter == "Specific Conductivity" & value > 2000))%>%
  filter(!(parameter == "pH" & value < 6.5))%>%
  filter(!(parameter == "pH" & value > 10 ))%>%
  filter(!(parameter == "Temperature" & value < 0))%>%
  filter(!(value == 0 ))



#site_order <- c("Canyon Mouth", "Tamasag", "Legacy", "Lincoln", "Timberline" , "Prospect", "Boxelder", "Archery", "River Bluffs"  )
site_order = c("Canyon Mouth", "Bellvue", "Salyer", "Udall", "Riverbend", "Cottonwood", "ELC", "Archery", "River Bluffs")

```



# Plots

## Function
```{r}
plot_sensor_grabs <- function(df, sites, parameters, renamed_sites, start_dt, end_dt, timestep, add_grabs, color_scheme = bg_colors, b_size = 30){
  
  
  
  all_data <- filter(df, site %in% sites & DT_round >= ymd_hm(start_dt) & DT_round <= ymd_hm(end_dt))%>%
    filter(parameter %in% parameters)
  

  create_plot <- function(param_arg) {

    if(param_arg == "Flow"){
      
      flow_plot <- function(sites,start_dt, end_dt, timestep){

  flow_sites <- tibble(
    site = c("pbd", "lincoln", "boxelder", "riverbluffs"), 
    #site_name = c("Canyon Mouth", "Lincoln", "Boxelder", "River Bluffs"  ),
    natural_name = c("Canyon Mouth", "Udall", "ELC", "River Bluffs"  ),
    source = c('CDWR', 'USGS', 'USGS', 'CDWR'), 
    abbrev = c("CLAFTCCO","06752260","06752280",   "CLARIVCO" ))%>%
    filter(site %in% sites)
  
  
  start_dt <- ymd_hm(start_dt, tz = "MST")
  end_dt <- ymd_hm(end_dt, tz = "MST")
  start_date <- floor_date(start_dt, unit = "day")
  end_date <- ceiling_date(end_dt, unit = "day")
  
  gather_q <- function(selected_sites, start_date, end_date, timestep) {


    all_q <- tibble()

    for (i in 1:nrow(flow_sites)) {
      if (flow_sites$source[i] == "USGS") {
        q_data <- readNWISuv(siteNumbers = flow_sites$abbrev[i],
                             startDate = start_date,
                             endDate = end_date,
                             parameterCd = "00060", tz = "America/Denver") %>%
          distinct() %>%
          mutate(DT_mst = with_tz(dateTime, tzone = "MST"),
                 source = "USGS") %>%
          dplyr::select(site = site_no, DT_mst, q_cfs = X_00060_00000, flag = X_00060_00000_cd)

      } else if (flow_sites$source[i] == "CDWR") {
        q_data <- get_telemetry_ts(
          abbrev = flow_sites$abbrev[i],
          parameter = "DISCHRG",
          start_date = start_date,
          end_date = end_date,
          timescale = "raw",
          include_third_party = TRUE) %>%
          distinct() %>%
          mutate(DT_mst = force_tz(datetime, tzone = "MST"),
                 flag = case_when(!is.na(flag_a) & !is.na(flag_b) ~ paste0(flag_a, ",", flag_b),
                                  is.na(flag_a) & !is.na(flag_b) ~ flag_b,
                                  is.na(flag_b) & !is.na(flag_b) ~ flag_a,
                                  TRUE ~ NA_character_),
                 source = "DWR") %>%
          dplyr::select(site = abbrev, DT_mst, q_cfs = meas_value, flag, source)
      }
      all_q <- bind_rows(all_q, q_data)
    }

  
      final_q <- all_q %>%
        mutate(DT_round = round_date(x = DT_mst, unit = timestep)) %>%
        group_by(site, DT_round) %>%
        summarise(q_cfs = mean(q_cfs, na.rm = TRUE)) %>%
        filter(!is.na(q_cfs))%>%
        left_join(flow_sites, by = c("site" = "abbrev"))
   

    return(final_q)
  }
  final_q <- gather_q(flow_sites, start_date, end_date, timestep)
  
  
  trim_q <- final_q%>%
    filter(between(DT_round, start_dt, end_dt))
    
  
  # Subset the colors since there are only a few sites where flow is available
  colors_selected <- tibble(site = sites)%>%
    left_join(site_names, by = c("site" = "site"))
  colors_selected$natural_name <- factor(colors_selected$natural_name, levels = site_order )
  
  
    colors_selected <- colors_selected %>%
      mutate(color = color_scheme[1:length(sites)])%>%
    filter(site %in% flow_sites$site)
    
    
    color_scheme <- colors_selected$color
  
  trim_q$natural_name <- factor(trim_q$natural_name, levels = site_order )
      
    
  
    ggplot(trim_q, aes(x = DT_round, y = q_cfs, color = natural_name)) +
      geom_line(size = 1.5, show.legend = F) +
      scale_color_manual(values = color_scheme) +
      labs( x = "Date", y = "Flow (cfs)", color = "")+
      theme_few(base_size = b_size) +
      theme(axis.title.x = element_blank(), legend.position = "none", 
            legend.text = element_blank())
  

      }
      
      plot <- flow_plot(sites, start_dt, end_dt, timestep)
      
      return(plot)
    }
    
    
    plot_data <- all_data %>%
      filter(parameter == param_arg)
    
    label <- labels %>%
      filter(param == param_arg) %>%
      pull(label)
    
    plot_data$natural_name <- factor(plot_data$natural_name, levels = site_order )
    
    # if(param_arg == "Specific Conductivity"){
    #   b_size = b_size - 5
    #   
    #   plot <- ggplot(plot_data, aes(x = DT_round, y = value, color = site_name)) +
    #   geom_line(linewidth = 2, show.legend = F) +
    #   scale_color_manual(name = "Site", values = color_scheme) +
    #   labs(x = "Date", y = label, color = "Site") +
    #   theme_few(base_size = b_size) +
    #   labs(color = "Site") +
    #   theme(axis.title.x = element_blank(), legend.position = "none")
    # }
    
    plot <- ggplot(plot_data, aes(x = DT_round, y = value, color = natural_name)) +
      geom_line(linewidth = 2) +
      scale_color_manual(name = "Site", values = color_scheme) +
      labs(x = "Date", y = label, color = "Site") +
      theme_few(base_size = b_size) +
      labs(color = "Site") +
      theme(axis.title.x = element_blank(), legend.position = "bottom")
    
    if (add_grabs) {
      grab_data <- tidy_correlated_df %>%
        filter(site %in% sites & grab_dt >= ymd_hm(start_dt) & grab_dt <= ymd_hm(end_dt))%>%
        left_join(site_names, by = c("site" = "site"))
      
      plot <- plot +
        geom_vline(data = grab_data, aes(xintercept = grab_dt, color = natural_name), linetype = "dashed", size = 1)
    }
    
    return(plot)
  }
  
  all_data <- all_data%>%
    mutate(DT_round = round_date(DT_round, unit = timestep))%>%
    group_by(DT_round, natural_name,site, parameter)%>%
    summarise(value = mean(value, na.rm = TRUE), .groups = "drop")


  all_plot <- map(parameters, create_plot)
  

  
  if(length(parameters) == 1){
    all_plot[[1]] <- all_plot[[1]] + theme(axis.title.x = element_text( size = b_size))
    
    plots <- wrap_plots(all_plot, ncol = 1) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom")
    
  }else if(length(parameters) == 2){
    all_plot[[1]] <- all_plot[[1]] + theme(axis.text.x = element_blank(), 
                                           legend.position = "none")
    all_plot[[2]] <- all_plot[[2]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
    
    return(plots)
  }else if(length(parameters) == 3){
    all_plot[[3]] <- all_plot[[3]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }else if(length(parameters) == 4){
    all_plot[[3]] <- all_plot[[3]] + theme(axis.title.x = element_text( size = b_size))
    all_plot[[4]] <- all_plot[[4]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 2) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }else if(length(parameters) == 5){
    all_plot[[5]] <- all_plot[[5]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 2) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }
  
  
  return(plots)
}




bg_colors <- c( "#01377D", "#009DD1", "#97E7F5",
                "#7ED348", "#26B170", "#000000") 

colors <- c("#01377D","#009DD1", "#D55E00")




```

## March Horsetooth Release

```{r}

sites_mh <- c("tamasag", "legacy", "lincoln", "boxelder")


march <-  plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_mh,  parameters = c("Flow", "Specific Conductivity","Turbidity","Temperature" ), start_dt = "2024-03-26  12:00",
                  end_dt = "2024-03-30 12:00",timestep =  "1 hour", add_grabs = F, color_scheme = bg_colors,b_size = 20)


march
ggsave("data/sharing/figures/2024/march_horsetooth_release.png", plot = march, width = 16, height = 10, units = "in", dpi = 300)
```


## April Cond spike

Find the ditch pulling water. Swap depth for flow data
clean up cond data


```{r}
sites_apr <- c("tamasag", "legacy", "lincoln", "boxelder", "riverbluffs")

apr <- plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_apr,  parameters = c("Flow", "Specific Conductivity","DO", "Temperature"), start_dt = "2024-04-07  00:00",
                  end_dt = "2024-04-18 23:00",timestep = "1 hour", add_grabs = F, color_scheme = bg_colors,b_size = 18)

apr
ggsave("data/sharing/figures/2024/april_drawdown_release.png", plot = apr, width = 16, height = 10, units = "in", dpi = 300)

```


## May Cond spike

```{r}
sites_may <- c("legacy", "lincoln", "prospect", "riverbluffs")

may <- plot_sensor_grabs(df = sensor_data_simple_clean,sites = sites_may,  parameters = c("Flow","Temperature", "Specific Conductivity", "DO"), start_dt = "2024-05-25  00:00",
                  end_dt = "2024-06-08 23:00",timestep = "1 hour", add_grabs = F, color_scheme = bg_colors,b_size = 18)
may

# #make a plot of the difference between legacy and riverbluffs specific conductivity over May 25- june 8th
# may_sc_comp <- sensor_data_simple_clean %>% mutate(date = as.Date(DT_round))%>%filter(site %in% c("legacy", "riverbluffs") & parameter == "Specific Conductivity" & date >= "2024-05-25  00:00" & date <= "2024-06-10 23:00") %>% select(site, date, value)%>%
#   group_by(date, site) %>% summarise(value = mean(value, na.rm = T))%>% pivot_wider(names_from = site, values_from = value)%>%mutate(diff_perc = (riverbluffs/legacy)*100, 
#                                                                                                                                      diff_abs = riverbluffs - legacy)
# 
# ggplotly(ggplot(may_sc_comp, aes(x = date, y = diff_abs)) + geom_line()+
#            geom_point(aes(y = riverbluffs), color = "green")+
#            geom_point(aes(y = legacy), color = "blue")
#          + theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + labs(y = "Riverbluffs / Legacy Specific Conductivity", x = "Date") + ggtitle("Riverbluffs / Legacy Specific Conductivity Ratio"))

ggsave("data/sharing/figures/2024/may_drawdown.png", plot = may, width = 16, height = 10, units = "in", dpi = 300)
```

## Low DO levels at lower sites due to low flows

Add in last year's data for comparison?

```{r}
sites_low_do <- c("lincoln",  "boxelder","prospect", "riverbluffs")

low_do <- plot_sensor_grabs(df = sensor_data_simple_clean,sites = sites_low_do,  parameters = c("Flow","DO",  "Specific Conductivity", "Temperature"), start_dt = "2024-07-31  00:00",
                  end_dt = "2024-08-11 00:00", timestep = "1 hour", add_grabs = F, color_scheme = bg_colors,b_size = 18)


save_2024_fig_plot(low_do,"low_do")

sites_low_do_2 <- c("tamasag", "lincoln", "timberline", "boxelder", "archery")
low_do2 <- plot_sensor_grabs(df = sensor_data_simple_clean,sites = sites_low_do_2,  parameters = c("Flow","DO",  "Specific Conductivity", "Temperature"), start_dt = "2024-09-01  00:00",
                  end_dt = "2024-10-05 00:00", timestep = "1 hour", add_grabs = F, color_scheme = bg_colors,b_size = 18)


save_2024_fig_plot(low_do2,"low_do2")
```

## August Storm

Add precip from 8/10


```{r}

sites_aug <- c("tamasag", "legacy", "lincoln","prospect", "boxelder")
aug <- plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_aug,  parameters = c("Flow", "Turbidity", "Specific Conductivity"), start_dt = "2024-08-09  00:00",
                  end_dt = "2024-08-15 00:00", timestep = "15 minute", add_grabs = F, color_scheme = bg_colors,b_size = 18)
aug
ggsave("data/sharing/figures/2024/august_storm.png", plot = aug, width = 16, height = 12, units = "in", dpi = 300)
```



## Late summer Timberline prospect cond trends

```{r}
sites_timberline <- c("timberline", "prospect")

timb_pros <-plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_timberline,  parameters = c("Depth", "Specific Conductivity", "Temperature"), start_dt = "2024-08-10  00:00",
                  end_dt = "2024-11-05 00:00", timestep = "4 hour", add_grabs = F, color_scheme = bg_colors,b_size = 18)
save_2024_fig_plot(timb_pros,"timb_pros")
```

## Fall Horsetooth release

Similar to previous year, there was a big release from horsetooth in mid october. This increased flows in the river and caused conducitivty to decrease. This shift was shorter at lower sites in the network as water was likely pulled between lincoln and Boxelder

```{r}
sites_fall <- c("legacy", "lincoln","timberline",  "boxelder", "riverbluffs")

fall_h <- plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_fall,  parameters = c("Flow", "Specific Conductivity", "pH", "Temperature"), start_dt = "2024-10-08  00:00",
                  end_dt = "2024-11-15 00:00", timestep = "12 hour", add_grabs = F, color_scheme = bg_colors,b_size = 18)
fall_h
# fall_h <- plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_fall,  parameters = c("Flow"), start_dt = "2024-10-05  00:00",
#                   end_dt = "2024-11-15 00:00", timestep = "12 hour", add_grabs = F, color_scheme = bg_colors,b_size = 18)

ggplotly(fall_h)
ggsave("data/sharing/figures/2024/oct_horsetooth_release.png", plot = fall_h, width = 16, height = 10, units = "in", dpi = 300)
```


## Month long comp of River Bluffs and Archery


Higher up sites (Boxelder, archery, lincoln) follow patterns consistent with flow level fluctuations whereas riverbluffs is more stable (flow doesn't change as much). Takes a much larger release/shift for riverbluffs to see a change in conductivity. pH is also elevated for an extended period. 

```{r}

sites_comp <- c("lincoln", "boxelder","archery","riverbluffs")
arch_rivr <-   plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_comp,  parameters = c("Flow", "Specific Conductivity", "Temperature", "pH"), start_dt = "2024-07-01  00:00",
                  end_dt = "2024-11-15 23:45", timestep = "5 day", add_grabs = F, color_scheme = bg_colors,b_size = 18)

save_2024_fig_plot(arch_rivr,"arch_rivr")
```





# Comparing 2023 and 2024 data
## Flow Function
```{r}
grab_flow_data <- function(sites,start_dt, end_dt, timestep){

  flow_sites <- tibble(
    site = c("pbd", "lincoln", "boxelder", "riverbluffs"), 
    site_name = c("Canyon Mouth", "Lincoln", "Boxelder", "River Bluffs"  ),
    source = c('CDWR', 'USGS', 'USGS', 'CDWR'), 
    abbrev = c("CLAFTCCO","06752260","06752280",   "CLARIVCO" ))%>%
    filter(site %in% sites)
  
  
  start_dt <- ymd_hm(start_dt, tz = "MST")
  end_dt <- ymd_hm(end_dt, tz = "MST")
  start_date <- floor_date(start_dt, unit = "day")
  end_date <- ceiling_date(end_dt, unit = "day")
  
  gather_q <- function(selected_sites, start_date, end_date, timestep) {


    all_q <- tibble()

    for (i in 1:nrow(flow_sites)) {
      if (flow_sites$source[i] == "USGS") {
        q_data <- readNWISuv(siteNumbers = flow_sites$abbrev[i],
                             startDate = start_date,
                             endDate = end_date,
                             parameterCd = "00060", tz = "America/Denver") %>%
          distinct() %>%
          mutate(DT_mst = with_tz(dateTime, tzone = "MST"),
                 source = "USGS") %>%
          dplyr::select(site = site_no, DT_mst, q_cfs = X_00060_00000, flag = X_00060_00000_cd)

      } else if (flow_sites$source[i] == "CDWR") {
        q_data <- get_telemetry_ts(
          abbrev = flow_sites$abbrev[i],
          parameter = "DISCHRG",
          start_date = start_date,
          end_date = end_date,
          timescale = "raw",
          include_third_party = TRUE) %>%
          distinct() %>%
          mutate(DT_mst = force_tz(datetime, tzone = "MST"),
                 flag = case_when(!is.na(flag_a) & !is.na(flag_b) ~ paste0(flag_a, ",", flag_b),
                                  is.na(flag_a) & !is.na(flag_b) ~ flag_b,
                                  is.na(flag_b) & !is.na(flag_b) ~ flag_a,
                                  TRUE ~ NA_character_),
                 source = "DWR") %>%
          dplyr::select(site = abbrev, DT_mst, q_cfs = meas_value, flag, source)
      }
      all_q <- bind_rows(all_q, q_data)
    }

  
      final_q <- all_q %>%
        mutate(DT_round = round_date(x = DT_mst, unit = timestep)) %>%
        group_by(site, DT_round) %>%
        summarise(q_cfs = mean(q_cfs, na.rm = TRUE)) %>%
        filter(!is.na(q_cfs))%>%
        left_join(flow_sites, by = c("site" = "abbrev"))
   

    return(final_q)
  }
  final_q <- gather_q(flow_sites, start_date, end_date, timestep)
  
  return(final_q)
}

flow_data <- grab_flow_data(sites = c("lincoln", "boxelder", "riverbluffs"), start_dt = "2023-01-01  00:00", end_dt = "2024-11-16 23:45", timestep = "1 hour")  


flow_data_clean <- flow_data%>%
  ungroup()%>%
  dplyr::select(DT_round, q_cfs, site = site.y)%>%
  mutate(year = year(DT_round), 
         week = week(DT_round))

seven_day_roll_flow <- flow_data_clean %>%
  group_by(site, week, year) %>%
  summarise(value = mean(q_cfs, na.rm = TRUE))%>%
  ungroup()%>%
  mutate(parameter = "Flow")
```

## sensor data

### Pull in 2023

```{r}

data_files <- list.files("data/virridy_verification/post_verified_directory/", full.names = T)

sensors_2023 <- map(data_files, read_rds)%>%bind_rows()

sensors_2023_clean <- sensors_2023%>%
  filter(parameter %in% c("Temperature", "Specific Conductivity", "DO", "pH"))%>%
  dplyr::select(DT_round,week, site, parameter, mean_verified, mean, flag, is_verified)%>%
  filter(site %in% c("tamasag", "legacy", "lincoln", "timberline", "prospect", "boxelder", "lincoln", "river bluffs", "archery"))%>%
  mutate(site = ifelse(site == "river bluffs", "riverbluffs", site))
  

seven_day_roll_2023 <- sensors_2023_clean %>%
  #mutate(DT_round = round_date(x = DT_round, unit = "7 days")) %>%
  filter(!is.na(mean_verified))%>%
  group_by(site, parameter, week) %>%
  summarise(value = mean(mean_verified, na.rm = TRUE))%>%
  ungroup()%>%
  na.omit()%>%
  mutate(year = 2023) 




```

## Seven day avg of sensor data

```{r}

#make a seven day rolling average of temperature, specific conductivity and DO
seven_day_roll <- sensor_data_simple_clean %>%
  filter(parameter %in% c("Temperature", "Specific Conductivity", "DO", "pH"))%>%
  mutate(week = week(DT_round))%>%
  group_by(site, parameter, week) %>%
  summarise(value = mean(value, na.rm = TRUE))%>%
  ungroup()%>%
  na.omit()%>%
  mutate(year = 2024)%>%
  filter(site %in% c("tamasag", "legacy", "lincoln", "timberline", "prospect", "boxelder", "lincoln", "riverbluffs", "archery"))


```

## Bind

```{r}

all_7day <- bind_rows(seven_day_roll, seven_day_roll_2023)%>%
  bind_rows(seven_day_roll_flow)%>%
  filter(between(week, 13, 46))%>%
  left_join(site_names, by = c("site"))

all_7day$natural_name <- factor(all_7day$natural_name, levels = site_order )

```

### Plot

### Function
```{r}

plot_seven_day_avg <- function( sites, parameters, renamed_sites, color_scheme = bg_colors, b_size = 30, line_w = 1){
  
  
  
  all_data <- filter(all_7day, site %in% sites)%>%
    filter(parameter %in% parameters)%>%
    mutate(date = as.Date(week * 7))
  
  

  create_plot <- function(param_arg) {

 
    plot_data <- all_data %>%
      filter(parameter == param_arg)
    
    label <- labels %>%
      filter(param == param_arg) %>%
      pull(label)
    
    plot_data$natural_name <- factor(plot_data$natural_name, levels = site_order )

       if(param_arg == "Flow"){
      
     flow_sites <- tibble(
    site = c("pbd", "lincoln", "boxelder", "riverbluffs"), 
    natural_name = c("Canyon Mouth", "Udall", "ELC", "River Bluffs"  ),
    source = c('CDWR', 'USGS', 'USGS', 'CDWR'), 
    abbrev = c("CLAFTCCO","06752260","06752280",   "CLARIVCO" ))%>%
    filter(site %in% sites)
        
  # Subset the colors since there are only a few sites where flow is available
  colors_selected <- tibble(site = sites)%>%
    left_join(site_names, by = c("site" = "site"))
  
  colors_selected$natural_name <- factor(colors_selected$natural_name, levels = site_order )
  
  
    colors_selected <- colors_selected %>%
      mutate(color = color_scheme[1:length(sites)])%>%
    filter(site %in% flow_sites$site)
    
    
    color_scheme <- colors_selected$color
  
    plot <- ggplot(plot_data,
       aes(x = date, y = value, color = natural_name, linetype = as.character(year))) +
  geom_line(show.legend = F,linewidth = line_w) +
  #facet_wrap(~parameter, scales = "free_y", ncol = 1) +
  theme_few(base_size = b_size) +
  scale_y_log10()+
  #theme(legend.position = "bottom", 
   #     axis.title.x = element_blank()) + # Rotate x-axis labels
  scale_color_manual(values = color_scheme) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") + # Format x-axis labels as abbreviated months
  labs(x = "Month",
       y = "Flow (cfs)",
       color = "", 
       linetype = "") +
      theme(axis.title.x = element_blank(), legend.position = "none", 
            legend.text = element_blank())
    
    return(plot)
    
    }
    
 
    
    
    
plot <- ggplot(plot_data,
       aes(x = date, y = value, color = natural_name, linetype = as.character(year))) +
  geom_line(linewidth = line_w) +
  #facet_wrap(~parameter, scales = "free_y", ncol = 1) +
  theme_few(base_size = 18) +
  theme(legend.position = "bottom", 
        axis.title.x = element_blank()) + # Rotate x-axis labels
  scale_color_manual(values = color_scheme) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") + # Format x-axis labels as abbreviated months
  labs(x = "Month",
       y = label,
       color = "Site", 
       linetype = "Year")

    
    return(plot)
  }
  


  all_plot <- map(parameters, create_plot)



  if(length(parameters) == 1){
    all_plot[[1]] <- all_plot[[1]] + theme(axis.title.x = element_text( size = b_size))

    plots <- wrap_plots(all_plot, ncol = 1) +
      plot_layout(guides = "collect") &
      theme(legend.position = "bottom")

  }else if(length(parameters) == 2){
    all_plot[[1]] <- all_plot[[1]] + theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[2]] <- all_plot[[2]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) +
      plot_layout(guides = "collect") &
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))

    return(plots)
  }else if(length(parameters) == 3){
    all_plot[[1]] <- all_plot[[1]]+ theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[2]] <- all_plot[[2]]+ theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[3]] <- all_plot[[3]]
    plots <- wrap_plots(all_plot, ncol = 1) +
      plot_layout(guides = "collect") &
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }else if(length(parameters) == 4){
    all_plot[[1]] <- all_plot[[1]]+ theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[2]] <- all_plot[[2]]+ theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[3]] <- all_plot[[3]]+ theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[4]] <- all_plot[[4]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) +
      plot_layout(guides = "collect") &
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }else if(length(parameters) == 5){
    all_plot[[5]] <- all_plot[[5]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) +
      plot_layout(guides = "collect") &
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }
  
  
  return(plots)
}



```

## Smoothing Data

```{r}

  #Loop

sites <- unique(all_7day$site)
parameters <- unique(all_7day$parameter)
years <- unique(all_7day$year)
cross_data <- expand.grid(site = sites, parameter = parameters, year = years)

all_7day_smooth <- tibble()
for(i in 1:nrow(cross_data)){
    
    param <- cross_data$parameter[i]  
    
    site_sel <- cross_data$site[i]
    year_sel <- cross_data$year[i]
    
    time_series_data <- all_7day %>%
      filter(site == site_sel & parameter == param & year == year_sel)
    
    #if time_series_data is empty, skip
    if(nrow(time_series_data) != 0){
          smoothed_data <- ksmooth(
        x = time_series_data$week,  # Time as numeric (days since origin)
        y = time_series_data$value,             # Values to smooth
        kernel = "normal",                      # Kernel type
        bandwidth = 3  )                      # Smoothing bandwidth (adjust as needed)

    smoothed <- as_tibble(smoothed_data)%>%
      mutate(site = site_sel, parameter = param, year = year_sel)%>%
      rename(smoothed_value = y, week = x)%>%
      left_join(time_series_data%>%select(week, value), by = "week")
      
    all_7day_smooth <- bind_rows(all_7day_smooth, smoothed)
    }



  }
all_7day_smooth<- all_7day_smooth%>%
  left_join(site_names, by = c("site"))

all_7day$site_name <- factor(all_7day$site_name, levels = site_order )


```





```{r}
plot_seven_day_smoothed <- function( sites, parameters, renamed_sites, color_scheme = bg_colors, b_size = 30){
  
  
  
  all_data <- filter(all_7day_smooth, site %in% sites)%>%
    filter(parameter %in% parameters)%>%
    mutate(date = as.Date(week * 7), 
           value = smoothed_value)
  
  

  create_plot <- function(param_arg) {

 
    plot_data <- all_data %>%
      filter(parameter == param_arg)
    
    label <- labels %>%
      filter(param == param_arg) %>%
      pull(label)
    
    plot_data$site_name <- factor(plot_data$site_name, levels = site_order )

       if(param_arg == "Flow"){
      
      flow_sites <- tibble(
    site = c("pbd", "lincoln", "boxelder", "riverbluffs"), 
    #site_name = c("Canyon Mouth", "Lincoln", "Boxelder", "River Bluffs"  ),
    natural_name = c("Canyon Mouth", "Udall", "ELC", "River Bluffs"  ),
    source = c('CDWR', 'USGS', 'USGS', 'CDWR'), 
    abbrev = c("CLAFTCCO","06752260","06752280",   "CLARIVCO" ))%>%
    filter(site %in% sites)
        
  # Subset the colors since there are only a few sites where flow is available
  colors_selected <- tibble(site = sites)%>%
    left_join(site_names, by = c("site" = "site"))
  
  colors_selected$natural_name <- factor(colors_selected$natural_name, levels = site_order )
  
  
    colors_selected <- colors_selected %>%
      mutate(color = color_scheme[1:length(sites)])%>%
    filter(site %in% flow_sites$site)
    
    
    color_scheme <- colors_selected$color
  
    

    
    
    
    plot <- ggplot(plot_data,
       aes(x = date, y = value, color = natural_name, linetype = as.character(year))) +
  geom_line(show.legend = F) +
  #facet_wrap(~parameter, scales = "free_y", ncol = 1) +
  theme_bw(base_size = 18) +
  scale_y_log10()+
  #theme(legend.position = "bottom", 
   #     axis.title.x = element_blank()) + # Rotate x-axis labels
  scale_color_manual(values = color_scheme) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") + # Format x-axis labels as abbreviated months
  labs(x = "Month",
       y = "Flow (cfs)",
       color = "", 
       linetype = "") +
      theme(axis.title.x = element_blank(), legend.position = "none", 
            legend.text = element_blank())
    
    
    
    # ggplot(trim_q, aes(x = DT_round, y = q_cfs, color = site_name)) +
    #   geom_line(size = 1.5, show.legend = F) +
    #   scale_color_manual(values = color_scheme) +
    #   labs( x = "Date", y = "Flow (cfs)", color = "")+
    #   theme_few(base_size = b_size) +
    #   theme(axis.title.x = element_blank(), legend.position = "none", 
    #         legend.text = element_blank())
    
    
    
    
    return(plot)
    
    }
    
 
    
    
    
plot <- ggplot(plot_data,
       aes(x = date, y = value, color = natural_name, linetype = as.character(year))) +
  geom_line() +
  #facet_wrap(~parameter, scales = "free_y", ncol = 1) +
  theme_bw(base_size = b_size) +
  theme(legend.position = "bottom", 
        axis.title.x = element_blank()) + # Rotate x-axis labels
  scale_color_manual(values = color_scheme) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") + # Format x-axis labels as abbreviated months
  labs(x = "Month",
       y = label,
       color = "Site", 
       linetype = "Year")

    
    return(plot)
  }
  


  all_plot <- map(parameters, create_plot)



  if(length(parameters) == 1){
    all_plot[[1]] <- all_plot[[1]] + theme(axis.title.x = element_text( size = b_size))

    plots <- wrap_plots(all_plot, ncol = 1) +
      plot_layout(guides = "collect") &
      theme(legend.position = "bottom")

  }else if(length(parameters) == 2){
    all_plot[[1]] <- all_plot[[1]] + theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[2]] <- all_plot[[2]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) +
      plot_layout(guides = "collect") &
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))

    return(plots)
  }else if(length(parameters) == 3){
    all_plot[[1]] <- all_plot[[1]]+ theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[2]] <- all_plot[[2]]+ theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[3]] <- all_plot[[3]]
    plots <- wrap_plots(all_plot, ncol = 1) +
      plot_layout(guides = "collect") &
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }else if(length(parameters) == 4){
    all_plot[[1]] <- all_plot[[1]]+ theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[2]] <- all_plot[[2]]+ theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[3]] <- all_plot[[3]]+ theme(axis.text.x = element_blank(),
                                           legend.position = "none")
    all_plot[[4]] <- all_plot[[4]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) +
      plot_layout(guides = "collect") &
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }else if(length(parameters) == 5){
    all_plot[[5]] <- all_plot[[5]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) +
      plot_layout(guides = "collect") &
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }
  
  
  return(plots)
}



flow_weekly <- plot_seven_day_smoothed( sites = c("lincoln", "boxelder", "riverbluffs"), 
                    parameters = c("Flow", "Specific Conductivity","Temperature"),
                                   #"DO"), 
                    color_scheme = bg_colors, b_size = 16)

flow_weekly
```


tamasag - lincoln

```{r}
bg_colors <- c( "#01377D",
                #"#009DD1",
                "#97E7F5",
                "#7ED348", 
                #"#26B170",
                "#000000")


tama_linc <- plot_seven_day_avg( sites = c("tamasag", "legacy", "lincoln"), 
                    parameters = c("Flow","Specific Conductivity", "Temperature", "DO"),
                                   #"DO"), 
                    color_scheme = bg_colors, b_size = 18)

tama_linc

```

timberline - Boxelder

```{r}

bg_colors <- c( "#01377D",
                #"#009DD1",
                "#97E7F5",
                "#7ED348", 
                "#26B170",
                "#000000")

timb_box <- plot_seven_day_avg( sites = c("timberline","prospect", "archery"), 
                    parameters = c("Specific Conductivity", "Temperature", "DO", "pH"),
                                   #"DO"), 
                    color_scheme = bg_colors, b_size = 18)
timb_box
```


Boxelder - Riverbluffs


```{r}

bg_colors <- c( "#01377D",
                #"#009DD1",
                "#97E7F5",
                "#7ED348", 
                #"#26B170",
                "#000000")

box_rivbluf <- plot_seven_day_avg( sites = c("boxelder","archery",  "riverbluffs"), 
                    parameters = c("Flow","Specific Conductivity", "Temperature"),
                                   #"DO"), 
                    color_scheme = bg_colors, b_size = 18)
box_rivbluf
```

Flow sites

```{r}

bg_colors <- c( "#01377D",
                "#009DD1",
                #"#97E7F5",
                "#7ED348", 
                "#26B170",
                "#000000")

flow_weekly <- plot_seven_day_avg( sites = c("lincoln", "boxelder",  "riverbluffs"), 
                    parameters = c("Flow", "Specific Conductivity","Temperature", "pH"),
                                   #"DO"), 
                    color_scheme = bg_colors, b_size = 16, line_w = 1)
flow_weekly

ggsave("data/sharing/figures/2024/flow_sites_2023_2024_pH.png", plot = flow_weekly, width = 16, height = 14, units = "in", dpi = 300)
```
