---
title: "PWQN Q2 Report"
author: "Sam Struthers"
date: "`r Sys.Date()`"
output: html_document
---

# Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(here)
library(tidyverse)
library(plotly)
library(arrow)
library(furrr)
# loading packages
package_loader <- function(x) {
  if (x %in% installed.packages()) {
    suppressMessages({
      library(x, character.only = TRUE)
    })
  } else {
    suppressMessages({
      install.packages(x)
      library(x, character.only = TRUE)
    })
  }
}

invisible(
  lapply(c("arrow",
           "data.table",
           "httr2",
           "tidyverse",
           "lubridate",
           "zoo",
           "padr",
           "stats",
           "RcppRoll",
           "yaml",
           "here",
           #"fcw.qaqc",
           "furrr", 
           "dataRetrieval", 
           "cdssr", 
           "ggplot2", 
           "ggthemes", 
           "patchwork"
  ),
  package_loader)
)

# 
# params <- paste(c("Chl-a Fluorescence","Depth", "Specific Conductivity",
#                    "Temperature", "Turbidity", "ORP", "pH", "DO", "FDOM Fluorescence"), collapse = "|")
# 
# 
#
# files <- tibble(filename = list.files(here("data","sharing","quarterly_meetings", "2025_Q2","flagged_final"), full.names = TRUE))%>%
#   filter(grepl(pattern = params, filename))%>%
#   #remove extras
#   filter(!grepl(pattern = "Level|MV", filename))
# 
# 
# # read in files
# all_data <- map_dfr(files, ~read_csv(.x, show_col_types = F)) %>%
#   #turn into individual dataframes by site and parameter
#   split(f = list(.$site, .$parameter), sep = "-") %>%
#   keep(~nrow(.) > 0)%>%
#   bind_rows()%>%
#   #convert to MST!
#   mutate(DT_round = with_tz(DT_round, tz = "MST"),
#          DT_join = as.character(DT_round))
# 
# 
# min_date <- min(all_data$DT_round, na.rm = TRUE)%>%
#   format("%Y-%m-%d")
# max_date <- max(all_data$DT_round, na.rm = TRUE)%>%
#   format("%Y-%m-%d")
# 
# # save to raw data file to be processed later on
# write_rds(all_data, here("data", "sharing", "quarterly_meetings", "2025_Q2", paste0("flagged_data_", min_date, "_", max_date, ".rds")))
```

# Setup folder to dump figures

```{r}
# Create a folder to save figures
fig_dir <- "data/sharing/figures/2025/"
if (!dir.exists(fig_dir)) {
  dir.create(fig_dir, recursive = TRUE)
}
```


# Site names, Parameter Labels and Colors
```{r, include= F}

#Site names
site_names <- tibble(site = c("pbd", "bellvue", "salyer", "udall", "riverbend", "cottonwood" ,"elc",  "archery", "riverbluffs"), 
                     site_name = c("Canyon Mouth", "Tamasag", "Legacy", "Lincoln", "Timberline", "Prospect" ,"Boxelder",  "Archery", "River Bluffs"), 
                     natural_name = c("Canyon Mouth", "Bellvue", "Salyer", "Udall", "Riverbend", "Cottonwood", "ELC", "Archery", "River Bluffs"))

#Site Order from up to downstream

site_order = c("Canyon Mouth", "Bellvue", "Salyer", "Udall", "Riverbend", "Cottonwood", "ELC", "Archery", "River Bluffs")


# Parameter labels
labels <- tibble(param = c("Turbidity", "Specific Conductivity", "Depth", "Chl-a Fluorescence", "FDOM Fluorescence", "Temperature", "DO", 'pH', "Flow"),
                 label = c("Turbidity (NTU)", "Specific Conductivity (uS/cm)", "Depth (ft)", "Chl-a Fluorescence (RFU)", "FDOM Fluorescence (RFU)", "Temperature (C)", "DO (mg/L)", 'pH', "Flow (cfs)"))

# Plot colors
bg_colors <- c( "#01377D", "#009DD1", "#97E7F5",
                "#7ED348", "#26B170", "#000000") 
bg_colors_full <- c( "#185BB4", "#009DD1", "#00F5DC", "#00F0C0",
                "#00D684", "#00BD48", "#00DB58","#0FFF6B" 
                , "#000000" ) 

colors <- c("#01377D","#009DD1", "#D55E00")
```

# Read in Sensor Data

```{r, include= F}

params <- paste(c("Chl-a Fluorescence","Depth", "Specific Conductivity",
                   "Temperature", "Turbidity", "ORP", "pH", "DO", "FDOM Fluorescence"), collapse = "|")

files <- tibble(filename = list.files(here("data","sharing","quarterly_meetings", "2025_Q2","flagged_final"), full.names = TRUE))%>%
  filter(grepl(pattern = params, filename))%>%
  #remove extras
  filter(!grepl(pattern = "Level|MV", filename))


# read in files
sensor_data <- map_dfr(files, ~read_csv(.x, show_col_types = F)) %>%
  #turn into individual dataframes by site and parameter
  # split(f = list(.$site, .$parameter), sep = "-") %>%
  # keep(~nrow(.) > 0)%>%
  bind_rows()%>%
  #convert to MST from UTC
  mutate(DT_round = with_tz(DT_round, tz = "MST"),
         DT_join = as.character(DT_round))%>%
  left_join(labels, by = c( "parameter" = "param"))%>%
  left_join(site_names, by = "site")

sensor_data_clean <- sensor_data %>%
  filter(
    is.na(mal_flag), # remove any known malfunctions
    !grepl("site visit|sv window", auto_flag), # remove site visit impacted data
    !grepl("sonde unsubmerged", auto_flag),!grepl("sonde not employed", auto_flag), !grepl("sensor malfunction", auto_flag), # remove simple sensor flags
    !(parameter == "Specific Conductivity" & mean > 2000), # remove instances of SC > 2000 uS/cm
    !(parameter == "pH" & mean < 4.5), # remove pH < 4 (storage solution)
    !(parameter == "pH" & mean > 10), # remove pH > 10 (sensor malfunction)
    !(parameter == "Temperature" & mean < 0), # remove frozen instances
    !(parameter == "Depth" & mean < 0), # remove negative depth values
    !(parameter == "Temperature" & mean > 30), # remove instances of temperature > 30 C (sensor error)
    !(parameter == "DO" & mean < 3), # remove DO < 3 mg/L (sensor error)
    !(mean == 0) # remove instances of 0 values
  ) %>%
  mutate(mean = case_when(
    parameter == "Turbidity" & mean > 1000 ~ 1000, # cap turbidity at 1000 NTU
    parameter == "Depth" ~ mean / 0.3048, # convert depth to ft
    TRUE ~ mean
  ))
```

# WQ Event Time Series Plots

## Function to create timeseries plots

```{r, include= F}
plot_sensor_grabs <- function(df, sites, parameters, renamed_sites, start_dt, end_dt, timestep, add_grabs, color_scheme = bg_colors, b_size = 30){
  
  
  
  all_data <- filter(df, site %in% sites & DT_round >= ymd_hm(start_dt) & DT_round <= ymd_hm(end_dt))%>%
    filter(parameter %in% parameters)
  

  create_plot <- function(param_arg) {

    if(param_arg == "Flow"){
      
      flow_plot <- function(sites,start_dt, end_dt, timestep){

  flow_sites <- tibble(
    site = c("pbd", "udall", "elc", "riverbluffs"), 
    #site_name = c("Canyon Mouth", "Lincoln", "Boxelder", "River Bluffs"  ),
    natural_name = c("Canyon Mouth", "Udall", "ELC", "River Bluffs"  ),
    source = c('CDWR', 'USGS', 'USGS', 'CDWR'), 
    abbrev = c("CLAFTCCO","06752260","06752280",   "CLARIVCO" ))%>%
    filter(site %in% sites)
  
  
  start_dt <- ymd_hm(start_dt, tz = "MST")
  end_dt <- ymd_hm(end_dt, tz = "MST")
  start_date <- floor_date(start_dt, unit = "day")
  end_date <- ceiling_date(end_dt, unit = "day")
  
  gather_q <- function(selected_sites, start_date, end_date, timestep) {


    all_q <- tibble()

    for (i in 1:nrow(flow_sites)) {
      if (flow_sites$source[i] == "USGS") {
        q_data <- readNWISuv(siteNumbers = flow_sites$abbrev[i],
                             startDate = start_date,
                             endDate = end_date,
                             parameterCd = "00060", tz = "America/Denver") %>%
          distinct() %>%
          mutate(DT_mst = with_tz(dateTime, tzone = "MST"),
                 source = "USGS") %>%
          dplyr::select(site = site_no, DT_mst, q_cfs = X_00060_00000, flag = X_00060_00000_cd)

      } else if (flow_sites$source[i] == "CDWR") {
        q_data <- get_telemetry_ts(
          abbrev = flow_sites$abbrev[i],
          parameter = "DISCHRG",
          start_date = start_date,
          end_date = end_date,
          timescale = "raw",
          include_third_party = TRUE) %>%
          distinct() %>%
          mutate(DT_mst = force_tz(datetime, tzone = "MST"),
                 flag = case_when(!is.na(flag_a) & !is.na(flag_b) ~ paste0(flag_a, ",", flag_b),
                                  is.na(flag_a) & !is.na(flag_b) ~ flag_b,
                                  is.na(flag_b) & !is.na(flag_b) ~ flag_a,
                                  TRUE ~ NA_character_),
                 source = "DWR") %>%
          dplyr::select(site = abbrev, DT_mst, q_cfs = meas_value, flag, source)
      }
      all_q <- bind_rows(all_q, q_data)
    }

  
      final_q <- all_q %>%
        mutate(DT_round = round_date(x = DT_mst, unit = timestep)) %>%
        group_by(site, DT_round) %>%
        summarise(q_cfs = mean(q_cfs, na.rm = TRUE)) %>%
        filter(!is.na(q_cfs))%>%
        left_join(flow_sites, by = c("site" = "abbrev"))
   

    return(final_q)
  }
  final_q <- gather_q(flow_sites, start_date, end_date, timestep)
  
  
  trim_q <- final_q%>%
    filter(between(DT_round, start_dt, end_dt))
    
  
  # Subset the colors since there are only a few sites where flow is available
  colors_selected <- tibble(site = sites)%>%
    left_join(site_names, by = c("site" = "site"))
  colors_selected$natural_name <- factor(colors_selected$natural_name, levels = site_order )
  
  
    colors_selected <- colors_selected %>%
      mutate(color = color_scheme[1:length(sites)])%>%
    filter(site %in% flow_sites$site)
    
    
    color_scheme <- colors_selected$color
  
  trim_q$natural_name <- factor(trim_q$natural_name, levels = site_order )
      
    
  
    ggplot(trim_q, aes(x = DT_round, y = q_cfs, color = natural_name)) +
      geom_line(size = 1.5, show.legend = F) +
      scale_color_manual(values = color_scheme) +
      labs( x = "Date", y = "Flow (cfs)", color = "")+
      theme_few(base_size = b_size) +
      theme(axis.title.x = element_blank(), legend.position = "none", 
            legend.text = element_blank())
  

      }
      
      plot <- flow_plot(sites, start_dt, end_dt, timestep)
      
      return(plot)
    }
    
    
    plot_data <- all_data %>%
      filter(parameter == param_arg)
    
    label <- labels %>%
      filter(param == param_arg) %>%
      pull(label)
    
    plot_data$natural_name <- factor(plot_data$natural_name, levels = site_order )
    
    # if(param_arg == "Specific Conductivity"){
    #   b_size = b_size - 5
    #   
    #   plot <- ggplot(plot_data, aes(x = DT_round, y = value, color = site_name)) +
    #   geom_line(linewidth = 2, show.legend = F) +
    #   scale_color_manual(name = "Site", values = color_scheme) +
    #   labs(x = "Date", y = label, color = "Site") +
    #   theme_few(base_size = b_size) +
    #   labs(color = "Site") +
    #   theme(axis.title.x = element_blank(), legend.position = "none")
    # }
    
    plot <- ggplot(plot_data, aes(x = DT_round, y = mean, color = natural_name)) +
      geom_line(linewidth = 2) +
      scale_color_manual(name = "Site", values = color_scheme) +
      labs(x = "Date", y = label, color = "Site") +
      theme_few(base_size = b_size) +
      labs(color = "Site") +
      theme(axis.title.x = element_blank(), legend.position = "bottom")
    
    if (add_grabs) {
      grab_data <- tidy_correlated_df %>%
        filter(site %in% sites & grab_dt >= ymd_hm(start_dt) & grab_dt <= ymd_hm(end_dt))%>%
        left_join(site_names, by = c("site" = "site"))
      
      plot <- plot +
        geom_vline(data = grab_data, aes(xintercept = grab_dt, color = natural_name), linetype = "dashed", size = 1)
    }
    
    return(plot)
  }
  
  all_data <- all_data%>%
    mutate(DT_round = round_date(DT_round, unit = timestep))%>%
    group_by(DT_round, natural_name,site, parameter)%>%
    summarise(mean = mean(mean, na.rm = TRUE), .groups = "drop")


  all_plot <- map(parameters, create_plot)
  

  
  if(length(parameters) == 1){
    all_plot[[1]] <- all_plot[[1]] + theme(axis.title.x = element_text( size = b_size))
    
    plots <- wrap_plots(all_plot, ncol = 1) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom")
    
  }else if(length(parameters) == 2){
    all_plot[[1]] <- all_plot[[1]] + theme(axis.text.x = element_blank(), 
                                           legend.position = "none")
    all_plot[[2]] <- all_plot[[2]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
    
    return(plots)
  }else if(length(parameters) == 3){
    all_plot[[3]] <- all_plot[[3]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }else if(length(parameters) == 4){
    all_plot[[3]] <- all_plot[[3]] + theme(axis.title.x = element_text( size = b_size))
    all_plot[[4]] <- all_plot[[4]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 2) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }else if(length(parameters) == 5){
    all_plot[[5]] <- all_plot[[5]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 2) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }
  
  
  return(plots)
}
```



## WQ Events: March

```{r april_drawdown, echo= F}


sites_march <- c( "udall", "cottonwood", "elc", "archery")


march_storm <-  plot_sensor_grabs(df = sensor_data_clean, sites = sites_march,  parameters = c("Depth", "Specific Conductivity","Turbidity" ), start_dt = "2025-03-28  00:00",
                  end_dt = "2025-04-02 24:00",timestep =  "30 minutes", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


march_storm
ggsave(paste0(fig_dir,"/march_storm.png"), plot = march_storm, width = 16, height = 10, units = "in", dpi = 300)

```



## WQ Events: April Drawdown

```{r april_drawdown, echo= F}

sites_april <- c("salyer", "udall", "riverbend", "elc", "archery")


april <-  plot_sensor_grabs(df = sensor_data_clean, sites = sites_april,  parameters = c("Depth", "Specific Conductivity","DO","Temperature" ), start_dt = "2025-04-13  00:00",
                  end_dt = "2025-04-17 24:00",timestep =  "30 minutes", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


april
ggsave(paste0(fig_dir,"/april_drawdown.png"), plot = april, width = 16, height = 10, units = "in", dpi = 300)

```

## WQ Events:  May Storm

```{r, echo= F}


sites_may_storm <- c( "udall", "elc", "archery", "riverbluffs")


may_storm <-  plot_sensor_grabs(df = sensor_data_clean, sites = sites_may_storm,  parameters = c("Depth", "DO" ,"Turbidity", "Temperature" ), start_dt = "2025-05-07  00:00",
                  end_dt = "2025-05-09 00:00",timestep =  "15 minutes", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


may_storm
ggsave(paste0(fig_dir,"/may_storm.png"), plot = may_storm, width = 16, height = 10, units = "in", dpi = 300)

```


## WQ Events: May DO shift

```{r, echo = F}


sites_may_1<- c( "bellvue", "salyer", "udall", "riverbend")


may_1 <-  plot_sensor_grabs(df = sensor_data_clean, sites = sites_may_1,  parameters = c("Depth","DO","Temperature" ), start_dt = "2025-05-02  12:00",
                  end_dt = "2025-05-04 12:00",timestep =  "15 minute", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


may_1
ggsave(paste0(fig_dir,"/may_do_shift.png"), plot = may_1, width = 16, height = 10, units = "in", dpi = 300)

```


## WQ Events: May SC Diversion

```{r, echo = F}


sites_may_2<- c("bellvue", "riverbend", "elc", "archery", "riverbluffs")


may_2 <-  plot_sensor_grabs(df = sensor_data_clean, sites = sites_may_2,  parameters = c("Depth", "Specific Conductivity","DO","Temperature" ), start_dt = "2025-05-01  00:00",
                  end_dt = "2025-05-15 24:00",timestep =  "2 hours", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


may_2

ggsave(paste0(fig_dir,"/may_drawdown.png"), plot = may_2, width = 16, height = 10, units = "in", dpi = 300)

```


## WQ Events: June FDOM increase

```{r}
sites_june <- c("salyer", "udall", "riverbend", "cottonwood", "elc")

june_fdom <-  plot_sensor_grabs(df = sensor_data_clean, sites = sites_june,  parameters = c("Depth", "FDOM Fluorescence","Specific Conductivity" ), start_dt = "2025-06-24  00:00",
                  end_dt = "2025-06-28 24:00",timestep =  "2 hours", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")

june_fdom

ggsave(paste0(fig_dir,"/june_fdom.png"), plot = june_fdom, width = 16, height = 10, units = "in", dpi = 300)
```



# WQ Monthly Summary

## Function for monthly boxplots

```{r}

generate_monthly_boxplot_summary <- function(sensor_data, year, month){
  
  # Parse the month string as part of a date and extract the month number
  month_number <- mdy(paste(month, "1, 2020")) %>% lubridate::month()
  month_name <- mdy(paste(month, "1, 2020")) %>% lubridate::month(label = TRUE)
  
  
  box_data <- sensor_data%>%
    filter(parameter != "Turbidity",
           parameter != "Depth", 
           parameter != "FDOM Fluorescence", 
           parameter != "Chl-a Fluorescence", 
           parameter != "ORP")%>%
    filter(site != "pbd", site != "springcreek")%>%
    filter(lubridate::month(DT_round) == month_number & lubridate::year(DT_round) == year)
  
  
  # Merge with your data using left_join
  box_data_with_limits <- box_data #%>%
  box_data_with_limits$natural_name <- factor(box_data_with_limits$natural_name, levels = site_order )
  
  
  convert_season_to_months <- function(season_range) {
    # Define month order
    months <- c("january", "february", "march", "april", "may", "june",
                "july", "august", "september", "october", "november", "december")
    
    # Split the season range
    season_parts <- strsplit(season_range, "-")[[1]]
    start_month <- tolower(season_parts[1])
    end_month <- tolower(season_parts[2])
    
    # Find positions of start and end months
    start_pos <- which(months == start_month)
    end_pos <- which(months == end_month)
    
    # Handle cases where season crosses year boundary
    if (start_pos <= end_pos) {
      selected_months <- months[start_pos:end_pos]
    } else {
      selected_months <- c(months[start_pos:12], months[1:end_pos])
    }
    
    return(paste(selected_months, collapse = "|"))
  }
  
  #read in cdphe standards collected by Sam Struthers from https://cdphe.colorado.gov/water-quality-control-commission-regulations
  #Parameter (DO, pH, Temp) thresholds: Reg 31, Table I 
  # Site classifications: Reg 38, ~ Pg 410
  
  month_standard <- readxl::read_xlsx(path = "data/metadata/site_cdphe_classification_2025.xlsx") %>%
    # Convert season_1 to pipe-separated months
    mutate(season = sapply(season, convert_season_to_months))%>%
    # Split ph column into ph_low and ph_high
    separate(ph, into = c("ph_low", "ph_high"), sep = "-", convert = TRUE) %>%
    filter(grepl(x = season, pattern = month_name, ignore.case = TRUE), 
           site %in% unique(box_data_with_limits$natural_name))
  
  # Get unique parameters from the data
  parameters <- unique(box_data_with_limits$label)
  
  # Create individual plots for each parameter
  parameter_plots <- list()
  
  for (param in parameters) {
    # Filter data for current parameter
    param_data <- box_data_with_limits %>% 
      filter(label == param)
    
    standards <- param_data %>%
      select(natural_name) %>%
      distinct() %>%
      left_join(month_standard, by = c("natural_name" = "site"))%>%
      mutate(site_num =  as.numeric(factor(natural_name, levels = site_order))-1)
    
    # Create base plot for current parameter
    p <- param_data %>%
      ggplot(aes(x = natural_name, y = mean, fill = natural_name)) +
      geom_boxplot() +
      #geom_blank(aes(y = y_min)) +  # Forces inclusion of minimum
      #geom_blank(aes(y = y_max)) +  # Forces inclusion of maximum
      scale_fill_manual(values = bg_colors_full) +
      labs(x = "Site", y = param) +  # Use parameter name as y-axis label
      theme_bw(base_size = 14) +  # Slightly smaller base size for multiple plots
      theme(legend.position = "none",
            axis.text.x = element_text(angle = 45, hjust = 1),
            axis.title.x = element_text(face = "bold"),
            axis.title.y = element_text(face = "bold"),
            plot.title = element_text(size = 12))  # Smaller title for individual plots
    
    # Add reference lines based on parameter type
    if (grepl("pH", param, ignore.case = TRUE)) {
      # Add horizontal lines for pH standards
      p <- p + 
        geom_hline(yintercept = 6.5, color = "red", linetype = "dashed", alpha = 0.7) +
        geom_hline(yintercept = 9, color = "red", linetype = "dashed", alpha = 0.7)
    }
    
    if (grepl("Temperature|Temp", param, ignore.case = TRUE)) {
      # Add chronic temperature lines (orange, dashed)
      if ("temp_chronic" %in% names(standards)) {
        chronic_data <- standards %>% 
          filter(!is.na(temp_chronic))
        
        if (nrow(chronic_data) > 0) {
          p <- p + 
            geom_segment(data = chronic_data,
                         aes(x = site_num - 0.5, xend = site_num + 0.5, 
                             y = temp_chronic, yend = temp_chronic),
                         color = "orange", linetype = "dashed", linewidth = 1, alpha = 0.8,
                         inherit.aes = FALSE)
        }
      }
      
      # Add acute temperature lines (red, solid)
      if ("temp_acute" %in% names(standards)) {
        acute_data <- standards %>% 
          filter(!is.na(temp_acute))
        
        if (nrow(acute_data) > 0) {
          p <- p + 
            geom_segment(data = acute_data,
                         aes(x = site_num - 0.5, xend = site_num + 0.5, 
                             y = temp_acute, yend = temp_acute),
                         color = "red", linetype = "solid", linewidth = 1, alpha = 0.8,
                         inherit.aes = FALSE)
        }
      }
    }
    if (grepl("DO", param, ignore.case = TRUE)) {
      
      # Add chronic temperature lines (orange, dashed)
      if ("do_chronic" %in% names(standards)) {
        do_chronic_data <- standards %>% 
          filter(!is.na(temp_chronic))
        
        if (nrow(do_chronic_data) > 0) {
          p <- p + 
            geom_segment(data = do_chronic_data,
                         aes(x = site_num - 0.4, xend = site_num + 0.4, 
                             y = do_chronic, yend = do_chronic),
                         color = "red", linetype = "solid", linewidth = 1, alpha = 0.8,
                         inherit.aes = FALSE)
        }
      }
    }
    
    parameter_plots[[param]] <- p +
      annotate("text", 
               x = -Inf, 
               y = Inf, 
               label = "PRELIMINARY RESULTS", 
               hjust = -0.1, 
               vjust = 2, 
               size = 4, 
               fontface = "bold",
               color = "red")
  }
  
  
  parameter_plots[[1]] <- parameter_plots[[1]]+
    theme(axis.title.x = element_blank())
  parameter_plots[[2]] <- parameter_plots[[2]]+
    theme(axis.title.x = element_blank())
  
  # Combine plots using patchwork
  combined_plot <- wrap_plots(parameter_plots, ncol = 2) +  # Adjust ncol as needed
    plot_annotation(
      title = paste0("Poudre Water Quality Network Data Summary: ", str_to_title(month_name),  " ", year),
      caption = "Preliminary Data, subject to revision.\n Red solid lines indicate state of Colorado chronic thresholds and orange dashed lines indicate acute thresholds for aquatic life.",
      theme = theme(plot.title = element_text(size = 16, hjust = 0.5, face = "bold"), 
                    plot.caption = element_text(size = 13))
    )
  
  # Display the combined plot
  return(combined_plot)
  
}

```

## Generate for each month

```{r}

monthly_plots <- map2(1:7,2025, ~{
  result<- tryCatch({
    generate_monthly_boxplot_summary(sensor_data = sensor_data_clean, month = .x, year = .y)
  }, error = function(e) {
    message(paste("Skipping month", .x, "- Error:", e$message))
    return(NULL)
  })
  # Add month-year as attribute to preserve original indices
  if (!is.null(result)) {
    attr(result, "year_month") <- paste0(.y, "_", .x)
  }
  return(result)
})%>%
keep(~ !is.null(.x))%>%
  set_names(map_chr(., ~ attr(.x, "year_month")))

monthly_plots

write_rds(monthly_plots, file = paste0(fig_dir, "monthly_boxplot_summaries.rds"))

walk(monthly_plots, ~ ggsave(.x, filename = paste0(fig_dir, "monthly_boxplot_summary_", attr(.x, "year_month"), ".png"), width = 16, height = 10, units = "in", dpi = 300))


```



