---
title: "2026 PWQN Report"
author: "Sam Struthers"
date: "`r Sys.Date()`"
output: html_document
---

# Set up

## Load Packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# loading packages
package_loader <- function(x) {
  if (x %in% installed.packages()) {
    suppressMessages({
      library(x, character.only = TRUE)
    })
  } else {
    suppressMessages({
      install.packages(x)
      library(x, character.only = TRUE)
    })
  }
}

invisible(
  lapply(c("arrow",
           "data.table",
           "httr",
           "httr2",
           "tidyverse",
           "lubridate",
           "zoo",
           "padr",
           "stats",
           "RcppRoll",
           "yaml",
           "ross.wq.tools",
           "here",
           "furrr", 
           "dataRetrieval", 
           "cdssr", 
           "ggplot2", 
           "ggthemes", 
           "patchwork",
           "sf", 
           "plotly",
           "viridisLite",
           "tmap"
  ),
  package_loader)
)

`%nin%` = Negate(`%in%`)

if ({
  require(systemfonts)
  ("Roboto" %in% system_fonts()$family)
}) {
  ROSS_theme <- theme_bw() +
    theme(plot.title = element_text(hjust = 0.5, face = 'bold', family = "Roboto"),
          plot.subtitle = element_text(hjust = 0.5, family = "Roboto"))
} else {
  message("You do not have the Roboto font family installed on your computer, currenly using ggplot default text family.
          See ROSS_themes.R for directions to install the font family on your computer.")
  ROSS_theme <- theme_bw() +
    theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
          plot.subtitle = element_text(hjust = 0.5))
}

```

## Year

```{r}
year = 2026
```

## Fig Folder

```{r}
# Create a folder to save figures

fig_dir <- here("docs","pwqn","figs", year)

if (!dir.exists(fig_dir)) {
  dir.create(fig_dir, recursive = TRUE)
}

cycle <- paste0(year, "_cycle")

```


## Site names, Parameter Labels and Colors

```{r, include= F}

#Site names
site_names <- tibble(site = c("pbd", "bellvue", "salyer", "udall", "riverbend", "cottonwood" ,"elc",  "archery", "riverbluffs"), 
                     site_name = c("Canyon Mouth", "Tamasag", "Legacy", "Lincoln", "Timberline", "Prospect" ,"Boxelder",  "Archery", "River Bluffs"), 
                     natural_name = c("Canyon Mouth", "Bellvue", "Salyer", "Udall", "Riverbend", "Cottonwood", "ELC", "Archery", "River Bluffs"), 
                     site_color = c( "#000000" ,      "#185BB4","#009DD1","#00F5DC", "#00F0C0", "#00D684", "#00BD48",  "#00DB58", "#0FFF6B" ) )

#Site Order from up to downstream

site_order = c("Canyon Mouth", "Bellvue", "Salyer", "Udall", "Riverbend", "Cottonwood", "ELC", "Archery", "River Bluffs")


# Parameter labels
labels <- tibble(param = c("Turbidity", "Specific Conductivity", "Depth", "Chl-a Fluorescence", "FDOM Fluorescence", "Temperature", "DO", 'pH', "Flow"),
                 label = c("Turbidity (NTU)", "Specific Conductivity (uS/cm)", "Depth (ft)", "Chl-a Fluorescence (RFU)", "FDOM Fluorescence (RFU)", "Temperature (C)", "DO (mg/L)", 'pH', "Flow (cfs)"))


chem_expressions <- list(
  "Turbidity" = expression(Turbidity ~ (NTU)),
  "Chl-a Fluoresence"      = expression(Chl-a ~ Fluoresence ~ (RFU)),
  "FDOM Fluoresence"      = expression(FDOM ~ Fluoresence ~ (RFU)),
  "Specific Conductivity" = expression(Specific ~ Conductivity ~ (mu ~ S ~ cm^{-1})),
  "Depth"      = expression(Depth ~ (ft)),
  "Temperature" = expression(Temperature ~ (degree ~ C)),
  "DO"        = expression(DO ~ (mg ~ L^{-1})),
  "Flow"      = expression(Flow ~ (cfs)),
  "pH"        = expression(pH)
)


params <- paste(labels$param, collapse = "|")



# Plot colors
bg_colors <- c( "#01377D", "#009DD1", "#97E7F5",
                "#7ED348", "#26B170", "#000000") 
bg_colors_full <- c( "#185BB4", "#009DD1", "#00F5DC", "#00F0C0",
                     "#00D684", "#00BD48", "#00DB58","#0FFF6B" 
                     , "#000000" ) 

colors_blue_orange <- c("#01377D","#009DD1", "#D55E00")

ROSS_lt_pal <- c("#002EA3", "#E70870", "#256BF5",
                 "#745CFB", "#1E4D2B", "#56104E")

ROSS_dk_pal <- c("#1E4D2B", "#E70870", "#256BF5",
                 "#FFCA3A", "#745CFB", "#C3F73A")

ROSS_acc_pal <- c( "#745CFB", "#FFCA3A", "#1E4D2B")

```

# Read in Sensor Data

## Current Year

```{r, include= F}

#select sensor data based on cycle folder structure
if(dir.exists(here("data", "raw", "sensor","manual_data_verification",cycle, "in_progress"))){
  
  files <- list.files(here("data", "raw", "sensor","manual_data_verification", cycle, "in_progress"), full.names = TRUE, recursive = T)%>%
    #don't pull from all data dir
    grep(pattern = "pre_verification_directory|verified_directory|intermediary_directory", ., value = TRUE)
  
  verified = T
} else {
  files <- list.files(here("data", "raw", "sensor","manual_data_verification",cycle, "hydro_vu_pull", "flagged_data"), full.names = TRUE)%>%
    grep(pattern = params, ., value = T)%>%
    #remove extras
    grep(pattern = "Level|MV", ., value = T, invert = T)
  
  verified = F
  
}


# read in files
sensor_data <- map_dfr(files, ~read_parquet(.x)) %>%
  bind_rows()%>%
  #convert to MST from UTC (if it is not already)
  mutate(DT_round = with_tz(DT_round, tz = "MST"),
         DT_join = as.character(DT_round))%>%
  left_join(labels, by = c( "parameter" = "param"))%>%
  left_join(site_names, by = "site")

if(verified){
  sensor_data_clean <- sensor_data %>%
    filter(
      #keep if final status is NA
      (is.na(final_status) | final_status == "PASS" | (final_status == "FLAGGED" & !grepl(pattern = "drift", x = user_flag))), # only keep PASSED or unflagged data
      !(mean == 0) # remove instances of 0 values
    ) %>%
    mutate(mean = case_when(
      parameter == "Turbidity" & mean > 1000 ~ 1000, # cap turbidity at 1000 NTU
      parameter == "Turbidity" & mean <= 1 ~ 1, # Lower bound turbidity at 1 NTU to avoid issues with log scale
      parameter == "Depth" ~ mean / 0.3048, # convert depth to ft
      TRUE ~ mean
    ))
  
}else{
  sensor_data_clean <- sensor_data %>%
    filter(
      is.na(mal_flag), # remove any known malfunctions
      !grepl("site visit|sv window", auto_flag), # remove site visit impacted data
      !grepl("sonde unsubmerged", auto_flag),!grepl("sonde not employed", auto_flag), !grepl("sensor malfunction", auto_flag), # remove simple sensor flags
      !(parameter == "Specific Conductivity" & mean > 3000), # remove instances of SC > 3000 uS/cm
      !(parameter == "pH" & mean < 4.5), # remove pH < 4 (storage solution)
      !(parameter == "pH" & mean > 11), # remove pH > 10 (sensor malfunction)
      !(parameter == "Temperature" & mean < 0), # remove frozen instances
      !(parameter == "Depth" & mean < 0), # remove negative depth values
      !(parameter == "Temperature" & mean > 40), # remove instances of temperature > 30 C (sensor error)
      !(parameter == "DO" & mean < 1), # remove DO < 1 mg/L (sensor error)
      !(mean == 0) # remove instances of 0 values
    ) %>%
    mutate(mean = case_when(
      parameter == "Turbidity" & mean > 1000 ~ 1000, # cap turbidity at 1000 NTU
      parameter == "Depth" ~ mean / 0.3048, # convert depth to ft
      TRUE ~ mean
    ))%>%
    mutate(
      doy = yday(DT_round)
    )
}


```

## Historical Data

```{r}
# Read in Historical Data
cleaned_files <- list.files(path = "data/collated/sensor/hydroshare_pub", pattern = "\\.parquet$", full.names = TRUE, recursive = T)%>%
  grep(pattern = "clean", ., value = T)


hist_data <- map(cleaned_files, ~ read_parquet(file = .x))%>%
  bind_rows()%>%
  filter(site %in% unique(sensor_data_clean$site))

hist_data_clean <- hist_data%>%
  distinct(site, parameter, DateTime_UTC, value_final)%>%
  select(site, parameter, DateTime_UTC, mean = value_final)%>%
  mutate(DateTime_MT = with_tz(DateTime_UTC, tz = "MST"))%>%
  mutate(date = as.Date(DateTime_MT))%>% 
  mutate(doy = yday(date))%>%
  summarise(median = median(mean, na.rm = TRUE),
            q5 = quantile(mean, 0.05, na.rm = TRUE),
            q10 = quantile(mean, 0.10, na.rm = TRUE),
            q25 = quantile(mean, 0.25, na.rm = TRUE),
            q75 = quantile(mean, 0.75, na.rm = TRUE),
            q90 = quantile(mean, 0.90, na.rm = TRUE),
            q95 = quantile(mean, 0.95, na.rm = TRUE),
            max = max(mean, na.rm = T),
            min = min(mean, na.rm = T),
            .by = c("doy", "site", "parameter"))%>%
  mutate(    plot_date = as.POSIXct(paste("2026", doy), format = "%Y %j"),
             q100 = ifelse(max == -Inf | max == Inf , NA, max), 
             q0 = ifelse(min == -Inf | min == Inf, NA, min))
```


# Read in Larimer County Precip Data

## Function to read in data

```{r}

pull_larimer_precip_q <- function(station_id = "11523",  start_dt = "2025-03-01", end_dt = "2026-07-08"){
  
  #format DTs for novastar API
  start_dt <- format(as.POSIXct(start_dt, tz = "MST"), "%Y-%m-%dT%H:%M:%S%z")
  start_dt <- paste0(substr(start_dt, 1, nchar(start_dt) - 2), ":", substr(start_dt, nchar(start_dt) - 1, nchar(start_dt)))
  end_dt <- format(as.POSIXct(end_dt, tz = "MST"), "%Y-%m-%dT%H:%M:%S%z")
  end_dt <- paste0(substr(end_dt, 1, nchar(end_dt) - 2), ":", substr(end_dt, nchar(end_dt) - 1, nchar(end_dt)))
  
  
  #URLs for metadata and data 
  start_meta <- "https://larimerco-ns5.trilynx-novastar.systems/novastar/data/api/v1/stationSummaries?forOperatorStationDashboard=true&stationNumId="
  start_data <- "https://larimerco-ns5.trilynx-novastar.systems/novastar/data/api/v1/stationSummaries?forOperatorStationDashboard=true&stationNumId="
  mid_data <- "&periodStart="  
  end_data <- "&periodEnd="
  
  site_meta_url <-  paste0(start_meta, station_id)
  site_data_url <-  paste0(start_data, station_id, mid_data, start_dt,end_data, end_dt)
  
  
  meta_request <- GET(url = site_meta_url)
  total_list <-content(meta_request) 
  
  if(is_empty(total_list[["stationSummaries"]])){
    message(paste0("No data found for station ", station_id))
    return(tibble())
  }
  sensor_list <- total_list[["stationSummaries"]][[1]][["dataTypes"]]
  
  # grab all sensors and their position within lists
  station_meta <- as.data.frame(do.call(rbind, sensor_list)) %>%
    mutate(name = as.character(name))%>%
    distinct(name)%>%
    mutate(sensor_list_num = row_number())%>%
    pivot_wider( names_from = "name", values_from = "sensor_list_num")%>%
    mutate(id = total_list[["stationSummaries"]][[1]][["id"]], 
           numid = total_list[["stationSummaries"]][[1]][["numId"]], 
           name = total_list[["stationSummaries"]][[1]][["name"]],
           elevation = total_list[["stationSummaries"]][[1]][["elevation"]],
           lat = total_list[["stationSummaries"]][[1]][["latitude"]],
           long = total_list[["stationSummaries"]][[1]][["longitude"]], 
           site_number = station_id, 
           site_meta_url = site_meta_url,
           site_data_url = site_data_url)
  
  message(paste0("Pulling data for station ", station_meta$name," (", station_meta$site_number, ")"))
  Sys.sleep(1)   
  
  #create request to novastar website using url created 
  request <- GET(url = site_data_url)
  
  #gives content of httr pull
  total_list <- content(request)
  
  unlist_site_data <- function(data_list) {
    # map_dfr handles the loop and binding automatically
    map_dfr(data_list, unlist)
  }
  
  if("Precip" %in% names(station_meta)){
    precip_sensor_num <-  as.numeric(station_meta$Precip[1]) 
    precip_data <- total_list[["stationSummaries"]][[1]][["ts"]][[precip_sensor_num]][["data"]]
    if(length(precip_data) == 0){
      precip_df <- tibble()
    } else {
      precip_df <- unlist_site_data(precip_data)%>%
        mutate(p_cm = as.double(v) * 2.54, # convert precip to cm from inches
               datetime = ymd_hms(dt, tz = "",quiet = TRUE), 
               DT_mst = with_tz(datetime, tzone = "MST"))%>%
        select( DT_mst, p_cm, flag = f)%>%
        pivot_longer(cols = c(p_cm), names_to = "parameter", values_to = "value")
    }
  }else{
    precip_df <- tibble()
  }
  
  if("DischargeRiver" %in% names(station_meta)){
    q_sensor_num <- as.numeric(station_meta$DischargeRiver[1]) # change to q name
    # find list where discharge data is stored
    discharge_data <- total_list[["stationSummaries"]][[1]][["ts"]][[q_sensor_num]][["data"]]
    
    if(length(discharge_data) == 0){
      q_df <- tibble()
    } else {
      q_df <- unlist_site_data(discharge_data)%>%
        mutate(q_cfs = as.double(v),
               datetime = ymd_hms(dt, tz = "",quiet = TRUE), 
               DT_mst = with_tz(datetime, tzone = "MST"))%>%
        select( DT_mst, q_cfs, flag = f)%>%
        pivot_longer(cols = c( q_cfs), names_to = "parameter", values_to = "value")
    }
  }else{
    q_df <- tibble()
  }
  
  import <- bind_rows(q_df, precip_df)
  
  if(nrow(import) != 0){
    import <- import %>%
      mutate( station_id = station_meta$site_number[1], 
              lat = station_meta$lat[1],
              long = station_meta$long[1],
              elevation = station_meta$elevation[1],
              name = station_meta$name[1],
              api_source = "Larimer County")
  }
  Sys.sleep(5) # add delay to avoid overwhelming server with requests
  return(import)
}


```
### Load in Larimer CO Precip/Flow data

```{r}

if(file.exists(here("data/collated/external_datasets/larimer_county_station_flow_precip_20210101_20260601.parquet"))){
  larimer_flow_precip <- read_parquet("data/collated/external_datasets/larimer_county_station_flow_precip_20210101_20260601.parquet")%>%
    filter(station_id != "11525" & watershed != "out")#this site appears to be an outlier with very high precip values, and is located outside of the watershed boundary, so removing from analysis.
}else{
  meta <- read_csv("data/raw/external_datasets/larimer_co_precip/larimer_county_station_data.csv", show_col_types = F) %>%
    mutate(site = as.character(numId))%>%
    select(site,name, lat, long, agency, watershed)
  
  all_data <- map(meta$site, ~pull_larimer_precip_q(station_id = .x,
                                                    start_dt = "2026-07-01", 
                                                    end_dt = "2026-09-21"))
  
  larimer_flow_precip  <- all_data%>%
    bind_rows()%>%
    left_join( meta%>%select(agency, watershed, site), by = c('station_id' = "site"))
  
  #Save data
  write_parquet(larimer_flow_precip,
                'data/collated/external_datasets/larimer_county_station_flow_precip_20260701_20260921.parquet')
  
}
```


## Function to create plots
```{r}

create_daily_precip_plot <- function(precip_flow_df, start_date, end_date, grouping){
  
  
  if(grouping == "ws"){
    
    precip_trim <- precip_flow_df %>% 
      filter(!watershed %in% c("out", "BigT") & station_id != "11525")%>%
      filter(!station_id == "11511")%>%
      filter(parameter == "p_cm" & value > 0)%>%
      filter(value < 20) %>% # remove precip values > 30 cm, which are likely errors
      pivot_wider(id_cols = c(DT_mst, station_id, watershed), names_from = parameter, values_from = value) %>%
      filter(DT_mst >= start_date & DT_mst <= end_date)%>% 
      mutate(DT_round = round_date(DT_mst, "day"))%>%
      group_by(DT_round, watershed) %>%
      summarise(
        total_precip = sum(p_cm),
        num_sites = n_distinct(station_id),
        avg_hourly_precip = total_precip / num_sites,
        .groups = "drop")
    
    #make a histogram bar plot with dt mst as X axis and color by name
    ggplot(precip_trim, aes(x = DT_round,y = avg_hourly_precip, fill = watershed))+
      #put the bars next to each other
      geom_col(linewidth = 2, position = "dodge")+
      scale_y_reverse()+
      labs(x = 'Date',
           y = 'Precipitation \n(cm/day)', 
           fill = "Watershed")+
      theme_bw(base_size = 18)+
      theme(legend.position = "bottom")
    
  }else{
    
    precip_trim <- precip_flow_df %>% 
      filter(!watershed %in% c("out", "BigT") & station_id != "11525")%>%
      filter(!station_id == "11511")%>%
      
      filter(parameter == "p_cm" & value > 0)%>%
      filter(value < 20)%>%
      pivot_wider(id_cols = c(DT_mst, station_id, watershed), names_from = parameter, values_from = value) %>%
      filter(DT_mst >= start_date & DT_mst <= end_date & p_cm > 0 )%>%
      mutate(date = as_date(DT_mst))%>%
      #find how many sites triggered on a day
      group_by(date, station_id) %>%
      summarise(
        avg_daily_precip = sum(p_cm))
    
    #make a histogram bar plot with dt mst as X axis and color by name
    ggplot(precip_trim, aes(x = date,y = avg_daily_precip, fill = station_id))+
      geom_col()+
      # add a geom rect around each date
      # geom_rect(aes(xmin = date - 0.5, xmax = date + 0.5, ymin = 0, ymax = max(avg_daily_precip)), fill = NA, color = "black")+
      labs(title = 'Larimer County Precipitation',
           x = 'Date',
           y = 'Precip (cm) at each site')+
      theme(legend.position = "none")
  }
  
  
}

create_storm_precip_plot <- function(precip_flow_df, station_id_oi, start_date, end_date){
  
  if(is_null(station_id_oi)){
    message("No station ID provided, cannot create storm precip plot.")
    return(NULL)
  }else{
    precip_flow_df %>% 
      select(name, parameter, DT_mst, station_id, value)%>%
      filter(station_id == station_id_oi & parameter == "p_cm" & value < 20 & DT_mst >= start_date & DT_mst <= end_date )%>%
      mutate(DT_round = round_date(DT_mst, "hour"))%>%
      group_by(DT_round, station_id, name)%>%
      summarise(value = sum(value))%>%
      ungroup()%>%
      complete(DT_round = seq(min(DT_round), max(DT_round), by = "hour"), 
               nesting(station_id, name)) %>%
      mutate(value = replace_na(value, 0)) %>%
      arrange(DT_round) %>%
      group_by(station_id) %>%                
      mutate(is_precip = value > 0) %>%
      mutate(last_rain_time = if_else(is_precip, DT_round, as.POSIXct(NA)))%>%
      fill(last_rain_time, .direction = "down") %>%
      mutate( time_since_last_rain = difftime(DT_round, last_rain_time, units = "hours")) %>%
      mutate(new_storm = time_since_last_rain > 6) %>%
      mutate(storm_id = cumsum(ifelse(is.na(new_storm), FALSE, new_storm)))%>%                
      group_by(station_id, storm_id) %>%                
      mutate(cumulative_storm_precip = cumsum(value)) %>%
      ungroup() %>%                
      mutate(name = paste0(name, " (", station_id, ")")) %>%              
      ggplot(aes(x = DT_round, y = cumulative_storm_precip, fill = name)) +
      geom_area(alpha = 0.5, color = "blue", size = 1) +
      scale_fill_manual(values = "skyblue") +
      scale_y_reverse()+
      labs(x = 'Date',                
           y = 'Cumulative Precipitation \n(cm)',                 
           fill = "Station") +                
      theme_bw(base_size = 18) +                
      theme(legend.position = "bottom")
    
  }
  
}


```

## Function to create maps of Precip

This function does work when there is precip
```{r}

create_precip_map <- function(precip_flow_df, date_sel){
  
  date_sel = as.Date(date_sel)
  
  # Filter the data based on the selected date
  filtered_data <- precip_flow_df  %>%
    filter(!watershed %in% c("BigT", "out"))%>%
    mutate(date = as_date(DT_mst))%>%
    filter(date == date_sel) %>%
    pivot_wider(id_cols = c(name, DT_mst,date, lat, long), names_from = parameter, values_from = value) %>%
    group_by(name, date, lat, long) %>%
    summarise(daily_precip = sum(p_cm), .groups = "drop")%>%
    st_as_sf(coords = c('long', "lat"), crs = 4326)
  
  if(nrow(filtered_data) == 0){
    return(NULL)
  }
  
  zero_data <- filtered_data%>%
    filter(daily_precip == 0)
  non_zero_data <- filtered_data%>%
    filter(daily_precip != 0)
  
  
  
  palfunc <- function(n, alpha = 1, begin = 0, end = 1, direction = 1){
    colors <- magma(11, direction = -1)
    if (direction < 0) colors <- rev(colors)
    colorRampPalette(colors, alpha = alpha)(n)
  }
  
  at_10 = c(0, 0.5, 1, 2, 5)
  at_limited = range(at_10)  # Extracts only min and max values
  
  colors <- magma(11, direction = -1)
  # Modified mapview call
  if(nrow(non_zero_data) > 0){
    map <- mapview::mapview(non_zero_data,
                            cex = 8,
                            zcol = "daily_precip",
                            layer.name = paste0("Daily Precipitation (cm) on ", date_sel),
                            col.regions = palfunc, 
                            at = at_10)  # Use only min and max for the legend
    return(map)
  }
  
  if(nrow(non_zero_data) == 0){
    return(NULL)
  }
  
}
#Creating a single map
create_precip_map(larimer_flow_precip,date_sel =  "2026-09-16")
#creating a sequence of maps over time
# dates <- seq(as.Date("2025-08-21"), as.Date("2025-09-01"), by = "day")
# list_of_maps <- map(dates, ~create_precip_map(precip_flow_df = larimer_flow_precip, date_sel = .x))%>%
#   #name list   elements by date
#   setNames(dates)

unique(larimer_flow_precip$parameter)
```

## Load in Flow data from the CLP 
In case we need to describe flows during events, we can pull in flow data from the CLP using the cdssr package. Below is an example of how to pull in flow data for the CLP stations and create a timeseries plot. Note that this code is not currently being used in the report, but can be used if needed to describe flow conditions during events.


```{r}
stations <- get_telemetry_stations(water_district = 3, api_key = read_yaml("creds/CDWRCreds.yml")$api_key)%>%filter(meas_date_time >= "2025-08-27" & grepl("DISCHRG",parameter ))%>% filter(abbrev %nin% c("BOBGLNCO","BHERTNCO","OLGBYPCO" ))%>%
  select(station_name, abbrev, parameter, stream_mile, station_type, structure_type, latitude, longitude)%>%
  #removing sites on the plains or  north
  filter(longitude <= -104.934 & latitude <= 40.79)%>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)

tmap_mode("view")

tm_shape(stations) +
  tm_dots(col = "station_type", size = 1, palette = "Set1") +
  tm_text("stream_mile", size = 1, ymod = 0.25) +
  tm_layout(legend.position = c("left", "bottom"))

flows_data <-map2(stations$abbrev,stations$parameter, 
                  ~get_telemetry_ts(abbrev = .x, 
                                    parameter = .y, 
                                    start_date = "2025-06-22", #change as needed
                                    end_date = "2025-06-27",  #change as needed
                                    api_key = read_yaml(file = "creds/CDWRCreds.yml")$api_key, 
                                    timescale = "raw"))
#quick plot to look at flow conditions during the event
bind_rows(flows_data) %>%
  filter(meas_unit == "cfs")%>%
  left_join(stations, by = "abbrev")%>%
  ggplot(aes(x = datetime, y = meas_value, color = station_type)) +
  geom_line() +
  labs(x = "Date", y = "Flow (cfs)", color = "Site Type") +
  theme_bw(base_size = 18) +
  theme(legend.position = "bottom"
  )+
  facet_wrap(~station_name, scale = "free_y")
```

# Down Days Plot

## Function
Should pull this out into it's own script later on!

```{r}
# This script identifies and summarizes "bad data days" for continuous
# water quality sensors in 2023 and 2024 across multiple monitoring sites.
#
# Two types of bad data days are flagged:
#   (1) Sensor malfunction days, where field notes indicate issues
#       (e.g., sensor malfunction, burial, biofouling, data labeled as OMIT) and at least
#       half of the day’s observations are affected.
#   (2) Missing-data days, identified using temperature records as a
#       proxy for full sensor outages when at least half of the day’s
#       values are NA.

plot_down_days <- function(sensor_df, year_oi){
  
  year_data <- sensor_df %>%
    filter(year(DT_round) == year_oi)
  
  if(nrow(year_data) == 0){
    stop(paste("No data available for year:", year_oi))
  }
  
  if("user_flag" %in% names(year_data)){
    flag_col = "user_flag"
  }else{
    flag_col = "auto_flag"
    year_data <- year_data %>%
      mutate(
      #if verification status doesn't exist, make a new column where it is NA if there is no mal flag, and "OMIT" if there is a mal flag
           verification_status = ifelse(!is.na(mal_flag), "OMIT", NA))
  }
  
  
  down_days_all_data <- year_data %>%
    filter(!parameter %in% c("Depth", "FDOM Fluorescence", "Chl-a Fluorescence")) %>%
    filter(site %in% c("bellvue", "salyer", "udall", "riverbend", "cottonwood",
                       "elc", "archery", "riverbluffs")) %>%
    mutate(site_id = as.numeric(factor(site, levels = c("bellvue", "salyer", "udall", "riverbend", "cottonwood",
                                                        "elc", "archery", "riverbluffs")))) %>%
    mutate(date = as_date(DT_join))
  
  flag_sym <- sym(flag_col)

  counts <- down_days_all_data %>%
    # Use !!flag_sym to evaluate the variable holding the column name
    filter(!is.na(!!flag_sym)) %>%                
    filter(grepl("sonde unsubmerged|outside of sensor specification range|sensor malfunction", !!flag_sym) | #usually |sonde burial is included but due to over flagging, we are removing for now
             #Look for excessive drift flags with high turbidity values as a proxy for biofouling
             (parameter == "Turbidity" & grepl("drift", !!flag_sym) & mean >= 40)|
             #Calibration Errors where the data had to be removed
             (grepl("calibration error", !! flag_sym) & verification_status == "OMIT") |
             #When data was omitted
             (verification_status == "OMIT")
    ) %>%
    filter(!is.na(mean)) %>%
    group_by(site, site_id, parameter, date) %>%
    summarize(total = n(), .groups = "drop_last") %>%
    filter(total >= 64) %>%
    ungroup() %>%
    distinct(site, site_id, date)
  
    cat("Number of days with poor sensor data:", nrow(counts), "\n")

  counts_p2 <- down_days_all_data%>%
    filter(parameter == "Temperature") %>%
    filter(is.na(mean)) %>%
    group_by(site, site_id, parameter, date) %>%
    summarize(total = n()) %>%
    filter(total >= 64) %>%
    ungroup() %>%
    select(site, site_id, date)
  
  cat("Number of days with missing temperature data:", nrow(counts_p2), "\n")
  
  counts_p2 <- counts_p2 %>%
    bind_rows(counts) %>%
    distinct(site, site_id, date)
  
  total_days <- down_days_all_data%>%
    distinct(site, date) %>%
    group_by(site) %>%
    summarize(days = n()) %>%
    left_join(., counts_p2 %>% group_by(site) %>% summarize(bad_days = n()))
  
  days <- total_days %>%
    mutate(bad_days_tot = ifelse(is.na(bad_days), 0, bad_days)) %>%
    mutate(perc_days_tot = 100 * (bad_days_tot / days))
  
  # new site names
  site_order <- setdiff(site_names$natural_name, "Canyon Mouth")
  
  # get date range
  date_range <- range(down_days_all_data$date)
  
  complete <- expand.grid(date = seq(date_range[1], date_range[2], by = "day"),
                          natural_name = site_order) %>%
    mutate(natural_name = factor(natural_name,
                                 levels = rev(site_order)))
  
  counts <- counts_p2 %>%
    left_join(site_names, by = c("site")) %>%
    # add factor levels for site ordering
    mutate(natural_name = factor(natural_name,
                                 levels = rev(site_order)))
  
  perc_down_days <- round((nrow(counts)/nrow(complete))*100, 1)
  #plot theme
  plot_theme <- theme_bw(base_size = 24) +
    theme(text = element_text(size = 20),
          axis.text.x = element_text(angle = 45, hjust = 1, size = 15),
          legend.position = "none",
          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"))
  
  color_palette <- c("#185BB4", "#009DD1", "#00F5DC", "#00F0C0",
                     "#00D684", "#00BD48", "#00DB58", "#0FFF6B")
  message(paste0("The PWQN was down for ", nrow(counts), " site days across the ", length(site_order), " sites."))
  
  message(paste0("The percentage of down days across the network was ", perc_down_days, "% (of ", nrow(complete), " total site days)."))
  
  ggplot() +
    # add full dataset as invisible points to maintain data structure
    geom_point(data = complete,
               aes(x = date, y = natural_name),
               color = "transparent") +
    geom_point(data = counts,
               aes(x = date, y = natural_name, color = natural_name),
               size = 3) +
    scale_x_date(limits = date_range,
                 date_breaks = "1 month",
                 date_labels = "%b") +
    scale_y_discrete(limits = rev(site_order)) +
    scale_color_manual(values = rev(color_palette)) +
    labs(x = "Date", y = NULL,
         title = paste0("PWQN Down Days for ", year_oi),
         subtitle = paste0("Total site days: ", nrow(counts), " (", perc_down_days, "%) across the ", length(site_order), " sites.")
    ) +
    plot_theme
  
  
}
```
## 2026
Using sensor_data_clean we can make this plot easily

```{r}
down_day_plot_2026 <- sensor_data_clean %>%
  #there were a few days where Udall wasn't recording on the Vulink so I will manually exclude them here:
  mutate(mean = ifelse(site == "udall" & DT_round >= as.POSIXct("2026-09-10 00:00:00", tz = "America/Denver") & DT_round <= as.POSIXct("2026-09-14 10:00:00", tz = "America/Denver"), NA, mean))%>%
plot_down_days(., 2026)

ggsave(here(fig_dir,"down_days_2026.png"), plot = down_day_plot_2026, width = 8, height = 12, units = "in", dpi = 300)
```

## 2025
Using sensor_data we can make this plot easily

```{r}
#down_day_plot_2025 <- plot_down_days(sensor_data, 2025)

```


## 2024

Read in 2024 verified data to see how we do

```{r}
files <- list.files(here("data", "raw", "sensor","manual_data_verification", "2024_cycle", "in_progress"), full.names = TRUE, recursive = T)%>%
  #don't pull from all data dir
  grep(pattern = "pre_verification_directory|verified_directory|intermediary_directory", ., value = TRUE)

# read in files
sensor_data_2024 <- map_dfr(files, ~read_parquet(.x)) %>%
  bind_rows()%>%
  #convert to MST from UTC (if it is not already)
  mutate(DT_round = with_tz(DT_round, tz = "MST"),
         DT_join = as.character(DT_round))%>%
  left_join(labels, by = c( "parameter" = "param"))%>%
  left_join(site_names, by = "site")


down_day_plot_2024 <- plot_down_days(sensor_data_2024, 2024)

full_plot<- (down_day_plot_2024 + down_day_plot_2025) + 
  plot_layout(ncol = 2, guides = "collect") & 
  theme(plot.margin = margin(5, 5, 5, 5))

ggsave(here(fig_dir,"down_days_2024_2025.png"), plot = full_plot, width = 14, height = 10, units = "in", dpi = 300)
```

# QAQC accuracy plot

Heat map plot where we compare the automatic QAQC flagging to user generated qaqc. 
**This will not run until we have manually verified data **

```{r}

pwqn_sites <- setdiff(site_names$site, "pbd")
# site accuracy
site_accuracy <- sensor_data %>%
  filter(site %in% pwqn_sites & parameter %in% c("Turbidity", "Specific Conductivity", "pH", "Temperature", "DO", "Chl-a Fluorescence")) %>%
  mutate(is_accurate = (is.na(flag) & is.na(user_flag)) | (!is.na(flag) & !is.na(user_flag))) %>%
  group_by(site, parameter) %>%
  summarize(accuracy = mean(is_accurate, na.rm = TRUE) * 100, .groups = "drop")%>%
  left_join(site_names, by = "site")

# network-wide accuracy per parameter
network_total <- sensor_data %>%
  filter(site %in% pwqn_sites & parameter %in% c("Turbidity", "Specific Conductivity", "pH", "Temperature", "DO", "Chl-a Fluorescence")) %>%
  mutate(is_accurate = (is.na(flag) & is.na(user_flag)) | (!is.na(flag) & !is.na(user_flag))) %>%
  group_by(parameter) %>%
  summarize(accuracy = mean(is_accurate, na.rm = TRUE) * 100, .groups = "drop") %>%
  mutate(natural_name = "Network Total")

mean(network_total$accuracy)

# combine
plot_data <- bind_rows(site_accuracy, network_total) %>%
  bind_rows( tibble(
    natural_name = " ", 
    parameter = unique(site_accuracy$parameter), 
    accuracy = NA
  ))%>%
  mutate(natural_name = factor(natural_name, levels = c(site_names$natural_name," ", "Network Total")), 
         parameter = factor(parameter, levels = rev(c("Turbidity", "Chl-a Fluorescence", "Specific Conductivity", "pH", "DO", "Temperature"))))

# plot
acc_plot <- ggplot(plot_data, aes(x = natural_name, y = parameter, fill = accuracy)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(accuracy, 1)), color = "black", size = 3) +
  scale_fill_gradientn(
    colors = c("#c23a4b", "#e0824f", "#f2b04d"),
    limits = c(50, 100),
    na.value = "white",
    name = "Accuracy (%)"
  ) +
  labs(title = "Auto-QA/QC Accuracy", x = NULL, y = NULL) +
  theme_minimal(base_size = 20) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid = element_blank()
  )

acc_plot

ggsave(here(fig_dir,"qaqc_accuracy.png"), plot = acc_plot, width = 10, height = 8, units = "in", dpi = 300)
```

## DO Burial Signal improvements

This was done in Juan's notebook (scratch/misc).



# WQ Event Time Series Plots


## Function to create timeseries plots

This will take in sensor data, pick sites/parameter/date range, summarize data to a timestep median, and make a panel of plot based on the selections. If we want, we can apply a binominal smoothing function to the data if smooth is TRUE. This function assumes that erroneous data has already been removed and will plot the `mean` column. Flow data is pulled from CDWR if needed. 

###   Plot Sensor Function
```{r}
plot_sensor <- function(df, sites, parameters, start_dt, end_dt, timestep, b_size = 30, smooth = TRUE){
  
  # Correct timestep
  if(grepl("minutes", timestep)){
    timestep <- gsub("minutes", "mins", timestep,ignore.case = T)
  }
  
  all_data <- df %>%
    filter(site %in% sites,
           parameter %in% parameters, 
           between(DT_round, ymd_hm(start_dt, tz = "MST")-days(1), ymd_hm(end_dt, tz = "MST")+ days(1)) )%>%
    mutate(DT_round = round_date(DT_round, unit = timestep)) %>%
    group_by(DT_round, natural_name, site, parameter, site_color) %>%
    summarise(mean = median(mean, na.rm = TRUE), .groups = "drop") %>%
    group_by(natural_name, site, parameter, site_color) %>%
    pad(
      by = "DT_round",
      interval = timestep
    ) %>%
    ungroup()%>%
    filter(between(DT_round, ymd_hm(start_dt, tz = "MST"), ymd_hm(end_dt, tz = "MST")))
  
  all_plot <- map(parameters, function(param_arg){
    
    # Flow plots using CDSSR/USGS data
    if (param_arg == "Flow") {
      
      flow_sites <- tibble(
        site = c("pbd", "udall", "elc", "riverbluffs"), 
        abbrev = c("CLAFTCCO", "CLAFORCO", "CLABOXCO", "CLARIVCO")
      ) %>%
        filter(site %in% sites)
      
      start_dt <- ymd_hm(start_dt, tz = "MST")
      end_dt <- ymd_hm(end_dt, tz = "MST")
      start_date <- floor_date(start_dt, unit = "day")
      end_date <- ceiling_date(end_dt, unit = "day")
      
      final_q <- map_dfr(flow_sites$abbrev, ~{
        q_data <- get_telemetry_ts(
          abbrev = .x,
          parameter = "DISCHRG",
          start_date = start_date,
          end_date = end_date,
          timescale = "raw",
          api_key = read_yaml("creds/CDWRCreds.yml")$api_key,
          include_third_party = TRUE ) %>%
          distinct() %>%
          mutate(DT_mst = force_tz(datetime, tzone = "MST"),
                 source = "DWR") %>%
          select(abbrev, DT_mst, q_cfs = meas_value, source)
      })%>%
        mutate(DT_round = round_date(DT_mst, unit = timestep)) %>%
        group_by(abbrev, DT_round) %>%
        summarise(q_cfs = median(q_cfs, na.rm = TRUE), .groups = "drop") %>%
        left_join(flow_sites, by = "abbrev") %>%
        left_join(site_names, by = "site")%>%  # Join to get site_color
        filter(between(DT_round, start_dt, end_dt))
      
      final_q$natural_name <- factor(final_q$natural_name, levels = site_order)
      
      gg <-  ggplot(final_q, aes(x = DT_round, y = q_cfs, color = natural_name)) +
        geom_line(size = 1.5, show.legend = FALSE) +
        scale_color_manual(values = setNames(final_q$site_color, final_q$natural_name)) +
        labs(x = "Date", y = "Flow (cfs)", color = "") +
        theme_few(base_size = b_size) +
        theme(axis.title.x = element_blank(),
              legend.position = "none")
      return(gg)
    }
    
    #All ross collected data
    plot_data <- all_data %>%
      filter(parameter == param_arg)
    
    if(timestep %in% c("15 mins", "15 minutes", "30 minutes", "30 mins") & smooth == TRUE){
      plot_data <- plot_data%>%
        #apply binominal smoothing
        group_by(natural_name) %>%
        arrange(DT_round) %>%
        mutate(mean = zoo::rollapply(mean, width = 5, FUN = function(x) {
          if (all(is.na(x))) {
            return(NA)
          } else {
            #binomial smoothing kernel (1,2,3,2,1)
            weights <- c(1,2,3,2,1)
            return(sum(x * weights, na.rm = TRUE) / sum(weights[!is.na(x)]))
          }
        }, fill = NA, align = "center"))
    }
    
    label <- labels %>%
      filter(param == param_arg) %>%
      pull(label)
    
    plot_data$natural_name <- factor(plot_data$natural_name, levels = site_order)
    
    gg <- ggplot(plot_data, aes(x = DT_round, y = mean, color = natural_name)) +
      geom_line(linewidth = 2) +
      scale_color_manual(name = "Site", values = setNames(plot_data$site_color, plot_data$natural_name)) +
      labs(x = "Date", y = label, color = "Site") +
      theme_few(base_size = b_size) +
      theme(axis.title.x = element_blank(), legend.position = "bottom")
    
    return(gg)
  })
  
  # Layout based on number of parameters
  n_params <- length(parameters)
  # Layout plot based on the number of parameters, with shared legend at the bottom
  layout_plot <- wrap_plots(all_plot, ncol = ifelse(n_params > 3, 2, 1)) +
    plot_layout(guides = "collect") &
    theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  
  layout_plot
  
}
```

###   Make Historical Plots

```{r}

date_range = range(sensor_data_clean$DT_round)

pct_bands <- tribble(
  ~ymin,  ~ymax,   ~label,                                          ~color,
  "q0",   "q5",    "Extreme (<5% / >95%)",                          "#8E857A",
  "q5",   "q10",   "Much below/above (5-10% / 90-95%)",             "#E8DAB2",
  "q10",  "q25",   "Below/above normal (10-25% / 75-90%)",          "#F0F7EB",
  "q25",  "q75",   "Normal range (25-75%)",                         "#9CC4DE",
  "q75",  "q90",   "Below/above normal (10-25% / 75-90%)",          "#F0F7EB",
  "q90",  "q95",   "Much below/above (5-10% / 90-95%)",             "#E8DAB2",
  "q95",  "q100",  "Extreme (<5% / >95%)",                          "#8E857A"
)

# One legend entry per unique label/color, in draw order
band_lookup <- pct_bands %>%
  distinct(label, color) %>%
  mutate(label = factor(label, levels = label))
# Turn pct_bands into one long lookup: label + color per band, in draw order
# (draw widest/most extreme bands first so narrower ones layer on top)

make_hist_plot <- function(param,
                           sites = c("bellvue", "salyer", "udall", "riverbend", "cottonwood",
                                     "elc", "archery", "riverbluffs"),
                           start_date = date_range[1],
                           end_date = date_range[2],
                           summary_level = c("hourly", "daily"),
                           summary_fun = c("percentiles_10_90", "mean", "median")) {
  
  summary_level <- match.arg(summary_level)
  summary_fun <- match.arg(summary_fun)
  
  date_floor_unit <- if (summary_level == "hourly") "hour" else "day"
  
  # Calculate summary stats based on chosen option
  plot_data <- sensor_data_clean %>% 
    filter(parameter == param) %>%
    filter(site %in% sites) %>%
    filter(between(DT_round, start_date, end_date)) %>%
    mutate(DT_summary = floor_date(DT_round, date_floor_unit))
  
  if (summary_fun == "percentiles_10_90") {
    plot_data <- plot_data %>%
      summarise(
        p10 = quantile(mean, probs = 0.10, na.rm = TRUE),
        p90 = quantile(mean, probs = 0.90, na.rm = TRUE),
        .by = c("site", "DT_summary", "parameter")
      )
  } else {
    summary_fn <- if (summary_fun == "mean") function(x) mean(x, na.rm = TRUE) else function(x) median(x, na.rm = TRUE)
    plot_data <- plot_data %>%
      summarise(
        value = summary_fn(mean),
        .by = c("site", "DT_summary", "parameter")
      )
  }
  
  plot_data <- plot_data %>%
    left_join(labels, by = c("parameter" = "param")) %>%
    left_join(site_names, by = "site")
  
  hist_data_plot <- hist_data_clean %>%
    filter(site %in% sites) %>%
    filter(parameter == param & between(plot_date, start_date - days(2), end_date + days(2))) %>%
    left_join(labels, by = c("parameter" = "param")) %>%
    left_join(site_names, by = "site") %>%
    na.omit()

  plot_data$natural_name <- factor(plot_data$natural_name, levels = site_order)
  hist_data_plot$natural_name <- factor(hist_data_plot$natural_name, levels = site_order)
  
  param_label <- chem_expressions[[param]]
  scales_param <- if (param == "Specific Conductivity") "free_y" else "free_x"
  
  p <- ggplot(hist_data_plot, aes(x = plot_date, y = median))
  
  # Historical percentile ribbons
  ribbon_layers <- pmap(pct_bands, function(ymin, ymax, label, color) {
    geom_ribbon(aes(ymin = .data[[ymin]], ymax = .data[[ymax]], fill = !!label),
                alpha = 0.6, color = NA)
  })
  p <- reduce(ribbon_layers, `+`, .init = p)
  
  # Base historical median line
  p <- p + geom_line(alpha = 0.7, linetype = "dashed", color = "black")
  
  # Add current sensor data layers according to summary_fun
  if (summary_fun == "percentiles_10_90") {
    p <- p +
      # p10 boundary line
      geom_line(data = plot_data, aes(x = DT_summary, y = p10, color = natural_name),
                linewidth = 1, linetype = "solid", alpha = 1) +
      # p90 boundary line
      geom_line(data = plot_data, aes(x = DT_summary, y = p90, color = natural_name),
                linewidth = 1, linetype = "solid", alpha = 1)
    
    title_summary <- "10th & 90th Percentiles"
  } else {
    p <- p +
      geom_line(data = plot_data, aes(x = DT_summary, y = value, color = natural_name),
                linewidth = 1.5, alpha = 1)
    
    title_summary <- str_to_title(summary_fun)
  }
  
  p +
    scale_color_manual(name = "Site", values = setNames(plot_data$site_color, plot_data$natural_name)) +
    scale_fill_manual(name = "Historical Range", 
                      values = setNames(band_lookup$color, band_lookup$label),
                      breaks = levels(band_lookup$label)) +
    facet_wrap(~natural_name, scales = scales_param, ncol = 2) +
    labs(x = "Date", y = param_label, color = "Site", 
         title = paste0(param, " Trends (", str_to_title(summary_level), " ", title_summary,
                        ") vs Historical (2019-2025) Data"), 
         subtitle = "Dashed lines show historical daily median values, with shaded bands showing historical percentile ranges") +
    ROSS_theme +
    theme(legend.position = "right")
}

```
# WQ Events

## WQ Event: Historical Data

```{r}
plots <- map(unique(sensor_data_clean$parameter), make_hist_plot)%>%
  setNames(unique(sensor_data_clean$parameter))


 DO <- make_hist_plot(param = "DO",summary_level = "daily", summary_fun = "percentiles_10_90", 
              sites = c( "salyer", "udall", "riverbend",
                        "elc", "archery", "riverbluffs"))

Temperature <- make_hist_plot(param = "Temperature",summary_level = "daily", summary_fun = "percentiles_10_90", 
              sites = c( "salyer", "udall", "riverbend",
                        "cottonwood", "archery", "riverbluffs"))

SpC <- make_hist_plot(param = "Specific Conductivity",summary_level = "daily", summary_fun = "median", 
              sites = c( "salyer", "udall", "riverbend",
                        "elc", "archery", "riverbluffs"))

ggsave(plot = DO, filename = here(fig_dir, "DO_hist_trends.png"), width = 16, height = 10)

ggsave(plot = Temperature, filename = here(fig_dir, "Temp_hist_trends.png"), width = 16, height = 10)

ggsave(plot = SpC, filename = here(fig_dir, "SC_hist_trends.png"), width = 16, height = 10)
```

### WQ Event: River Bluffs Beaver Dam Failure

```{r}


dam_plot <- sensor_data_clean%>%
  filter(site == "riverbluffs" & parameter %nin% c("FDOM Fluorescence","DO", "pH", "ORP","Chl-a Fluorescence")  &
           DT_round >= ymd("2026-04-08") & DT_round <= ymd("2026-04-20"))%>%
  mutate(mean = if_else(parameter == "Turbidity" & mean > 10 & !is.na(auto_flag), NA, mean))%>%
  ggplot(., aes(DT_round, mean))+
  geom_rect(aes(xmin = as.POSIXct("2026-04-15 02:00 MST"), xmax = as.POSIXct("2026-04-15 12:00 MST"), ymin = -Inf, ymax = Inf), fill = "red", alpha = 0.005)+
  geom_line()+
  facet_wrap(~label, scales = "free")+
  labs(title = "River Bluffs Sensor Data in 2026",
       subtitle = "Note the drop in depth and increase in turbidity around 04-15 due to beaver dam failure",
       x = "Date", y = "Sensor Value")+
  theme_clean(base_size = 20)

ggsave(plot = dam_plot, filename = here(fig_dir, "River_Bluffs_Beaver_Dam_Failure.png"), width = 16, height = 10)
```


## WQ Events: EXAMPLE

```{r april_drawdown, echo= F}


sites_march <- c( "udall", "cottonwood", "elc", "archery")


march_storm <-  plot_sensor(df = sensor_data_clean, sites = sites_march,  parameters = c("Flow", "Specific Conductivity","Turbidity" ), start_dt = "2025-03-28  00:00",
                            end_dt = "2025-04-02 24:00",timestep =  "30 minutes", b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


march_storm
ggsave(paste0(fig_dir,"/march_storm.png"), plot = march_storm, width = 16, height = 10, units = "in", dpi = 300)

```


## WQ Events: September Storm Event

```{r}
sites_sept <- c("bellvue", "udall", "cottonwood", "archery")

sept_storms <-  plot_sensor(df = sensor_data_clean, sites = sites_sept,  parameters = c("Flow", "Turbidity","DO", "FDOM Fluorescence" ), start_dt = "2026-09-15  00:00",
                              end_dt = "2026-09-21 23:00",timestep =  "1 hours",b_size = 20)+
labs(caption = "Preliminary Data, subject to revision")

sept_storms

sept_storms_precip <-   create_storm_precip_plot(precip_flow_df = larimer_flow_precip,
                                               station_id_oi = "11029", 
                                               start_date = "2026-09-10",
                                               end_date = "2026-09-21")


left_side <- wrap_elements(sept_storms)

# 2. Define the design 
# Here, 'A' is your 4-panel block, 'B' is your precip plot
layout <- "
AAAA BB
"

# 3. Combine them
final_plot <- sept_storms_precip + left_side + 
  plot_layout(design = layout)

final_plot
ggsave(paste0(fig_dir,"/sept_storms.png"), plot = sept_storms, width = 18, height = 12, units = "in", dpi = 500)

ggsave(paste0(fig_dir,"/sept_storms_precip.png"), plot = final_plot, width = 18, height = 12, units = "in", dpi = 500)

```

## WQ Events: Riverbluffs Chl-a

```{r april_drawdown, echo= F}


algal_conditions_sites <- c( "udall", "archery", "riverbluffs")


  algal_conditions_plot <- plot_sensor(df = sensor_data_clean, sites = algal_conditions_sites,  parameters = c("Flow", "pH","DO", "Chl-a Fluorescence" ), start_dt = "2026-07-01  00:00",
                            end_dt = "2026-09-21 23:00",timestep =  "24 hours", b_size = 20)+
  labs(caption = "Daily medians. Preliminary Data, subject to revision")


ggsave(paste0(fig_dir,"/algal_conditions.png"), plot = algal_conditions_plot, width = 16, height = 10, units = "in", dpi = 500)

```


#WQ Event - Storm Event

```{r}
date_range = as.Date(c("2026-06-20", "2026-06-30"))

storm_plot <- function(param){
  plot_data <- sensor_data_clean%>% 
    filter(parameter == param)%>%
    filter(site %in% c("udall", "riverbend", "cottonwood",
                   "elc", "archery"))%>%
    filter(between(as.Date(DT_round), date_range[1], date_range[2]))%>%
    mutate(DT_hourly = floor_date(DT_round, "hour"))%>%
    summarise(mean = mean(mean, na.rm = TRUE), .by = c("site", "DT_hourly", "parameter"))%>%
    left_join(labels, by = c( "parameter" = "param"))%>%
    left_join(site_names, by = "site")
  
  plot_data$natural_name <- factor(plot_data$natural_name, levels = site_order)
  
  param_label <-chem_expressions[[param]]
  
  if(param == "Specific Conductivity"){
    scales_param = "free_y"
  }else{
    scales_param = "free_x"
  }
  ggplot(plot_data, aes(x = DT_hourly, y = mean, color = natural_name))+
    geom_line(linewidth = 1.5, alpha = 1)+
    scale_color_manual(name = "Site", values = setNames(plot_data$site_color, plot_data$natural_name)) +
    facet_wrap(~natural_name, scales = scales_param, ncol = 2)+
    labs(x = "Date", y = param_label, color = "Site", 
         title = paste0(param, ": Storm Event (6/25/2026)"))+
    theme_clean(base_size = 16)+
    theme(legend.position = "right")
}

plots <- map(unique(sensor_data_clean$parameter), storm_plot)%>%
  setNames(unique(sensor_data_clean$parameter))
plots$`Specific Conductivity`
plots$DO
plots$Turbidity

ggsave(plot = plots$DO, filename = here(fig_dir, "DO_storm_event.png"), width = 16, height = 10)
ggsave(plot = plots$Turbidity, filename = here(fig_dir, "Turb_storm_event.png"), width = 16, height = 10)
ggsave(plot = plots$`Specific Conductivity`, filename = here(fig_dir, "SC_storm_event.png"), width = 16, height = 10)

#combined plot
date_range <- as.Date(c("2026-06-20", "2026-06-30"))

params_to_plot <- c("Specific Conductivity", "DO", "Turbidity")

combined_data <- sensor_data_clean %>%
  filter(parameter %in% params_to_plot) %>%
  filter(site %in% c("salyer", "riverbend", "elc", "archery")) %>%
  filter(between(as.Date(DT_round), date_range[1], date_range[2])) %>%
  mutate(DT_hourly = floor_date(DT_round, "hour")) %>%
  summarise(mean = mean(mean, na.rm = TRUE), 
            .by = c("site", "DT_hourly", "parameter")) %>%
  left_join(labels, by = c("parameter" = "param")) %>%
  left_join(site_names, by = "site")

combined_data$natural_name <- factor(combined_data$natural_name, levels = site_order)
combined_data$parameter <- factor(combined_data$parameter, levels = params_to_plot)

param_labeller <- as_labeller(function(x) sapply(x, function(p) chem_expressions[[p]]),
                               default = label_parsed)

combined_plot <- ggplot(combined_data, aes(x = DT_hourly, y = mean, color = natural_name)) +
  geom_line(linewidth = 1.2, alpha = 1) +
  scale_color_manual(name = "Site", 
                      values = setNames(combined_data$site_color, combined_data$natural_name)) +
  facet_grid(parameter ~ natural_name, scales = "free_y", 
             switch = "y",
             labeller = labeller(parameter = param_labeller)) +
  labs(x = "Date", y = NULL, color = "Site",
       title = "Storm Event (6/25/2026)") +
  theme_clean(base_size = 15) +
  theme(legend.position = "none",
        strip.text.y.left = element_text(face = "bold", size = 9, angle = 90),
        strip.text.x = element_text(face = "bold"),
        strip.placement = "outside",
        strip.background.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
        axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face = "bold"))

combined_plot

ggsave(plot = combined_plot, filename = here(fig_dir, "storm_event_combined.png"), width = 16, height = 10)

```


# WQ Monthly Summary

## Function for monthly boxplots

```{r}

generate_monthly_boxplot_summary <- function(sensor_data, year, month){
  
  # Parse the month string as part of a date and extract the month number
  month_number <- mdy(paste(month, "1, 2020")) %>% lubridate::month()
  month_name <- mdy(paste(month, "1, 2020")) %>% lubridate::month(label = TRUE)
  
  
  box_data <- sensor_data%>%
    filter(parameter != "Turbidity",
           parameter != "Depth", 
           parameter != "FDOM Fluorescence", 
           parameter != "Chl-a Fluorescence", 
           parameter != "ORP")%>%
    filter(site %in% c("bellvue", "salyer", "udall", "riverbend", "cottonwood", "elc", "archery", "riverbluffs"))%>%
    filter(lubridate::month(DT_round) == month_number & lubridate::year(DT_round) == year)
  
  
  # Merge with your data using left_join
  box_data_with_limits <- box_data #%>%
  box_data_with_limits$natural_name <- factor(box_data_with_limits$natural_name, levels = site_order )
  
  
  convert_season_to_months <- function(season_range) {
    # Define month order
    months <- c("january", "february", "march", "april", "may", "june",
                "july", "august", "september", "october", "november", "december")
    
    # Split the season range
    season_parts <- strsplit(season_range, "-")[[1]]
    start_month <- tolower(season_parts[1])
    end_month <- tolower(season_parts[2])
    
    # Find positions of start and end months
    start_pos <- which(months == start_month)
    end_pos <- which(months == end_month)
    
    # Handle cases where season crosses year boundary
    if (start_pos <= end_pos) {
      selected_months <- months[start_pos:end_pos]
    } else {
      selected_months <- c(months[start_pos:12], months[1:end_pos])
    }
    
    return(paste(selected_months, collapse = "|"))
  }
  
  #read in cdphe standards collected by Sam Struthers from https://cdphe.colorado.gov/water-quality-control-commission-regulations
  #Parameter (DO, pH, Temp) thresholds: Reg 31, Table I 
  # Site classifications: Reg 38, ~ Pg 410
  
  month_standard <- readxl::read_xlsx(path = here("data","raw", "spatial", "metadata", "site_cdphe_classification_2025.xlsx")) %>%
    # Convert season_1 to pipe-separated months
    mutate(season = sapply(season, convert_season_to_months))%>%
    # Split ph column into ph_low and ph_high
    separate(ph, into = c("ph_low", "ph_high"), sep = "-", convert = TRUE) %>%
    filter(grepl(x = season, pattern = month_name, ignore.case = TRUE), 
           site %in% unique(box_data_with_limits$natural_name))
  
  # Get unique parameters from the data
  parameters <- unique(box_data_with_limits$label)
  
  # Create individual plots for each parameter
  parameter_plots <- list()
  
  for (param in parameters) {
    # Filter data for current parameter
    param_data <- box_data_with_limits %>% 
      filter(label == param)
    
    standards <- param_data %>%
      select(natural_name) %>%
      distinct() %>%
      left_join(month_standard, by = c("natural_name" = "site"))%>%
      mutate(site_num =  as.numeric(factor(natural_name, levels = site_order))-1)
    
    # Create base plot for current parameter
    p <- param_data %>%
      ggplot(aes(x = natural_name, y = mean, fill = natural_name)) +
      geom_boxplot() +
      #geom_blank(aes(y = y_min)) +  # Forces inclusion of minimum
      #geom_blank(aes(y = y_max)) +  # Forces inclusion of maximum
      scale_fill_manual(values = bg_colors_full) +
      labs(x = "Site", y = param) +  # Use parameter name as y-axis label
      theme_bw(base_size = 14) +  # Slightly smaller base size for multiple plots
      theme(legend.position = "none",
            axis.text.x = element_text(angle = 45, hjust = 1),
            axis.title.x = element_text(face = "bold"),
            axis.title.y = element_text(face = "bold"),
            plot.title = element_text(size = 12))  # Smaller title for individual plots

        # Add reference lines based on parameter type
    if (grepl("pH", param, ignore.case = TRUE)) {
      # Add horizontal lines for pH standards
      p <- p + 
        geom_hline(yintercept = 6.5, color = "red", linetype = "dashed", alpha = 0.7) +
        geom_hline(yintercept = 9, color = "red", linetype = "dashed", alpha = 0.7)
    }
    
    if (grepl("Temperature|Temp", param, ignore.case = TRUE)) {
      # Add chronic temperature lines (orange, dashed)
      if ("temp_chronic" %in% names(standards)) {
        chronic_data <- standards %>% 
          filter(!is.na(temp_chronic))
        
        if (nrow(chronic_data) > 0) {
          p <- p + 
            geom_segment(data = chronic_data,
                         aes(x = site_num - 0.5, xend = site_num + 0.5, 
                             y = temp_chronic, yend = temp_chronic),
                         color = "orange", linetype = "dashed", linewidth = 1, alpha = 0.8,
                         inherit.aes = FALSE)
        }
      }
      
      # Add acute temperature lines (red, solid)
      if ("temp_acute" %in% names(standards)) {
        acute_data <- standards %>% 
          filter(!is.na(temp_acute))
        
        if (nrow(acute_data) > 0) {
          p <- p + 
            geom_segment(data = acute_data,
                         aes(x = site_num - 0.5, xend = site_num + 0.5, 
                             y = temp_acute, yend = temp_acute),
                         color = "red", linetype = "solid", linewidth = 1, alpha = 0.8,
                         inherit.aes = FALSE)
        }
      }
    }
    if (grepl("DO", param, ignore.case = TRUE)) {
      
      # Add chronic temperature lines (orange, dashed)
      if ("do_chronic" %in% names(standards)) {
        do_chronic_data <- standards %>% 
          filter(!is.na(temp_chronic))
        
        if (nrow(do_chronic_data) > 0) {
          p <- p + 
            geom_segment(data = do_chronic_data,
                         aes(x = site_num - 0.4, xend = site_num + 0.4, 
                             y = do_chronic, yend = do_chronic),
                         color = "red", linetype = "solid", linewidth = 1, alpha = 0.8,
                         inherit.aes = FALSE)
        }
      }
    }
    
    parameter_plots[[param]] <- p +
      annotate("text", 
               x = -Inf, 
               y = Inf, 
               label = "PRELIMINARY RESULTS", 
               hjust = -0.1, 
               vjust = 2, 
               size = 4, 
               fontface = "bold",
               color = "red")
  }
  
  
  parameter_plots[[1]] <- parameter_plots[[1]]+
    theme(axis.title.x = element_blank())
  parameter_plots[[2]] <- parameter_plots[[2]]+
    theme(axis.title.x = element_blank())
  
  # Combine plots using patchwork
  combined_plot <- wrap_plots(parameter_plots, ncol = 2) +  # Adjust ncol as needed
    plot_annotation(
      title = paste0("Poudre Water Quality Network Data Summary: ", str_to_title(month_name),  " ", year),
      caption = "Preliminary Data, subject to revision.\n Red solid lines indicate state of Colorado chronic thresholds and orange dashed lines indicate acute thresholds for aquatic life.",
      theme = theme(plot.title = element_text(size = 16, hjust = 0.5, face = "bold"), 
                    plot.caption = element_text(size = 13))
    )
  
  # Display the combined plot
  return(combined_plot)
  
}

```

## Generate for each month

```{r}

monthly_plots <- map2(1:11,2026, ~{
  result<- tryCatch({
    generate_monthly_boxplot_summary(sensor_data = sensor_data_clean, month = .x, year = .y)
  }, error = function(e) {
    message(paste("Skipping month", .x, "- Error:", e$message))
    return(NULL)
  })
  # Add month-year as attribute to preserve original indices
  if (!is.null(result)) {
    attr(result, "year_month") <- paste0(.y, "_", .x)
  }
  return(result)
})%>%
  keep(~ !is.null(.x))%>%
  set_names(map_chr(., ~ attr(.x, "year_month")))

monthly_plots

#write_rds(monthly_plots, file = paste0(fig_dir, "monthly_boxplot_summaries.rds"))

walk(monthly_plots, ~ ggsave(.x, filename = paste0(fig_dir, "monthly_boxplot_summary_", attr(.x, "year_month"), ".png"), width = 16, height = 10, units = "in", dpi = 300))


```

# Long Term Comparisons

Typically for each years report, we want to compare the current water year to historical min/max and median values. This is a good way to visualize how the current year compares to previous years.

# Current WY flow analysis vs historic min/max

```{r}
library(cdssr)
library(jsonlite)

#using CDWR lincoln, boxelder, and fossil creek gauges

gauges <- c("CLAFORCO", "CLABOXCO", "CLARIVCO")

gauge_labels <- c(
  CLAFORCO = "Lincoln",
  CLABOXCO = "Boxelder",
  CLARIVCO = "Poudre River Below Fossil Creek")

wy_start   <- as.Date("2025-10-01")
today_date <- Sys.Date()

#historic data
hist_raw <- map_df(gauges, ~get_telemetry_ts(abbrev = .x, 
                                             parameter = "DISCHRG", 
                                             start_date = ("2000-01-01"), 
                                             end_date = format(today_date, "%Y-%m-%d"),
                                             timescale = "day"))
hist_raw <- hist_raw %>%
  mutate(
    abbrev = factor(abbrev, levels = gauges),
    water_year = if_else(month(meas_date) >= 10, year(meas_date) + 1, year(meas_date)),
    plot_year  = if_else(month(meas_date) >= 10, 2025, 2026),
    plot_date  = as.Date(paste0(plot_year, "-", month(meas_date), "-", day(meas_date)),
                          format = "%Y-%m-%d")
  ) %>%
  filter(!is.na(plot_date))

hist_stats <- hist_raw %>%
  filter(water_year != 2026) %>%
  summarise(
    median = median(.data$meas_value, na.rm = TRUE),
    min    = min(.data$meas_value, na.rm = TRUE),
    max    = max(.data$meas_value, na.rm = TRUE),
    .by = c("abbrev", "plot_date")
  )

#current wy data
current_wy <- hist_raw %>%
  filter(water_year == 2026) %>%
  select(abbrev, meas_date, plot_date, meas_value)

today_plot_date <- current_wy %>% pull(plot_date) %>% max(na.rm = TRUE)

WY_flow_plot <- ggplot(hist_stats, aes(x = plot_date, y = median, color = abbrev)) +
  geom_line(alpha = 0.7, linetype = "dashed") +
  geom_ribbon(aes(ymin = min, ymax = max), color = "grey", alpha = 0.2) +
  geom_line(data = current_wy, aes(x = plot_date, y = meas_value, color = abbrev),
            linewidth = 1.5, alpha = 1) +
  scale_x_date(limits = c(wy_start, today_plot_date), date_labels = "%b") +
  scale_y_log10()+
  facet_wrap(~abbrev, scales = "free_y", ncol = 1,
             labeller = labeller(abbrev = gauge_labels)) +
  labs(
    x = "Date", y = "Discharge (cfs)", color = "Gauge",
    title = "2026 WY Flow vs Historical Min/Max",
    subtitle = "Dashed line = historical daily median; grey ribbon = historical daily min/max range"
  ) +
  theme_clean(base_size = 15) +
  theme(legend.position = "none",
        strip.text = element_text(face = "bold", size = 10),
        axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face = "bold"))

WY_flow_plot

ggsave(plot = WY_flow_plot, filename = here(fig_dir, "WY_flow_plot.png"), width = 16, height = 10)

```


# Site Summaries

Read in the field notes so we can write paragraphs about the site's condition throughout the year

```{r}

field_notes <- grab_mWater_sensor_notes(load_mWater())%>%
  filter(site %in% site_names$site & year(DT_round) == "2025")

map(site_names$site, ~{
  field_notes%>%
    filter(site == .x)%>% 
    arrange(DT_round)%>%
    select(DT_round,crew,  visit_type, cals_performed, sensor_malfunction, visit_comments)%>%
    kableExtra::kable() %>%
    kableExtra::kable_styling(full_width = F, position = "left", font_size = 12)
})

```

