---
title: "PSN Data Manager Tools"
author: "Sam Struthers"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(openxlsx)
library(readxl)
```


# Loading field notes and sensor tracking file path

Update file path as needed

```{r}
#current file path for tracking sonde SNs, etc
sonde_tracking_file_path <- here("data", "raw", "management", "equipment_tracking", "2025_sensor_tracking.xlsx")

#source clean mwater script for all notes cleaned
source("src/load_mWater_notes.R")
all_notes_cleaned <- load_mWater_notes()
```

# Update Station Info

Updating the tracking sheet to most up to date sonde/vulinks and SNs in `station_info` tab. 
Pulls in field notes and using sonde deployment records, updates station info tab

```{r}
#update the current_sonde tab so that file missing is correct
source("src/update_station_info.R")
update_station_info(field_notes = all_notes_cleaned,
                    sonde_tracking_file_path)
```

# Files Missing

This function looks at the user inputs for calibration report collect and logs collected. Based on these inputs, it looks at all the uploaded logs or calibration reports and will print out what logs are missing and who to contact to get those files uploaded.

```{r}
source("src/files_missing.R")
files_missing(field_notes = all_notes_cleaned,
              sonde_tracking_file_path)

```

## Current Sensor Locations

Goal: 
- Track sensor locations & SNs using most recent calibration reports
- update the sensor tracking sheet with site and sonde SN


```{r}
source("src/update_sensor_current_locations.R")
update_sensor_current_locations(field_notes = all_notes_cleaned,
                                sonde_tracking_file_path)

```


## Water Sampling Data:

Goal:

-   Save data in the correct format for RMRS spreadsheet

-   Save all water sampling probe values in a spreadsheet

```{r}
#source function
source("src/sampling_spreadsheet_creator.R")
# # To get the RMRS style data for a specfic date of sampling, 
# # Input the date of interest in sampling_spreadsheet_creator
# 
# sampling_spreadsheet_creator(date_oi = "2025-07-01")

#sampling_spreadsheet_creator(date_oi = "2023-11-17")


# To get all the water sampling data and save to CSV in sampling notes
# This also returns the df sampling_notes in case you want to review in R
sampling_spreadsheet_creator(all_dates = TRUE)
```

## Photos

Goal:

-   Download all user created photos ( upstream, downstream, clarity, filter and other pictures)

-   Label according to site, date, description in the format site_YYYYMMDD_descriptor.jpg

-   Only download photos which have not yet been downloaded

```{r}
source("src/download_pictures.R")
  
#RUN TO DOWNLOAD NEW PICTURES
# It takes about 2-5 minutes to download ~25-50 photos
# Sometimes the request to mWater time out, just re run the function below if that happens

download_pictures(field_notes = all_notes_cleaned, download_path = here("data", "raw", "field_notes", "field_pics"))
```



# Remove extra objects
```{r}
rm(all_notes, sampling_sites, upper_sites, all_notes_cleaned)
```

