---
title: "Create PWQN Timelapse"
author: "Sam Struthers- CSU ROSSyndicate"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
`%nin%` = Negate(`%in%`)
library(tidyverse)
library(animation)
library(gganimate)
library(dygraphs)
library(lubridate)
library(xts)
library(exifr)
library(imputeTS)
library(png)
library(grid)
library(ggthemes)
library(patchwork)
library(jpeg)
library(ggdark)
library(animation)
library(magick)


source("scratch/reporting/grab_raw_data.R")
source("src/timelapse/get_tl_photo_filenames.R")
source("src/timelapse/basic_plot.R")
source("src/timelapse/photo_plotter.R")

```

# Enter dates, site and parameters for timelapse

sites: "tamasag", "legacy", "timberline", "prospect", "boxelder", "archery", "river bluffs"

```{r}

start_dt <- "2023-4-30 08:00"
end_dt  = "2023-5-21 12:00"
site = "boxelder"
#first param should be depth usually
parameters = c( "Depth", "Specific Conductivity")

param_unit  = c("ft", "us/cm" )


#Pull in timelapse images
tl_filenames <- get_tl_photo_filenames(site, start_dt,end_dt)

#check to see if there are any photos for this site and time period
if(nrow(tl_filenames) == 0 ){
  print("No photos for this site and time period. Please choose a different site")
}else{
  #pull in WQ data if there are photos
  wq_data <- grab_raw_data(sites = site, parameters = parameters, start_dt = start_dt, end_dt = end_dt)%>%
  mutate(DT_round = with_tz(DT_round, "MST"))%>%
  pivot_wider(names_from = parameter, values_from = value, id_cols = "DT_round")

  if(nrow(wq_data) == 0){
  print("No data for this site and time period. Please choose different parameters")
    }
  if(nrow(wq_data) > 0){
   wq_tl <- left_join(tl_filenames, wq_data, by = "DT_round")%>%
     na.omit()

cat("There are", nrow(wq_tl), "photos with wq observations over the selected period.")
}}

```

# Timelapse Prep

## View Water Quality Data

This grabs wq data from wq_tl object and makes a simple plot of the selected parameters. Run the chunk below to see the data

```{r}
basic_plot()
```

If the data is satisfactory, continue. Otherwise, choose different dates/ sites above. 

## Give name of event (make it unique!)

```{r}
tl_name <- "boxelder_may2023"
```


## Create frames

This will create each individual frame which includes a photo, and a plot of two parameters. Depth should be the first parameter and a WQ variable can be the second. Change the folder path below to where you'd like to save the photos (make sure it is empty!)
Run the chunk below to create all the images (~ takes 5 minutes per day at a 30 min interval)

```{r}
# individual frames will be saved to photo plotter output under the name given above
folder_path <- paste0("data/timelapse_photos/photo_plotter_output/", tl_name, "/")

map(1:nrow(wq_tl), ~photo_plotter(.x, output_folder = folder_path))
```

# Create Timelapse


Run chunk below if you have verified:
- Verified the WQ data is appropriate
- You have saved all the individual plots to a folder
- Created a unique name for the timelapse 

```{r}
tl_name <- paste0("data/timelapse_photos/finished_tl/", tl_name, ".mp4")

tl_photos <- (list.files(folder_path, full.names = TRUE))

#This extracts the underlying height, width, and type of image.
img.height <- magick::image_info(magick::image_read(tl_photos[1]))$height
img.width <- magick::image_info(magick::image_read(tl_photos[1]))$width
img.type <- magick::image_info(magick::image_read(tl_photos[1]))$format

#This tells FFmpeg that each picture should be displayed for 0.25 seconds,
# the height of the image, the width of the image, and the appropriate
# image engine to use.
#Note: tolower() converts uppercase letters to lowercase letters.
animation::ani.options(interval = 0.075,
                       ani.height = img.height,
                       ani.width = img.width,
                       ani.dev = tolower(img.type),
                       ani.type = tolower(img.type))

#By default the input dimensions of the image (designated here by img.height
# and img.width) dictate the output resolution. Below, I'm increasing the
# video dimensions to improve the image quality.
opts <- paste("-s ", img.height * 2, "x", img.width * 2, sep = "")

animation::saveVideo(

  for(i in 1:length(tl_photos)){
    tl_image <- magick::image_read(tl_photos[i])
    plot(tl_image)
  },
  #Designate the name of the image within the working directory.
  video.name = tl_name)

```


