```{r}
library(tidyverse)
library(readxl)
library(here)

# Load functions
walk(list.files('src/', pattern = "*.R", full.names = TRUE, recursive = TRUE), source)
```


Once all of the data has been verified it will need to get fixed with the errors
that we found while manually verifying the data. 

# Clean up the issues to resolve data set
```{r}
# Read in the issues to resolved data
issues_df <- read_xlsx(here('data','virridy_verification','verification_assignments_notes.xlsx'), sheet = "issues to resolve")

# site list 
site_list <- c('tamasag', 'legacy', 'lincoln', 'timberline', 'prospect', 'boxelder', 'archery', 'river bluffs')

site_list <- paste(site_list, collapse = "|")
```

```{r}
# Fix the date time columns
issues_df$date_found <- update(issues_df$date_found, year = 2024)

# make sure that the verifier column is all capitalized
filtered_issues_df <- issues_df %>% 
  mutate(verifier = str_to_upper(verifier),
         site = str_to_lower(site)) %>% 
  filter(grepl(site_list, site, ignore.case = T),
         !grepl("virridy", site, ignore.case = T),
         year(start_dt) == 2023,
         year(end_dt) == 2023) %>% 
  group_by(site, param) %>%
  arrange(start_dt, .by_group = T)

# we can filter out more data because not all of them have issues that need to be fixed
site_params_with_issues <- unique(filtered_issues_df[, c('site', 'param')]) %>% 
  mutate(site_params = paste(site, param, sep = "-")) %>% 
  pull(site_params)
```

# Pull in all of the verified data
```{r}
verified_file_names <- tibble(names = list.files(path = here('data', 'virridy_verification', 'verified_directory'))) %>% 
  filter(grepl(site_list, names, ignore.case = T),
         !grepl("virridy", names, ignore.case = T)) %>% 
  arrange() %>%
  pull(names)

verified_data <- map(.x = verified_file_names,~{
  read_rds(here('data', 'virridy_verification', 'verified_directory', .x))
}) 

names(verified_data) <- verified_file_names

# filter the verified files for data that has issues that need to be resolved
verified_data <- verified_data[names(verified_data) %in% site_params_with_issues]
```

# Remove any of the data that is already resolved
```{r}
post_verified_file_names <- tibble(names = list.files(path = here('data', 'virridy_verification', 'post_verified_directory'))) %>% 
  arrange() %>% 
  pull(names)

# This is data that needs to be resolved still
verified_data <- verified_data[!names(verified_data) %in% post_verified_file_names]
```

```{r}
# quick look up function to explore the data easily
lookup <- function(site_param) {
  df <- verified_data[[site_param]] %>% 
    select(DT_join, site, parameter, raw_flag, flag, mean, mean_verified, is_verified, verification_status, day, week, month, year)
  View(df)
}
```

Now we only have 16 data frames that we need to fix. 
Lets make a huge function that goes through each issue individually.
Still need to go through and solve the depth calibration issues. Those have not 
been fixed in this script

```{r}
# use this function in imap
post_manual_verification_clean_up <- function(idx, df) {
  
  site_param <- idx
  
  # Archery ----
  # BETA AT800 sonde deployed resulting in very different chla values from original sonde, add flag (deployment error or...?) but do not remove?
  if (site_param == "archery-Chl-a Fluorescence") {
    post_verified_df <- df %>% 
      add_flag(between(DT_round, date("2023-04-20 00:00:00"), date("2023-05-23 23:59:59")),
               "deployment error")
  }
  
  if (site_param == "archery-DO") {
    fail_dts <- paste(c("2023-09-15 11:15:00", "2023-04-23 12:15:00", "2023-04-23 12:30:00"), collapse = "|")
    post_verified_df <- df %>% 
      mutate(mean_verified = if_else(grepl(fail_dts, DT_join, ignore.case = T), NA, mean_verified),
             verification_status = if_else(grepl(fail_dts, DT_join, ignore.case = T), "FAIL", verification_status))
  }
  
  if (site_param == "archery-Depth") {
    # flag is Sonde not deployed, but the data looks fine
    post_verified_df <- df %>% 
      mutate(mean_verified = if_else(between(DT_round, date("2023-05-16 14:15:00"), date("2023-05-21 00:00:00")), 
                                     mean, 
                                     mean_verified),
             verification_status = if_else(between(DT_round, date("2023-05-16 14:15:00"), date("2023-05-21 00:00:00")), 
                                           "FAIL", 
                                           verification_status))
  }
  
  if (site_param == "archery-Specific Conductivity") {
    # Sensor malfunction can be removed for this period of time since data looks good
    post_verified_df <- df %>% 
      mutate(mean_verified = if_else(between(DT_round, date("2023-09-15 10:29:00"), date("2023-10-16 00:29:00")), 
                                     NA, 
                                     mean_verified),
             verification_status = if_else(between(DT_round, date("2023-09-15 10:29:00"), date("2023-10-16 00:29:00")), 
                                           "FAIL", 
                                           verification_status))
  }
  
  # Boxelder ----
  if (site_param == "boxelder-Specific Conductivity") { 
    # There seems to be a sensor malfunction, but the data seems to be tracking the up/downstream data.
    post_verified_df <- df %>%
      mutate(mean_verified = if_else(between(DT_round, date("2023-07-31 17:59:00"), date("2023-08-04 10:59:00")), 
                                     mean, 
                                     mean_verified),
             verification_status = if_else(between(DT_round, date("2023-07-31 17:59:00"), date("2023-08-04 10:59:00")), 
                                           "FAIL", 
                                           verification_status))
  }
  
  if (site_param == "boxelder-pH") {
    post_verified_df <- df %>% 
      # Sensor malfunction flag can be removed for this period of time since data looks good and in line with up/downstream sites
      mutate(mean_verified = if_else(between(DT_round, date("2023-07-31 17:59:00"), date("2023-08-04 10:59:00")), 
                                     mean, 
                                     mean_verified),
             verification_status = if_else(between(DT_round, date("2023-07-31 17:59:00"), date("2023-08-04 10:59:00")), 
                                           "FAIL", 
                                           verification_status)) %>% 
      # Sonde burial that is not being tracked in the field notes
      add_flag(between(DT_round, date("2023-05-26 12:29:00"), date("2023-05-30 18:14:00")), "sonde burial") %>% 
      # Failed data when it should have been passed
      mutate(mean_verified = if_else(between(DT_round, date("2023-05-30 18:29:00"), date("2023-06-04 23:59:00")) & is.na(flag), 
                                     mean, 
                                     mean_verified),
             verification_status = if_else(between(DT_round, date("2023-05-30 18:29:00"), date("2023-06-04 23:59:00")) & is.na(flag), 
                                           "PASS", 
                                           verification_status))
  }
  
  if (site_param == "boxelder-Turbidity") {
    post_verified_df <- df %>% 
      # Sensor malfunction, but the data seems to be tracking what was happening at prospect pretty well.
      mutate(mean_verified = ifelse(between(DT_round, date("2023-08-01 09:29:00"), date("2023-08-03 13:59:00")),
                                    mean,
                                    mean_verified),
             verification_status = if_else(between(DT_round, date("2023-08-01 09:29:00"), date("2023-08-03 13:59:00")) & is.na(flag),
                                           "PASS",
                                           verification_status))
  }
  
  # Lincoln ----
  if (site_param == "lincoln-Chl-a Fluorescence") {
    post_verified_df <- df %>% 
      # Failed flagged points, should be Pass failed points
      mutate(mean_verified = if_else(between(DT_round, date("2023-09-25 00:00:00"), date("2023-10-01 00:00:00")) & !is.na(flag),
                                    NA,
                                    mean_verified),
             verification_status = if_else(between(DT_round, date("2023-09-25 00:00:00"), date("2023-10-01 00:00:00")),
                                           "PASS",
                                           verification_status))
  }
  
  # River Bluffs ----
  # depth is a calibration that will not get resolved in this script
  # need to make a depth calibration function
  
  if (site_param == 'river bluffs-Chl-a Fluorescence') {
    post_verified_df <- df %>% 
      # Value should be flagged, this point was passed
      mutate(mean_verified = if_else(DT_join == "2023-04-09 17:45:00",
                                     NA,
                                     mean_verified),
             verification_status = if_else(DT_join == "2023-04-09 17:45:00",
                                           "FAIL",
                                           verification_status)) %>% 
      # Chla drift (until sonde burial)
      mutate(mean_verifed = if_else(between(DT_round, date("2023-04-21 23:59:00"), date("2023-05-04 10:46:00")) & is.na(flag),
                                    NA,
                                    mean_verified),
             verification_status = if_else(between(DT_round, date("2023-04-21 23:59:00"), date("2023-05-04 10:46:00")) & is.na(flag),
                                           "FAIL",
                                           verification_status)) %>% 
      add_flag(between(DT_round, date("2023-04-21 23:59:00"), date("2023-05-04 10:46:00")), "drift")
  }
  
  if (site_param == 'river bluffs-Temperature') {
    post_verified_df <- df %>% 
      # Indicates sonde burial, but data looks good
      mutate(mean_verifed = if_else(between(DT_round, date("2023-04-11 23:44:00"), date("2023-04-16 13:31:00")),
                                    mean,
                                    mean_verified),
             verification_status = if_else(between(DT_round, date("2023-04-11 23:44:00"), date("2023-04-16 13:31:00")) & !is.na(flag),
                                           "FAIL",
                                           verification_status))
  }
  
  if (site_param == 'river bluffs-Specific Conductivity') {
    post_verified_df <- df %>% 
      # Sonde burial for like 2 months but the data looks mostly fine
      mutate(mean_verified = if_else(between(DT_round, date("2023-05-04 16:14:00"), date("2023-07-05 20:59:00")),
                                     mean,
                                     mean_verified),
             verification_status = if_else(between(DT_round, date("2023-05-04 16:14:00"), date("2023-07-05 20:59:00")),
                                           "FAIL",
                                           verification_status))
  }
  
  if (site_param == "river bluffs-ORP") {
    post_verified_df <- df %>% 
      # Field note flag. Sensor was visited one day and returned the next and it seems like it was kept running over night.
      add_flag(between(DT_round, date("2023-07-17 13:59:00"), date("2023-07-18 09:46:00")), "sonde not employed") %>% 
      # Sonde burial flag on other parameters during this time but not on ORP
      add_flag(between(DT_round, date("2023-05-04 16:14:00"), date("2023-07-05 20:59:00")), "sonde burial")
  }
  
  if (site_param == "river bluffs-DO") {
    # "Passed failed points, should be ff/sonde burial, definitely a handful of points that reflect that but otherwise looks fine" note dates
    # have to test if this actually needs the timezone information
    timezone = "America/Denver"
    periods <- interval(
      start = c(
        ymd_hms("2023-05-08 17:29:00", tz = timezone),
        ymd_hms("2023-05-10 17:44:00", tz = timezone),
        ymd_hms("2023-05-22 16:59:00", tz = timezone),
        ymd_hms("2023-06-01 09:29:00", tz = timezone),
        ymd_hms("2023-06-06 12:14:00", tz = timezone),
        ymd_hms("2023-06-06 20:44:00", tz = timezone),
        ymd_hms("2023-06-08 14:29:00", tz = timezone),
        ymd_hms("2023-06-16 04:44:00", tz = timezone),
        ymd_hms("2023-06-21 09:29:00", tz = timezone),
        ymd_hms("2023-06-29 11:14:00", tz = timezone)),
      end = c(
        ymd_hms("2023-05-09 19:31:00", tz = timezone),
        ymd_hms("2023-05-12 16:01:00", tz = timezone),
        ymd_hms("2023-05-30 00:01:00", tz = timezone),
        ymd_hms("2023-06-02 13:46:00", tz = timezone),
        ymd_hms("2023-06-06 19:31:00", tz = timezone),
        ymd_hms("2023-06-07 15:31:00", tz = timezone),
        ymd_hms("2023-06-09 11:01:00", tz = timezone),
        ymd_hms("2023-06-17 02:31:00", tz = timezone),
        ymd_hms("2023-06-22 09:46:00", tz = timezone),
        ymd_hms("2023-07-01 23:46:00", tz = timezone)))
    
    post_verified_df <- df %>% 
      # Passed failed points, should be ff
      mutate(mean_verified = if_else(DT_round %within% periods,
                                     mean,
                                     mean_verified),
             verification_status = if_else(DT_round %within% periods,
                                           "FAIL",
                                           verification_status))
    
  }
  
  # Tamasag
  # depth calibration will not get resolved in this script
  
  # Make sure site visits always gets flagged (in case these flags were removed accidentally) ----
  always_fail_text <- paste(c("sv window", "site visit"), collapse = "|")

  post_verified_df <- post_verified_df %>% 
    mutate(mean_verified = if_else(grepl(always_fail_text, flag, ignore.case = T), NA, mean_verified),
           is_verified = if_else(grepl(always_fail_text, flag, ignore.case = T), TRUE, mean_verified),
           verification_status = if_else(grepl(always_fail_text, flag, ignore.case = T), "PASS", verification_status))
  
  return(post_verified_df)
  
}
```

```{r}
# filter the verified for those sites that I have finished and need massaging
# Some sites issues were resolved outside of this script

# finished site list 
finished_site_list <- paste(c("archery-Chl-a Fluorescence", "archery-DO", "archery-Depth",
                              "archery-Specific Conductivity", "boxelder-Specific Conductivity",
                              "boxelder-pH", "boxelder-Turbidity", "lincoln-Chl-a Fluorescence"), collapse = "|")

# filter the verified files for data that has issues that need to be resolved
finished_verified_data <- verified_data[grepl(finished_site_list, names(verified_data))]

post_verified_data <- imap(finished_verified_data, ~ post_manual_verification_clean_up(idx = .y, df = .x))
```

```{r}
# Upload all of the files that we needed to manually post verify
iwalk(post_verified_data, ~{
  write_rds(.x, here("data", "virridy_verification", "post_verified_directory", .y))
})
```

```{r}
# Upload all of the files that did not need to be manually post verified
verified_file_names <- tibble(names = list.files(path = here('data', 'virridy_verification', 'verified_directory'))) %>%
  filter(grepl(site_list, names, ignore.case = T),
         !grepl("virridy", names, ignore.case = T)) %>%
  arrange() %>%
  pull(names)

verified_data <- map(.x = verified_file_names,~{
  read_rds(here('data', 'virridy_verification', 'verified_directory', .x))
})

names(verified_data) <- verified_file_names

# filter the verified files for data that have no
no_issue_verified_data <- verified_data[!names(verified_data) %in% site_params_with_issues]

iwalk(no_issue_verified_data, ~{
  write_rds(.x, here("data", "virridy_verification", "post_verified_directory", .y))
})
```

```{r}
# data that still needs to get added
final_data <- paste(c("boxelder-ORP", "legacy-pH", "prospect-pH"), collapse = "|")


verified_file_names <- tibble(names = list.files(path = here('data', 'virridy_verification', 'verified_directory'))) %>%
  filter(grepl(site_list, names, ignore.case = T),
         !grepl("virridy", names, ignore.case = T)) %>%
  arrange() %>%
  pull(names)

verified_data <- map(.x = verified_file_names,~{
  read_rds(here('data', 'virridy_verification', 'verified_directory', .x))
})

names(verified_data) <- verified_file_names

# filter the verified files for data that has issues that need to be resolved
last_verified_data <- verified_data[grepl(final_data, names(verified_data))]

iwalk(last_verified_data, ~{
  write_rds(.x, here("data", "virridy_verification", "post_verified_directory", .y))
})
```

# data that still needs to get added but is not done
"legacy-Turbidity"
"prospect-Turbidity"
