```{r}
# Load necessary libraries
library(tidyverse)
library(ggpubr)
library(here)

# set function directory paths
fxn_path <- here("src")

# Source functions
invisible(map(
  list.files(fxn_path, pattern = "*.R", full.names = TRUE),
  ~ source(.x, echo = FALSE)
))

# load all the flagged data, pre verification
flagged_data <- read_rds(here("data","virridy_verification","all_data_flagged_complete.RDS"))
```

```{r}
# Make list of parameter specifications for joining
unique_parameters <- names(flagged_data) %>% 
  str_extract(pattern = "(?<=-).*") %>% 
  unique(.)

parameter_specifications <- tibble(
  parameter = unique_parameters,
  accuracy = c(
    NA,
    NA,
    0.1,
    NA,
    5,
    0.1,
    0.5, # these are percentages
    0.1,
    2 # Percentage
  ),
  precision = c(
    NA,
    NA,
    0.01,
    NA,
    0.1,
    0.01,
    0.1,
    0.01,
    0.01
  )
)
```

## Note on percent change vs percent difference:

Percent change: 100*(new_value - old_value)/old_value
Used when tracking changes over time
Shows the direction of change
Uses the old value as a reference
Asymmetric

Percent difference: 100*(abs(new_value - old_value)/mean(new_value,old_value))
Used when you want to compare the relative difference between two independent values
Does not show the direction of change
uses the mean of both values as a reference
Symmetric

```{r}
flagged_data_altered <- map(flagged_data, function(df) {
  
  altered_df <- df %>% 
    # select for the most relevant columns
    select(DT_join, DT_round, site, parameter, mean, flag) %>% 
    # raw values before and after a site visit (dif between values 2 hours apart).
    mutate(before = lag(mean, 2),
           after = lead(mean, 5),
           # calculate difference
           difference = after - before,
           # calculate percent change
           percent_change = if_else(
             after != 0 & before != 0, # prevent divide by 0 errors
             ((after - before)/abs(before))*100,
             NA_integer_),
           # calculate percent difference
           percent_difference = if_else(
             after != 0 & before != 0, # prevent divide by 0 errors
             (abs(after - before)/abs((after+before)/2))*100,
             NA_integer_)) %>%
    left_join(., parameter_specifications, by = "parameter")
  
  return(altered_df)
})
```


Parse out times NOT in the field. (WE WOULD ALSO IDEALLY REMOVE ALL THE BAD DATA AHEAD OF TIME, TOO!)
```{r}
non_sf_data <-  map(flagged_data_altered, function(df) {
  altered_df <- df %>% 
    filter(!grepl("site visit|sv window", flag))
}) %>%
  bind_rows() %>%
  group_by(site, parameter) %>%
  summarize(mean_dif = mean(percent_difference, na.rm = TRUE),
            mean_change = mean(percent_change, na.rm = TRUE))
```

Parse out site visits and site visit windows
```{r}
sv_data <- map(flagged_data_altered, function(df) {
  altered_df <- df %>% 
    filter(grepl("site visit", flag))
}) %>%
  bind_rows() %>%
  filter(!is.na(percent_difference)) %>%
  left_join(non_sf_data, by = c("site", "parameter")) %>%
  # ID "acceptable" jumps between site visits. That is, a jump less than
  # the average jumps calculated with non-site visit data
  mutate(acceptable_dif = ifelse(percent_difference > mean_dif, "BAD", "GOOD"),
         acceptable_change = ifelse(percent_change > mean_change, "BAD", "GOOD"))

# How often do bad jumps occur?
bad_change <- filter(sv_data, 
                     acceptable_change == "BAD") %>%
  group_by(site, parameter) %>%
  summarize(instances = n())

```

Can we do anything with our calibration data? (STILL DEEP WIP, but goal is to pull in all calibration report data into a single table.
```{r}
cal_tabler <- function(cal_files){

    #cal_files <- list.files("data/calibration_reports") # for testing

    cal <- read_html(paste0(getwd(), "/data/calibration_reports/", cal_files)) %>%
      html_nodes("div") %>%
      html_text() %>%
      as_tibble()

    rdo <- cal %>% filter(grepl("RDO", value)) %>% pull() %>% str_replace_all(., " ", "") %>% tolower()

    ph_orp <- cal %>% filter(grepl("pH/ORP", value)) %>% pull() %>% str_replace_all(., " ", "") %>% tolower()

    conductivity <- cal %>% filter(grepl("Conductivity",value)) %>% pull() %>% str_replace_all(., " ", "") %>% tolower()

    if(length(cal %>% filter(grepl("Turbidity",value)) %>% pull() %>% str_replace_all(., " ", "") %>% tolower()) != 0){

      turbidity <- cal %>% filter(grepl("Turbidity",value)) %>% pull() %>% str_replace_all(., " ", "") %>% tolower()

    } else {

      turbidity <- "No Turbidity Sensor"

    }

    # Always the last sensor when depth is available:
    depth <- ifelse(str_detect(cal %>% .[nrow(.),] %>% pull() %>% str_replace_all(., " ", "") %>% tolower(), "pressure"),#"psireferencedepth"),
                    cal %>% .[nrow(.),] %>% pull() %>% str_replace_all(., " ", "") %>% tolower(),
                    "No Depth Sensor")

    time_mst <- paste0(str_sub(str_match(cal_files, "(\\d+)_mst")[, 2:1][1], 1, 2), ":",
                       str_sub(str_match(cal_files, "(\\d+)_mst")[, 2:1][1], 3, 4))
    #str_sub(cal_files, -13, -12),":", str_sub(cal_files, -11, -10))

    date <- str_match(cal_files, "^[^_]+_([0-9]{8})_")[, 2]

    #str_sub(cal_files, -22, -19),"-", str_sub(cal_files, -18, -17),"-", str_sub(cal_files, -16, -15))

    cal_table <- tibble(site = sub("\\_.*", "", cal_files) %>% tolower(),

                        DT = ymd_hm(paste(date, time_mst, tz = "MST")),

                        # Dissolved Oxygen
                        rdo_cal_date = as.character(mdy(str_match(rdo, "lastcalibrated\\s*(.*?)\\s*calibrationdetails")[,2])),
                        rdo_slope = str_match(rdo, "slope\\s*(.*?)\\s*offset")[,2],
                        rdo_offset = str_match(rdo, "offset\\s*(.*?)\\s*mg/l")[,2],
                        rdo_100 = str_match(rdo, "premeasurement\\s*(.*?)\\s*%satpost")[,2],
                        rdo_conc = str_match(rdo, "concentration\\s*(.*?)\\s*mg/lpremeasurement")[,2],
                        rdo_temp = str_match(rdo, "temperature\\s*(.*?)\\s*°c")[,2],
                        rdo_pressure = str_match(rdo, "pressure\\s*(.*?)\\s*mbar")[,2],

                        # pH
                        ph_cal_date = as.character(mdy(str_match(ph_orp, "lastcalibrated\\s*(.*?)\\s*calibrationdetails")[,2])),
                        ph_slope_pre = str_match(ph_orp, "offset1slope\\s*(.*?)\\s*mv/ph")[,2],
                        ph_offset_pre = str_match(ph_orp, "mv/phoffset\\s*(.*?)\\s*mvslopeandoffset2")[,2],
                        ph_slope_post = str_match(ph_orp, "offset2slope\\s*(.*?)\\s*mv/ph")[,2],
                        ph_offset_post = str_match(ph_orp, paste0(ph_slope_post,"mv/phoffset\\s*(.*?)\\s*mvorporp"))[,2],
                        # Sometimes, the post value can actually be in the high 6 pH... therefore the post measurement regex matching text is conditional
                        ph_7_nice = str_sub(str_match(ph_orp, "postmeasurementph7\\s*(.*?)\\s*mvcal")[,2], 10, nchar(str_match(ph_orp, "postmeasurementph7\\s*(.*?)\\s*mvcal")[,2])),
                        ph_7_high = str_sub(str_match(ph_orp, "postmeasurementph8\\s*(.*?)\\s*mvcal")[,2], 10, nchar(str_match(ph_orp, "postmeasurementph8\\s*(.*?)\\s*mvcal")[,2])),
                        ph_7_low = str_sub(str_match(ph_orp, "postmeasurementph6\\s*(.*?)\\s*mvcal")[,2], 10, nchar(str_match(ph_orp, "postmeasurementph6\\s*(.*?)\\s*mvcal")[,2])),
                        ph_7 = ifelse(!is.na(ph_7_nice), ph_7_nice,
                               ifelse(!is.na(ph_7_high), ph_7_high, ph_7_low)),
                        # pH
                        ph_4_pre = str_match(ph_orp, "premeasurementph\\s*(.*?)\\s*phph")[,2],
                        ph_4_post =  str_match(ph_orp, paste0("postmeasurementph\\s*(.*?)\\s*phph")[,2],
                         # Sometimes, the post value can actually be in the high 6 pH... therefore the post measurement regex matching text is conditional
                        
                        ph_7_nice = str_sub(str_match(ph_orp, "premeasurementph7\\s*(.*?)\\s*mvcal")[,2], 10, 11),
                        ph_7_high = str_sub(str_match(ph_orp, "premeasurementph8\\s*(.*?)\\s*mvcal")[,2], 10, 11),
                        ph_7_low = str_sub(str_match(ph_orp, "premeasurementph6\\s*(.*?)\\s*mvcal")[,2], 10, 11),
                        ph_7_pre = ifelse(!is.na(ph_7_nice), ph_7_nice,
                        # ORP
                        #Newly encountered thing: sometimes the calibration report calls the ORP standard Zobell's, sometimes it's just called "ORP Standard":
                        orp_offset = ifelse(is.na(str_match(ph_orp, "zobell'soffset\\s*(.*?)\\s*mvtemperature")[,2]) & is.na(str_match(ph_orp, "quickcal\\s*(.*?)\\s*mvtemperature")[,2]),
                                            str_match(ph_orp, "orpstandardoffset\\s*(.*?)\\s*mvtemperature")[,2],
                                            ifelse(is.na(str_match(ph_orp, "zobell'soffset\\s*(.*?)\\s*mvtemperature")[,2]) & is.na(str_match(ph_orp, "orpstandardoffset\\s*(.*?)\\s*mvtemperature")[,2]),
                                                   str_match(ph_orp, "quickcal\\s*(.*?)\\s*mvtemperature")[,2],
                                                   str_match(ph_orp, "zobell'soffset\\s*(.*?)\\s*mvtemperature")[,2])),
                        orp_pre = str_match(ph_orp, "°cpremeasurement\\s*(.*?)\\s*mvpostmeasurement")[,2],
                        orp_post = str_match(ph_orp, paste0(orp_pre,"mvpostmeasurement\\s*(.*?)\\s*mv"))[,2],

                        # Conductivity
                        cond_cal_date = as.character(mdy(str_match(conductivity, "lastcalibrated\\s*(.*?)\\s*calibrationdetails")[,2])),
                        tds_conversion_ppm = str_sub(str_match(conductivity, "tdsconversionfactor\\s*(.*?)\\s*cellconstant")[,2], 6, nchar(str_match(conductivity, "tdsconversionfactor\\s*(.*?)\\s*cellconstant")[,2])),

                        # calibration report formatting has changed in 2024 for this variable. Therefore a post-2024 correction must occur
                        cond_cell_constant = ifelse(year(DT) < 2024, str_match(conductivity, "cellconstant\\s*(.*?)\\s*referencetemperature")[,2],
                                                    str_match(conductivity, "cellconstant\\s*(.*?)\\s*offset")[,2]),

                        cond_offset = ifelse(year(DT) < 2024, NA,
                                             str_match(conductivity, "offset\\s*(.*?)\\s*µs/cm")[,2]),

                        cond_pre = str_match(conductivity,paste0(str_match(conductivity,
                                                                           "premeasurementactual\\s*(.*?)\\s*specificconductivity")[,2],"specificconductivity\\s*(.*?)\\s*µs/cmpost"))[,2],
                        cond_post = str_match(conductivity,paste0(str_match(conductivity,
                                                                            "postmeasurementactual\\s*(.*?)\\s*specificconductivity")[,2],"specificconductivity\\s*(.*?)\\s*µs/cm"))[,2]) %>%
                        # if(turbidity == "No Turbidity Sensor"){
                        # # Turbidity
                        # turb_cal_date = "None",
                        # ntu_slope = "None",
                        # ntu_offset = "None",
                        # ntu_10 = "None",
                        # ntu_100 = "None") %>%

    select(-c(ph_7_nice, ph_7_high, ph_7_low))

    # Not all sondes have depth.
    if(!is.na(str_match(depth, "lastcalibrated"))){#\\s*(.*?)\\s*calibrationdetails")[,2])){
      cal_table <- cal_table %>%
        mutate(
          # Depth
          depth_cal_date = as.character(mdy(str_match(depth, "lastcalibrated\\s*(.*?)\\s*calibrationdetails")[,2])),
          depth_offset = str_match(depth, "zerooffset\\s*(.*?)\\s*psireferencedepth")[,2],
          depth_ref_depth = str_match(depth, "psireferencedepth\\s*(.*?)\\s*ftreferenceoffset")[,2],
          depth_ref_offset = str_match(depth, "ftreferenceoffset\\s*(.*?)\\s*psipremeasurement")[,2],
          depth_pre_psi = str_match(depth, "psipremeasurement\\s*(.*?)\\s*psipostmeasurement")[,2],
          depth_post_psi = str_match(depth, "psipostmeasurement\\s*(.*?)\\s*psi")[,2])
    }

    if(depth == "No Depth Sensor"){

      cal_table <- cal_table %>%
        mutate(# Depth
      depth_cal_date = "No Depth Sensor",
      depth_offset = "No Depth Sensor",
      depth_ref_depth = "No Depth Sensor",
      depth_ref_offset = "No Depth Sensor",
      depth_pre_psi = "No Depth Sensor",
      depth_post_psi = "No Depth Sensor")
    }


    if(!is.na(str_match(turbidity, "lastcalibrated"))){#calibrationpoint1premeasurement\\s*(.*?)\\s*ntupost")[,2])){
      # Not all sondes have turbidity.
      cal_table <- cal_table %>%
        mutate(
          # Turbidity
          turb_cal_date = as.character(mdy(str_match(turbidity, "lastcalibrated\\s*(.*?)\\s*calibrationdetails")[,2])),
          ntu_slope = str_match(turbidity, "slope\\s*(.*?)\\s*offset")[,2],
          ntu_offset = str_match(turbidity, "offset\\s*(.*?)\\s*ntu")[,2],
          ntu_10 = str_match(turbidity, "calibrationpoint1premeasurement\\s*(.*?)\\s*ntupost")[,2],
          ntu_100 = str_match(turbidity, "calibrationpoint2premeasurement\\s*(.*?)\\s*ntupost")[,2])
    }

    if(turbidity == "No Turbidity Sensor"){
      cal_table <- cal_table %>%
        mutate(
          # Turbidity
          turb_cal_date = "No Turbidity Sensor",
          ntu_slope = "No Turbidity Sensor",
          ntu_offset = "No Turbidity Sensor",
          ntu_10 = "No Turbidity Sensor",
          ntu_100 = "No Turbidity Sensor")




    }


    cal_table <- cal_table %>%
      mutate(
        #Factory Defaults
        factory_defaults = paste0(ifelse(grepl("factorydefault", turbidity), "Turbidity ", ""),
                                  ifelse(grepl("factorydefault", rdo), "RDO ", ""),
                                  ifelse(is.na(ph_slope_post), "pH ", ""),
                                  ifelse(is.na(orp_offset), "ORP ", ""),
                                  ifelse(grepl("factorydefault", conductivity), "Conductivity ", ""),
                                  ifelse(grepl("factorydefaults", depth), "Depth ", ""))) %>%
      # convert all columns to character values to preserve info
      mutate(across(.cols = everything(), .fns = as.character)) %>%
      # remove "," from big numbers
      mutate(across(everything(), ~str_replace_all(., ",", "")))

  }


cal_files <- list.files("data/calibration_reports") %>% map(~try(cal_tabler(cal_files = .))) %>%
  bind_rows() %>%
  filter(year(DT) == 2023)
```
