---
title: "Add Field Note Flags"
author: "ROSSyndicate"
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
editor_options: 
  markdown: 
    wrap: 90
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE) 
```

```{r, include=FALSE}
source("src/package_loader.R")
lapply(c("data.table", "tidyverse", "kableExtra"), package_loader)
```

# `add_field_flag()`

This function adds three flags:

1. `"sonde not employed"`
2. `"site visit"`
3. `"sv window"`

These flags are determined using the field notes that staff take when they are servicing the sondes. 

```{r, eval=FALSE}
add_field_flag <- function(df) {
  df <- df %>%
    # flag when sonde was not employed in the river
    add_flag(sonde_employed == 1, "sonde not employed") %>%
    # flag when sonde was handled in a site visit
    add_flag(as.character(last_site_visit) == as.character(DT_round), "site visit") %>%
    # Add flags for the next 45 minutes after a site visit
    add_flag(lag(str_detect(flag, "site visit"), n = 3), "sv window") %>%
    add_flag(lag(str_detect(flag, "site visit"), n = 2), "sv window") %>%
    add_flag(lag(str_detect(flag, "site visit"), n = 1), "sv window")
  return(df)
}
```

## Add `"sonde not employed"` flag.
**The sonde not employed flag is triggered when the `sonde_employed` column is equal to one. The `sonde_employed` column is generated in the `clean_field_notes` function and uses the `sensor_pulled` and `sensor_deployed` columns from the original field notes**
```{r, eval=FALSE}
add_flag(sonde_employed == 1,
         "sonde not employed") 
```
- `sonde_employed` = Binary result from the `clean_field_notes()` step in the pipeline.
- `"sonde not employed"` = Flag descriptor inserted into the `flag` column.

## Add `"site visit"` flag.
**The site visit flag is triggered when the `last_site_visit` column is equal to the `DT_round` column. The `last_site_visit` column is created during the `clean_field_notes()` step, and is filled during the `summarize_site_param()` step, after it has been joined to the HydroVu API data.**
```{r, eval=FALSE}
add_flag(as.character(last_site_visit) == as.character(DT_round), 
         "site visit")
```

# Add `"sv window flag"` flag.
**The sv window flag is triggered if the `"site visit"` flag is detected within the previous three data points.**
```{r, eval=FALSE}
add_flag(lag(str_detect(flag, "site visit"), n = [1/2/3]), 
         "sv window")
```

# Analysis
```{r, echo=FALSE}
sd_flag_data <- read_csv("data/flag_report.csv") %>% 
  filter(flag %in% c("sonde not employed", "site visit", "sv window"),
         !(parameter %in% c("Baro", "Battery Level", "External Voltage")),
         data_points_flagged_percentage_sans_na > 0 | dates_flagged_percentage_sans_na > 0
         ) %>% 
  select(Site = site, 
         Parameter = parameter,
         Flag = flag, 
         `% of Total Data Points Flagged` = data_points_flagged_percentage_sans_na,
         `% of Total Dates Flagged` = dates_flagged_percentage_sans_na)

kable(sd_flag_data, format = "markdown", align = "c")
```

# Examples
