---
title: "Add Sensor Specifications Flag"
author: "ROSSyndicate"
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
editor_options: 
  markdown: 
    wrap: 90
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE) 
```

```{r, include=FALSE}
source("src/package_loader.R")
lapply(c("data.table", "tidyverse", "kableExtra"), package_loader)
```

# `add_spec_flag()`

This function will add a flag if a data point's value falls outside of In Situ's sensor range specifications.

```{r}
add_spec_flag <- function(df){

  # get the parameter from the parameter column in the df of interest
  parameter_name <- unique(na.omit(df$parameter))
  # Pull the sensor specification range from the yaml file
  sensor_min <- eval(parse(text = sensor_spec_ranges[[parameter_name]]$min))
  sensor_max <- eval(parse(text = sensor_spec_ranges[[parameter_name]]$max))

  df <- df %>%
    add_flag(parameter == parameter_name & (mean < sensor_min | mean > sensor_max),
             paste("outside of", parameter_name, "sensor specification range")) %>%

    return(df)

}
```
- `parameter_name` = The sensor under evaluation for that data point.
- `sensor_min` = The lower limit for the sensor.
- `sensor_max` = The upper limit for the sensor.
- `paste("outside of", parameter_name, "sensor specification range")` = Dynamic flag descriptor inserted into the `flag` column.

# Analysis
```{r, echo=FALSE}
sd_flag_data <- read_csv("data/flag_report.csv") %>% 
  filter(str_detect(flag, "sensor specification range"),
         !(parameter %in% c("Baro", "Battery Level", "External Voltage")),
         data_points_flagged_percentage_sans_na > 0 | dates_flagged_percentage_sans_na > 0
         ) %>% 
  select(Site = site, 
         Parameter = parameter,
         Flag = flag, 
         `% of Total Data Points Flagged` = data_points_flagged_percentage_sans_na,
         `% of Total Dates Flagged` = dates_flagged_percentage_sans_na)

kable(sd_flag_data, format = "markdown", align = "c")
```
# Examples
