---
title: "2022 Report and Figures"
author: "Sam Struthers"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
source("src/package_loader.R")
lapply(c("tidyverse", "feather", "data.table", "ggpubr", "tidyr", "broom", "flextable", "officer"), package_loader)

#walk(list.files('src/qaqc/explore_and_fix_fxns', pattern = "*.R", full.names = TRUE, recursive = TRUE), source)
# Source most recent flagging data
all_data_flagged <- readRDS("data/flagged/sjs_all_data_flagged.RDS")%>%
  bind_rows()
# %>%
#   mutate(mean_public = ifelse(is.na(flag), mean, NA))%>%
#   filter(!(parameter == "pH" & mean < 6))%>%
#   filter(!(parameter == "pH" & mean > 10))

cleaned_data <- filter(all_data_flagged, is.na(cleaner_flag))
options(dplyr.summarise.inform = FALSE)

site_names <- tibble(site = c("tamasag", "legacy", "lincoln", "timberline", "prospect" ,"boxelder",  "archery", "river bluffs"), 
                        site_upper = c("Tamasag", "Legacy", "Lincoln", "Timberline", "Prospect" ,"Boxelder",  "Archery", "River Bluffs"))

site_upper_order <- pull(site_names, site_upper)

`%nin%` = Negate(`%in%`)

```


```{r get_basic_stats}
calc_sum_stats <- function(site_select, param_select){
  
   site_select_upper <- filter(site_names, site %in% site_select)%>%pull(site_upper)
  
  site_stats <- all_data_flagged%>%
    filter(site == site_select & parameter == param_select & !is.na(mean_public) & year == 2023)%>%
    select(DT_round, mean)%>%
    summarize(
    n_obs = n(),
    min = min(mean, na.rm = TRUE),
    q1 = quantile(mean, 0.25, na.rm = TRUE),
    median = median(mean, na.rm = TRUE),
    q3 = quantile(mean, 0.75, na.rm = TRUE),
    max = max(mean, na.rm = TRUE), 
    sd = sd(mean, na.rm = TRUE)
  )%>%
    mutate(Site = site_select_upper, 
           parameter = param_select)%>%
    select(Site, parameter, `observations` = n_obs, min, median, max, sd )
  

  return(site_stats)
} 


site_select <- c("tamasag","legacy", "timberline", "prospect", "archery", "river bluffs")  
site_select_stat_order <- c("Tamasag","Legacy", "Timberline", "Prospect", "Archery", "River Bluffs")
param_select<- c("Temperature", "Specific Conductivity", "pH", "ORP", "DO")

# Create all combinations of sites and params
combinations <- expand_grid(site_select, param_select)


site_sum_stats <- pmap_df(combinations, function(site_select, param_select) {
  calc_sum_stats(site_select, param_select)
})
```

# Summary stats table

```{r create_table}


create_table <- function(parameter_select = "Temperature", max_color = "#CC3311", min_color =  "#0077BB"){
  
subset_stats <- filter(site_sum_stats, parameter == {{parameter_select}} )
subset_stats$Site <- factor(subset_stats$Site, levels = site_select_stat_order)

#create standard border color and width
std_border <- fp_border_default(width = 1, color = "black")
  
ft <- flextable(subset_stats)%>%
  separate_header() %>%
  align(align = "center", part = "all")%>%
  colformat_double( big.mark = ",", decimal.mark = ".", digits = 3)%>%
  set_table_properties(layout = "fixed")%>%
  border_remove()%>%
  border_outer(part="all", border = std_border )%>%
  border_inner_h(border = std_border, part="all")%>%
   border_inner_v(border = std_border, part="all")%>%
  autofit()%>%
  italic( j = "Site")%>%
  fontsize( size = 8, part = "body")

#Highlighting columns for max and min
   
highlight_max_min <- function(column){
  
   col_index <- which(colnames(subset_stats) == column)
    max_row_index <- which.max(subset_stats[[column]])
    min_row_index <- which.min(subset_stats[[column]])
    
#     color MAX
     ft <- color(ft, j = col_index,i = max_row_index, color = max_color)
  
     # color Min
      ft <- color(ft, j = col_index, i = min_row_index, color = min_color)
     #    
      ft   
}
ft <- highlight_max_min(column = "min")
ft <- highlight_max_min(column = "median")
ft <- highlight_max_min(column = "max")
ft <- highlight_max_min(column = "sd")

return(ft)
}
  
create_table(parameter_select = "pH")
create_table(parameter_select = "DO")
create_table(parameter_select = "Specific Conductivity")


# sect_properties <- prop_section(
#   page_size = page_size(
#     orient = "landscape",
#     width = 8.3, height = 11.7
#   ),
#   type = "continuous",
#   page_margins = page_mar()
# )
# 
# ft
# 
# # Save the table to a Word document
# save_as_docx(ft, path = "data/table_export.docx", pr_section = sect_properties)


  
```


```{r}
color_code <- tibble(flag = c("missing data", "sonde not employed", 
                              "site visit", "sv window", 
                              "slope violation", "repeated value", 
                              "outside of seasonal range", "outside sd range", 
                              "outside of sensor specification range", "suspect data"),
                     color = c("grey", "black",
                               "#FFBA00", "#FFBA00",
                               "#002FA7", "#7DF365",
                               "#D55E00", "#1C7C54", 
                               "#FF69B4", "#bdcffc"))


color_joiner <-function(data, flag_type) {
  
  data %>%
    filter(grepl(flag_type, flag)) %>%
    mutate(flag = flag_type) %>%
    left_join(color_code, by = "flag")
  
}  
site_colors <- c("Tamasag" = "#bd90f8" ,"Legacy"= "#01377D", "Lincoln" =  "#009DD1", "Timberline" = "#97E7F5",
                "Prospect" =  "#26B170","Boxelder"="#F5E15A","Archery" =  "#FEA305", "River Bluffs" =   "#F26021")



bg_colors <- c( "#01377D", "#009DD1", "#97E7F5", "#7ED348", "#26B170", "#000000")
or_colors <-c("#F5E15A", "#F4BE1D", "#FEA305", "#F26021", "#F34646")

site_names <- tibble(site = c("tamasag", "legacy", "lincoln", "timberline", "prospect" ,"boxelder",  "archery", "river bluffs"), 
                        site_upper = c("Tamasag", "Legacy", "Lincoln", "Timberline", "Prospect" ,"Boxelder",  "Archery", "River Bluffs"))

```

```{r test vars}



sites = c("legacy", "timberline" ,"boxelder",  "archery", "river bluffs")
start_date = "2023-05-09 08:30:00"
end_date = "2023-05-16 09:30:00"
parameter_select = "Specific Conductivity"
title = "Sp. Conductivity"
units = "uS/cm"
hourly = TRUE
clean = FALSE

parameters <- c("Temperature", "Turbidity", "Specific Conductivity", "pH", "ORP", "DO", "Depth", "Battery Level", "Chl-a Fluorescence")
print(parameters)
```

# Plotter Function
```{r}


plotter <- function(clean = FALSE, hourly = TRUE, sites = c("legacy", "timberline" ,"boxelder",  "archery", "river bluffs"),
                           start_date = "2023-05-08 08:30:00", end_date = "2023-05-18 09:30:00", 
                           parameter_select = "Specific Conductivity", title = "Sp. Conductivity", units = "Sp. Conductivity (uS/cm) "){
  
  site_select_upper <- filter(site_names, site %in% sites)%>%pull(site_upper)
  site_select_join <- filter(site_names, site %in% sites)
  
  
  flag_start_date <- ymd_hms(start_date)
  flag_end_date <- ymd_hms(end_date)
  
  grab_site_data <- function(site_select){
    flag_plot_data <- filter(all_data_flagged, site == site_select & parameter == parameter_select) %>% 
    filter(DT_round >= flag_start_date & DT_round <= flag_end_date)%>%
      #At a minimum remove site visits
    filter(!grepl("site visit", flag))
    
    # Ive found for storm events that flags remove valuable trends due to to their sharp increases in slope
    if(clean == TRUE){
   flag_plot_data <- flag_plot_data %>%
     filter(is.na(flag))
    }
    if(hourly == TRUE){
    flag_plot_data <- flag_plot_data%>%
    group_by(DT_round = floor_date(DT_round, unit = "hour"),
             t_mean01, t_mean99) %>% 
    summarize(mean = median(mean, na.rm = TRUE)) %>% 
    ungroup()%>%
      mutate(site = site_select)
    }
    
  }
  
  all_flag_plot_data <- map(sites, grab_site_data)%>%
    bind_rows()%>%
    left_join(site_select_join, by  = "site")
    
  
  all_flag_plot_data$site_upper <- factor(all_flag_plot_data$site_upper, levels = site_select_upper)
  
  
  
  ggplot() +
    geom_line(data = all_flag_plot_data, 
               aes(x = DT_round, y = mean, color = site_upper), size = 2) +
    scale_color_manual(name = "Site", values = bg_colors) +
    labs(x = "Date",
         y = paste(units)) +
    #ggtitle(paste(title)) +
    #ylim(y_min, y_max) +
    theme_classic(base_size = 28)
  
}

#plotter()

```

#Storms
## May rain storm
sites: Legacy, Timberline, Boxelder, Archery (maybe riverbluffs)
Params: Turbidity, Specific Conductivity, DO, Depth

```{r} 

#precip plot
may_precip <-read_csv("data/context_data/2023_report/utility_center_precip_may.csv")%>%
  rename(precip_accum_in = "PrecipAccum-Storm(6320)")%>%
  filter(DateTime >= ymd_hms("2023-05-08 08:30:00") & DateTime <= ymd_hms("2023-05-18 09:30:00"))%>%
  mutate(precip_accum_cm = precip_accum_in*2.54)

precip_plot <- ggplot(may_precip, aes(x= DateTime, y = precip_accum_cm))+
  geom_col(color = "#002FA7", size = 3)+
  # Reverse the y-axis
  scale_y_reverse() +

  labs(
    x = "Date",
    y = "Precipitation (cm)"
  ) +
  theme_classic(base_size = 28)+
  theme( legend.position = "none",
         axis.title.x  = element_blank(),
         axis.title.y = element_text(size = 20,face = "bold") )
precip_plot
                           
may_sites <- c("legacy", "timberline", "boxelder", "archery")

#COND
clean_spec_cond_may <- plotter(sites = may_sites ,clean = FALSE)+ 
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
#Depth
clean_depth_may <- plotter(sites = may_sites, clean = TRUE, parameter_select = "Depth", units = "Depth (m)")+
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
#DO
clean_do_may <- plotter(sites = may_sites, clean = TRUE, parameter_select = "DO", units = "DO (mg/L)")+
  theme(legend.position = "none",
        axis.title.y = element_text(size = 22,face = "bold"))
#TURB
clean_temp_may <- plotter(sites = may_sites, clean = TRUE, parameter_select = "Temperature", units = "Temperature (C)")+
  theme(legend.position = "none",
        axis.title.y = element_text(size = 22,face = "bold"))


  ggarrange( precip_plot, precip_plot, clean_depth_may,clean_spec_cond_may,  clean_do_may , clean_temp_may, ncol = 2, nrow = 3, legend = "bottom", common.legend = T)

  ggsave("data/sharing/figures/2023/DRAFT_urban_storm_may_2023.jpg",width = 20, height = 14, dpi = 300)
```

## July 31st storm

Sites: "tamasag","timberline", "prospect", "archery"
Params: Turb (Not at Archery ), Depth, Cond, DO

```{r}

july_sites <- c("tamasag", "legacy", "timberline", "prospect", "archery")
july_start_date <- "2023-07-28 12:00:00"
july_end_date <- "2023-08-08 12:00:00"
#COND
july_spec_cond <- plotter(sites = july_sites ,clean = FALSE, 
                          start_date = july_start_date, 
                          end_date = july_end_date)+ 
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))

#Depth
july_depth <- plotter(sites = july_sites, clean = FALSE,
                        start_date = july_start_date, 
                          end_date = july_end_date, 
                      parameter_select = "Depth", units = "Depth (m)")+
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
#DO
july_do <- plotter(sites = july_sites, 
                         start_date = july_start_date, 
                          end_date = july_end_date, clean = FALSE, parameter_select = "DO", units = "DO (mg/L)")+
  theme(legend.position = "none",
        axis.title.y = element_text(size = 22,face = "bold"))
#TURB
july_turb <- plotter(sites = c("tamasag", "timberline", "prospect" ), clean = FALSE,
                     start_date = july_start_date, 
                          end_date = july_end_date, 
                     parameter_select = "Turbidity", units = "Turbidity (NTU)")+
  theme(legend.position = "none",
        axis.title.y = element_text(size = 22,face = "bold"))+
  scale_y_log10()




   ggarrange( july_depth,july_spec_cond,  july_do , july_turb, ncol = 2, nrow = 2, legend = "bottom", common.legend = T)
  # 
   ggsave("data/sharing/figures/2023/DRAFT_urban_storm_july_2023.jpg",width = 20, height = 14, dpi = 300)

```

## September 4th Storm

```{r}
sept_sites <- c("tamasag", "legacy", "prospect", "archery")
sept_sites_turb <- c("tamasag", "legacy", "prospect")
sept_start_date <-  "2023-09-03 01:00:00"
sept_end_date <- "2023-09-07 12:00:00"


#COND
sept_spec_cond <- plotter(sites = sept_sites ,clean = FALSE, 
                          start_date = sept_start_date, 
                          end_date = sept_end_date)+ 
  theme(legend.position = "none", 
        
        axis.title.y = element_text(size = 22,face = "bold"))

#Depth
sept_depth <- plotter(sites = sept_sites, clean = FALSE,
                        start_date = sept_start_date, 
                          end_date = sept_end_date, 
                      parameter_select = "Depth", units = "Depth (m)")+
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
#DO
sept_do <- plotter(sites = sept_sites, 
                         start_date = sept_start_date, 
                          end_date = sept_end_date, clean = FALSE, parameter_select = "DO", units = "DO (mg/L)")+
  theme(legend.position = "none",
        axis.title.y = element_text(size = 22,face = "bold"))
#TURB
sept_turb <- plotter(sites = sept_sites_turb, clean = FALSE,
                     start_date = sept_start_date, 
                          end_date = sept_end_date, 
                     parameter_select = "Turbidity", units = "Turbidity (NTU)")+
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))

#Temp
sept_temp <- plotter(sites = sept_sites, clean = FALSE,
                     start_date = sept_start_date, 
                          end_date = sept_end_date, 
                     parameter_select = "Temperature", units = "Temperature (C)")+
  theme(legend.position = "none",
        axis.title.y = element_text(size = 22,face = "bold"))
#pH
sept_ph<- plotter(sites = sept_sites, clean = TRUE,
                     start_date = sept_start_date, 
                          end_date = sept_end_date, 
                     parameter_select = "pH", units = "pH")+
  theme(legend.position = "none",
        axis.title.y = element_text(size = 22,face = "bold"))

ggarrange( sept_depth, sept_turb,sept_spec_cond, sept_do ,   ncol = 2, nrow = 2, legend = "bottom", common.legend = T)

ggsave("data/sharing/figures/2023/DRAFT_blackwater_sept_2023.jpg",width = 20, height = 14, dpi = 300)


```




# Reservoir Releases

## Fossil Creek release (Nov 10th)

Sites: "archery", "river bluffs"
Params: pH, Depth, Temp, Chl-a

```{r}
foscrk_sites <- c("archery", "river bluffs")
foscrk_start_date <- "2023-11-05 12:00:00"
foscrk_end_date <- "2023-11-15 12:00:00"

fos_creek_Q <- read_csv("data/context_data/2023_report/fossil_creek_Q_2023.csv")%>%
  mutate(dt =mdy_hm(gsub("\"", "", `Date Time`)))%>%
  filter(dt >= as.POSIXct(foscrk_start_date) &dt <= as.POSIXct(foscrk_end_date)& !is.na(`DISCHRG Value`))%>%
  mutate(site = "Fossil Creek Canal")

# clp_Q <- read_csv("data/context_data/2023_report/clp_below_little_cache_2023.csv")%>%
#   mutate(dt =mdy_hm(gsub("\"", "", `Date Time`)))%>%
#   filter(dt >= as.POSIXct(foscrk_start_date) &dt <= as.POSIXct(foscrk_end_date)& !is.na(`DISCHRG Value`))%>%
#   mutate(site = "Poudre River")
#Fos crk Q
foscrk_Q <-  ggplot() +
    geom_line(data = fos_creek_Q, 
               aes(x = dt, y = `DISCHRG Value`), size = 2, color = "#002FA7") +
  # geom_line(data = clp_Q, 
  #              aes(x = dt, y = `DISCHRG Value`), size = 2, color = "cyan") +
    labs(x = "Date",
         y = "Discharge (cfs)") +
    theme_classic(base_size = 28)+
    theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))

#DO
foscrk_do <- plotter(sites = foscrk_sites, clean = FALSE,
                          start_date = foscrk_start_date, 
                          end_date = foscrk_end_date, 
                      parameter_select = "DO", units = "DO (mg/L)")+
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
#chla
foscrk_chla <- plotter(sites = foscrk_sites, clean = TRUE,hourly = TRUE,
                          start_date = foscrk_start_date, 
                          end_date = foscrk_end_date, 
                      parameter_select = "Chl-a Fluorescence", units = "Chl-a Fluorescence (RFU)")+
  geom_smooth(method = "lm", se = FALSE, size = 2)+
  theme(legend.position = "none",
        axis.title.y = element_text(size = 22,face = "bold"))+
  ylim(1.25,3.5)
#ph
foscrk_pH <- plotter(sites = foscrk_sites, clean = FALSE,
                          start_date = foscrk_start_date, 
                          end_date = foscrk_end_date, 
                      parameter_select = "pH", units = "pH")+
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
#temp
foscrk_temp <- plotter(sites = foscrk_sites, clean = FALSE,
                          start_date = foscrk_start_date, 
                          end_date = foscrk_end_date, 
                      parameter_select = "Temperature", units = "Temperature (C)")+
  theme(legend.position = "none",
        axis.title.y = element_text(size = 22,face = "bold"))

ggarrange(foscrk_Q, foscrk_pH, foscrk_do, ncol = 1, nrow= 3, common.legend = TRUE, legend = "bottom")
ggsave("data/sharing/figures/2023/DRAFT_foscrk_release.jpg",width = 20, height = 14, dpi = 300)

#ggarrange(foscrk_chla_raw, foscrk_chla, ncolums = 2, nrow = 1, common.legend = TRUE, legend = "bottom")

```



## Horsetooth release (Oct 15- Nov 2)
Sites: "tamasag", "lincoln","prospect", "archery", "river bluffs"
Params: pH, Depth, Temp, Chl-a

```{r}

horse_sites <- c("tamasag", "lincoln","prospect", "archery", "river bluffs")
horse_start_date <- "2023-10-18 12:00:00"
horse_end_date <- "2023-10-26 12:00:00"

#Depth
horse_depth <- plotter(clean = TRUE, sites = horse_sites, 
                       start_date = horse_start_date, end_date = horse_end_date, 
                       parameter_select = "Depth", units = "Depth (m)")+
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
#pH
horse_ph<- plotter(clean = TRUE, sites = horse_sites, 
                       start_date = horse_start_date, end_date = horse_end_date, 
                       parameter_select = "pH", units = "pH")+
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
#Temp
horse_temp <- plotter(clean = FALSE, sites = horse_sites, 
                       start_date = horse_start_date, end_date = horse_end_date, 
                       parameter_select = "Temperature", units = "Temperature (C)")+
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
#Cond
horse_cond <- plotter(clean = TRUE, sites = horse_sites, 
                       start_date = horse_start_date, end_date = horse_end_date)+
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
#DO
horse_DO <- plotter(clean = FALSE, sites = horse_sites, 
                       start_date = horse_start_date, end_date = horse_end_date,
                       parameter_select = "DO", units = "DO (mg/L)")+
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.title.y = element_text(size = 22,face = "bold"))
# #turbidity
# horse_turb <- plotter(clean = TRUE, sites = c("legacy", "lincoln","prospect"), 
#                        start_date = horse_start_date, end_date = horse_end_date,
#                        parameter_select = "Turbidity", units = "Turbidity (NTU)")+
#   theme(legend.position = "none", 
#         axis.title.x=element_blank(),
#         axis.title.y = element_text(size = 22,face = "bold"))

ggarrange(horse_depth, horse_DO,horse_cond,  horse_temp, ncol = 2, nrow = 2, legend = "bottom", common.legend = T)
ggsave("data/sharing/figures/2023/DRAFT_horsetooth_release_oct.jpg",width = 20, height = 14, dpi = 300)

```

# Testing
```{r}
plotter(clean = TRUE, hourly = TRUE, sites = c("tamasag", "legacy"), start_date = "2023-04-01 12:00:00", end_date = "2023-05-26 12:00:00", parameter_select = "pH", units = "pH")+
  theme(legend.position = "none",
        axis.title.y = element_text(size = 22,face = "bold"))

start_dt <- ymd_hms("2023-05-01 12:00:00", tz = "MST")
end_dt <- ymd_hms("2023-05-25 12:00:00", tz = "MST")


ggplot(filter(all_data_flagged, site == "river bluffs" & year == 2023 & parameter %in% c("DO") & between(DT_round, start_dt, end_dt )& is.na(flag) ), aes(x = DT_round, y = mean)) +
  geom_line(color = "red")+
    #aes(color = !is.na(flag))) +
  #geom_line()+
  geom_line(data = filter(all_data_flagged, site == "boxelder"& year == 2023 & parameter %in% c("DO") & between(DT_round, start_dt, end_dt)& !is.na(mean)), aes(group = site), color = "black") +
  labs(color = "Flagged", y = "DO") +
  theme_bw()
```



