---
title: "PWQN Q2 Report"
author: "Sam Struthers"
date: "`r Sys.Date()`"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(here)
library(tidyverse)
library(plotly)
library(arrow)
library(furrr)
# loading packages
package_loader <- function(x) {
  if (x %in% installed.packages()) {
    suppressMessages({
      library(x, character.only = TRUE)
    })
  } else {
    suppressMessages({
      install.packages(x)
      library(x, character.only = TRUE)
    })
  }
}

invisible(
  lapply(c("arrow",
           "data.table",
           "httr2",
           "tidyverse",
           "lubridate",
           "zoo",
           "padr",
           "stats",
           "RcppRoll",
           "yaml",
           "here",
           #"fcw.qaqc",
           "furrr", 
           "dataRetrieval", 
           "cdssr", 
           "ggplot2", 
           "ggthemes", 
           "patchwork"
  ),
  package_loader)
)

# 
# params <- paste(c("Chl-a Fluorescence","Depth", "Specific Conductivity",
#                    "Temperature", "Turbidity", "ORP", "pH", "DO", "FDOM Fluorescence"), collapse = "|")
# 
# 
# #get files in hydrovu_2024_data
# files <- tibble(filename = list.files(here("data","sharing","quarterly_meetings", "2025_Q2","flagged_final"), full.names = TRUE))%>%
#   filter(grepl(pattern = params, filename))%>%
#   #remove extras
#   filter(!grepl(pattern = "Level|MV", filename))
# 
# 
# # read in files
# all_data <- map_dfr(files, ~read_csv(.x, show_col_types = F)) %>%
#   #turn into individual dataframes by site and parameter
#   split(f = list(.$site, .$parameter), sep = "-") %>%
#   keep(~nrow(.) > 0)%>%
#   bind_rows()%>%
#   #convert to MST!
#   mutate(DT_round = with_tz(DT_round, tz = "MST"),
#          DT_join = as.character(DT_round))
# 
# 
# min_date <- min(all_data$DT_round, na.rm = TRUE)%>%
#   format("%Y-%m-%d")
# max_date <- max(all_data$DT_round, na.rm = TRUE)%>%
#   format("%Y-%m-%d")
# 
# # save to raw data file to be processed later on
# write_rds(all_data, here("data", "sharing", "quarterly_meetings", "2025_Q2", paste0("flagged_data_", min_date, "_", max_date, ".rds")))
```

```{r, include= F}
site_names <- tibble(site = c("pbd", "bellvue", "salyer", "udall", "riverbend", "cottonwood" ,"elc",  "archery", "riverbluffs"), 
                        site_name = c("Canyon Mouth", "Tamasag", "Legacy", "Lincoln", "Timberline", "Prospect" ,"Boxelder",  "Archery", "River Bluffs"), 
                     natural_name = c("Canyon Mouth", "Bellvue", "Salyer", "Udall", "Riverbend", "Cottonwood", "ELC", "Archery", "River Bluffs"))

labels <- tibble(param = c("Turbidity", "Specific Conductivity", "Depth", "Chl-a Fluorescence", "FDOM Fluorescence", "Temperature", "DO", 'pH', "Flow"),
                 label = c("Turbidity (NTU)", "Specific Conductivity (uS/cm)", "Depth (ft)", "Chl-a Fluorescence (RFU)", "FDOM Fluorescence (RFU)", "Temperature (C)", "DO (mg/L)", 'pH', "Flow (cfs)"))

sensor_data <- read_rds(file = "data/sharing/quarterly_meetings/2025_Q2/flagged_data_2025-03-27_2025-06-02.rds")%>%
  left_join(site_names, by = c("site"))%>%
  left_join(labels, by = c( "parameter" = "param")) 


#sensor_data_auto_clean <- filter(sensor_data, auto_cleaned_flag_binary == 0)

sensor_data_simple_clean <- sensor_data%>%
  filter(is.na(mal_flag))%>%
  filter(!grepl("site visit|sv window", auto_flag))%>%
  filter(!grepl("sonde unsubmerged", auto_flag))%>%
  filter(!grepl("sonde not employed", auto_flag))%>%
  filter(!grepl("sensor malfunction", auto_flag))  %>%
filter(!(parameter == "Specific Conductivity" & mean > 2000))%>%
  filter(!(parameter == "pH" & mean < 6.5))%>%
  filter(!(parameter == "pH" & mean > 10 ))%>%
  filter(!(parameter == "Temperature" & mean < 0))%>%
   filter(!(parameter == "Depth" & mean < 0))%>%
   filter(!(parameter == "Temperature" & mean > 25 ))%>%
  filter(!(parameter == "DO" & mean < 4 ))%>%
  filter(!(mean == 0 ))%>%
  mutate(mean = case_when(
    parameter == "Turbidity" & mean > 1000 ~ 1000, 
    parameter == "Depth"  ~ mean / 0.3048, #convert to ft
    TRUE ~ mean
  ))



#site_order <- c("Canyon Mouth", "Tamasag", "Legacy", "Lincoln", "Timberline" , "Prospect", "Boxelder", "Archery", "River Bluffs"  )
site_order = c("Canyon Mouth", "Bellvue", "Salyer", "Udall", "Riverbend", "Cottonwood", "ELC", "Archery", "River Bluffs")



plot_sensor_grabs <- function(df, sites, parameters, renamed_sites, start_dt, end_dt, timestep, add_grabs, color_scheme = bg_colors, b_size = 30){
  
  
  
  all_data <- filter(df, site %in% sites & DT_round >= ymd_hm(start_dt) & DT_round <= ymd_hm(end_dt))%>%
    filter(parameter %in% parameters)
  

  create_plot <- function(param_arg) {

    if(param_arg == "Flow"){
      
      flow_plot <- function(sites,start_dt, end_dt, timestep){

  flow_sites <- tibble(
    site = c("pbd", "udall", "elc", "riverbluffs"), 
    #site_name = c("Canyon Mouth", "Lincoln", "Boxelder", "River Bluffs"  ),
    natural_name = c("Canyon Mouth", "Udall", "ELC", "River Bluffs"  ),
    source = c('CDWR', 'USGS', 'USGS', 'CDWR'), 
    abbrev = c("CLAFTCCO","06752260","06752280",   "CLARIVCO" ))%>%
    filter(site %in% sites)
  
  
  start_dt <- ymd_hm(start_dt, tz = "MST")
  end_dt <- ymd_hm(end_dt, tz = "MST")
  start_date <- floor_date(start_dt, unit = "day")
  end_date <- ceiling_date(end_dt, unit = "day")
  
  gather_q <- function(selected_sites, start_date, end_date, timestep) {


    all_q <- tibble()

    for (i in 1:nrow(flow_sites)) {
      if (flow_sites$source[i] == "USGS") {
        q_data <- readNWISuv(siteNumbers = flow_sites$abbrev[i],
                             startDate = start_date,
                             endDate = end_date,
                             parameterCd = "00060", tz = "America/Denver") %>%
          distinct() %>%
          mutate(DT_mst = with_tz(dateTime, tzone = "MST"),
                 source = "USGS") %>%
          dplyr::select(site = site_no, DT_mst, q_cfs = X_00060_00000, flag = X_00060_00000_cd)

      } else if (flow_sites$source[i] == "CDWR") {
        q_data <- get_telemetry_ts(
          abbrev = flow_sites$abbrev[i],
          parameter = "DISCHRG",
          start_date = start_date,
          end_date = end_date,
          timescale = "raw",
          include_third_party = TRUE) %>%
          distinct() %>%
          mutate(DT_mst = force_tz(datetime, tzone = "MST"),
                 flag = case_when(!is.na(flag_a) & !is.na(flag_b) ~ paste0(flag_a, ",", flag_b),
                                  is.na(flag_a) & !is.na(flag_b) ~ flag_b,
                                  is.na(flag_b) & !is.na(flag_b) ~ flag_a,
                                  TRUE ~ NA_character_),
                 source = "DWR") %>%
          dplyr::select(site = abbrev, DT_mst, q_cfs = meas_value, flag, source)
      }
      all_q <- bind_rows(all_q, q_data)
    }

  
      final_q <- all_q %>%
        mutate(DT_round = round_date(x = DT_mst, unit = timestep)) %>%
        group_by(site, DT_round) %>%
        summarise(q_cfs = mean(q_cfs, na.rm = TRUE)) %>%
        filter(!is.na(q_cfs))%>%
        left_join(flow_sites, by = c("site" = "abbrev"))
   

    return(final_q)
  }
  final_q <- gather_q(flow_sites, start_date, end_date, timestep)
  
  
  trim_q <- final_q%>%
    filter(between(DT_round, start_dt, end_dt))
    
  
  # Subset the colors since there are only a few sites where flow is available
  colors_selected <- tibble(site = sites)%>%
    left_join(site_names, by = c("site" = "site"))
  colors_selected$natural_name <- factor(colors_selected$natural_name, levels = site_order )
  
  
    colors_selected <- colors_selected %>%
      mutate(color = color_scheme[1:length(sites)])%>%
    filter(site %in% flow_sites$site)
    
    
    color_scheme <- colors_selected$color
  
  trim_q$natural_name <- factor(trim_q$natural_name, levels = site_order )
      
    
  
    ggplot(trim_q, aes(x = DT_round, y = q_cfs, color = natural_name)) +
      geom_line(size = 1.5, show.legend = F) +
      scale_color_manual(values = color_scheme) +
      labs( x = "Date", y = "Flow (cfs)", color = "")+
      theme_few(base_size = b_size) +
      theme(axis.title.x = element_blank(), legend.position = "none", 
            legend.text = element_blank())
  

      }
      
      plot <- flow_plot(sites, start_dt, end_dt, timestep)
      
      return(plot)
    }
    
    
    plot_data <- all_data %>%
      filter(parameter == param_arg)
    
    label <- labels %>%
      filter(param == param_arg) %>%
      pull(label)
    
    plot_data$natural_name <- factor(plot_data$natural_name, levels = site_order )
    
    # if(param_arg == "Specific Conductivity"){
    #   b_size = b_size - 5
    #   
    #   plot <- ggplot(plot_data, aes(x = DT_round, y = value, color = site_name)) +
    #   geom_line(linewidth = 2, show.legend = F) +
    #   scale_color_manual(name = "Site", values = color_scheme) +
    #   labs(x = "Date", y = label, color = "Site") +
    #   theme_few(base_size = b_size) +
    #   labs(color = "Site") +
    #   theme(axis.title.x = element_blank(), legend.position = "none")
    # }
    
    plot <- ggplot(plot_data, aes(x = DT_round, y = mean, color = natural_name)) +
      geom_line(linewidth = 2) +
      scale_color_manual(name = "Site", values = color_scheme) +
      labs(x = "Date", y = label, color = "Site") +
      theme_few(base_size = b_size) +
      labs(color = "Site") +
      theme(axis.title.x = element_blank(), legend.position = "bottom")
    
    if (add_grabs) {
      grab_data <- tidy_correlated_df %>%
        filter(site %in% sites & grab_dt >= ymd_hm(start_dt) & grab_dt <= ymd_hm(end_dt))%>%
        left_join(site_names, by = c("site" = "site"))
      
      plot <- plot +
        geom_vline(data = grab_data, aes(xintercept = grab_dt, color = natural_name), linetype = "dashed", size = 1)
    }
    
    return(plot)
  }
  
  all_data <- all_data%>%
    mutate(DT_round = round_date(DT_round, unit = timestep))%>%
    group_by(DT_round, natural_name,site, parameter)%>%
    summarise(mean = mean(mean, na.rm = TRUE), .groups = "drop")


  all_plot <- map(parameters, create_plot)
  

  
  if(length(parameters) == 1){
    all_plot[[1]] <- all_plot[[1]] + theme(axis.title.x = element_text( size = b_size))
    
    plots <- wrap_plots(all_plot, ncol = 1) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom")
    
  }else if(length(parameters) == 2){
    all_plot[[1]] <- all_plot[[1]] + theme(axis.text.x = element_blank(), 
                                           legend.position = "none")
    all_plot[[2]] <- all_plot[[2]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
    
    return(plots)
  }else if(length(parameters) == 3){
    all_plot[[3]] <- all_plot[[3]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 1) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }else if(length(parameters) == 4){
    all_plot[[3]] <- all_plot[[3]] + theme(axis.title.x = element_text( size = b_size))
    all_plot[[4]] <- all_plot[[4]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 2) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }else if(length(parameters) == 5){
    all_plot[[5]] <- all_plot[[5]] + theme(axis.title.x = element_text( size = b_size))
    plots <- wrap_plots(all_plot, ncol = 2) + 
      plot_layout(guides = "collect") & 
      theme(legend.position = "bottom", legend.text = element_text(size = b_size))
  }
  
  
  return(plots)
}


bg_colors <- c( "#01377D", "#009DD1", "#97E7F5",
                "#7ED348", "#26B170", "#000000") 
bg_colors_full <- c( "#185BB4", "#009DD1", "#00F5DC", "#00F0C0",
                "#00D684", "#00BD48", "#00DB58","#0FFF6B" 
                , "#000000" ) 

colors <- c("#01377D","#009DD1", "#D55E00")



```

## PWQN Q2 meeting

### Date: `r format(Sys.Date(), "%B %d, %Y")`

## Spring Housing Updates

-   Bellvue: Removed bottom most bracket to allow for better flushing and less debris to be caught
-   ELC: Removed original housing (2018-2021)
-   Riverbluffs: Moved bottom most bracket up to allow for better flushing and less debris to be caught on end of housing

## Spring Field Updates

-   AT800s at most sites
    -   Added FDOM, Chlorophyll a (or turbidity)
    -   Improved reliability
-   Sensor swapping/bench calibration
    -   Reduces time in field and calibration supplies needed
    -   Still optimizing process and methods to check sensor validation pre/post calibration

## WQ Events: March

```{r april_drawdown, echo= F}


sites_march <- c( "udall", "cottonwood", "elc", "archery")


march_storm <-  plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_march,  parameters = c("Depth", "Specific Conductivity","Turbidity" ), start_dt = "2025-03-28  00:00",
                  end_dt = "2025-04-02 24:00",timestep =  "30 minutes", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


march_storm
ggsave("data/sharing/quarterly_meetings/2025_Q2/figs/march_storm.png", plot = march_storm, width = 16, height = 10, units = "in", dpi = 300)

```



## WQ Events: April Drawdown

```{r april_drawdown, echo= F}

sites_april <- c("salyer", "udall", "riverbend", "elc", "archery")


april <-  plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_april,  parameters = c("Depth", "Specific Conductivity","DO","Temperature" ), start_dt = "2025-04-13  00:00",
                  end_dt = "2025-04-17 24:00",timestep =  "30 minutes", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


april
ggsave("data/sharing/quarterly_meetings/2025_Q2/figs/april_drawdowns.png", plot = april, width = 16, height = 10, units = "in", dpi = 300)

```

## WQ Events:  May Storm

```{r, echo= F}


sites_may_storm <- c( "udall", "elc", "archery", "riverbluffs")


may_storm <-  plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_may_storm,  parameters = c("Depth", "DO" ,"Turbidity", "Temperature" ), start_dt = "2025-05-07  00:00",
                  end_dt = "2025-05-09 00:00",timestep =  "15 minutes", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


may_storm
ggsave("data/sharing/quarterly_meetings/2025_Q2/figs/may_storm.jpg", plot = may_storm, width = 16, height = 10, units = "in", dpi = 300)

```


## WQ Events: May DO shift

```{r, echo = F}


sites_may_1<- c( "bellvue", "salyer", "udall", "riverbend")


may_1 <-  plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_may_1,  parameters = c("Depth","DO","Temperature" ), start_dt = "2025-05-02  12:00",
                  end_dt = "2025-05-04 12:00",timestep =  "15 minute", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


may_1
ggsave("data/sharing/quarterly_meetings/2025_Q2/figs/may_do_shift.png", plot = may_1, width = 16, height = 10, units = "in", dpi = 300)

```


## WQ Events: May SC Diversion

```{r, echo = F}


sites_may_2<- c("bellvue", "riverbend", "elc", "archery", "riverbluffs")


may_2 <-  plot_sensor_grabs(df = sensor_data_simple_clean, sites = sites_may_2,  parameters = c("Depth", "Specific Conductivity","DO","Temperature" ), start_dt = "2025-05-01  00:00",
                  end_dt = "2025-05-15 24:00",timestep =  "2 hours", add_grabs = F, color_scheme = bg_colors,b_size = 20)+
  labs(caption = "Preliminary Data, subject to revision")


may_2

ggsave("data/sharing/quarterly_meetings/2025_Q2/figs/may_drawdowns.png", plot = may_2, width = 16, height = 10, units = "in", dpi = 300)

```


## WQ Summary




```{r}
# Define Y-axis limits for each parameter using tibble
y_limits <- tibble(
  parameter = c("Temperature", "pH", "DO", "Specific Conductivity"),
  y_min = c(0, 6, 4, 0),
  y_max = c(30, 10, 20, 2000)
)

```

### March & April

```{r}
#create boxplots for each site/parameter following site ordering

box_data <- sensor_data_simple_clean%>%
         filter(parameter != "Turbidity",
                parameter != "Depth", 
                parameter != "FDOM Fluorescence", 
                parameter != "Chl-a Fluorescence", 
                parameter != "ORP")%>%
         filter(site != "pbd", site != "springcreek")%>%
  filter(month(DT_round) %in% c(3,4))

# Merge with your data using left_join
box_data_with_limits <- box_data %>%
  left_join(y_limits, by = "parameter")

 box_data_with_limits$natural_name <- factor(box_data_with_limits$natural_name, levels = site_order )

april_box_plot <- box_data_with_limits %>%
  ggplot(aes(x = natural_name, y = mean, fill = natural_name)) +
  geom_boxplot() +
  facet_wrap(~label, scales = "free_y", strip.position = "left") +
  geom_blank(aes(y = y_min)) +  # Forces inclusion of minimum
  geom_blank(aes(y = y_max)) +  # Forces inclusion of maximum
  scale_fill_manual(values = bg_colors_full) +
  labs(x = "Site", y = "", 
       title = "Poudre Water Quality Network Data Summary: End of March and April 2025",
       caption = "Preliminary Data, subject to revision") +
  theme_bw(base_size = 20) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1), 
        strip.background = element_blank(),
        strip.placement = "outside")
  

april_box_plot
ggsave("data/sharing/quarterly_meetings/2025_Q2/figs/april_boxplots.png", plot = april_box_plot, width = 16, height = 10, units = "in", dpi = 300)

```

## May

```{r}


box_data <- sensor_data_simple_clean%>%
         filter(parameter != "Turbidity",
                parameter != "Depth", 
                parameter != "FDOM Fluorescence", 
                parameter != "Chl-a Fluorescence", 
                parameter != "ORP")%>%
         filter(site != "pbd", site != "springcreek")%>%
  filter(month(DT_round) == 5)



# Merge with your data using left_join
box_data_with_limits <- box_data %>%
  left_join(y_limits, by = "parameter")
 box_data_with_limits$natural_name <- factor(box_data_with_limits$natural_name, levels = site_order )

may_box_plot <- box_data_with_limits %>%
  ggplot(aes(x = natural_name, y = mean, fill = natural_name)) +
  geom_boxplot() +
  facet_wrap(~label, scales = "free_y", strip.position = "left") +
  geom_blank(aes(y = y_min)) +  # Forces inclusion of minimum
  geom_blank(aes(y = y_max)) +  # Forces inclusion of maximum
  scale_fill_manual(values = bg_colors_full) +
  labs(x = "Site", y = "", 
       title = "Poudre Water Quality Network Data Summary: May 2025",
       caption = "Preliminary Data, subject to revision") +
  theme_bw(base_size = 20) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1), 
        strip.background = element_blank(),
        strip.placement = "outside")

may_box_plot
ggsave("data/sharing/quarterly_meetings/2025_Q2/figs/may_boxplots.png", plot = may_box_plot, width = 16, height = 10, units = "in", dpi = 300)

```




